%!TeX root=../viewsbodytop.tex
\addchap{The Vindictive Story of the Footsteps that Ran}

\lettrine[lines=4]{M}{r} Bunter withdrew his head from beneath the focusing cloth.

\zz
»I fancy that will be quite adequate, sir,« he said deferentially, »unless there are any further patients, if I may call them so, which you would wish put on record.«

»Not to-day,« replied the doctor. He took the last stricken rat gently from the table, and replaced it in its cage with an air of satisfaction. »Perhaps on Wednesday, if Lord~Peter can kindly spare your services once again\longdash«

»What's that?« murmured his lordship, withdrawing his long nose from the investigation of a number of unattractive-looking glass jars. »Nice old dog,« he added vaguely. »Wags his tail when you mention his name, what? Are these monkey-glands, Hartman, or a south-west elevation of Cleopatra's duodenum?«

»You don't know anything, do you?« said the young physician, laughing. »No use playing your bally-fool-with-an-eyeglass tricks on me, Wimsey. I'm up to them. I was saying to Bunter that I'd be no end grateful if you'd let him turn up again three days hence to register the progress of the specimens—always supposing they do progress, that is.«

»Why ask, dear old thing?« said his lordship. »Always a pleasure to assist a fellow-sleuth, don't you know. Trackin' down murderers—all in the same way of business and all that. All finished? Good egg! By the way, if you don't have that cage mended you'll lose one of your patients—Number 5. The last wire but one is workin' loose—assisted by the intelligent occupant. Jolly little beasts, ain't they? No need of dentists—wish I was a rat—wire much better for the nerves than that fizzlin' drill.«

Dr~Hartman uttered a little exclamation.

»How in the world did you notice that, Wimsey? I didn't think you'd even looked at the cage.«

»Built noticin'—improved by practice,« said Lord~Peter quietly. »Anythin' wrong leaves a kind of impression on the eye; brain trots along afterwards with the warnin'. I saw that when we came in. Only just grasped it. Can't say my mind was glued on the matter. Shows the victim's improvin', anyhow. All serene, Bunter?«

»Everything perfectly satisfactory, I trust, my lord,« replied the manservant. He had packed up his camera and plates, and was quietly restoring order in the little laboratory, whose fittings—compact as those of an ocean liner—had been disarranged for the experiment.

»Well,« said the doctor, »I am enormously obliged to you, Lord~Peter, and to Bunter too. I am hoping for a great result from these experiments, and you cannot imagine how valuable an assistance it will be to me to have a really good series of photographs. I can't afford this sort of thing—yet,« he added, his rather haggard young face wistful as he looked at the great camera, »and I can't do the work at the hospital. There's no time; I've got to be here. A struggling \textsc{g.p.} can't afford to let his practice go, even in Bloomsbury. There are times when even a half-crown visit makes all the difference between making both ends meet and having an ugly hiatus.«

»As Mr~Micawber said,« replied Wimsey, »»Income twenty pounds, expenditure nineteen, nineteen, six—result: happiness; expenditure twenty pounds, ought, six—result: misery.« Don't prostrate yourself in gratitude, old bean; nothin' Bunter loves like messin' round with pyro and hyposulphite. Keeps his hand in. All kinds of practice welcome. Finger-prints and process plates spell seventh what-you-may-call-it of bliss, but focal-plane work on scurvy-ridden rodents (good phrase!) acceptable if no crime forthcoming. Crimes have been rather short lately. Been eatin' our heads off, haven't we, Bunter? Don't know what's come over London. I've taken to prying into my neighbour's affairs to keep from goin' stale. Frightened the postman into a fit the other day by askin' him how his young lady at Croydon was. He's a married man, livin' in Great Ormond Street.«

»How did you know?«

»Well, I didn't really. But he lives just opposite to a friend of mine—Inspector Parker; and his wife—not Parker's; he's unmarried; the postman's, I mean—asked Parker the other day whether the flyin' shows at Croydon went on all night. Parker, bein' flummoxed, said »No,« without thinkin'. Bit of a give-away, what? Thought I'd give the poor devil a word in season, don't you know. Uncommonly thoughtless of Parker.«

The doctor laughed. »You'll stay to lunch, won't you?« he said. »Only cold meat and salad, I'm afraid. My woman won't come Sundays. Have to answer my own door. Deuced unprofessional, I'm afraid, but it can't be helped.«

»Pleasure,« said Wimsey, as they emerged from the laboratory and entered the dark little flat by the back door. »Did you build this place on?«

»No,« said Hartman; »the last tenant did that. He was an artist. That's why I took the place. It comes in very useful, ramshackle as it is, though this glass roof is a bit sweltering on a hot day like this. Still, I had to have something on the ground-floor, cheap, and it'll do till times get better.«

»Till your vitamin experiments make you famous, eh?« said Peter cheerfully. »You're goin' to be the comin' man, you know. Feel it in my bones. Uncommonly neat little kitchen you've got, anyhow.«

»It does,« said the doctor. »The lab. makes it a bit gloomy, but the woman's only here in the daytime.«

He led the way into a narrow little dining-room, where the table was laid for a cold lunch. The one window at the end farthest from the kitchen looked out into Great James Street. The room was little more than a passage, and full of doors—the kitchen door, a door in the adjacent wall leading into the entrance-hall, and a third on the opposite side, through which his visitor caught a glimpse of a moderate-sized consulting-room.

Lord~Peter Wimsey and his host sat down to table, and the doctor expressed a hope that Mr~Bunter would sit down with them. That correct person, however, deprecated any such suggestion.

»If I might venture to indicate my own preference, sir,« he said, »it would be to wait upon you and his lordship in the usual manner.«

»It's no use,« said Wimsey. »Bunter likes me to know my place. Terrorisin' sort of man, Bunter. Can't call my soul my own. Carry on, Bunter; we wouldn't presume for the world.«

Mr~Bunter handed the salad, and poured out the water with a grave decency appropriate to a crusted old tawny port.

It was a Sunday afternoon in that halcyon summer of 1921. The sordid little street was almost empty. The ice-cream man alone seemed thriving and active. He leaned luxuriously on the green post at the corner, in the intervals of driving a busy trade. Bloomsbury's swarm of able-bodied and able-voiced infants was still presumably within-doors, eating steamy Sunday dinners inappropriate to the tropical weather. The only disturbing sounds came from the flat above, where heavy footsteps passed rapidly to and fro.

»Who's the merry-and-bright bloke above?« enquired Lord~Peter presently. »Not an early riser, I take it. Not that anybody is on a Sunday mornin'. Why an inscrutable Providence ever inflicted such a ghastly day on people livin' in town I can't imagine. I ought to be in the country, but I've got to meet a friend at Victoria this afternoon. Such a day to choose.... Who's the lady? Wife or accomplished friend? Gather she takes a properly submissive view of woman's duties in the home, either way. That's the bedroom overhead, I take it.«

Hartman looked at Lord~Peter in some surprise.

»'Scuse my beastly inquisitiveness, old thing,« said Wimsey. »Bad habit. Not my business.«

»How did you\longdash«

»Guesswork,« said Lord~Peter, with disarming frankness. »I heard the squawk of an iron bedstead on the ceiling and a heavy fellow get out with a bump, but it may quite well be a couch or something. Anyway, he's been potterin' about in his stocking feet over these few feet of floor for the last half-hour, while the woman has been clatterin' to and fro, in and out of the kitchen and away into the sittin'-room, with her high heels on, ever since we've been here. Hence deduction as to domestic habits of the first-floor tenants.«

»I thought,« said the doctor, with an aggrieved expression, »you'd been listening to my valuable exposition of the beneficial effects of Vitamin B, and Lind's treatment of scurvy with fresh lemons in 1755.«

»I was listenin'« agreed Lord~Peter hastily, »but I heard the footsteps as well. Fellow's toddled into the kitchen—only wanted the matches, though; he's gone off into the sittin'-room and left her to carry on the good work. What was I sayin'? Oh, yes! You see, as I was sayin' before, one hears a thing or sees it without knowin' or thinkin' about it. Then afterwards one starts meditatin', and it all comes back, and one sorts out one's impressions. Like those plates of Bunter's. Picture's all there, l—la—what's the word I want, Bunter?«

»Latent, my lord.«

»That's it. My right-hand man, Bunter; couldn't do a thing without him. The picture's latent till you put the developer on. Same with the brain. No mystery. Little grey books all my respected grandmother! Little grey matter's all you want to remember things with. As a matter of curiosity, was I right about those people above?«

»Perfectly. The man's a gas-company's inspector. A bit surly, but devoted (after his own fashion) to his wife. I mean, he doesn't mind hulking in bed on a Sunday morning and letting her do the chores, but he spends all the money he can spare on giving her pretty hats and fur coats and what not. They've only been married about six months. I was called in to her when she had a touch of 'flu in the spring, and he was almost off his head with anxiety. She's a lovely little woman, I must say—Italian. He picked her up in some eating-place in Soho, I believe. Glorious dark hair and eyes; Venus sort of figure; proper contours in all the right places; good skin—all that sort of thing. She was a bit of a draw to that restaurant while she was there, I fancy. Lively. She had an old admirer round here one day—awkward little Italian fellow, with a knife—active as a monkey. Might have been unpleasant, but I happened to be on the spot, and her husband came along. People are always laying one another out in these streets. Good for business, of course, but one gets tired of tying up broken heads and slits in the jugular. Still, I suppose the girl can't help being attractive, though I don't say she's what you might call stand-offish in her manner. She's sincerely fond of Brotherton, I think, though—that's his name.«

Wimsey nodded inattentively. »I suppose life is a bit monotonous here,« he said.

»Professionally, yes. Births and drunks and wife-beatings are pretty common. And all the usual ailments, of course. Just at present I'm living on infant diarrhœa chiefly—bound to, this hot weather, you know. With the autumn, 'flu and bronchitis set in. I may get an occasional pneumonia. Legs, of course, and varicose veins—God!« cried the doctor explosively, »if only I could get away, and do my experiments!«

»Ah!« said Peter, »where's that eccentric old millionaire with a mysterious disease, who always figures in the novels? A lightning diagnosis—a miraculous cure—»God bless you, doctor; here are five thousand pounds«—Harley Street\longdash«

»That sort doesn't live in Bloomsbury,« said the doctor.

»It must be fascinatin', diagnosin' things,« said Peter thoughtfully. »How d'you do it? I mean, is there a regular set of symptoms for each disease, like callin' a club to show you want your partner to go no trumps? You don't just say: »This fellow's got a pimple on his nose, therefore he has fatty degeneration of the heart\longdash««

»I hope not,« said the doctor drily.

»Or is it more like gettin' a clue to a crime?« went on Peter. »You see somethin'—a room, or a body, say, all knocked about anyhow, and there's a damn sight of symptoms of somethin' wrong, and you've got just to pick out the ones which tell the story?«

»That's more like it,« said Dr~Hartman. »Some symptoms are significant in themselves—like the condition of the gums in scurvy, let us say—others in conjunction with\longdash«

He broke off, and both sprang to their feet as a shrill scream sounded suddenly from the flat above, followed by a heavy thud. A man's voice cried out lamentably; feet ran violently to and fro; then, as the doctor and his guests stood frozen in consternation, came the man himself—falling down the stairs in his haste, hammering at Hartman's door.

»Help! Help! Let me in! My wife! He's murdered her!«

They ran hastily to the door and let him in. He was a big, fair man, in his shirt-sleeves and stockings. His hair stood up, and his face was set in bewildered misery.

»She is dead—dead. He was her lover,« he groaned. »Come and look—take her away—Doctor! I have lost my wife! My Maddalena\longdash« He paused, looked wildly for a moment, and then said hoarsely, »Someone's been in—somehow—stabbed her—murdered her. I'll have the law on him, doctor. Come quickly—she was cooking the chicken for my dinner. Ah-h-h!«

He gave a long, hysterical shriek, which ended in a hiccupping laugh. The doctor took him roughly by the arm and shook him. »Pull yourself together, Mr~Brotherton,« he said sharply. »Perhaps she is only hurt. Stand out of the way!«

»Only hurt?« said the man, sitting heavily down on the nearest chair. »No—no—she is dead—little Maddalena—Oh, my God!«

Dr~Hartman snatched a roll of bandages and a few surgical appliances from the consulting-room, and he ran upstairs, followed closely by Lord~Peter. Bunter remained for a few moments to combat hysterics with cold water. Then he stepped across to the dining-room window and shouted.

»Well, wot is it?« cried a voice from the street.

»Would you be so kind as to step in here a minute, officer?« said Mr~Bunter. »There's been murder done.«

When Brotherton and Bunter arrived upstairs with the constable, they found Dr~Hartman and Lord~Peter in the little kitchen. The doctor was kneeling beside the woman's body. At their entrance he looked up, and shook his head.

»Death instantaneous,« he said. »Clean through the heart. Poor child. She cannot have suffered at all. Oh, constable, it is very fortunate you are here. Murder appears to have been done—though I'm afraid the man has escaped. Probably Mr~Brotherton can give us some help. He was in the flat at the time.«

The man had sunk down on a chair, and was gazing at the body with a face from which all meaning seemed to have been struck out. The policeman produced a notebook.

»Now, sir,« he said, »don't let's waste any time. Sooner we can get to work the more likely we are to catch our man. Now, you was 'ere at the time, was you?«

Brotherton stared a moment, then, making a violent effort, he answered steadily:

»I was in the sitting-room, smoking and reading the paper. My—\textit{she}—was getting the dinner ready in here. I heard her give a scream, and I rushed in and found her lying on the floor. She didn't have time to say anything. When I found she was dead, I rushed to the window, and saw the fellow scrambling away over the glass roof there. I yelled at him, but he disappeared. Then I ran down\longdash«

»'Arf a mo',« said the policeman. »Now, see 'ere, sir, didn't you think to go after 'im at once?«

»My first thought was for her,« said the man. »I thought maybe she wasn't dead. I tried to bring her round\longdash« His speech ended in a groan.

»You say he came in through the window,« said the policeman.

»I beg your pardon, officer,« interrupted Lord~Peter, who had been apparently making a mental inventory of the contents of the kitchen. »Mr~Brotherton suggested that the man went \textit{out} through the window. It's better to be accurate.«

»It's the same thing,« said the doctor. »It's the only way he could have come in. These flats are all alike. The staircase door leads into the sitting-room, and Mr~Brotherton was there, so the man couldn't have come that way.«

»And,« said Peter, »he didn't get in through the bedroom window, or we should have seen him. We were in the room below. Unless, indeed, he let himself down from the roof. Was the door between the bedroom and the sitting-room open?« he asked suddenly, turning to Brotherton.

The man hesitated a moment. »Yes,« he said finally. »Yes, I'm sure it was.«

»Could you have seen the man if he had come through the bedroom window?«

»I couldn't have helped seeing him.«

»Come, come, sir,« said the policeman, with some irritation, »better let \textit{me} ask the questions. Stands to reason the fellow wouldn't get in through the bedroom window in full view of the street.«

»How clever of you to think of that,« said Wimsey. »Of course not. Never occurred to me. Then it must have been this window, as you say.«

»And, what's more, here's his marks on the window-sill,« said the constable triumphantly, pointing to some blurred traces among the London soot. »That's right. Down he goes by that drain-pipe, over the glass roof down there—what's that the roof of?«

»My laboratory,« said the doctor. »Heavens! to think that while we were there at dinner this murdering villain\longdash«

»Quite so, sir,« agreed the constable. »Well, he'd get away over the wall into the court be'ind. 'E'll 'ave been seen there, no fear; you needn't anticipate much trouble in layin' 'ands on 'im, sir. I'll go round there in 'arf a tick. Now then, sir«—turning to Brotherton—»'ave you any idea wot this party might have looked like?«

Brotherton lifted a wild face, and the doctor interposed.

»I think you ought to know, constable,« he said, »that there was—well, not a murderous attack, but what might have been one, made on this woman before—about eight weeks ago—by a man named Marincetti—an Italian waiter—with a knife.«

»Ah!« The policeman licked his pencil eagerly. »Do you know this party as 'as been mentioned?« he enquired of Brotherton.

»That's the man,« said Brotherton, with concentrated fury. »Coming here after my wife—God curse him! I wish to God I had him dead here beside her!«

»Quite so,« said the policeman. »Now, sir«—to the doctor—»'ave you got the weapon wot the crime was committed with?«

»No,« said Hartman, »there was no weapon in the body when I arrived.«

»Did \textit{you} take it out?« pursued the constable, to Brotherton.

»No,« said Brotherton, »he took it with him.«

»Took it with 'im,« the constable entered the fact in his notes. »Phew! Wonderful 'ot it is in 'ere, ain't it, sir?« he added, mopping his brow.

»It's the gas-oven, I think,« said Peter mildly. »Uncommon hot thing, a gas-oven, in the middle of July. D'you mind if I turn it out? There's the chicken inside, but I don't suppose you want\longdash«

Brotherton groaned, and the constable said: »Quite right, sir. A man wouldn't 'ardly fancy 'is dinner after a thing like this. Thank you, sir. Well now, doctor, wot kind of weapon do you take this to 'ave been?«

»It was a long, narrow weapon—something like an Italian stiletto, I imagine,« said the doctor, »about six inches long. It was thrust in with great force under the fifth rib, and I should say it had pierced the heart centrally. As you see, there has been practically no bleeding. Such a wound would cause instant death. Was she lying just as she is now when you first saw her, Mr~Brotherton?«

»On her back, just as she is,« replied the husband.

»Well, that seems clear enough,« said the policeman. »This 'ere Marinetti, or wotever 'is name is, 'as a grudge against the poor young lady\longdash«

»I believe he was an admirer,« put in the doctor.

»Quite so,« agreed the constable. »Of course, these foreigners are like that—even the decentest of 'em. Stabbin' and such-like seems to come nateral to them, as you might say. Well, this 'ere Marinetti climbs in 'ere, sees the poor young lady standin' 'ere by the table all alone, gettin' the dinner ready; 'e comes in be'ind, catches 'er round the waist, stabs 'er—easy job, you see; no corsets nor nothink—she shrieks out, 'e pulls 'is stiletty out of 'er an' makes tracks. Well, now we've got to find 'im, and by your leave, sir, I'll be gettin' along. We'll 'ave 'im by the 'eels before long, sir, don't you worry. I'll 'ave to put a man in charge 'ere, sir, to keep folks out, but that needn't worry you. Good mornin', gentlemen.«

»May we move the poor girl now?« asked the doctor.

»Certainly. Like me to 'elp you, sir?«

»No. Don't lose any time. We can manage.« Dr~Hartman turned to Peter as the constable clattered downstairs. »Will you help me, Lord~Peter?«

»Bunter's better at that sort of thing,« said Wimsey, with a hard mouth.

The doctor looked at him in some surprise, but said nothing, and he and Bunter carried the still form away. Brotherton did not follow them. He sat in a grief-stricken heap, with his head buried in his hands. Lord~Peter walked about the little kitchen, turning over the various knives and kitchen utensils, peering into the sink bucket, and apparently taking an inventory of the bread, butter, condiments, vegetables, and so forth which lay about in preparation for the Sunday meal. There were potatoes in the sink, half peeled, a pathetic witness to the quiet domestic life which had been so horribly interrupted. The colander was filled with green peas. Lord~Peter turned these things over with an inquisitive finger, gazed into the smooth surface of a bowl of dripping as though it were a divining-crystal, ran his hands several times right through a bowl of flour—then drew his pipe from his pocket and filled it slowly.

The doctor returned, and put his hand on Brotherton's shoulder.

»Come,« he said gently, »we have laid her in the other bedroom. She looks very peaceful. You must remember that, except for that moment of terror when she saw the knife, she suffered nothing. It is terrible for you, but you must try not to give way. The police\longdash«

»The police can't bring her back to life,« said the man savagely. »She's dead. Leave me alone, curse you! Leave me alone, I say!«

He stood up, with a violent gesture.

»You must not sit here,« said Hartman firmly. »I will give you something to take, and you must try to keep calm. Then we will leave you, but if you don't control yourself\longdash«

After some further persuasion, Brotherton allowed himself to be led away.

»Bunter,« said Lord~Peter, as the kitchen door closed behind them, »do you know why I am doubtful about the success of those rat experiments?«

»Meaning Mr~Hartman's, my lord?«

»Yes. Dr~Hartman has a theory. In any investigations, my Bunter, it is most damnably dangerous to have a theory.«

»I have heard you say so, my lord.«

»Confound you—you know it as well as I do! What is wrong with the doctor's theories, Bunter?«

»You wish me to reply, my lord, that he only sees the facts which fit in with the theory.«

»Thought-reader!« exclaimed Lord~Peter bitterly.

»And that he supplies them to the police, my lord.«

»Hush!« said Peter, as the doctor returned.

»I have got him to lie down,« said Dr~Hartman, »and I think the best thing we can do is to leave him to himself.«

»D'you know,« said Wimsey, »I don't cotton to that idea, somehow.«

»Why? Do you think he's likely to destroy himself?«

»That's as good a reason to give as any other, I suppose,« said Wimsey, »when you haven't got any reason which can be put into words. But my advice is, don't leave him for a moment.«

»But why? Frequently, with a deep grief like this, the presence of other people is merely an irritant. He begged me to leave him.«

»Then for God's sake go back to him,« said Peter.

»Really, Lord~Peter,« said the doctor, »I think I ought to know what is best for my patient.«

»Doctor,« said Wimsey, »this is not a question of your patient. A crime has been committed.«

»But there is no mystery.«

»There are twenty mysteries. For one thing, when was the window-cleaner here last?«

»The window-cleaner?«

»Who shall fathom the ebony-black enigma of the window-cleaner?« pursued Peter lightly, putting a match to his pipe. »You are quietly in your bath, in a state of more or less innocent nature, when an intrusive head appears at the window, like the ghost of Hamilton Tighe, and a gruff voice, suspended between earth and heaven, says »Good morning, sir.« Where do window-cleaners go between visits? Do they hibernate, like busy bees? Do they\longdash?«

»Really, Lord~Peter,« said the doctor, »don't you think you're going a bit beyond the limit?«

»Sorry you feel like that,« said Peter, »but I really want to know about the window-cleaner. Look how clear these panes are.«

»He came yesterday, if you want to know,« said Dr~Hartman, rather stiffly.

»You are sure?«

»He did mine at the same time.«

»I thought as much,« said Lord~Peter. `In the words of the song:

\begin{verse}
I thought as much,\\
It was a little—window-cleaner,'
\end{verse}

»In that case,« he added, »it is absolutely imperative that Brotherton should not be left alone for a moment. Bunter! Confound it all, where's that fellow got to?«

The door into the bedroom opened.

»My lord?« Mr~Bunter unobtrusively appeared, as he had unobtrusively stolen out to keep an unobtrusive eye upon the patient.

»Good,« said Wimsey. »Stay where you are.« His lackadaisical manner had gone, and he looked at the doctor as four years previously he might have looked at a refractory subaltern.

»Dr~Hartman,« he said, »something is wrong. Cast your mind back. We were talking about symptoms. Then came the scream. Then came the sound of feet running. \textit{Which direction did they run in?}«

»I'm sure I don't know.«

»Don't you? Symptomatic, though, doctor. They have been troubling me all the time, subconsciously. Now I know why. They ran \textit{from the kitchen}.«

»Well?«

»Well! And now the window-cleaner\longdash«

»What about him?«

»Could you swear that it wasn't the window-cleaner who made those marks on the sill?«

»And the man Brotherton saw—?«

»Have we examined your laboratory roof for his footsteps?«

»But the weapon? Wimsey, this is madness! Someone took the weapon.«

»I know. But did you think the edge of the wound was clean enough to have been made by a smooth stiletto? It looked ragged to me.«

»Wimsey, what are you driving at?«

»There's a clue here in the flat—and I'm damned if I can remember it. I've seen it—I know I've seen it. It'll come to me presently. Meanwhile, don't let Brotherton\longdash«

»What?«

»Do whatever it is he's going to do.«

»But what is it?«

»If I could tell you that I could show you the clue. Why couldn't he make up his mind whether the bedroom door was open or shut? Very good story, but not quite thought out. Anyhow—I say, doctor, make some excuse, and strip him, and bring me his clothes. And send Bunter to me.«

The doctor stared at him, puzzled. Then he made a gesture of acquiescence and passed into the bedroom. Lord~Peter followed him, casting a ruminating glance at Brotherton as he went. Once in the sitting-room, Lord~Peter sat down on a red velvet arm-chair, fixed his eyes on a gilt-framed oleograph, and became wrapped in contemplation.

Presently Bunter came in, with his arms full of clothing. Wimsey took it, and began to search it, methodically enough, but listlessly. Suddenly he dropped the garments, and turned to the manservant.

»No,« he said, »this is a precaution, Bunter mine, but I'm on the wrong track. It wasn't here I saw—whatever I did see. It was in the kitchen. Now, what was it?«

»I could not say, my lord, but I entertain a conviction that I was also, in a manner of speaking, conscious—not consciously conscious, my lord, if you understand me, but still conscious of an incongruity.«

»Hurray!« said Wimsey suddenly. »Cheer-oh! for the sub-conscious what's-his-name! Now let's remember the kitchen. I cleared out of it because I was gettin' obfuscated. Now then. Begin at the door. Fryin'-pans and saucepans on the wall. Gas-stove—oven goin'—chicken inside. Rack of wooden spoons on the wall, gas-lighter, pan-lifter. Stop me when I'm gettin' hot. Mantelpiece. Spice-boxes and stuff. Anything wrong with them? No. Dresser. Plates. Knives and forks—all clean; flour dredger—milk-jug—sieve on the wall—nutmeg-grater. Three-tier steamer. Looked inside—no grisly secrets in the steamer.«

»Did you look in all the dresser drawers, my lord?«

»No. That could be done. But the point is, I \textit{did} notice somethin'. What did I notice? That's the point. Never mind. On with the dance—let joy be unconfined! Knife-board. Knife-powder. Kitchen table. Did you speak?«

»No,« said Bunter, who had moved from his attitude of wooden deference.

»Table stirs a chord. Very good. On table. Choppin'-board. Remains of ham and herb stuffin'. Packet of suet. Another sieve. Several plates. Butter in a glass dish. Bowl of drippin'\longdash«

»Ah!«

»Drippin'—! Yes, there was\longdash«

»Something unsatisfactory, my lord\longdash«

»About the drippin'! Oh, my head! What's that they say in \textit{Dear Brutus}, Bunter? »Hold on to the workbox.« That's right. Hold on to the drippin'. Beastly slimy stuff to hold on to—Wait!«

There was a pause.

»When I was a kid,« said Wimsey, »I used to love to go down into the kitchen and talk to old cookie. Good old soul she was, too. I can see her now, gettin' chicken ready, with me danglin' my legs on the table. \textit{She} used to pluck an' draw 'em herself. I revelled in it. Little beasts boys are, ain't they, Bunter? Pluck it, draw it, wash it, stuff it, tuck its little tail through its little what-you-may-call-it, truss it, grease the dish—Bunter?«

»My lord!«

»Hold on to the dripping!«

»The bowl, my lord\longdash«

»The bowl—visualise it—what was wrong!«

»It was full, my lord!«

»Got it—got it—\textit{got} it! The bowl was full—smooth surface. Golly! I knew there was something queer about it. Now why shouldn't it be full? Hold on to the\longdash«

»The bird was in the oven.«

»Without dripping!«

»Very careless cookery, my lord.«

»The bird—in the oven—no dripping, Bunter! Suppose it was never put in till after she was dead? Thrust in hurriedly by someone who had something to hide—horrible!«

»But with what object, my lord?«

»Yes, why? That's the point. One more mental association with the bird. It's just coming. Wait a moment. Pluck, draw, wash, stuff, tuck up, truss—By God!«

»My lord?«

»Come on, Bunter. Thank Heaven we turned off the gas!«

He dashed through the bedroom, disregarding the doctor and the patient, who sat up with a smothered shriek. He flung open the oven door and snatched out the baking-tin. The skin of the bird had just begun to discolour. With a little gasp of triumph, Wimsey caught the iron ring that protruded from the wing, and jerked out—the six-inch spiral skewer.

The doctor was struggling with the excited Brotherton in the doorway. Wimsey caught the man as he broke away, and shook him into the corner with a jiu-jitsu twist.

»Here is the weapon,« he said.

»Prove it, blast you!« said Brotherton savagely.

»I will,« said Wimsey. »Bunter, call in the policeman whom you will find at the door. Doctor, we shall need your microscope.«

In the laboratory the doctor bent over the microscope. A thin layer of blood from the skewer had been spread upon the slide.

»Well?« said Wimsey impatiently.

»It's all right,« said Hartman. »The roasting didn't get anywhere near the middle. My God, Wimsey, yes, you're right—round corpuscles, diameter 1/3621—mammalian blood—probably human—«

»Her blood,« said Wimsey.

»It was very clever, Bunter,« said Lord~Peter, as the taxi trundled along on the way to his flat in Piccadilly. »If that fowl had gone on roasting a bit longer the blood-corpuscles might easily have been destroyed beyond all hope of recognition. It all goes to show that the unpremeditated crime is usually the safest.«

»And what does your lordship take the man's motive to have been?«

»In my youth,« said Wimsey meditatively, »they used to make me read the Bible. Trouble was, the only books I ever took to naturally were the ones they weren't over and above keen on. But I got to know the Song of Songs pretty well by heart. Look it up, Bunter; at your age it won't hurt you; it talks sense about jealousy.«

»I have perused the work in question, your lordship,« replied Mr~Bunter, with a sallow blush. »It says, if I remember rightly: »\textit{Jealousy is cruel as the grave}«.«