%!TeX root=../cloudstop.tex

\chapter{The Alibi}

\epigraph{When actually in the embrace of a voracious and powerful wild animal, the desirability of leaving a limb is not a matter to be subjected to
lengthy consideration.}{\textit{The Wallet Of Kai-Lung}}

\lettrine[lines=4,ante=`]{I}{} tripped right into it,' said Wimsey's voice steadily, out of the blackness. »One sinks very fast. You'd better not come near, or you'll go too. We'll yell a bit. I don't think we can be very far from Grider's Hole.«

\zz
»If your lordship will keep shouting,« returned Mr Bunter, »I think—I can—get to you,« he panted, untying with his teeth the hard knot of a coil of string.

»Oy!« cried Lord Peter obediently. »Help! Oy! Oy!«

Mr Bunter groped towards the voice, feeling cautiously before him with his walking-stick.

»Wish you'd keep away, Bunter,« said Lord Peter peevishly. »Where's the sense of both of us—?« He squelched and floundered again.

»Don't do that, my lord,« cried the man entreatingly. »You'll sink farther in.«

»I'm up to my thighs now,« said Lord Peter.

»I'm coming,« said Bunter. »Go on shouting. Ah, here's where it gets soggy.«

He felt the ground carefully, selected a tussocky bit which seemed reasonably firm, and drove his stick well into it.

»Oy! Hi! Help!« said Lord Peter, shouting lustily.

Mr Bunter tied one end of the string to the walking-stick, belted his Burberry tightly about him, and, laying himself cautiously down upon his belly, advanced, clue in hand, like a very Gothic Theseus of a late and degenerate school.

The bog heaved horribly as he crawled over it, and slimy water squelched up into his face. He felt with his hands for tussocks of grass, and got support from them when he could.

»Call out again, my lord!«

»Here!« The voice was fainter and came from the right. Bunter had lost his line a little, hunting for tussocks. »I daren't come faster,« he explained. He felt as though he had been crawling for years.

»Get out while there's time,« said Peter. »I'm up to my waist. Lord!  this is rather a beastly way to peg out.«

»You won't peg out,« grunted Bunter. His voice was suddenly quite close. »Your hands now.«

For a few agonizing minutes two pairs of hands groped over the invisible slime. Then:

»Keep yours still,« said Bunter. He made a slow, circling movement. It was hard work keeping his face out of the mud. His hands slithered over the slobbery surface—and suddenly closed on an arm.

»Thank God!« said Bunter. »Hang on here, my lord.«

He felt forward. The arms were perilously close to the sucking mud. The hands crawled clingingly up his arms and rested on his shoulders. He grasped Wimsey beneath the armpits and heaved. The exertion drove his own knees deep into the bog. He straightened himself hurriedly. Without using his knees he could get no purchase, but to use them meant certain death. They could only hang on desperately till help came—or till the strain became too great. He could not even shout, it was almost more than he could do to keep his mouth free of water. The dragging strain on his shoulders was intolerable; the mere effort to breathe meant an agonizing crick in the neck.

»You must go on shouting, my lord.«

Wimsey shouted. His voice was breaking and fading.

»Bunter, old thing,« said Lord Peter, »I'm simply beastly sorry to have let you in for this.«

»Don't mention it, my lord,« said Bunter, with his mouth in the slime.  A thought struck him.

»What became of your stick, my lord?«

»I dropped it. It should be somewhere near, if it hasn't sunk in.«

Bunter cautiously released his left hand and felt about.

»Hi! Hi! Help!«

Bunter's hand closed over the stick, which, by a happy accident, had fallen across a stable tuft of grass. He pulled it over to him, and laid it across his arms, so that he could just rest his chin upon it.  The relief to his neck was momentarily so enormous that his courage was renewed. He felt he could hang on for ever.

»Help!« 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

Minutes passed like hours. 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

»See that?«

A faint, flickering gleam somewhere away to the right. With desperate energy both shouted together.

»Help! Help! Oy! Oy! Help!«

An answering yell. The light swayed—came nearer—a spreading blur in the fog.

»We \textit{must} keep it up,« panted Wimsey. They yelled again.

»Where be?«

»Here!«

»Hello!« A pause. Then:

»Here be stick,« said a voice, suddenly near.

»Follow the string!« yelled Bunter. They heard two voices, apparently arguing. Then the string was twitched.

»Here! Here! Two of us! Make haste!«

More consultation.

»Hang on, canst a?«

»Yes, if you're quick.«

»Fetchin' hurdle. Two on `ee, sayst a?«

»Yes.«

»Deep in?«

»One of us.«

»Aw reet. Jem's comin'.«

A splattering noise marked the arrival of Jem with a hurdle. Then came an endless wait. Then another hurdle, the string twitching, and the blur of the lantern bobbing violently about. Then a third hurdle was flung down, and the light came suddenly out of the mist. A hand caught Bunter by the ankle.

»Where's other?«

»Here—nearly up to his neck. Have you a rope?«

»Aye, sure. Jem! T'rope!«

The rope came snaking out of the fog. Bunter grasped it, and passed it round his master's body.

»Now—coom tha back and heave.«

Bunter crawled cautiously backwards upon the hurdle. All three set hands upon the rope. It was like trying to heave the earth out of her course.

»'Fraid I'm rooted to Australia,« panted Peter apologetically. Bunter sweated and sobbed.

»It's aw reet—he's coomin'!«

With slow heavings the rope began to come towards them. Their muscles cracked.

Suddenly, with a great \textit{plop!} the bog let go its hold. The three at the rope were hurled head over heels upon the hurdles. Something unrecognizable in slime lay flat, heaving helplessly. They dragged at him in a kind of frenzy, as though he might be snatched back from them again. The evil bog stench rose thickly round them. They crossed the first hurdle—the second—the third—and rose staggeringly to their feet on firm ground.

»What a beastly place,« said Lord Peter faintly. »'Pologise, stupid of me to have forgotten—what'sy name?«

»Well, tha's loocky,« said one of their rescuers. »We thowt we heerd someun a-shouting. There be few folks as cooms oot o' Peter's Pot dead or alive, I reckon.«

»Well, it was nearly potted Peter that time,« said his lordship, and fainted. 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

To Lord Peter the memory of his entry that night into the farmhouse at Grider's Hole always brought with it a sensation of nightmare.  The coils of fog rolled in with them as the door opened, and through them the firelight leapt steamily. A hanging lamp made a blur. The Medusa-head of Mrs Grimethorpe, terribly white against her black hair, peered over him. A hairy paw caught her by the shoulder and wrenched her aside.

»Shameless! A mon—ony mon—that's a' tha thinks on. Bide till tha's wanted. What's this?«

Voices—voices—ever so many fierce faces peering down all round.

»Peter's Pot? An' what were `ee a-wanting on t'moor this time night? No good. Nobbody but a fool or a thief `ud coom oop ere i' t'fog.«

One of the men, a farm laborer with wry shoulders and a thin, malicious face, suddenly burst into tuneless song: 

\begin{verse}
\begin{altverse}
I been a-courtin' Mary Jane\\
On Ilkla' Moor bar t'at.\\
\end{altverse}
\end{verse}

 »Howd toong!« yelled Grimethorpe, in a fury. »Doost want Ah should break ivery bwoan i' thi body?« He turned on Bunter. »Tak thesen off, Ah tell tha. Tha'rt here for no good.«

»But, William\longdash« began his wife. He snapped round at her like a dog, and she shrank back.

»Naay now, naay now,« said a man, whom Wimsey dimly recognized as the fellow who had befriended him on his previous visit, »tha mun' taak them in for t' night, racken, or there'll be trouble wi' t' folk down yonder at t' Lodge, lat aloan what police `ull saay. Ef t' fellow `m coom to do harm, `ee's doon it already—to `unself. Woan't do no more tonight—look at `un. Bring `un to fire, mon,« he added to Bunter, and then, turning to the farmer again, »'Tes tha'll be in Queer Street ef `e wor to goo an' die on us wi' noomony or rhoomaticks.«

This reasoning seemed partly to convince Grimethorpe. He made way, grumbling, and the two chilled and exhausted men were brought near the fire. Somebody brought two large, steaming tumblers of spirits.  Wimsey's brain seemed to clear, then swim again drowsily, drunkenly. 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

Presently he became aware that he was being carried upstairs and put to bed. A big, old-fashioned room, with a fire on the hearth and a huge, grim four-poster. Bunter was helping him out of soaked clothes; rubbing him. Another man appeared from time to time to help him. From below came the bellowing sound of Grimethorpe's voice, blasphemously uplifted. Then the harsh, brassy singing of the wry-shouldered man: 

\clearpage

\begin{verse}
\begin{altverse}
Then woorms will coom an' ate thee oop\\
On Ilkla' Moor bar t'at\dots\\
Then doocks will coom an' ate oop woorms\\
On Ilkla' Moor\dots\\
\end{altverse}
\end{verse}


Lord Peter rolled into bed.

»Bunter—where—you all right? Never said thank you—dunno what I'm doing—anywhere to sleep—what?«

He drifted away into oblivion. The old song came up mockingly, and wound its horrible fancies into his dreams: 

\begin{verse}
\begin{altverse}
Then we shall coom an' ate oop doocks\\
On Ilkla' Moor bar t'at\dots\\
An' that is how—{\small an' that is how—}{\footnotesize is how\dots}\\
\end{altverse}
\end{verse}

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

When Wimsey next opened his eyes a pale November sun was struggling in at the window. It seemed that the fog had fulfilled its mission and departed. For some time he lay, vaguely unaware of how he came to be where he was; then the outlines of recollection straightened themselves, the drifting outposts of dreams were called back, the burden of his preoccupation settled down as usual. He became aware of an extreme bodily lassitude, and of the dragging pain of wrenched shoulder muscles. Examining himself perfunctorily, he found a bruised and tender zone beneath the armpits and round his chest and back, where the rescuing rope had hauled at him. It was painful to move, so he lay back and closed his eyes once more.

Presently the door opened to admit Bunter, neatly clothed and bearing a tray from which rose a most excellent odour of ham and eggs.

»Hullo, Bunter!«

»Good morning, my lord! I trust your lordship has rested.«

»Feel as fit as a fiddle, thanks—come to think of it, why fiddle?—except for a general feeling of havin' been violently massaged by some fellow with cast-iron fingers and knobbly joints. How about you?«

»The arms are a trifle fatigued, thank you, my lord; otherwise, I am happy to say, I feel no trace of the misadventure. Allow me, my lord.«

He set the tray tenderly upon Lord Peter's ready knees.

»They must be jolly well dragged out of their sockets,« said his lordship, »holdin' me up all that ghastly long time. I'm so beastly deep in debt to you already, Bunter, it's not a bit of use tryin' to repay it. You know I won't forget, anyhow, don't you? All right, I won't be embarrassin' or anything—thanks awfully, anyhow. That's that.  What? Did they give you anywhere decent to sleep? I didn't seem to be able to sit up an' take notice last night.«

»I slept excellently, I thank your lordship.« Mr Bunter indicated a kind of truckle-bed in a corner of the room. »They would have given me another room, my lord, but in the circumstances, I preferred to remain with your lordship, trusting you would excuse the liberty. I told them that I feared the effects of prolonged immersion upon your lordship's health. I was uneasy, besides, about the intention of Grimethorpe. I feared he might not feel altogether hospitably disposed, and that he might be led into some hasty action if we were not together.«

»I shouldn't wonder. Most murderous-lookin' fellow I ever set eyes on.  I'll have to talk to him this morning—or to Mrs Grimethorpe. I'd take my oath she could tell us something, what?«

»I should say there was very little doubt of it, my lord.«

»Trouble is,« pursued Wimsey, with his mouth full of egg, »I don't know how to get at her. That jolly husband of hers seems to cherish the most unpleasant suspicions of anything that comes this way in trousers. If he found out we'd been talkin' to her, what you may call privately, he might, as you say, be hurried by his feelin's into doin' something regrettable.«

»Just so, my lord.«

»Still, the fellow must go an' look after his bally old farm some time, and then, p'raps, we'll be able to tackle her. Queer sort of woman—damn fine one, what? Wonder what she made of Cathcart?« he added musingly.

Mr Bunter volunteered no opinion on this delicate point.

»Well, Bunter, I think I'll get up. I don't suppose we're altogether welcome here. I didn't fancy the look in our host's eye last night.«

»No, my lord. He made a deal of opposition about having your lordship conveyed to this room.«

»Why, whose room is it?«

»His own and Mrs Grimethorpe's, my lord. It appeared most suitable, there being a fireplace, and the bed already made up. Mrs Grimethorpe showed great kindness, my lord, and the man Jake pointed out to Grimethorpe that it would doubtless be to his pecuniary advantage to treat your lordship with consideration.«

»H'm. Nice, graspin' character, ain't he? Well, it's up and away for me. O Lord! I \textit{am} stiff. I say, Bunter, have I any clothes to put on?«

»I have dried and brushed your lordship's suit to the best of my ability, my lord. It is not as I should wish to see it, but I think your lordship will be able to wear it to Riddlesdale.«

»Well, I don't suppose the streets will be precisely crowded,« retorted his lordship. »I \textit{do} so want a hot bath. How about shavin' water?«

»I can procure that from the kitchen, my lord.«

Bunter padded away, and Lord Peter, having pulled on a shirt and trousers with many grunts and groans, roamed over to the window. As usual with hardy country dwellers, it was tightly shut, and a thick wedge of paper had been rammed in to keep the sash from rattling. He removed this and flung up the sash. The wind rollicked in, laden with peaty moor scents. He drank it in gladly. It was good to see the jolly old sun after all—he would have hated to die a sticky death in Peter's Pot. For a few minutes he stood there, returning thanks vaguely in his mind for the benefits of existence. Then he withdrew to finish dressing. The wad of paper was still in his hand, and he was about to fling it into the fire, when a word caught his eye. He unrolled the paper. As he read it his eyebrows went up and his mouth pursed itself into an indescribable expression of whimsical enlightenment. Bunter, returning with the hot water, found his master transfixed, the paper in one hand, and his socks in the other, and whistling a complicated passage of Bach under his breath.

»Bunter,« said his lordship, »I am, without exception, the biggest ass in Christendom. When a thing is close under my nose I can't see it. I get a telescope, and look for the explanation in Stapley. I deserve to be crucified upside-down, as a cure for anæmia of the brain. Jerry!  Jerry! But, naturally, of course, you rotten ass, isn't it obvious?  Silly old blighter. Why couldn't he tell Murbles or me?«

Mr Bunter advanced, the picture of respectful inquiry.

»Look at it—look at it!« said Wimsey, with a hysterical squeak of laughter. »O Lord! O Lord! Stuck into the window-frame for anybody to find. \textit{Just} like Jerry. Signs his name to the business in letters a foot long, leaves it conspicuously about, and then goes away and is chivalrously silent.«

Mr Bunter put the jug down upon the washstand in case of accident, and took the paper.

It was the missing letter from Tommy Freeborn.

No doubt about it. There it was—the evidence which established the truth of Denver's evidence. More—which established his alibi for the night of the 13\textsuperscript{th}.

Not Cathcart—Denver.

Denver suggesting that the shooting party should return in October to Riddlesdale, where they had opened the grouse season in August.  Denver sneaking hurriedly out at 11:30 to walk two miles across the fields on a night when Farmer Grimethorpe had gone to buy machinery.  Denver carelessly plugging a rattling sash on a stormy night with an important letter bearing his title on it for all to see. Denver padding back at three in the morning like a homing tom-cat, to fall over his guest's dead body by the conservatory. Denver, with his kind, stupid, English-gentleman ideas about honour, going obstinately off to prison, rather than tell his solicitor where he had been. Denver misleading them all into the wildest and most ingenious solutions of a mystery which now stood out clear as seven sunbeams. Denver, whose voice the woman had thought she recognized on the memorable day when she flung herself into the arms of his brother. Denver calmly setting in motion the enormous, creaking machinery of a trial by his noble peers in order to safeguard a woman's reputation.

This very day, probably, a Select Committee of lords was sitting »to inspect the Journals of this House upon former trials of peers in criminal cases, in order to bring the Duke of Denver to a speedy trial, and to report to the House what they should think proper thereupon.« There they were: moving that an address be presented to His Majesty by the lords with white staves, to acquaint His Majesty of the date proposed for the trial; arranging for fitting up the Royal Gallery at Westminster; humbly requesting the attendance of a sufficient police force to keep clear the approaches leading to the House; petitioning His Majesty graciously to appoint a Lord High Steward; ordering, in sheeplike accordance with precedent, that all lords be summoned to attend in their robes; that every lord, in giving judgment, disclose his opinion upon his honour, laying his right hand upon his heart; that the Sergeant-at-Arms be within the House to make proclamations in the King's name for keeping silence—and so on, and on, unendingly.  And there, jammed in the window-sash, was the dirty little bit of paper which, discovered earlier, would have made the whole monstrous ceremonial unnecessary.

Wimsey's adventure in the bog had unsettled his nerves. He sat down on the bed and laughed, with the tears streaming down his face.

Mr Bunter was speechless. Speechlessly he produced a razor—and to the end of his days Wimsey never knew how or from whom he had so adequately procured it—and began to strop it thoughtfully upon the palm of his hand.

Presently Wimsey pulled himself together and staggered to the window for a little cooling draught of moor air. As he did so, a loud hullabaloo smote his ear, and he perceived, in the courtyard below, Farmer Grimethorpe striding among his dogs; when they howled he struck at them with a whip, and they howled again. Suddenly he glanced up at the window, with an expression of such livid hatred that Wimsey stepped hurriedly back as though struck.

While Bunter shaved him he was silent. 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

The interview before Lord Peter was a delicate one; the situation, however one looked at it, unpleasant. He was under a considerable debt of gratitude to his hostess; on the other hand, Denver's position was such that minor considerations really had to go to the wall. His lordship had, nevertheless, never felt quite such a cad as he did while descending the staircase at Grider's Hole.

In the big farm kitchen he found a stout country-woman, stirring a pot of stew. He asked for Mr Grimethorpe, and was told that he had gone out.

»Can I speak to Mrs Grimethorpe, please?«

The woman looked doubtfully at him, wiped her hands on her apron, and, going into the scullery, shouted, »Mrs Grimethorpe!« A voice replied from somewhere outside.

»Gentleman wants see tha.«

»Where is Mrs Grimethorpe?« broke in Peter hurriedly.

»I' t'dairy, recken.«

»I'll go to her there,« said Wimsey, stepping briskly out. He passed through a stone-paved scullery, and across a yard, in time to see Mrs Grimethorpe emerging from a dark doorway opposite.

Framed there, the cold sunlight just lighting upon her still, dead-white face and heavy, dark hair, she was more wonderful than ever.  There was no trace of Yorkshire descent in the long, dark eyes and curled mouth. The curve of nose and cheekbones vouched for an origin immensely remote; coming out of the darkness, she might have just risen from her far tomb in the Pyramids, dropping the dry and perfumed grave-bands from her fingers.

Lord Peter pulled himself together.

»Foreign,« he said to himself matter-of-factly. »Touch of Jew perhaps, or Spanish, is it? Remarkable type. Don't blame Jerry. Couldn't live with Helen myself. Now for it.«

He advanced quickly.

»Good morning,« she said, »are you better?«

»Perfectly all right, thank you—thanks to your kindness, which I do not know how to repay.«

»You will repay any kindness best by going at once,« she answered in her remote voice. »My husband does not care for strangers, and `twas unfortunate the way you met before.«

»I will go directly. But I must first beg for the favour of a word with you.« He peered past her into the dimness of the dairy. »In here, perhaps?«

»What do you want with me?«

She stepped back, however, and allowed him to follow her in.

»Mrs Grimethorpe, I am placed in a most painful position. You know that my brother, the Duke of Denver, is in prison, awaiting his trial for a murder which took place on the night of October 13\textsuperscript{th}?«

Her face did not change. »I have heard so.«

»He has, in the most decided manner, refused to state where he was between eleven and three on that night. His refusal has brought him into great danger of his life.«

She looked at him steadily.

»He feels bound in honour not to disclose his whereabouts, though I know that, if he chose to speak, he could bring a witness to clear him.«

»He seems to be a very honourable man.« The cold voice wavered a trifle, then steadied again.

»Yes. Undoubtedly, from his point of view, he is doing the right thing. You will understand, however, that, as his brother, I am naturally anxious to have the matter put in its proper light.«

»I don't understand why you are telling me all this. I suppose, if the thing is disgraceful, he doesn't want it known.«

»Obviously. But to us—to his wife and young son, and to his sister and myself—his life and safety are matters of the first importance.«

»Of more importance than his honour?«

»The secret is a disgraceful one in a sense, and will give pain to his family. But it would be an infinitely greater disgrace that he should be executed for murder. The stigma in that case would involve all those who bear his name. The shame of the truth will, I fear, in this very unjust society of ours, rest more upon the witness to his alibi than upon himself.«

»Can you in that case expect the witness to come forward?«

»To prevent the condemnation of an innocent man? Yes, I think I may venture to expect even that.«

»I repeat—why are you telling me all this?«

»Because, Mrs Grimethorpe, you know, even better than I, how innocent my brother is of this murder. Believe me, I am deeply distressed at having to say these things to you.«

»I know nothing about your brother.«

»Forgive me, that is not true.«

»I know nothing. And surely, if the Duke will not speak, you should respect his reasons.«

»I am not bound in any way.«

»I am afraid I cannot help you. You are wasting time. If you cannot produce your missing witness, why do you not set about finding the real murderer? If you do so you surely need not trouble about this alibi.  Your brother's movements are his own business.«

»I could wish,« said Wimsey, »you had not taken up this attitude.  Believe me, I would have done all I could to spare you. I have been working hard to find, as you say, the real murderer, but with no success. The trial will probably take place at the end of the month.«

Her lips twitched a little at that, but she said nothing.

»I had hoped that with your help we might agree on some explanation—less than the truth, perhaps, but sufficient to clear my brother. As it is, I fear I shall have to produce the proof I hold, and let matters take their course.«

That, at last, struck under her guard. A dull flush crept up her cheeks; one hand tightened upon the handle of the churn, where she had rested it.

»What do you mean by proof?«

»I can prove that on the night of the 13\textsuperscript{th} my brother slept in the room I occupied last night,« said Wimsey, with calculated brutality.

She winced. »It is a lie. You cannot prove it. He will deny it. I shall deny it.«

»He was not there?«

»No.«

»Then how did this come to be wedged in the sash of the bedroom window?«

At sight of the letter she broke down, crumpling up in a heap against the table. The set lines of her face distorted themselves into a mere caricature of terror.

»No, no, no! It is a lie! God help me!«

»Hush!« said Wimsey peremptorily. »Someone will hear you.« He dragged her to her feet. »Tell the truth, and we will see if we can find a way out. It is true—he was here that night?«

»You know it.«

»When did he come?«

»At a quarter past twelve.«

»Who let him in?«

»He had the keys.«

»When did he leave you?«

»A little after two.«

»Yes, that fits in all right. Three quarters of an hour to go and three quarters to come back. He stuck this into the window, I suppose, to keep it from rattling?«

»There was a high wind—I was nervous. I thought every sound was my husband coming back.«

»Where was your husband?«

»At Stapley.«

»Had he suspected this?«

»Yes, for some time.«

»Since my brother was here in August?«

»Yes. But he could get no proof. If he had had proof he would have killed me. You have seen him. He is a devil.«

»M'm.«

Wimsey was silent. The woman glanced fearfully at his face and seemed to read some hope there, for she clutched him by the arm.

»If you call me to give evidence,« she said, »he will know. He \textit{will} kill me. For God's sake, have pity. That letter is my death-warrant.  Oh, for the mother that bore you, have mercy upon me. My life is a hell, and when I die I shall go to hell for my sin. Find some other way—you can—you must.«

Wimsey gently released himself.

»Don't do that, Mrs Grimethorpe. We might be seen. I am deeply sorry for you, and, if I can get my brother out of this without bringing you in, I promise you I will. But you see the difficulty. Why don't you leave this man? He is openly brutal to you.«

She laughed.

»Do you think he'd leave me alive while the law was slowly releasing me? Knowing him, do you think so?«

Wimsey really did not think so.

»I will promise you this, Mrs Grimethorpe. I will do all I can to avoid having to use your evidence. But if there should be no other way, I will see that you have police protection from the moment that the subpoena is served on you.«

»And for the rest of my life?«

»When you are once in London we will see about freeing you from this man.«

»No. If you call upon me, I am a lost woman. But you will find another way?«

»I will try, but I can promise nothing. I will do everything that is possible to protect you. If you care at all for my brother\longdash«

»I don't know. I am so horribly afraid. He was kind and good to me. He was—so different. But I am afraid—I'm afraid.«

Wimsey turned. Her terrified eyes had seen the shadow cross the threshold. Grimethorpe was at the door, glowering in upon them.

»Ah, Mr Grimethorpe,« exclaimed Wimsey cheerfully, »there you are.  Awfully pleased to see you and thank you, don'tcherknow, for puttin' me up. I was just saying so to Mrs Grimethorpe, an' asking her to say good-bye to you for me. Must be off now, I'm afraid. Bunter and I are ever so grateful to you both for all your kindness. Oh, and I say, could you find me the stout fellows who hauled us out of that Pot of yours last night—if it is yours. Nasty, damp thing to keep outside the front door, what? I'd like to thank `em.«

»Dom good thing for unwelcome guests,« said the man ferociously. »An' tha'd better be off afore Ah throws thee out.«

»I'm just off,« said Peter. »Good-bye again, Mrs Grimethorpe, and a thousand thanks.«

He collected Bunter, rewarded his rescuers suitably, took an affectionate farewell of the enraged farmer, and departed, sore in body and desperately confused in mind. 
