%!TeX root=../cloudstop.tex

\chapter{Bar Falling}

\epigraph{Copyright by Reuter, Press Association Exchange Telegraph, and Central News.}{}


\lettrine[lines=4]{W}{hen} Sir Impey Biggs rose to make his opening speech for the defence on the second day, it was observed that he looked somewhat worried—a thing very unusual in him. His remarks were very brief, yet in those few words he sent a thrill through the great assembly.

»My lords, in rising to open this defence I find myself in a more than usually anxious position. Not that I have any doubt of your lordships' verdict. Never perhaps has it been possible so clearly to prove the innocence of any accused person as in the case of my noble client. But I will explain to your lordships at once that I may be obliged to ask for an adjournment, since we are at present without an important witness and a decisive piece of evidence. My lords, I hold here in my hand a cablegram from this witness—I will tell you his name; it is Lord~Peter Wimsey, the brother of the accused. It was handed in yesterday at New York. I will read it to you. He says: »Evidence secured. Leaving tonight with Air Pilot Grant. Sworn copy and depositions follow by S.S. \textit{Lucarnia} in case accident. Hope arrive Thursday.« My lords, at this moment this all-important witness is cleaving the air high above the wide Atlantic. In this wintry weather he is braving a peril which would appal any heart but his own and that of the world-famous aviator whose help he has enlisted, so that no moment may be lost in freeing his noble brother from this terrible charge. My lords, the barometer is falling.«

An immense hush, like the stillness of a black frost, had fallen over the glittering benches. The lords in their scarlet and ermine, the peeresses in their rich furs, counsel in their full-bottomed wigs and billowing gowns, the Lord~High Steward upon his high seat, the ushers and the heralds and the gaudy kings-of-arms, rested rigid in their places. Only the prisoner looked across at his counsel and back to the Lord~High Steward in a kind of bewilderment, and the reporters scribbled wildly and desperately stop-press announcements—lurid headlines, picturesque epithets, and alarming weather predictions, to halt hurrying London on its way: »\textsc{Peer's Son Flies Atlantic}«; »\textsc{Brother's Devotion}«; »\textsc{Will Wimsey Be in Time?}«; »\textsc{Riddlesdale Murder Charge: Amazing Development}«. This was news. A million tape-machines ticked it out in offices and clubs, where clerks and messenger-boys gloated over it and laid wagers on the result; the thousands of monster printing-presses sucked it in, boiled it into lead, champed it into slugs, engulfed it in their huge maws, digested it to paper, and flapped it forth again with clutching talons; and a blue-nosed, ragged veteran of Vimy Ridge, who had once assisted to dig Major Wimsey out of a shell-hole, muttered: »Gawd 'elp 'im, 'e's a real decent little blighter,« as he tucked his newspapers into the iron grille of a tree in Kingsway and displayed his placard to the best advantage.

After a brief statement that he intended, not merely to prove his noble client's innocence but (as a work of supererogation) to make clear every detail of the tragedy, Sir Impey Biggs proceeded without further delay to call his witnesses.

Among the first was Mr~Goyles, who testified that he had found Cathcart already dead at 3 \textsc{a.m.}, with his head close to the water-trough which stood near the well. Ellen, the maid-servant, next confirmed James Fleming's evidence with regard to the post-bag, and explained how she changed the blotting-paper in the study every day.

The evidence of Detective-Inspector~Parker aroused more interest and some bewilderment. His description of the discovery of the green-eyed cat was eagerly listened to. He also gave a minute account of the footprints and marks of dragging, especially the imprint of a hand in the flower-bed. The piece of blotting-paper was then produced, and photographs of it circulated among the peers. A long discussion ensued on both these points, Sir Impey Biggs endeavouring to show that the imprint on the flower-bed was such as would have been caused by a man endeavouring to lift himself from a prone position, Sir Wigmore Wrinching doing his best to force an admission that it might have been made by deceased in trying to prevent himself from being dragged along.

»The position of the fingers being towards the house appears, does it not, to negative the suggestion of dragging?« suggested Sir Impey.

Sir Wigmore, however, put it to the witness that the wounded man might have been dragged head foremost.

»If, now,« said Sir Wigmore. »I were to drag you by the coat-collar—my lords will grasp my contention\longdash«

»It appears,« observed the Lord~High Steward, »to be a case for \textit{solvitur ambulando}«. (Laughter.) »I suggest that when the House rises for lunch, some of us should make the experiment, choosing a member of similar height and weight to the deceased.« (All the noble lords looked round at one another to see which unfortunate might be chosen for the part.)

Inspector~Parker then mentioned the marks of forcing on the study window.

»In your opinion, could the catch have been forced back by the knife found on the body of the deceased?«

»I know it could, for I made the experiment myself with a knife of exactly similar pattern.«

After this the message on the blotting-paper was read backwards and forwards and interpreted in every possible way, the defence insisting that the language was French and the words »\textit{Je suis fou de douleur}«, the prosecution scouting the suggestion as far-fetched, and offering an English interpretation, such as »is found« or »his foul.« A handwriting expert was then called, who compared the handwriting with that of an authentic letter of Cathcart's, and was subsequently severely handled by the prosecution.

These knotty points being left for the consideration of the noble lords, the defence then called a tedious series of witnesses: the manager of Cox's and Monsieur Turgeot of the Crédit Lyonnais, who went with much detail into Cathcart's financial affairs; the concierge and Madame Leblanc from the Rue St~Honoré; and the noble lords began to yawn, with the exception of a few of the soap and pickles lords, who suddenly started to make computations in their note-books, and exchanged looks of intelligence as from one financier to another.

Then came Monsieur Briquet, the jeweller from the Rue de la Paix, and the girl from his shop, who told the story of the tall, fair, foreign lady and the purchase of the green-eyed cat—whereat everybody woke up.  After reminding the assembly that this incident took place in February, when Cathcart's fiancée was in Paris, Sir Impey invited the jeweller's assistant to look round the house and tell them if she saw the foreign lady. This proved a lengthy business, but the answer was finally in the negative.

»I do not want there to be any doubt about this,« said Sir Impey, »and, with the learned Attorney-General's permission, I am now going to confront this witness with Lady~Mary Wimsey.«

Lady~Mary was accordingly placed before the witness, who replied immediately and positively: »No, this is not the lady; I have never seen this lady in my life. There is the resemblance of height and colour and the hair bobbed, but there is nothing else at all—not the least in the world. It is not the same type at all. Mademoiselle is a charming English lady, and the man who marries her will be very happy, but the other was \textit{belle à se suicider}—a woman to kill, suicide one's self, or send all to the devil for, and believe me, gentlemen« (with a wide smile to her distinguished audience), »we have the opportunity to see them in my business.«

There was a profound sensation as this witness took her departure, and Sir Impey scribbled a note and passed it down to Mr~Murbles. It contained the one word, »Magnificent!« Mr~Murbles scribbled back:

»Never said a word to her. Can you beat it?« and leaned back in his seat smirking like a very neat little grotesque from a Gothic corbel.

The witness who followed was Professor Hébert, a distinguished exponent of international law, who described Cathcart's promising career as a rising young diplomat in Paris before the war. He was followed by a number of officers who testified to the excellent war record of the deceased. Then came a witness who gave the aristocratic name of du Bois-Gobey Houdin, who perfectly recollected a very uncomfortable dispute on a certain occasion when playing cards with le Capitaine Cathcart, and having subsequently mentioned the matter to Monsieur Thomas Freeborn, the distinguished English engineer. It was Parker's diligence that had unearthed this witness, and he looked across with an undisguised grin at the discomfited Sir Wigmore Wrinching. When Mr~Glibbery had dealt with all these the afternoon was well advanced, and the Lord~High Steward accordingly asked the lords if it was their pleasure that the House be adjourned till the next day at 10:30 of the clock in the forenoon, and the lords replying »Aye« in a most exemplary chorus, the House was accordingly adjourned.

A scurry of swift black clouds with ragged edges was driving bleakly westward as they streamed out into Parliament Square, and the seagulls screeched and wheeled inwards from the river. Charles Parker wrapped his ancient Burberry closely about him as he scrambled on to a 'bus to get home to Great Ormond Street. It was only one more drop in his cup of discomfort that the conductor greeted him with »Outside only!« and rang the bell before he could get off again. He climbed to the top and sat there holding his hat on. Mr~Bunter returned sadly to 110 Piccadilly, and wandered restlessly about the flat till seven o'clock, when he came into the sitting-room and switched on the loud speaker.

»London calling,« said the unseen voice impartially. »2LO calling. Here is the weather forecast. A deep depression is crossing the Atlantic, and a secondary is stationary over the British Isles. Storms, with heavy rain and sleet, will be prevalent, rising to a gale in the south and south-west\dots«

»You never know,« said Bunter. »I suppose I'd better light a fire in his bedroom.«

»Further outlook similar.«
