%!TeX root=../cloudstop.tex

\chapter{Who Goes Home?}

\epigraph{Drunk as a lord? As a class they are really very sober.}{Judge Cluer, In Court}


\lettrine[lines=4]{W}{hile} the Attorney-General was engaged in the ungrateful task of trying to obscure what was not only plain, but agreeable to everybody's feelings, Lord Peter hauled Parker off to a Lyons over the way, and listened, over an enormous dish of eggs and bacon, to a brief account of Mrs Grimethorpe's dash to town, and a long one of Lady Mary's cross-examination.
»What are you grinning about?« snapped the narrator.

»Just natural imbecility,« said Lord Peter. »I say, poor old Cathcart.  She \textit{was} a girl! For the matter of that, I suppose she still is. I don't know why I should talk as if she'd died away the moment I took my eyes off her.«

»Horribly self-centered, you are,« grumbled Mr Parker.

»I know. I always was from a child. But what worries me is that I seem to be gettin' so susceptible. When Barbara turned me down\longdash«

»You're cured,« said his friend brutally. »As a matter of fact, I've noticed it for some time.«

Lord Peter sighed deeply. »I value your candor, Charles,« he said, »but I wish you hadn't such an unkind way of putting things. Besides\allowbreak---\allowbreak I say, are they coming out?«

The crowd in Parliament Square was beginning to stir and spread. Sparse streams of people began to drift across the street. A splash of scarlet appeared against the grey stone of St Stephen's. Mr Murbles's clerk dashed in suddenly at the door.

»All right, my lord\allowbreak---\allowbreak acquitted---unanimously\allowbreak---\allowbreak and will you please come across, my lord?«

They ran out. At sight of Lord Peter some excited bystanders raised a cheer. The great wind tore suddenly through the Square, bellying out the scarlet robes of the emerging peers. Lord Peter was bandied from one to the other, till he reached the center of the group.

»Excuse me, your grace.«

It was Bunter. Bunter, miraculously, with his arms full of scarlet and ermine, enveloping the shameful blue serge suit which had been a badge of disgrace.

»Allow me to offer my respectful congratulations, your grace.«

»Bunter!« cried Lord Peter. »Great God, the man's gone mad! Damn you, man, take that thing away,« he added, plunging at a tall photographer in a made-up tie.

»Too late, my lord,« said the offender, jubilantly pushing in the slide.

»Peter,« said the Duke. »Er\allowbreak---\allowbreak thanks, old man.«

»All right,« said his lordship. »Very jolly trip and all that. You're lookin' very fit. Oh, don't shake hands\allowbreak---\allowbreak there, I knew it! I heard that man's confounded shutter go.«

They pushed their way through the surging mob to the cars. The two Duchesses got in, and the Duke was following, when a bullet crashed through the glass of the window, missing Denver's head by an inch, and ricocheting from the wind-screen among the crowd.

A rush and a yell. A big bearded man struggled for a moment with three constables; then came a succession of wild shots, and a fierce rush\allowbreak---\allowbreak the crowd parting, then closing in, like hounds on the fox, streaming past the Houses of Parliament, heading for Westminster Bridge.

»He's shot a woman\allowbreak---\allowbreak he's under that 'bus\allowbreak---\allowbreak no, he isn't\allowbreak---\allowbreak hi!---murder!---stop him!« Shrill screams and yells\allowbreak---\allowbreak police whistles blowing\allowbreak---\allowbreak constables darting from every corner\allowbreak---\allowbreak swooping down in taxis\allowbreak---\allowbreak running.

The driver of a taxi spinning across the bridge saw the fierce face just ahead of his bonnet, and jammed on the brakes, as the madman's fingers closed for the last time on the trigger. Shot and tyre exploded almost simultaneously; the taxi slewed giddily over to the right, scooping the fugitive with it, and crashed horribly into a tram standing vacant on the Embankment dead-end.

»I couldn't 'elp it,« yelled the taxi-man, »'e fired at me. Ow, Gawd, I couldn't 'elp it.«

Lord Peter and Parker arrived together, panting.

»Here, constable,« gasped his lordship; »I know this man. He has an unfortunate grudge against my brother. In connection with a poaching matter\allowbreak---\allowbreak up in Yorkshire. Tell the coroner to come to me for information.«

»Very good, my lord.«

»Don't photograph \textit{that},« said Lord Peter to the man with the reflex, whom he suddenly found at his elbow.

The photographer shook his head.

»They wouldn't like to see that, my lord. Only the scene of the crash and the ambulance-men. Bright, newsy pictures, you know. Nothing gruesome«---with an explanatory jerk of the head at the great dark splotches in the roadway---»it doesn't pay.«

A red-haired reporter appeared from nowhere with a note-book.

»Here,« said his lordship, »do you want the story? I'll give it you now.« 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

There was not, after all, the slightest trouble in the matter of Mrs  Grimethorpe. Seldom, perhaps, has a ducal escapade resolved itself with so little embarrassment. His grace, indeed, who was nothing if not a gentleman, braced himself gallantly for a regretful and sentimental interview. In all his rather stupid affairs he had never run away from a scene, or countered a storm of sobs with that maddening »Well, I'd better be going now« which has led to so many despairs and occasionally to cold shot. But, on this occasion, the whole business fell flat. The lady was not interested.

»I am free now,« she said. »I am going back to my own people in Cornwall. I do not want anything, now that he is dead.« The Duke's dutiful caress was a most uninteresting failure.

Lord Peter saw her home to a respectable little hotel in Bloomsbury.  She liked the taxi, and the large, glittering shops, and the sky-signs.  They stopped at Piccadilly Circus to see the Bonzo dog smoke his gasper and the Nestlé's baby consume his bottle of milk. She was amazed to find that the prices of the things in Swan \& Edgar's window were, if anything, more reasonable than those current in Stapley.

»I should like one of those blue scarves,« she said, »but I'm thinking 'twould not be fitting, and me a widow.«

»You could buy it now, and wear it later on,« suggested his lordship, »in Cornwall, you know.«

»Yes.« She glanced at her brown stuff gown. »Could I buy my blacks here? I shall have to get some for the funeral. Just a dress and a hat\allowbreak---\allowbreak and a coat, maybe.«

»I should think it would be a very good idea.«

»Now?«

»Why not?«

»I have money,« she said; »I took it from his desk. It's mine now, I suppose. Not that I'd wish to be beholden to him. But I don't look at it that way.«

»I shouldn't think twice about it, if I were you,« said Lord Peter.

She walked before him into the shop\allowbreak---\allowbreak her own woman at last. 

\noindent\hfil\rule{0.5\textwidth}{.4pt}\hfil 

In the early hours of the morning Inspector Sugg, who happened to be passing Parliament Square, came upon a taxi-man apparently addressing a heated expostulation to the statue of Lord Palmerston. Indignant at this senseless proceeding, Mr Sugg advanced, and then observed that the statesman was sharing his pedestal with a gentleman in evening dress, who clung precariously with one hand, while with the other he held an empty champagne-bottle to his eye, and surveyed the surrounding streets.

»Hi,« said the policeman, »what are you doing there? Come off of it!«

»Hullo!« said the gentleman, losing his balance quite suddenly, and coming down in a jumbled manner. »Have you seen my friend? Very odd thing\allowbreak---\allowbreak damned odd. 'Spec you know where find him, what? When in doubt\allowbreak---\allowbreak tasker pleeshman, what? Friend of mine. Very dignified sort of man 'nopera-hat. Freddy\allowbreak---\allowbreak good ol' Freddy. Alwaysh answersh t'name\allowbreak---\allowbreak jush like jolly ol' bloodhound!« He got to his feet and stood beaming on the officer.

»Why, if it ain't his lordship,« said Inspector Sugg, who had met Lord Peter in other circumstances. »Better be gettin' home, my lord. Night air's chilly-like, ain't it? You'll catch a cold or summat o' that.  Here's your taxi\allowbreak---\allowbreak just you jump in now.«

»No,« said Lord Peter. »No. Couldn' do that. Not without frien'. Good ol' Freddy. Never\allowbreak---\allowbreak desert---friend! Dear ol' Sugg. Wouldn't desert Freddy.« He attempted an attitude, with one foot poised on the step of the taxi, but, miscalculating his distance, stepped heavily into the gutter, thus entering the vehicle unexpectedly, head first.

Mr Sugg tried to tuck his legs in and shut him up, but his lordship thwarted this movement with unlooked-for agility, and sat firmly on the step.

»Not my taxi,« he explained solemnly. »Freddy's taxi. Not right\allowbreak---\allowbreak run away with frien's taxi. Very odd. Jush went roun' corner to fesh Fred'sh taxshi\allowbreak---\allowbreak Freddy jush went roun' corner fesh \textit{my} taxi\allowbreak---\allowbreak fesh friend'sh taxshi\allowbreak---\allowbreak friendship sush a beautiful thing\allowbreak---\allowbreak don't you thing-so, Shugg? Can't leave frien'. Beshides\allowbreak---\allowbreak there'sh dear ol' Parker.«

»Mr Parker?« said the Inspector apprehensively. »Where?«

»Hush!« said his lordship. »Don' wake baby, theresh good shoul.  Neshle'sh baby\allowbreak---\allowbreak jush shee 'm neshle, don't he neshle nishely?«

Following his lordship's gaze, the horrified Sugg observed his official superior cozily tucked up on the far side of Palmerston and smiling a happy smile in his sleep. With an exclamation of alarm he bent over and shook the sleeper.

»Unkind!« cried Lord Peter in a deep, reproachful tone. »Dishturb poor fellow\allowbreak---\allowbreak poor hardworkin' pleeshman. Never getsh up till alarm goes....  'Stra'or'nary thing,« he added, as though struck by a new idea, »why hashn't alarm gone off, Shugg?« He pointed a wavering finger at Big Ben. »They've for-forgotten to wind it up. Dishgrayshful. I'll write to \textit{The T-T-Timesh} about it.«

Mr Sugg wasted no words, but picked up the slumbering Parker and hoisted him into the taxi.

»Never\allowbreak---\allowbreak never---deshert\longdash« began Lord Peter, resisting all efforts to dislodge him from the step, when a second taxi, advancing from Whitehall, drew up, with the Hon. Freddy Arbuthnot cheering loudly at the window.

»Look who's here!« cried the Hon. Freddy. »Jolly, jolly, jolly ol' Sugg. Let'sh all go home together.«

»That'sh \textit{my} taxshi,« interposed his lordship, with dignity, staggering across to it. The two whirled together for a moment; then the Hon. Freddy was flung into Sugg's arms, while his lordship, with a satisfied air, cried »Home!« to the new taxi-man, and instantly fell asleep in a corner of the vehicle.

Mr Sugg scratched his head, gave Lord Peter's address, and watched the cab drive off. Then, supporting the Hon. Freddy on his ample bosom, he directed the other man to convey Mr Parker to 12a Great Ormond Street.

»Take me home,« cried the Hon. Freddy, bursting into tears, »they've all gone and left me!«

»You leave it to me, sir,« said the Inspector. He glanced over his shoulder at St Stephen's, whence a group of Commons were just issuing from an all-night sitting.

»Mr Parker an' all,« said Inspector Sugg, adding devoutly, »Thank Gawd there weren't no witnesses.«
\vfill

\begin{center}\setstretch{1.8}\mytitlefont\reasonablyhuge
	The End
\end{center}