%!TeX root=../bellonatop.tex
\chapter{The Queen Is Out}
\lettrine[lines=4]{I}{t} is doubtful which occurrence was more disagreeable to the senior members of the Bellona Club\allowbreak---\allowbreak the grotesque death of General Fentiman in their midst or the indecent neurasthenia of his grandson. Only the younger men felt no sense of outrage; they knew too much. Dick Challoner\allowbreak---\allowbreak known to his intimates as Tin-Tummy Challoner, owing to the fact that he had been fitted with a spare part after the second battle of the Somme\allowbreak---\allowbreak took the gasping Fentiman away into the deserted library for a stiffener. The Club Secretary hurried in, in his dress-shirt and trousers, the half-dried lather still clinging to his jaws. After one glance he sent an agitated waiter to see if Dr Penberthy was still in the Club. Colonel Marchbanks laid a large silk handkerchief reverently over the rigid face in the arm-chair and remained quietly standing. A little circle formed about the edge of the hearthrug, not quite certain what to do. From time to time it was swelled by fresh arrivals, whom the news had greeted in the hall as they wandered in. A little group appeared from the bar. \enquote{What? old Fentiman?} they said. \enquote{Good God, you don't say so. Poor old blighter. Heart gone at last, I suppose}; and they extinguished cigars and cigarettes, and stood by, not liking to go away again.

Dr Penberthy was just changing for dinner. He came down hurriedly, caught just as he was going out to an Armistice dinner, his silk hat tilted to the back of his head, his coat and muffler pushed loosely open. He was a thin, dark man with the abrupt manner which distinguishes the Army Surgeon from the West-end practitioner. The group by the fire made way for him, except Wimsey, who hung rather foolishly upon the big elbow-chair, gazing in a helpless way at the body.

Penberthy ran practiced hands quickly over neck, wrists and knee-joints.

\enquote{Dead several hours,} he pronounced, sharply. \enquote{Rigor well-established\allowbreak---\allowbreak beginning to pass off.} He moved the dead man's left leg in illustration; it swung loose at the knee. \enquote{I've been expecting this. Heart very weak. Might happen any moment. Any one spoken to him to-day?}

He glanced around interrogatively.

\enquote{I saw him here after lunch,} volunteered somebody. \enquote{I didn't speak.}

\enquote{I thought he was asleep,} said another.

Nobody remembered speaking to him. They were so used to old General Fentiman, slumbering by the fire.

\enquote{Ah, well,} said the doctor. \enquote{What's the time? Seven?} He seemed to make a rapid calculation. \enquote{Say five hours for rigor to set in\allowbreak---\allowbreak must have taken place very rapidly\allowbreak---\allowbreak he probably came in at his usual time, sat down and died straight away.}

\enquote{He always walked from Dover Street,} put in an elderly man, \enquote{I told him it was too great an exertion at his age. You've heard me say so, Ormsby.}

\enquote{Yes, yes, quite,} said the purple-faced Ormsby. \enquote{Dear me, just so.}

\enquote{Well, there's nothing to be done,} said the doctor. \enquote{Died in his sleep. Is there an empty bedroom we can take him to, Culyer?}

\enquote{Yes, certainly,} said the Secretary. \enquote{James, fetch the key of number sixteen from my office and tell them to put the bed in order. I suppose, eh, doctor?---when the rigor passes off we shall be able to\allowbreak---\allowbreak eh?}

\enquote{Oh, yes, you'll be able to do everything that's required. I'll send the proper people in to lay him out for you. Somebody had better let his people know\allowbreak---\allowbreak only they'd better not show up till we can get him more presentable.}

\enquote{Captain Fentiman knows already,} said Colonel Marchbanks. \enquote{And Major Fentiman is staying in the Club\allowbreak---\allowbreak he'll probably be in before long. Then there's a sister, I think.}

\enquote{Yes, old Lady Dormer,} said Penberthy, \enquote{she lives round in Portman Square. They haven't been on speaking terms for years. Still, she'll have to know.}

\enquote{I'll ring them up,} said the Colonel. \enquote{We can't leave it to Captain Fentiman, he's in no fit state to be worried, poor fellow. You'll have to have a look at him, doctor, when you've finished here. An attack of the old trouble\allowbreak---\allowbreak nerves, you know.}

\enquote{All right. Ah! is the room ready, Culyer? Then we'll move him. Will somebody take his shoulders\allowbreak---\allowbreak no, not you, Culyer} (for the Secretary had only one sound arm), \enquote{Lord Peter, yes, thank you\allowbreak---\allowbreak lift carefully.}

Wimsey put his long, strong hands under the stiff arms; the doctor gathered up the legs; they moved away. They looked like a dreadful little Guy Fawkes procession, with that humped and unreverend mannikin bobbing and swaying between them.

The door closed after them, and a tension seemed removed. The circle broke up into groups. Somebody lit a cigarette. The planet's tyrant, dotard Death, had held his gray mirror before them for a moment and shown them the image of things to come. But now it was taken away again. The unpleasantness had passed. Fortunate, indeed, that Penberthy was the old man's own doctor. He knew all about it. He could give a certificate. No inquest. Nothing undesirable. The members of the Bellona Club could go to dinner.

Colonel Marchbanks turned to go through the far door towards the library. In a narrow ante-room between the two rooms there was a convenient telephone cabinet for the use of those members who did not wish to emerge into the semi-publicity of the entrance-hall.

\enquote{Hi, colonel! not that one. That instrument's out of order,} said a man called Wetheridge, who saw him go. \enquote{Disgraceful, I call it. I wanted to use the 'phone this morning, and\allowbreak---\allowbreak oh! hullo! the notice has gone. I suppose it's all right again. They ought to let one know.}

Colonel Marchbanks paid little attention to Wetheridge. He was the club grumbler, distinguished even in that fellowship of the dyspeptic and peremptory\allowbreak---\allowbreak always threatening to complain to the Committee, harassing the Secretary and constituting a perennial thorn in the sides of his fellow-members. He retired, murmuring, to his chair and the evening paper, and the Colonel stepped into the telephone cabinet to call up Lady Dormer's house in Portman Square.

Presently he came out through the library into the entrance-hall, and met Penberthy and Wimsey just descending the staircase.

\enquote{Have you broken the news to Lady Dormer?} asked Wimsey.

\enquote{Lady Dormer is dead,} said the Colonel. \enquote{Her maid tells me she passed quietly away at half-past ten this morning.}