%!TeX root=../bellonatop.tex
\chapter{Lord Peter Leads a Club}
\lettrine[lines=4,ante=‘]{Y}{ou} are quite sure this suit is all right, Bunter?' said Lord Peter, anxiously. It was an easy lounge suit, tweedy in texture, and a trifle more pronounced in colour and pattern than Wimsey usually permitted himself. While not unsuitable for town wear, it yet diffused a faint suggestion of hills and the sea.

»I want to look approachable,« he went on, »but on no account loud. I can't help wondering whether that stripe of invisible green wouldn't have looked better if it had been a remote purple.«

This suggestion seemed to disconcert Bunter. There was a pause while he visualized a remote purple stripe. At length, however, the palpitating balance of his mind seemed to settle definitely down.

»No, my lord,« he said firmly, »I do \textit{not} think purple would be an improvement. Interesting—yes; but, if I may so express myself, decidedly less affable.«

»Thank goodness,« said his lordship, »I'm sure you're right. You always are. And it would have been a bore to get it changed now. You are sure you've removed all the newness, eh? Hate new clothes.«

»Positive, my lord. I assure your lordship that the garments have every appearance of being several months old.«

»Oh, all right. Well, give me the malacca with the foot-rule marked on it—and where's my lens?«

»Here, my lord,« Bunter produced an innocent-looking monocle, which was, in reality, a powerful magnifier. »And the finger-print powder is in your lordship's right-hand coat-pocket.«

»Thanks. Well, I think that's all. I'll go on now, and I want you to follow on with the doings in about an hour's time.«

The Bellona Club is situated in Piccadilly, not many hundred yards west of Wimsey's own flat, which overlooks the Green Park. The commissionaire greeted him with a pleased smile.

»Mornin', Rogers, how are you?«

»Very well, my lord, I thank you.«

»D'you know if Major Fentiman is in the Club, by the way?«

»No, my lord. Major Fentiman is not residing with us at present. I believe he is occupying the late General Fentiman's flat, my lord.«

»Ah, yes—very sad business, that.«

»Very melancholy, my lord. Not a pleasant thing to happen in the Club. Very shocking, my lord.«

»Yes—still, he was a very old man. I suppose it had to be some day. Queer to think of `em all sittin' round him there and never noticin', eh, what?«

»Yes, my lord. It gave Mrs Rogers quite a turn when I told her about it.«

»Seems almost unbelievable, don't it? Sittin' round all those hours—must have been several hours, I gather, from what the doctor says. I suppose the old boy came in at his usual time, eh?«

»Ah! regular as clock-work, the General was. Always on the stroke of ten. `Good morning, Rogers', he'd say, a bit stiff-like, but very friendly. And then, `Fine morning,' he'd say, as like as not. And sometimes ask after Mrs Rogers and the family. A fine old gentleman, my lord. We shall all miss him.«

»Did you notice whether he seemed specially feeble or tired that morning at all?« inquired Wimsey, casually, tapping a cigarette on the back of his hand.

»Why, no, my lord. I beg your pardon, I fancied you knew. I wasn't on duty that day, my lord. I was kindly given permission to attend the ceremony at the Cenotaph. Very grand sight, it was, too, my lord. Mrs Rogers was greatly moved.«

»Oh, of course, Rogers—I was forgetting. Naturally, you would be there. So you didn't see the General to say good-bye, as it were. Still, it wouldn't have done to miss the Cenotaph. Matthews took your duty over, I suppose.«

»No, my lord. Matthews is laid up with `flu, I am sorry to say. It was Weston was at the door all morning, my lord.«

»Weston? Who's he?«

»He's new, my lord. Took the place of Briggs. You recollect Briggs—his uncle died and left him a fish-shop.«

»Of course he did; just so. When does Weston come on parade? I must make his acquaintance.«

»He'll be here at one o'clock, when I go to my lunch, my lord.«

»Oh, right! I'll probably be about then. Hallo, Penberthy! You're just the man I want to see. Had your morning's inspiration? Or come in to look for it?«

»Just tracking it to its lair. Have it with me.«

»Right you are, old chap—half a mo' while I deposit my outer husk. I'll follow you.«

He glanced irresolutely at the hall-porter's desk, but seeing the man already engaged with two or three inquiries, plunged abruptly into the cloak-room, where the attendant, a bright cockney with a Sam Weller face and an artificial leg, was ready enough to talk about General Fentiman.

»Well, now, my lord, that's funny you should ask me that,« he said, when Wimsey had dexterously worked in an inquiry as to the time of the General's arrival at the Bellona. »Dr Penberthy was askin' the same question. It's a fair puzzle, that is. I could count on the fingers of one `and the mornings I've missed seein' the General come in. Wonderful regular, the General was, and him being such a very old gentleman, I'd make a point of being `andy, to `elp him off with his overcoat and such. But there! He must a' come in a bit late, that morning, for I never see him, and I thought at lunch-time, `The General must be ill,' I thinks. And I goes round, and there I see his coat and `at `ung up on his usual peg. So I must `a missed him. There was a lot of gentlemen in and out that morning, my lord, bein' Armistice Day. A number of members come up from the country and wanting their `ats and boots attended to, my lord, so that's how I come not to notice, I suppose.«

»Possibly. Well, he was in before lunch, at any rate.«

»Oh, yes, my lord. `Alf-past twelve I goes off, and his hat and coat were on the peg then, because I see `em.«

»That gives us a terminus ad quem at any rate,« said Wimsey, half to himself.

»I beg your lordship's pardon?«

»I was saying, that shows he came in before half-past twelve—and later than ten o'clock, you think.«

»Yes, my lord. I couldn't say to a fraction, but I'm sure if `e'd arrived before a quarter-past ten I should have seen `em. But after that, I recollect I was very busy, and he must `a slipped in without me noticing him.«

»Ah, yes—poor old boy! Still, no doubt he'd have liked to pass out quietly like that. Not a bad way to go home, Williamson.«

»Very good way, my lord. We've seen worse than that. And what's it all come to, after all? They're all sayin' as it's an unpleasant thing for the Club, but \textit{I} say, where's the odds? There ain't many `ouses what somebody ain't died in, some time or another. We don't think any the worse of the `ouses, so why think the worse of the Club?«

»You're a philosopher, Williamson.« Wimsey climbed the short flight of marble steps and turned into the bar. »It's narrowin' down,« he muttered to himself. »Between ten-fifteen and twelve-thirty. Looks as if it was goin' to be a close run for the Dormer stakes. But—dash it all! Let's hear what Penberthy has to say.«

The doctor was already standing at the bar with a whisky-and-soda before him. Wimsey demanded a Worthington and dived into his subject without more ado.

»Look here,« he said, »I just wanted a word with you about old Fentiman. Frightfully confidential, and all that. But it seems the exact time of the poor old blighter's departure has become an important item. Question of succession. Get me? They don't want a row made. Asked me, as friend of the family and all that, don't y' know, to barge round and ask questions. Obviously, you're the first man to come to. What's your opinion? Medical opinion, apart from anything else?«

Penberthy raised his eyebrows.

»Oh? there's a question, is there? Thought there might be. That lawyer-fellow, what's-his-name, was here the other day, trying to pin me down. Seemed to think one can say to a minute when a man died by looking at his back teeth. I told him it wasn't possible. Once give these birds an opinion, and the next thing is, you find yourself in a witness-box, swearing to it.«

»I know. But one gets a general idea.«

»Oh, yes. Only you have to check up your ideas by other things—facts, and so on. You can't just theorize.«

»Very dangerous things, theories. F'r instance—take this case—I've seen one or two stiff `uns in my short life, and, if I'd started theorizin' about this business, just from the look of the body, d'you know what I'd have said?«

»God knows what a layman would say about a medical question,« retorted the doctor, with a sour little grin.

»Hear, hear!—Well, I should have said he'd been dead a long time.«

»That's pretty vague.«

»You said yourself that rigour was well advanced. Give it, say, six hours to set in and—when did it pass off?«

»It was passing off then—I remarked upon it at the time.«

»So you did. I thought rigour usually lasted twenty-four hours or so.«

»It does, sometimes. Sometimes it goes off quickly. Quick come, quick go, as a rule. Still, I agree with you, that in the absence of other evidence, I should have put the death rather earlier than ten o'clock.«

»You admit that?«

»I do. But we know he came in not earlier than a quarter-past ten.«

»You've seen Williamson, then?«

»Oh, yes. I thought it better to check up on the thing as far as possible. So I can only suppose that, what with the death being sudden, and what with the warmth of the room—he was very close to the fire, you know—the whole thing came on and worked itself off very quickly.«

»H'm! Of course, you knew the old boy's constitution very well.«

»Oh, rather. He was very frail. Heart gets a bit worn-out when you're over the four-score and ten, you know. I should never have been surprised at his dropping down anywhere. And then, he'd had a bit of a shock, you see.«

»What was that?«

»Seeing his sister the afternoon before. They told you about that, I imagine, since you seem to know all about the business. He came along to Harley Street afterwards and saw me. I told him to go to bed and keep quiet. Arteries very strained, and pulse erratic. He was excited—naturally. He ought to have taken a complete rest. As I see it, he must have insisted on getting up, in spite of feeling groggy, walked here—he would do it—and collapsed straight away.«

»That's all right, Penberthy, but when—just when—did it happen?«

»Lord knows. I don't. Have another?«

»No, thanks; not for the moment. I say, I suppose you are perfectly satisfied about it all?«

»Satisfied?« The doctor stared at him. »Yes, of course. If you mean, satisfied as to what he died of—of course I'm satisfied. I shouldn't have given a certificate if I hadn't been satisfied.«

»Nothing about the body struck you as queer?«

»What sort of thing?«

»You know what I mean as well as I do,« said Wimsey, suddenly turning and looking the other straight in the face. The change in him was almost startling—it was as if a steel blade had whipped suddenly out of its velvet scabbard. Penberthy met his eye, and nodded slowly.

»Yes, I do know what you mean. But not here. We'd better go up to the Library. There won't be anybody there.«