%!TeX root=../bellonatop.tex
\chapter{—And Finds The Club Suit Blocked}
\lettrine[lines=4]{T}{here} never was anybody in the library at the Bellona. It was a large, quiet, pleasant room, with the bookshelves arranged in bays; each of which contained a writing-table and three or four chairs. Occasionally some one would wander in to consult the \textit{Times Atlas}, or a work on Strategy and Tactics, or to hunt up an ancient Army list, but for the most part it was deserted. Sitting in the farthest bay, immured by books and silence, confidential conversation could be carried on with all the privacy of the confessional.

\enquote{Well, now,} said Wimsey, \enquote{what about it?}

\enquote{About---?} prompted the doctor, with professional caution.

\enquote{About that leg?}

\enquote{I wonder if anybody else noticed that?} said Penberthy.

\enquote{I doubt it. I did, of course. But then, I make that kind of thing my hobby. Not a popular one, perhaps\allowbreak---\allowbreak an ill-favored thing, but mine own. In fact, I've got rather a turn for corpses. But not knowin' quite what it meant, and seein' you didn't seem to want to call attention to it, I didn't put myself forward.}

\enquote{No\allowbreak---\allowbreak I wanted to think it over. You see, it suggested, at the first blush, something rather\longdash}

\enquote{Unpleasant,} said Wimsey. \enquote{If you knew how often I'd heard that word in the last two days! Well, let's face it. Let's admit, straight away, that, once rigor sets in, it stays in till it starts to pass off, and that, when it \textit{does} start to go it usually begins with the face and jaw, and not suddenly in one knee-joint. Now Fentiman's jaw and neck were as rigid as wood\allowbreak---\allowbreak I felt 'em. But the left leg swung loose from the knee. Now how do you explain that?}

\enquote{It is extremely puzzling. As no doubt you are aware, the obvious explanation would be that the joint had been forcibly loosened by somebody or something, after rigor had set in. In that case of course, it wouldn't stiffen up again. It would remain loose until the whole body relaxed. But how it happened\longdash}

\enquote{That's just it. Dead people don't go about jamming their legs into things and forcing their own joints. And surely, if anybody had found the body like that he would have mentioned it. I mean, can you imagine one of the waiter-johnnies, for instance, finding an old gentleman stiff as a poker in the best arm-chair and then just givin' him a dose of knee-jerks and leavin' him there?}

\enquote{The only thing I could think of,} said Penberthy, \enquote{was that a waiter or somebody had found him, and tried to move him\allowbreak---\allowbreak and then got frightened and barged off without saying anything. It sounds absurd. But people do do odd things, especially if they're scared.}

\enquote{But what was there to be scared of?}

\enquote{It might seem alarming to a man in a very nervous state. We have one or two shell-shock cases here that I wouldn't answer for in an emergency. It would be worth considering, perhaps, if any one had shown special signs of agitation or shock that day.}

\enquote{That's an idea,} said Wimsey, slowly. \enquote{Suppose\allowbreak---\allowbreak suppose, for instance, there was somebody connected in some way with the General, who was in an unnerved state of mind\allowbreak---\allowbreak and suppose he came suddenly on this stiff corpse. You think he might\allowbreak---\allowbreak possibly---lose his head?}

\enquote{It's certainly possible. I can imagine that he might behave hysterically, or even violently, and force the knee-joint back with some unbalanced idea of straightening the body out and making it look more seemly. And then, you know he might just run away from the thing and pretend it hadn't happened. Mind you, I'm not saying it was so, but I can easily see it happening. And that being so, I thought it better to say nothing about it. It would be a very unpl\allowbreak---\allowbreak distressing thing to bring to people's notice. And it might do untold harm to the nervous case to question him about it. I'd rather let sleeping dogs lie. There was nothing wrong about the death, that's definite. As for the rest\allowbreak---\allowbreak our duty is to the living; we can't help the dead.}

\enquote{Quite. Tell you what, though, I'll have a shot at finding out whether\allowbreak---\allowbreak we may as well say what we mean\allowbreak---\allowbreak whether George Fentiman was alone in the smoking-room at any time during the day. One of the servants may have noticed. It seems the only possible explanation. Well, thanks very much for your help. Oh, by the way, you said at the time that the rigor was passing off when we found the body\allowbreak---\allowbreak was that just camouflage, or does it still hold good?}

\enquote{It was just beginning to pass off in the face and jaw as a matter of fact. It had passed away completely by midnight.}

\enquote{Thanks. That's another fact, then. I like facts, and there are annoyin'ly few of them in this case. Won't you have another whisky?}

\enquote{No thanks. Due at my surgery. See you another time. Cheerio!}

Wimsey remained for a few moments after he had gone, smoking meditatively. Then he turned his chair to the table, took a sheet of paper from the rack and began to jot down a few notes of the case with his fountain-pen. He had not got far, however, before one of the Club servants entered, peering into all the bays in turn, looking for somebody.

\enquote{Want me, Fred?}

\enquote{Your lordship's man is here, my lord, and says you may wish to be advised of his arrival.}

\enquote{Quite right. I'm just coming.} Wimsey took up the blotting-pad to blot his notes. Then his face changed. The corner of a sheet of paper protruded slightly. On the principle that nothing is too small to be looked at, Wimsey poked an inquisitive finger between the leaves, and extracted the paper. It bore a few scrawls relating to sums of money, very carelessly and shakily written. Wimsey looked at it attentively for a moment or two, and shook the blotter to see if it held anything further. Then he folded the sheet, handling it with extreme care by the corners, put it in an envelope and filed it away in his note-case. Coming out of the library, he found Bunter waiting in the hall, camera and tripod in hand.

\enquote{Ah, here you are, Bunter. Just a minute, while I see the Secretary.} He looked in at the office, and found Culyer immersed in some accounts.

\enquote{Oh, I say, Culyer---\enquote{mornin} and all that\allowbreak---\allowbreak yes, disgustingly healthy, thanks, always am\allowbreak---\allowbreak I say, you recollect old Fentiman poppin' off in that inconsiderate way a little time ago?}

\enquote{I'm not likely to forget it,} said Culyer, with a wry face. \enquote{I've had three notes of complaint from Wetheridge\allowbreak---\allowbreak one, because the servants didn't notice the matter earlier, set of inattentive rascals and all that; two, because the undertaker's men had to take the coffin past his door and disturbed him; three, because somebody's lawyer came along and asked him questions\allowbreak---\allowbreak together with distant allusions to the telephones being out of order and a shortage of soap in the bathroom. Who'd be a secretary?}

\enquote{Awfully sorry for you,} said Wimsey with a grin. \enquote{I'm not here to make trouble. Au contraire, as the man said in the Bay of Biscay when they asked if he'd dined. Fact is, there's a bit of a muddle about the exact minute when the old boy passed out\allowbreak---\allowbreak mind you, this is in strict confidence\allowbreak---\allowbreak and I'm havin' a look into it. Don't want a fuss made, but I'd like a few photographs of the place, just to look at in absence and keep the lie of the land under my hawk-like optic, what? I've got my man here with a camera. D'you mind pretendin' he's the bloke from \textit{The Twaddler} or the \textit{Picture News}, or something, and givin' him your official blessin' while he totters round with the doings?}

\enquote{Mysterious idiot\allowbreak---\allowbreak of course, if you like. Though how photographs of the place to-day are going to give you a line on the time of a death which happened ten days ago, I don't pretend to understand. But, I say\allowbreak---\allowbreak it's all fair and aboveboard? We don't want any\longdash}

\enquote{Of course not. That's the idea. Strictest confidence\allowbreak---\allowbreak any sum up to \textsterling 50,000 on your note of hand alone, delivered in plain vans, no reference needed. Trust little Peter.}

\enquote{Oh, right-ho! What d'you want done?}

\enquote{I don't want to go round with Bunter. Give the show away. May he be called in here?}

\enquote{Certainly.}

A servant was sent to fetch Bunter, who came in looking imperturbably prim and point-device. Wimsey looked him over and shook his head.

\enquote{I'm sorry, Bunter, but you don't look in the least like the professional photographer from \textit{The Twaddler}. That dark-gray suit is all right, but you haven't got quite the air of devil-may-care seediness that marks the giants of Fleet Street. D'you mind stickin' all those dark-slides into one pocket and a few odd lenses and doodahs into the other, and rufflin' your manly locks a trifle? That's better. Why have you no pyro stains on the right thumb and forefinger?}

\enquote{I attribute it, my lord, principally to the circumstance that I prefer metol-quinol for the purpose of development.}

\enquote{Well, you can't expect an outsider to grasp a thing like that. Wait a minute. Culyer, you seem to have a fairly juicy pipe there. Give us a cleaner.}

Wimsey thrust the instrument energetically through the stem of the pipe, bringing out a revolting collection of brown, oily matter.

\enquote{Nicotine poisoning, Culyer\allowbreak---\allowbreak that's what you'll die of if you aren't jolly careful. Here you are, Bunter. Judiciously smeared upon the finger tips, that should give quite the right effect. Now, look here, Mr Culyer here will take you round. I want a shot of the smoking-room from the entrance, a close up of the fireplace, showing General Fentiman's usual chair, and another shot from the door of the ante-room that leads into the library. Another shot through the ante-room into the library, and some careful studies of the far bay of the library from all points of view. After that, I want two or three views of the hall, and a shot of the cloak-room; get the attendant there to show you which was General Fentiman's customary peg, and take care that that gets into the picture. That's all for the moment, but you can take anything else that seems necessary for purposes of camouflage. And I want all the detail you can possibly get in, so stop down to whatever it is and take as long as you like. You'll find me knocking about somewhere when you've finished, and you'd better get some more plates in, because we're going on to another place.}

\enquote{Very good, my lord.}

\enquote{Oh, and, Culyer, by the way. Dr Penberthy sent a female in to lay the General out, didn't he? D'you happen to remember when she arrived?}

\enquote{About nine o'clock the next morning, I think.}

\enquote{Have you got her name, by any chance?}

\enquote{I don't think so. But I know she came from Merritt's, the undertakers\allowbreak---\allowbreak round Shepherd's Market way. They'd probably put you on to her.}

\enquote{Thanks frightfully, Culyer. I'll make myself scarce now. Carry on, Bunter.}

Wimsey thought for a moment; then strolled across to the smoking-room, exchanged a mute greeting with one or two of the assembled veterans, picked up the \textit{Morning Post,} and looked round for a seat. The great arm-chair with ears still stood before the fire, but some dim feeling of respect for the dead had left it vacant. Wimsey sauntered over to it, and dropped lazily into its well-sprung depths. A veteran close at hand looked angrily at him and rustled the \textit{Times} loudly. Wimsey ignored these signals, barricading himself behind his paper. The veteran sank back again, muttering something about \enquote{young men} and \enquote{no decency.} Wimsey sat on unmoved, and paid no attention, even when a man from \textit{The Twaddler} came in, escorted by the Secretary, to take photographs of the smoking-room. A few sensitives retired before this attack. Wetheridge waddled away with a grumbling protest into the library. It gave Wimsey considerable satisfaction to see the relentless camera pursue him into that stronghold.

It was half-past twelve before a waiter approached Lord Peter to say that Mr Culyer would be glad to speak to him for a moment. In the office, Bunter reported his job done, and was despatched to get some lunch and a fresh supply of plates. Wimsey presently went down to the dining-room, where he found Wetheridge already established, getting the first cut off the saddle of mutton, and grumbling at the wine. Wimsey went deliberately over, greeted him heartily, and sat down at the same table.

Wetheridge said it was beastly weather. Wimsey agreed amiably. Wetheridge said it was scandalous, seeing what one paid for one's food in this place, that one couldn't get anything fit to eat. Wimsey, who was adored by chef and waiters alike for his appreciation of good food, and had been sent the choicest cut without having to ask for it, sympathized with this sentiment too. Wetheridge said he had been chased all over the Club that morning by an infernal photographer fellow, and that one got no peace these days with all this confounded publicity. Wimsey said it was all done for advertisement, and that advertisement was the curse of the age. Look at the papers\allowbreak---\allowbreak nothing but advertisements from cover to cover. Wetheridge said that in his time, by gad, a respectable Club would have scorned advertisements, and that he could remember the time when newspapers were run by gentlemen for gentlemen. Wimsey said that nothing was what it had been; he thought it must be due to the War.

\enquote{Infernal slackness, that's what it is,} said Wetheridge. \enquote{The service in this place is a disgrace. That fellow Culyer doesn't know his job. This week it's the soap. Would you believe it, there was none\allowbreak---\allowbreak actually none\allowbreak---\allowbreak in the bathroom yesterday. Had to ring for it. Made me late for dinner. Last week it was the telephone. Wanted to get through to a man down in Norfolk. Brother was a friend of mine\allowbreak---\allowbreak killed on the last day of the War, half an hour before the guns stopped firing\allowbreak---\allowbreak damnable shame\allowbreak---\allowbreak always ring up on Armistice Day, say a few words, don't you know\allowbreak---\allowbreak hr'rm!}

Wetheridge, having unexpectedly displayed this softer side of his character, relapsed into a snorting silence.

\enquote{Couldn't you get through, sir?} inquired Wimsey, with feeling. Anything that had happened at the Bellona Club on Armistice Day was of interest to him.

\enquote{I got \textit{through} all right,} said Wetheridge, morosely. \enquote{But, confound it all, I had to go down to the cloak-room to get a call from one of the boxes there. Didn't want to hang about the entrance. Too many imbeciles coming in and out. Exchanging silly anecdotes. Why a solemn national occasion should be an excuse for all these fools meeting and talking rot, I don't know.}

\enquote{Beastly annoyin'. But why didn't you tell 'em to put the call through to the box by the library?}

\enquote{Aren't I telling you? The damned thing was out of order. Damned great notice stuck across it as cool as you please---'Instrument out of order.' Just like that. No apology. Nothing. Sickening, I call it. I told the fellow at the switch-board it was a disgrace. And all he said was, he hadn't put the notice up, but he'd draw attention to the matter.}

\enquote{It was all right in the evening,} said Wimsey, \enquote{because I saw Colonel Marchbanks using it.}

\enquote{I know it was. And then, dashed if we didn't get the fool thing ringing, ringing at intervals all the next morning. Infuriating noise. When I told Fred to stop it, he just said it was the Telephone Company testing the line. They've no business to make a row like that. Why can't they test it quietly, that's what I want to know?}

Wimsey said telephones were an invention of the devil. Wetheridge grumbled his way through to the end of lunch, and departed. Wimsey returned to the entrance-hall, where he found the assistant commissionaire on duty, and introduced himself.

Weston, however, was of no assistance. He had not noticed General Fentiman's arrival on the eleventh. He was not acquainted with many of the members, having only just taken over his new duties. He thought it odd that he should not have noticed so very venerable a gentleman, but the fact remained that he had not. He regretted it extremely. Wimsey gathered that Weston was annoyed at having lost a chance of reflected celebrity. He had missed his scoop, as the reporters say.

Nor was the hall-porter any more helpful. The morning of November  11\textsuperscript{th} had been a busy one. He had been in and out of his little glass pigeonhole continually, shepherding guests into various rooms to find the members they wanted, distributing letters and chatting to country members who visited the Bellona seldom and liked to \enquote{have a chat with Piper} when they did. He could not recollect seeing the General. Wimsey began to feel that there must have been a conspiracy to overlook the old gentleman on the last morning of his life.

\enquote{You don't think he never was here at all, do you, Bunter?} he suggested. \enquote{Walkin' about invisible and tryin' hard to communicate, like the unfortunate ghost in that story of somebody or other's?}

Bunter was inclined to reject the psychic view of the case. \enquote{The General must have been here in the body, my lord, because there \textit{was} the body.}

\enquote{That's true,} said Wimsey. \enquote{I'm afraid we can't explain away the body. S'pose that means I'll have to question every member of this beastly Club separately. But just at the moment I think we'd better go round to the General's flat and hunt up Robert Fentiman. Weston, get me a taxi, please.}