%!TeX root=../bellonatop.tex
\chapter{Knave High}

\lettrine[lines=4,ante=‘]{L}{ook} here, Wimsey,' said Captain Culyer of the Bellona Club, \enquote{aren't you ever going to get finished with this investigation or whatever it is? The members are complaining, really they are, and I can't blame them. They find your everlasting questions an intolerable nuisance, old boy, and I can't stop them from thinking there must be something behind it. People complain that they can't get attention from the porters or the waiters because you're everlastingly there chatting, and if you're not there, you're hanging round the bar, eavesdropping. If this is your way of conducting an inquiry tactfully, I wish you'd do it tactlessly. It's becoming thoroughly unpleasant. And no sooner do you stop it, than the other fellow begins.}

\enquote{What other fellow?}

\enquote{That nasty little skulking bloke who's always turning up at the service door and questioning the staff.}

\enquote{I don't know anything about \textit{him},} replied Wimsey, \enquote{I never heard of him. I'm sorry I'm being a bore and all that, though I swear I couldn't be worse than some of your other choice specimens in that line, but I've hit a snag. This business\allowbreak---\allowbreak quite in your ear, old bean\allowbreak---\allowbreak isn't as straightforward as it looks on the surface. That fellow Oliver whom I mentioned to you\longdash}

\enquote{He's not known here, Wimsey.}

\enquote{No, but he may have been here.}

\enquote{If nobody saw him, he can't have been here.}

\enquote{Well, then, where did General Fentiman go to when he left? And when he did leave? That's what I want to know. Dash it all, Culyer, the old boy's a landmark. We know he came back here on the evening of the  10\textsuperscript{th}---the driver brought him to the door, Rogers saw him come in and two members noticed him in the smoking-room just before seven. I have a certain amount of evidence that he went into the library. And he can't have stayed long, because he had his outdoor things with him. Somebody \textit{must} have seen him leave. It's ridiculous. The servants aren't all blind. I don't like to say it, Culyer, but I can't help thinking that somebody has been bribed to hold his tongue.... Of course, I knew that would annoy you, but how can you account for it? Who's this fellow you say has been hangin' round the kitchen?}

\enquote{I came across him one morning when I'd been down to see about the wine. By the way, there's a case of Margaux come in which I'd like your opinion on some day. The fellow was talking to Babcock, the wine steward, and I asked him pretty sharply what he wanted. He thanked me, and said he had come from the railway to inquire after a packing-case that had gone astray, but Babcock, who is a very decent fellow, told me afterwards that he had been working the pump-handle about old Fentiman, and I gathered he had been pretty liberal with his cash. I thought you were up to your tricks again.}

\enquote{Is the fellow a sahib?}

\enquote{Good God, no. Looks like an attorney's clerk or something. A nasty little tout.}

\enquote{Glad you told me. I shouldn't wonder if he's the snag I'm up against. Probably Oliver coverin' his tracks.}

\enquote{Do you suspect this Oliver of something wrong?}

\enquote{Well\allowbreak---\allowbreak I rather think so. But I'm damned if I know quite what. I think he knows something about old Fentiman that we don't. And of course he knows how he spent the night, and that's what I'm after.}

\enquote{What the devil does it matter how he spent the night? He can't have been very riotous, at his age.}

\enquote{It might throw some light on the time he arrived in the morning, mightn't it?}

\enquote{Oh\allowbreak---\allowbreak Well, all I can say is, I hope to God you'll hurry up and finish with it. This Club's becoming a perfect bear-garden. I'd almost rather have the police in.}

\enquote{Keep hopin'. You may get 'em yet.}

\enquote{You don't mean that, seriously?}

\enquote{I'm never serious. That's what my friends dislike about me. Honestly, I'll try and make as little row as I can. But if Oliver is sending his minions to corrupt your staff and play old harry with my investigations, it's going to make it damned awkward. I wish you'd let me know if the fellow turns up again. I'd like to cast my eye over him.}

\enquote{All right, I will. And do clear out now, there's a good fellow.}

\enquote{I go,} said Wimsey, \enquote{my tail well tucked down between my legs and a flea in each ear. Oh! by the way\longdash}

\enquote{\textit{Well?}} (in an exasperated tone).

\enquote{When did you last see George Fentiman?}

\enquote{Not for donkey's years. Not since it happened.}

\enquote{I thought not. Oh, and by the way\longdash}

\enquote{\textit{Yes?}}

\enquote{Robert Fentiman was actually staying in the Club at the time, wasn't he?}

\enquote{Which time?}

\enquote{The time it happened, you ass.}

\enquote{Yes, he was. But he's living at the old man's place now.}

\enquote{I know, thanks. But I wondered whether\allowbreak---\allowbreak Where does he live when he isn't in town?}

\enquote{Out at Richmond, I think. In rooms, or something.}

\enquote{Oh, does he? Thanks very much. Yes, I really will go. In fact, I've practically gone.}

He went. He never stopped going till he came to Finsbury Park. George was out, and so, of course, was Mrs Fentiman, but the charwoman said she had heard the Captain mention he was going down to Great Portland Street. Wimsey went in pursuit. A couple of hours spent lounging round show-rooms and talking to car-demonstrators, nearly all of whom were, in one manner or another, his dear old pals, resulted in the discovery that George Fentiman was being taken on by the Walmisley-Hubbard outfit for a few weeks to show what he could do.

\enquote{Oh, he'll do you all right,} said Wimsey, \enquote{he's a damn fine driver. Oh, lord, yes! \textit{He's} all right.}

\enquote{He looks a bit nervy,} said the particular dear old pal attached to the Walmisley-Hubbard show. \enquote{Wants bucking up, what? That reminds me. What about a quick one?}

Wimsey submitted to a mild quick one and then wandered back to look at a new type of clutch. He spun out this interesting interview till one of the Walmisley-Hubbard \enquote{shop 'buses} came in with Fentiman at the wheel.

\enquote{Hullo!} said Wimsey, \enquote{trying her out?}

\enquote{Yes. I've got the hang of her all right.}

\enquote{Think you could sell her?} asked the old pal.

\enquote{Oh, yes. Soon learn to show her off. She's a jolly decent 'bus.}

\enquote{That's good. Well, I expect you're about ready for a quick one. How about it, Wimsey?}

They had a quick one together. After this, the dear old pal remembered that he must buzz off because he'd promised to hunt up a customer.

\enquote{You'll turn up to-morrow, then?} he said to George. \enquote{There's an old bird down at Malden wants to have a trial trip. I can't go, so you can have a shot at him. All right?}

\enquote{Perfectly.}

\enquote{Righty-ho! I'll have the 'bus ready for you at eleven. Cheer-most-frightfully-ho! So long.}

\enquote{Little sunbeam about the house, isn't he?} said Wimsey.

\enquote{Rather. Have another?}

\enquote{I was thinking, how about lunch? Come along with me if you have nothing better to do.}

George accepted and put forward the names of one or two restaurants.

\enquote{No,} said Wimsey, \enquote{I've got a fancy to go to Gatti's to-day, if you don't mind.}

\enquote{Not at all, that will do splendidly. I've seen Murbles, by the bye, and he's prepared to deal with the MacStewart man. He thinks he can hold him off till it's all settled up\allowbreak---\allowbreak if it ever \textit{is} settled.}

\enquote{That's good,} said Wimsey, rather absently.

\enquote{And I'm damned glad about this chance of a job,} went on George. \enquote{If it turns out any good, it'll make things a lot easier\allowbreak---\allowbreak in more than one way.}

Wimsey said heartily that he was sure it would, and then relapsed into a silence unusual with him, which lasted all the way to the Strand.

At Gatti's he left George in a corner while he went to have a chat with the head waiter, emerging from the interview with a puzzled expression which aroused even George's curiosity, full as he was of his own concerns.

\enquote{What's up? Isn't there anything you can bear to eat?}

\enquote{It's all right. I was just wondering whether to have \textit{moules marinières} or not.}

\enquote{Good idea.}

Wimsey's face cleared, and for some time they absorbed mussels from the shell with speechless, though not altogether silent, satisfaction.

\enquote{By the way,} said Wimsey, suddenly, \enquote{you never told me that you had seen your grandfather the afternoon before he died.}

George flushed. He was struggling with a particularly elastic mussel, firmly rooted to the shell, and could not answer for a moment.

\enquote{How on earth?---confound it all, Wimsey, are \textit{you} behind this infernal watch that's being kept on me?}

\enquote{Watch?}

\enquote{Yes, I said watch. I call it a damn rotten thing to do. I never thought for a moment you had anything to do with it.}

\enquote{I haven't. Who's keeping a watch on you?}

\enquote{There's a fellow following me about. A spy. I'm always seeing him. I don't know whether he's a detective or what. He looks like a criminal. He came down in the 'bus with me from Finsbury Park this morning. He was after me all day yesterday. He's probably about now. I won't have it. If I catch sight of him again I shall knock his dirty little head off. Why should I be followed and spied on? I haven't done anything. And now \textit{you} begin.}

\enquote{I swear I've nothing to do with anybody following you about. Honestly, I haven't. I wouldn't employ a man, anyway, who'd let a bloke see that he was being followed. No. When I start huntin' you, I shall \textit{be} as silent and stealthy as a gas-leak. What's this incompetent bloodhound like to look at?}

\enquote{Looks like a tout. Small, thin, with his hat pulled down over his eyes and an old rain-coat with the collar turned up. And a very blue chin.}

\enquote{Sounds like a stage detective. He's a silly ass anyway.}

\enquote{He gets on my nerves.}

\enquote{Oh, all right. Next time you see him, punch his head.}

\enquote{But what does he want?}

\enquote{How should I know? What have you been doing?}

\enquote{Nothing, of course. I tell you, Wimsey, I believe there's some sort of conspiracy going on to get me into trouble, or do away with me, or something. I can't stand it. It's simply damnable. Suppose this fellow starts hanging round the Walmisley-Hubbard place. Look nice, won't it, for their salesman to have a 'tec on his heels all the time? Just as I hoped things were coming right\longdash}

\enquote{Bosh!} said Wimsey. \enquote{Don't let yourself get rattled. It's probably all imagination, or just a coincidence.}

\enquote{It isn't. I wouldn't mind betting he's outside in the street now.}

\enquote{Well, then, we'll settle his hash when we get outside. Give him in charge for annoying you. Look here, forget him for a bit. Tell me about the old General. How did he seem, that last time you saw him?}

\enquote{Oh, he seemed fit enough. Crusty, as usual.}

\enquote{Crusty, was he? What about?}

\enquote{Private matters,} said George, sullenly.

Wimsey cursed himself for having started his questions tactlessly. The only thing now was to retrieve the situation as far as possible.

\enquote{I'm not at all sure,} he said, \enquote{that relations shouldn't all be painlessly put away after threescore and ten. Or at any rate segregated. Or have their tongues sterilized, so that they can't be poisonously interferin'.}

\enquote{I wish they were,} growled George. \enquote{The old man\allowbreak---\allowbreak damn it all, I know he was in the Crimea, but he's no idea what a real war's like. He thinks things can go on just as they did half a century ago. I daresay he never did behave as I do. Anyway, I know he never had to go to his wife for his pocket-money, let alone having the inside gassed out of him. Coming preaching to me\allowbreak---\allowbreak and I couldn't say anything, because he was so confoundedly old, you know.}

\enquote{Very trying,} murmured Wimsey, sympathetically.

\enquote{It's all so damned unfair,} said George. \enquote{Do you know,} he burst out, the sense of grievance suddenly overpowering his wounded vanity, \enquote{the old devil actually threatened to cut me out of the miserable little bit of money he had to leave me if I didn't 'reform my domestic behavior.' That's the way he talked. Just as if I was carrying on with another woman or something. I know I did have an awful row with Sheila one day, but of course I didn't mean half I said. She knows that, but the old man took it all seriously.}

\enquote{Half a moment,} broke in Wimsey, \enquote{did he say all this to you in the taxi that day?}

\enquote{Yes, he did. A long lecture, all about the purity and courage of a good woman, driving round and round Regent's Park. I had to promise to turn over a new leaf and all that. Like being back at one's prep. school.}

\enquote{But didn't he mention anything about the money Lady Dormer was leaving to him?}

\enquote{Not a word. I don't suppose he knew about it.}

\enquote{I think he did. He'd just come from seeing her, you know, and I've a very good idea she explained matters to him then.}

\enquote{Did she? Well, that rather explains it. I thought he was being very pompous and stiff about it. He said what a responsibility money was, you know, and how he would like to feel that anything he left to me was being properly used and all that. And he rubbed it in about my not having been able to make good for myself\allowbreak---\allowbreak that was what got my goat\allowbreak---\allowbreak and about Sheila. Said I ought to appreciate a good woman's love more, my boy, and cherish her and so on. As if I needed him to tell me that. But of course, if he knew he was in the running for this half-million, it makes rather a difference. By jove, yes! I expect he would feel a bit anxious at the idea of leaving it all to a fellow he looked on as a waster.}

\enquote{I wonder he didn't mention it.}

\enquote{You didn't know grandfather. I bet he was thinking over in his mind whether it wouldn't be better to give my share to Sheila, and he was sounding me, to see what sort of disposition I'd got. The old fox! Well, I did my best to put myself in a good light, of course, because just at the moment I didn't want to lose my chance of his two thousand. But I don't think he found me satisfactory. I say,} went on George, with rather a sheepish laugh, \enquote{perhaps it's just as well he popped off when he did. He might have cut me off with a shilling, eh?}

\enquote{Your brother would have seen you through in any case.}

\enquote{I suppose he would. Robert's quite a decent sort, really, though he does get on one's nerves so.}

\enquote{Does he?}

\enquote{He's so thick-skinned; the regular unimaginative Briton. I believe Robert would cheerfully go through another five years of war and think it all a very good rag. Robert was proverbial, you know, for never turning a hair. I remember Robert, at that ghastly hole at Carency, where the whole ground was rotten with corpses\allowbreak---\allowbreak ugh!---potting those swollen great rats for a penny a time, and laughing at them. Rats. Alive and putrid with what they'd been feeding on. Oh, yes. Robert was thought a damn good soldier.}

\enquote{Very fortunate for him,} said Wimsey.

\enquote{Yes. He's the same sort as grandfather. They liked each other. Still, grandfather was very decent about me. A beast, as the school-boy said, but a just beast. And Sheila was a great favorite of his.}

\enquote{Nobody could help liking her,} said Wimsey, politely.

Lunch ended on a more cheerful note than it had begun. As they came out into the street, however, George Fentiman glanced round uneasily. A small man in a buttoned-up overcoat and with a soft hat pulled down over his eyes, was gazing into the window of a shop near at hand.

George strode up to him.

\enquote{Look here, you!} he said. \enquote{What the devil do you mean by following me about? You clear off, d'you hear?}

\enquote{I think you are mistaken, sir,} said the man, quietly enough. \enquote{I have never seen you before.}

\enquote{Haven't you, by jove? Well, \textit{I've} seen \textit{you} hanging about, and if you do it any more, I'll give you something to remember me by. D'you hear?}

\enquote{Hullo!} said Wimsey, who had stopped to speak to the commissionaire, \enquote{what's up?---Here, you, wait a moment!}

But at sight of Wimsey, the man had slipped like an eel among the roaring Strand traffic, and was lost to view.

George Fentiman turned to his companion triumphantly.

\enquote{Did you see that? That lousy little beggar! Made off like a shot when I threatened him. That's the fellow who's been dogging me about for three days.}

\enquote{I'm sorry,} said Wimsey, \enquote{but it was not your prowess, Fentiman. It was my awful aspect that drove him away. What is it about me? Have I a front like Jove to threaten and command? Or am I wearing a repulsive tie?}

\enquote{He's gone, anyway.}

\enquote{I wish I'd had a better squint at him. Because I've got a sort of idea that I've seen those lovely features before, and not so long ago, either. Was this the face that launched a thousand ships? No, I don't think it was that.}

\enquote{All I can say is,} said George, \enquote{that if I see him again, I'll put such a face on him that his mother won't know him.}

\enquote{Don't do that. You might destroy a clue. I\allowbreak---\allowbreak wait a minute\allowbreak---\allowbreak I've got an idea. I believe it must be the same man who's been haunting the Bellona and asking questions. Oh, hades! and we've let him go. And I'd put him down in my mind as Oliver's minion. If ever you see him again, Fentiman, freeze on to him like grim death. I want to talk to him.}