%!TeX root=../bellonatop.tex
\chapter{Lord Peter Turns A Trick}
\lettrine[lines=4]{D}{etective}-Inspector Parker came to dinner encircled in a comfortable little halo of glory. The Crate Mystery had turned out well and the Chief Commissioner had used expressions suggestive of promotion in the immediate future. Parker did justice to his meal and, when the party had adjourned to the library, gave his attention to Lord Peter's account of the Bellona affair with the cheerful appreciation of a connoisseur sampling a vintage port. Mr Murbles, on the other hand, grew more and more depressed as the story was unfolded.

\enquote{And what do you think of it?} inquired Wimsey.

Parker opened his mouth to reply, but Mr Murbles was beforehand with him.

\enquote{This Oliver appears to be a very elusive person,} said he.

\enquote{Isn't he?} agreed Wimsey, dryly. \enquote{Almost as elusive as the famous Mrs Harris. Would it altogether surprise you to learn that when I asked a few discreet questions at Gatti's, I discovered not only that nobody there had the slightest recollection of Oliver, but that no inquiries about him had ever been made by Major Fentiman?}

\enquote{Oh, dear me!} said Mr Murbles.

\enquote{You forced Fentiman's hand very ingeniously by sending him down with your private sleuth to Charing Cross,} remarked Parker, approvingly.

\enquote{Well, you see, I had a feeling that unless we did something pretty definite, Oliver would keep vanishing and reappearing like the Cheshire Cat, whenever our investigations seemed to be taking an awkward turn.}

\enquote{You are intimating, if I understand you rightly,} said Mr Murbles, \enquote{that this Oliver has no real existence.}

\enquote{Oliver was the carrot on the donkey's nose,} said Peter, \enquote{my noble self being cast for the part of the donkey. Not caring for the rôle, I concocted a carrot of my own, in the person of Sleuths Incorporated. No sooner did my trusting sleuth depart to his lunch than, lo and behold! the hue and cry is off again after Oliver. Away goes friend Fentiman\allowbreak---\allowbreak and away goes Sleuth Number Two, who was there all the time, neatly camouflaged, to keep his eye on Fentiman. Why Fentiman should have gone to the length of assaulting a perfect stranger and accuse him of being Oliver, I don't know. I fancy his passion for thoroughness made him over-reach himself a bit there.}

\enquote{But what exactly has Major Fentiman been doing?} asked Mr Murbles. \enquote{This is a very painful business, Lord Peter. It distresses me beyond words. Do you suspect him of\allowbreak---\allowbreak er---?}

\enquote{Well,} said Wimsey, \enquote{I knew \textit{something} odd had happened, you know, as soon as I saw the General's body\allowbreak---\allowbreak when I pulled the \textit{Morning Post} away so easily from his hands. If he had really died clutching it, the rigor would have made his clutch so tight that one would have had to pry the fingers open to release it. And then, that knee-joint!}

\enquote{I didn't quite follow about that.}

\enquote{Well, you know that when a man dies, rigor begins to set in after a period of some hours, varying according to the cause of death, temperature of the room and a lot of other conditions. It starts in the face and jaw and extends gradually over the body. Usually it lasts about twenty-four hours and then passes off again in the same order in which it started. But if, during the period of rigidity, you loosen one of the joints by main force, then it doesn't stiffen again, but remains loose. Which is why, in a hospital, if the nurses have carelessly let a patient die and stiffen with his knees up, they call in the largest and fattest person on the staff to sit on the corpse's knees and break the joints loose again.}

Mr Murbles shuddered distastefully.

\enquote{So that, taking the loose knee-joint and the general condition of the body together, it was obvious from the start that somebody had been tampering with the General. Penberthy knew that too, of course, only, being a doctor, he wasn't going to make any indiscreet uproar if he could avoid it. It doesn't pay, you know.}

\enquote{I suppose not.}

\enquote{Well, then, you came round to me, sir, and insisted on making the uproar. I warned you, you know, to let sleeping dogs lie.}

\enquote{I wish you had spoken more openly.}

\enquote{If I had, would you have cared to hush the matter up?}

\enquote{Well, well,} said Mr Murbles, polishing his eye-glasses.

\enquote{Just so. The next step was to try and find out what had actually happened to the General on the night of the  10\textsuperscript{th}, and morning of the  11\textsuperscript{th}. And the moment I got round to his flat I was faced with two entirely contradictory pieces of evidence. First, there was the story about Oliver, which appeared more or less remarkable upon the face of it. And secondly, there was Woodward's evidence about the clothes.}

\enquote{What about them?}

\enquote{I asked him, you remember, whether anything at all had been removed from the clothes after he had fetched them away from the cloak-room at the Bellona, and he said, nothing. His memory as to other points seemed pretty reliable, and I felt sure that he was honest and straightforward. So I was forced to the conclusion that, wherever the General had spent the night, he had certainly never set foot in the street the next morning.}

\enquote{Why?} asked Mr Murbles. \enquote{What did you expect to find on the clothes?}

\enquote{My dear sir, consider what day it was. November  11\textsuperscript{th}. Is it conceivable that, if the old man had been walking in the streets as a free agent on Armistice Day, he would have gone into the Club without his Flanders poppy? A patriotic, military old bird like that? It was really unthinkable.}

\enquote{Then where was he? And how did he get into the Club? He was there, you know.}

\enquote{True; he \textit{was} there\allowbreak---\allowbreak in a state of advanced rigor. In fact, according to Penberthy's account, which, by the way, I had checked by the woman who laid out the body later, the rigor was even then beginning to pass off. Making every possible allowance for the warmth of the room and so on, he must have been dead long before ten in the morning, which was his usual time for going to the Club.}

\enquote{But, my dear lad, bless my soul, that's impossible. He couldn't have been carried in there dead. Somebody would have noticed it.}

\enquote{So they would. And the odd thing is that nobody ever saw him arrive at all. What is more, nobody saw him leave for the last time on the previous evening. General Fentiman\allowbreak---\allowbreak one of the best-known figures in the Club! And he seems to have become suddenly invisible. That won't do, you know.}

\enquote{What is your idea, then? That he slept the night in the Club?}

\enquote{I think he slept a very peaceful and untroubled sleep that night\allowbreak---\allowbreak in the Club.}

\enquote{You shock me inexpressibly,} said Mr Murbles. \enquote{I understand you to suggest that he died\longdash}

\enquote{Some time the previous evening. Yes.}

\enquote{But he couldn't have sat there all night in the smoking-room. The servants would have been bound to\allowbreak---\allowbreak er---notice him.}

\enquote{Of course. But it was to somebody's interest to see that they didn't notice. Somebody who wanted it thought that he hadn't died till the following day, after the death of Lady Dormer.}

\enquote{Robert Fentiman.}

\enquote{Precisely.}

\enquote{But how did Robert know about Lady Dormer?}

\enquote{Ah! That is a point I'm not altogether happy about. George had an interview with General Fentiman after the old man's visit to his sister. George denies that the General mentioned anything to him about the will, but then, if George was in the plot he naturally would deny it. I am rather concerned about George.}

\enquote{What had he to gain?}

\enquote{Well, if George's information was going to make a difference of half a million to Robert, he would naturally expect to be given a share of the boodle, don't you think?}

Mr Murbles groaned.

\enquote{Look here,} broke in Parker, \enquote{this is a very pretty theory, Peter, but, allowing that the General died, as you say, on the evening of the tenth, where was the body? As Mr Murbles says, it would have been a trifle noticeable if left about.}

\enquote{No, no,} said Mr Murbles, seized with an idea. \enquote{Repellent as the whole notion is to me, I see no difficulty about that. Robert Fentiman was at that time living in the Club. No doubt the General died in Robert's bedroom and was concealed there till the next morning!}

Wimsey shook his head. \enquote{That won't work. I think the General's hat and coat and things were in Robert's bedroom, but the corpse couldn't have been. Think, sir. Here is a photograph of the entrance-hall, with the big staircase running up in full view of the front door and the desk and the bar-entrance. Would you risk carrying a corpse downstairs in the middle of the morning, with servants and members passing in and out continually? And the service stairs would be even worse. They are right round the other side of the building, with continual kitchen traffic going on all the time. No. The body wasn't in Robert's bedroom.}

\enquote{Where, then?}

\enquote{Yes, where? After all, Peter, we've got to make this story hold water.}

Wimsey spread the rest of the photographs out upon the table.

\enquote{Look for yourselves,} he said. \enquote{Here is the end bay of the library, where the General was sitting making notes about the money he was to inherit. A very nice, retired spot, invisible from the doorway, supplied with ink, blotter, writing-paper and every modern convenience, including the works of Charles Dickens elegantly bound in morocco. Here is a shot of the library taken from the smoking-room, clean through the ante-room and down the gangway\allowbreak---\allowbreak again a tribute to the convenience of the Bellona Club. Observe how handily the telephone cabinet is situated, in case\longdash}

\enquote{The telephone cabinet?}

\enquote{Which, you will remember, was so annoyingly labeled \enquote{Out of Order} when Wetheridge wanted to telephone. I can't find anybody who remembers putting up that notice, by the way.}

\enquote{Good God, Wimsey. Impossible. Think of the risk.}

\enquote{What risk? If anybody opened the door, there was old General Fentiman, who had gone in, not seeing the notice, and died of fury at not being able to get his call. Agitation acting on a weak heart and all that. Not \textit{very} risky, really. Unless somebody was to think to inquire about the notice, and probably it wouldn't occur to any one in the excitement of the moment.}

\enquote{You're an ingenious beast, Wimsey.}

\enquote{Aren't I? But we can prove it. We're going down to the Bellona Club to prove it now. Half-past eleven. A nice, quiet time. Shall I tell you what we are going to find inside that cabinet?}

\enquote{Finger-prints?} suggested Mr Murbles, eagerly.

\enquote{Afraid that's too much to hope for after all this time. What do you say, Charles?}

\enquote{I say we shall find a long scratch on the paint,} said Parker, \enquote{where the foot of the corpse rested and stiffened in that position.}

\enquote{Holed it in one, Charles. And that, you see, was when the leg had to be bent with violence in order to drag the corpse out.}

\enquote{And as the body was in a sitting position,} pursued Parker, \enquote{we shall, of course, find a seat inside the cabinet.}

\enquote{Yes, and, with luck, we \textit{may} find a projecting nail or something which caught the General's trouser-leg when the body was removed.}

\enquote{And possibly a bit of carpet.}

\enquote{To match the fragment of thread I got off the corpse's right boot? I hope so.}

\enquote{Bless my soul,} said Mr Murbles. \enquote{Let us go at once. Really, this is most exciting. That is, I am profoundly grieved. I hope it is not as you say.}

They hastened downstairs and stood for a few moments waiting for a taxi to pass. Suddenly Wimsey made a dive into a dark corner by the porch. There was a scuffle, and out into the light came a small man, heavily muffled in an overcoat, with his hat thrust down to his eyebrows in the manner of a stage detective. Wimsey unbonneted him with the air of a conjuror producing a rabbit from a hat.

\enquote{So it's you, is it? I thought I knew your face. What the devil do you mean by following people about like this?}

The man ceased struggling and glanced sharply up at him with a pair of dark, beady eyes.

\enquote{Do you think it wise, my lord, to use violence?}

\enquote{Who is it?} asked Parker.

\enquote{Pritchard's clerk. He's been hanging round George Fentiman for days. Now he's hanging round me. He's probably the fellow that's been hanging round the Bellona. If you go on like this, my man, you'll find yourself hanging somewhere else one of these days. Now, see here. Do you want me to give you in charge?}

\enquote{That is entirely as your lordship pleases,} said the clerk, with a cunning sneer. \enquote{There is a policeman just round the corner, if you wish to attract publicity.}

Wimsey looked at him for a moment, and then began to laugh.

\enquote{When did you last see Mr Pritchard? Come on, out with it! Yesterday? This morning? Have you seen him since lunch-time?}

A shadow of indecision crossed the man's face.

\enquote{You haven't? I'm sure you haven't! Have you?}

\enquote{And why not, my lord?}

\enquote{You go back to Mr Pritchard,} said Wimsey, impressively, and shaking his captive gently by the coat-collar to add force to his words, \enquote{and if he doesn't countermand your instructions and call you off this sleuthing business (which, by the way, you do very amateurishly), I'll give you a fiver. See? Now, hop it. I know where to find you and you know where to find me. Good-night and may Morpheus hover over your couch and bless your slumbers. Here's our taxi.}

