%!TeX root=../bellonatop.tex
\chapter{Spades are Trumps}
\lettrine[lines=4]{I}{t} was close on one o'clock when the three men emerged from the solemn portals of the Bellona Club. Mr Murbles was very much subdued. Wimsey and Parker displayed the sober elation of men whose calculations have proved satisfactory. They had found the scratches. They had found the nail in the seat of the chair. They had even found the carpet. Moreover, they had found the origin of Oliver. Reconstructing the crime, they had sat in the end bay of the library, as Robert Fentiman might have sat, casting his eyes around him while he considered how he could best hide and cover up this extremely inopportune decease. They had noticed how the gilt lettering on the back of a volume caught the gleam from the shaded reading lamp. \textit{Oliver Twist.} The name, not consciously noted at the time, had yet suggested itself an hour or so later to Fentiman, when, calling up from Charing Cross, he had been obliged to invent a surname on the spur of the moment.

And, finally, placing the light, spare form of the unwilling Mr Murbles in the telephone cabinet, Parker had demonstrated that a fairly tall and strong man could have extricated the body from the box, carried it into the smoking-room and arranged it in the arm-chair by the fire, all in something under four minutes.

Mr Murbles made one last effort on behalf of his client.

»There were people in the smoking-room all morning, my dear Lord Peter. If it were as you suggest, how could Fentiman have made sure of four, or even three minutes secure from observation while he brought the body in?«

»Were people there \textit{all} morning, sir? Are you sure? Wasn't there just one period when one could be certain that everybody would be either out in the street or upstairs on the big balcony that runs along in front of the first-floor windows, looking out—and listening? It was Armistice Day, remember.«

Mr Murbles was horror-struck.

»The two-minutes' silence?—God bless my soul! How abominable! How—how blasphemous! Really, I cannot find words. This is the most disgraceful thing I ever heard of. At the moment when all our thoughts should be concentrated on the brave fellows who laid down their lives for us—to be engaged in perpetrating a fraud—an irreverent crime\longdash«

»Half a million is a good bit of money,« said Parker, thoughtfully.

»Horrible!« said Mr Murbles.

»Meanwhile,« said Wimsey, »what do you propose to do about it?«

»Do?« spluttered the old solicitor, indignantly. »Do?—Robert Fentiman will have to confess to this disgraceful plot immediately. Bless my soul! To think that I should be mixed up in a thing like this! He will have to find another man of business in future. We shall have to explain matters to Pritchard and apologize. I really hardly know how to tell him such a thing.«

»I rather gather he suspects a good deal of it already,« said Parker, mildly. »Else why should he have sent that clerk of his to spy on you and George Fentiman? I daresay he has been keeping tabs on Robert, too.«

»I shouldn't wonder,« said Wimsey. »He certainly treated me like a conspirator when I called on him. The only thing that puzzles me now is why he should have suddenly offered to compromise.«

»Probably Miss Dorland lost patience, or they despaired of proving anything,« said Parker. »While Robert stuck to that Oliver story, it would be very hard to prove anything.«

»Exactly,« said Wimsey. »That is why I had to hang on so long, and press Robert so hard about it. I might suspect Oliver to be non-existent, but one can't prove a negative.«

»And suppose he still sticks to the story now?«

»Oh! I think we can put the wind up him all right,« said Wimsey. »By the time we've displayed our proofs and told him exactly what he was doing with himself on November  10\textsuperscript{th} and  11\textsuperscript{th}, he'll have no more spirit in him than the Queen of Sheba.«

»It must be done at once,« said Mr Murbles. »And of course this exhumation business will have to be stopped. I will go round and see Robert Fentiman to-morrow—this morning, that is.«

»Better tell him to trot round to your place,« said Wimsey. »I'll bring all the evidence round there, and I'll have the varnish on the cabinet analysed and shown to correspond with the sample I took from the General's boots. Make it for two o'clock, and then we can all go round and interview Pritchard afterwards.«

Parker supported this suggestion. Mr Murbles was so wrought up that he would gladly have rushed away to confront Robert Fentiman immediately. It being, however, pointed out to him that Fentiman was in Richmond, that an alarm at this ungodly hour might drive him to do something desperate, and also that all three investigators needed repose, the old gentleman gave way and permitted himself to be taken home to Staple Inn.

Wimsey went round to Parker's flat in Great Ormond Street to have a drink before turning in, and the session was prolonged till the small hours had begun to grow into big hours and the early workman was abroad.

Lord Peter, having set the springe for his woodcock, slept the sleep of the just until close upon eleven o'clock the next morning. He was aroused by voices without, and presently his bedroom door was flung open to admit Mr Murbles, of all people, in a high state of agitation, followed by Bunter, protesting.

»Hullo, sir!« said his lordship, much amazed. »What's up?«

»We have been outwitted,« cried Mr Murbles, waving his umbrella, »we have been forestalled! We should have gone to Major Fentiman last night. I wished to do so, but permitted myself to be persuaded against my better judgment. It will be a lesson to me.«

He sat down, panting a little.

»My dear Mr Murbles,« said Wimsey, pleasantly, »your method of recalling one to the dull business of the day is as delightful as it is unexpected. Anything better calculated to dispel that sluggish feeling I can scarcely imagine. But pardon me—you are somewhat out of breath. Bunter! a whisky-and-soda for Mr Murbles.«

»Indeed no!« ejaculated the solicitor, hurriedly. »I couldn't touch it. Lord Peter\longdash«

»A glass of sherry?« suggested his lordship, helpfully.

»No, no—nothing, thanks. A shocking thing has occurred. We are left\longdash«

»Better and better. A shock is exactly what I feel to need. My \textit{café-au-lait}, Bunter—and you may turn the bath on. Now, sir—out with it. I am fortified against anything.«

»Robert Fentiman,« announced Mr Murbles, impressively, »has disappeared.«

He thumped his umbrella.

»Good God!« said Wimsey.

»He has gone,« repeated the solicitor. \enquote{At ten o'clock this morning I attended in person at his rooms in Richmond—in \textit{person}—in order to bring him the more effectually to a sense of his situation. I rang the bell. I asked for him. The maid told me he had left the night before. I asked where he had gone. She said she did not know. He had taken a suit-case with him. I interviewed the landlady. She told me that Major Fentiman had received an urgent message during the evening and had informed her that he was called away. He had not mentioned where he was going nor how soon he would return. I left a note addressed to him, and hastened back to Dover Street. The flat there was shut up and untenanted. The man Woodward was nowhere to be found. I then came immediately to you. And I find you\longdash}

Mr Murbles waved an expressive hand at Wimsey, who was just taking from Bunter's hands a chaste silver tray, containing a Queen Anne coffee-pot and milk-jug, a plate of buttered toast, a delicate china coffee-cup and a small pile of correspondence.

»So you do,« said Wimsey. »A depraved sight, I am afraid. H'm! It looks very much as though Robert had got wind of trouble and didn't like to face the music.«

He sipped his \textit{café-au-lait} delicately, his rather bird-like face cocked sideways. »But why worry? He can't have got very far.«

»He may have gone abroad.«

»Possibly. All the better. The other party won't want to take proceedings against him over there. Too much bother—however spiteful they may feel. Hallo! Here's a writing I seem to recognize. Yes. It is my sleuth from Sleuths Incorporated. Wonder what \textit{he} wants. I told him to go home and send the bill in.—Whew!«

»What is it?«

»This is the bloke who chased Fentiman to Southampton. Not the one who went on to Venice after the innocent Mr Postlethwaite; the other. He's writing from Paris. He says:

\begin{quotation}
\noindent \textsc{My lord,}

While making a few inquiries at Southampton pursuant to the investigation with which your lordship entrusted me 
\end{quotation}

(what marvelous English those fellows write, don't they? Nearly as good as the regular police), 

\begin{quotation}I came, almost accidentally\end{quotation} 

(»almost« is good) 

\begin{quotation}
	upon the trifling clue which led me to suppose that the party whom I was instructed by your lordship to keep under observation had been less in error than we were led to suppose, and had merely been misled by a confusion of identity natural in a gentleman not scientifically instructed in the art of following up suspected persons. In short
\end{quotation} 

(thank God for that!) 

\begin{quotation}
in short, I believe that I have myself come upon the track of O.
\end{quotation} 

(These fellows are amazingly cautious; he might just as well write Oliver and have done with it), 

\begin{quotation}
and have followed the individual in question to this place. I have telegraphed to the gentleman your friend
\end{quotation} 

(I presume that means Fentiman) 

\begin{quotation}to join me immediately with a view to identifying the party. I will of course duly acquaint your lordship with any further developments in the case, and believe me\end{quotation}—and so forth.«

»Well, I'm damned!«

»The man must be mistaken, Lord Peter.«

»I jolly well hope so,« said Wimsey, rather red in the face. »It'll be a bit galling to have Oliver turning up, just when we've proved so conclusively that he doesn't exist. Paris! I suppose he means that Fentiman spotted the right man at Waterloo and lost him on the train or in the rush for the boat. And got hold of Postlethwaite instead. Funny. Meanwhile, Fentiman's off to France. Probably taken the 10.30 boat from Folkestone. I don't know how we're to get hold of him.«

»How very extraordinary,« said Mr Murbles. »Where does that detective person write from?«

»Just »Paris,«« said Wimsey. »Bad paper and worse ink. And a small stain of \textit{vin ordinaire}. Probably written in some little café yesterday afternoon. Not much hope there. But he's certain to let me know where they get to.«

»We must send some one to Paris immediately in search of them,« declared Mr Murbles.

»Why?«

»To fetch Major Fentiman back.«

»Yes, but look here, sir. If there really is an Oliver after all, it rather upsets our calculations, doesn't it?«

Mr Murbles considered this.

»I cannot see that it affects our conclusions as to the hour of the General's death,« he said.

»Perhaps not, but it considerably alters our position with regard to Robert Fentiman.«

»Ye—es. Yes, that is so. Though,« said Mr Murbles, severely, »I still consider that the story requires close investigation.«

»Agreed. Well, look here. I'll run over to Paris myself and see what I can do. And you had better temporize with Pritchard. Tell him you think there will be no need to compromise and that we hope soon to be in possession of the precise facts. That'll show him we don't mean to have any truck with anythin' fishy. I'll learn him to cast nasturtiums at me!«

»And—oh, dear! there's another thing. We must try and get hold of Major Fentiman to stop this exhumation.«

»Oh, lord!—Yes. That's a bit awkward. Can't you stop it by yourself?«

»I hardly think I can. Major Fentiman has applied for it as executor, and I cannot quite see what I can do in the matter without his signature. The Home Office would hardly\longdash«

»Yes. I quite see that you can't mess about with the Home Office. Well, though, that's easy. Robert never was keen on the resurrection idea. Once we've got his address, he'll be only too happy to send you a chit to call the whole thing off. You leave it to me. After all, even if we don't find Robert for a few days and the old boy has to be dug up after all, it won't make things any worse. Will it?«

Mr Murbles agreed, dubiously.

»Then I'll pull the old carcass together,« said Wimsey, brightly, flinging the bedclothes aside and leaping to his feet, »and toddle off to the City of Light. Will you excuse me for a few moments, sir? The bath awaits me. Bunter, put a few things into a suit-case and be ready to come with me to Paris.«

On second thoughts, Wimsey waited till the next day, hoping, as he explained, to hear from the detective. As nothing reached him, however, he started in pursuit, instructing the head office of Sleuths Incorporated to wire any information received to him at the Hôtel Meurice. The next news that arrived from him was a card to Mr Murbles written on a P.L.M. express, which said simply, \textsc{Quarry gone on to Rome. Hard on trail. P.W.} The next day came a foreign telegram: \textsc{Making for Sicily. Faint but pursuing. P.W.}

In reply to this, Mr Murbles wired: \textsc{Exhumation fixed for day after to-morrow. Please make haste.}

To which Wimsey replied: \textsc{Returning for exhumation. P.W.}

He returned alone.

»Where is Robert Fentiman?« demanded Mr Murbles, agitatedly.

Wimsey, his hair matted damply and his face white from traveling day and night, grinned feebly.

»I rather fancy,« he said, in a wan voice, »that Oliver is at his old tricks again.«

»Again?« cried Mr Murbles, aghast. »But the letter from your detective was genuine.«

»Oh, yes—that was genuine enough. But even detectives can be bribed. Anyhow, we haven't seen hide or hair of our friends. They've been always a little ahead. Like the Holy Grail, you know. Fainter by day but always in the night blood-red, and sliding down the blackened marsh, blood-red—perfectly bloody, in fact. Well, here we are. When does the ceremony take place? Quietly, I take it? No flowers?«

The »ceremony« took place, as such ceremonies do, under the discreet cover of darkness. George Fentiman, who, in Robert's absence, attended to represent the family, was nervous and depressed. It is trying enough to go to the funeral of one's friends and relations, amid the grotesque pomps of glass hearses, and black horses, and wreaths, and appropriate hymns »beautifully« rendered by well-paid choristers, but, as George irritably remarked, the people who grumble over funerals don't realize their luck. However depressing the thud of earth on the coffin-lid may be, it is music compared to the rattle of gravel and thump of spades which herald a premature and unreverend resurrection, enveloped in clouds of formalin and without benefit of clergy.

Dr Penberthy also appeared abstracted and anxious to get the business over. He made the journey to the cemetrey ensconced in the farthest corner of the big limousine, and discussed thyroid abnormalities with Dr Horner, Sir James Lubbock's assistant, who had come to help with the autopsy. Mr Murbles was, naturally, steeped in gloom. Wimsey devoted himself to his accumulated correspondence, out of which one letter only had any bearing on the Fentiman case. It was from Marjorie Phelps, and ran:

\begin{quote}If you want to meet Ann Dorland, would you care to come along to a »do« at the Rushworth's Wednesday week? It will be very deadly, because Naomi Rushworth's new young man is going to read a paper on ductless glands which nobody knows anything about. However, it appears that ductless glands will be »news« in next to no time—ever so much more up-to-date than vitamins—so the Rushworths are all over glands—in the social sense, I mean. Ann D. is certain to be there, because as I told you, she is taking to this healthy bodies for all stunt, or whatever it is, so you'd better come. It will be company for me!—and I've got to go, anyway, as I'm supposed to be a friend of Naomi's. Besides, they say that if one paints or sculps or models, one ought to know all about glands, because of the way they enlarge your jaw and alter your face, or something. Do come, because if you don't I shall be fastened on by some deadly bore or other—and I shall have to hear all Naomi's raptures about the man, which will be too awful.
\end{quote}

Wimsey made a note to be present at this enlivening party, and looking round, saw that they were arriving at the Necropolis—so vast, so glittering with crystal-globed wreaths, so towering with sky-scraping monuments, that no lesser name would serve it. At the gate they were met by Mr Pritchard in person (acidulated in his manner and elaborately polite to Mr Murbles), and by the Home Office representative (suave and bland and disposed to see reporters lurking behind every tombstone.) A third person, coming up, proved to be an official from the Cemetrey Company, who took charge of the party and guided them along the neat graveled walks to where digging operations were already in process.

The coffin, being at length produced and identified by its brass plate, was then carefully borne to a small outbuilding close at hand, which appeared to be a potting-shed in ordinary life, converted by a board and a couple of trestles into a temporary mortuary. Here a slight halt and confusion was caused by the doctors, demanding in aggressively cheerful and matter-of-fact tones more light and space to work in. The coffin was placed on a bench; somebody produced a mackintosh sheet and spread it on the trestle table; lamps were brought and suitably grouped. After which, the workmen advanced, a little reluctantly, to unscrew the coffin-lid, preceded by Dr Penberthy, scattering formalin from a spray, rather like an infernal thurifer at some particularly unwholesome sacrifice.

»Ah! very nice indeed,« said Dr Horner, appreciatively, as the corpse was disengaged from the coffin and transferred to the table. »Excellent. Not much difficulty over this job. That's the best of getting on to it at once. How long has he been buried, did you say? Three or four weeks? He doesn't look it. Will you make the autopsy or shall I? Just as you like. Very well. Where did I put my bag? Ah! thank you, Mr.—er—er\longdash« (An unpleasantly occupied pause during which George Fentiman escaped, murmuring that he thought he'd have a smoke outside). »Undoubted heart trouble, of course, I don't see any unusual appearances, do you?... I suppose we'd better secure the stomach as it stands \textellipsis  pass me the gut, would you? Thanks. D'you mind holding while I get this ligature on? Ta.« (Snip, snip.) »The jars are just behind you. Thanks. Look out! You'll have it over. Ha! ha! that was a near thing. Reminds me of Palmer, you know—and Cook's stomach—always think that a very funny story, ha, ha!—I won't take all the liver—just a sample—it's only a matter of form—and sections of the rest—yes—better have a look at the brain while we are about it, I suppose. Have you got the large saw?«

»How callous these medical men seem,« murmured Mr Murbles.

»It's nothing to them,« said Wimsey. »Horner does this kind of job several times a week.«

»Yes, but he need not be so noisy. Dr Penberthy behaves with decorum.«

»Penberthy runs a practise,« said Wimsey with a faint grin. »He has to exercise a little restraint over himself. Besides, he knew old Fentiman, and Horner didn't.«

At length the relevant portions of General Fentiman's anatomy having been collected into suitable jars and bottles, the body was returned to the coffin and screwed down. Penberthy came across to Wimsey and took his arm.

»We ought to be able to get a pretty good idea of what you want to know,« he said. »Decomposition is very little advanced, owing to an exceptionally well-made coffin. By the way« (he dropped his voice) »that leg, you know—did it ever occur to you—or rather, did you ever discover any explanation of that?«

»I \textit{did} have an idea about it,« admitted Wimsey, »but I don't yet know whether it was the right one. I shall probably know for certain in a day or two.«

»You think the body was interfered with?« said Penberthy, looking him steadily in the face.

»Yes, and so do you,« replied Wimsey, returning the gaze.

»I've had my suspicions all the time, of course. I told you so, you know. I wonder whether—you don't think I was wrong to give the certificate, do you?«

»Not unless you suspected anything wrong with the death itself,« said Wimsey. »Have you and Horner noticed anything queer?«

»No. But—oh, well! having patients dug up always makes me worried, you know. It's easy to make a mistake and one looks an awful fool in court. I'd hate being made to look a fool just at present,« added the doctor with a nervous laugh. »I'm thinking of—great Scott, man! how you startled me!«

Dr Horner had brought a large, bony hand down on his shoulder. He was a red-faced, jovial man, and he smiled as he held up his bag before them.

»All packed up and ready,« he announced. »Got to be getting back now, aha! Got to be getting back.«

»Have the witnesses signed the labels?« asked Penberthy, rather shortly.

»Yes, yes, quite all right. Both the solicitor johnnies, so they can't quarrel about \textit{that} in the witness-box,« replied Horner. »Come along, please—I've got to get off.«

They found George Fentiman outside, seated on a tombstone, and sucking at an empty pipe.

»Is it all over?«

»Yes.«

»Have they found anything?«

»Haven't looked yet,« broke in Horner, genially. »Not at the part which interests \textit{you}, that is. Leave that for my colleague Lubbock, you know. Soon give you an answer—say, in a week's time.«

George passed his handkerchief over his forehead, which was beaded with little drops of sweat.

»I don't like it,« he said. »But I suppose it had to be done. What was that? I thought—I'd swear I saw something moving over there.«

»A cat, probably,« said Penberthy, »there's nothing to be alarmed at.«

»No,« said George, »but sitting about here, one—fancies things.« He hunched his shoulders, squinting round at them with the whites of his eyeballs showing.

»Things,« he said, »people—going to and fro \textellipsis  and walking up and down. Following one.«