%!TeX root=../bellonatop.tex
\chapter{Grand Slam in Spades}

\lettrine[lines=4]{O}{n} the seventh morning after the exhumation—which happen\-ed to be a Tuesday—Lord~Peter walked briskly into Mr~Murb\-les' chambers in Staple Inn, with Detective-Inspector Parker at his heels.

\zz
»Good morning,« said Mr~Murbles, surprised.

»Good morning,« said Wimsey. »Hark! hark! the lark at heaven's gate sings. He is coming, my own, my sweet, were it ever so airy a tread. He will be here in a quarter of an hour.«

»Who will?« demanded Mr~Murbles, somewhat severely.

»Robert Fentiman.«

Mr~Murbles gave a little ejaculation of surprise.

»I had almost given up hope in that direction,« he said.

»So had I. I said to myself, he is not lost but gone before. And it was so. Charles, we will lay out the \textit{pièces de conviction} on the table. The boots. The photographs. The microscopic slides showing the various specimens. The paper of notes from the library. The outer garments of the deceased. Just so. And \textit{Oliver Twist}. Beautiful. Now, as Sherlock Holmes says, we shall look imposing enough to strike terror into the guilty breast, though armed in triple steel.«

»Did Fentiman return of his own accord?«

»Not altogether. He was, if I may so express myself, led. Almost, in fact, led on. O'er moor and fen, o'er crag and torrent till, don't you know. What is that noise in the outer room? It is, it is the cannon's opening roar.«

It was, indeed, the voice of Robert Fentiman, not in the best of tempers. In a few seconds he was shown in. He nodded curtly to Mr~Murbles, who replied with a stiff bow, and then turned violently upon Wimsey.

»Look here, what's the meaning of all this? Here's that damned detective fellow of yours leading me a devil of a dance all over Europe and home again, and then this morning he suddenly turns round and tells me that you want to see me here with news about Oliver. What the devil do you know about Oliver?«

»Oliver?« said Wimsey. »Oh, yes—he's an elusive personality. Almost as elusive in Rome as he was in London. Wasn't it odd, Fentiman, the way he always seemed to bob up directly your back was turned? Wasn't it funny, the way he managed to disappear from places the moment you set foot in 'em? Almost like the way he used to hang about Gatti's and then give you and me the slip. Did you have a jolly time abroad, old man? I suppose you didn't like to tell your companion that he and you were chasing a will o' the wisp?«

Robert Fentiman's face was passing through phases ranging from fury to bewilderment and back again. Mr~Murbles interrupted.

»Has this detective vouchsafed any explanation of his extraordinary behaviour, in keeping us in the dark for nearly a fortnight as to his movements?«

»I'm afraid I owe you the explanation,« said Wimsey, airily. »You see, I thought it was time the carrot was dangled before the other donkey. I knew that if we pretended to find Oliver in Paris, Fentiman would be in honour bound to chase after him. In fact, he was probably only too pleased to get away—weren't you, Fentiman?«

»Do you mean to say that you invented all this story about Oliver, Lord~Peter?«

»I did. Not the original Oliver, of course, but the Paris Oliver. I told the sleuth to send a wire from Paris to summon our friend away and keep him away.«

»But why?«

»I'll explain that later. And of course you had to go, hadn't you, old man? Because you couldn't very well refuse to go without confessing that there was no such person as Oliver?«

»Damnation!« burst out Fentiman, and then suddenly began to laugh. »You cunning little devil! I began to think there was something fishy about it, you know. When that first wire came, I was delighted. Thought the sleuth-hound fellow had made a perfectly providential floater, don't you know. And the longer we kept tootin' round Europe the better I was pleased. But when the hare started to double back to England, home and beauty, I began to get the idea that somebody was pullin' my leg. By the way, was that why I was able to get all my visas with that uncanny facility at an unearthly hour overnight?«

»It was,« said Wimsey, modestly.

»I might have known there was something wrong about it. You devil! Well—what now?—if you've exploded Oliver, I suppose you've spilled all the rest of the beans, eh?«

»If you mean by that expression,« said Mr~Murbles, »that we are aware of your fraudulent and disgraceful attempt to conceal the true time of General Fentiman's decease, the answer is, Yes—we do know it. And I may say that it has come as a most painful shock to my feelings.«

Fentiman flung himself into a chair, slapping his thigh and roaring with laughter.

»I might have known you'd be on to it,« he gasped, »but it was a damn good joke, wasn't it? Good lord! I couldn't help chuckling to myself, you know. To think of all those refrigerated old imbeciles at the Club sittin' solemnly round there, and comin' in and noddin' to the old guv'nor like so many mandarins, when he was as dead as a door-nail all the time. That leg of his was a bit of a slip-up, of course, but that was an accident. Did you ever find out where he was all the time?«

»Oh, yes—pretty conclusively. You left your marks on the cabinet, you know.«

»No, did we? Hell!«

»Yes—and when you stuck the old boy's overcoat back in the cloak-room, you forgot to stick a poppy in it.«

»Oh, lord! that \textit{was} a bloomer. D'you know, I never thought of that. Oh, well! I suppose I couldn't hope to carry it off with a confounded bloodhound like you on the trail. But it was fun while it lasted. Even now, the thought of old Bunter solemnly callin' up two and a half columns of Olivers makes me shout with joy. It's almost as good as getting the half-million.«

»That reminds me,« said Wimsey. »The one thing I don't know is how you knew about the half-million. Did Lady Dormer tell you about her will? Or did you hear of it from George?«

»George? Great Scott, no! George knew nothing about it. The old boy told me himself.«

»General Fentiman?«

»Of course. When he came back to the Club that night, he came straight up to see me.«

»And we never thought of that,« said Wimsey, crushed. »Too obvious, I suppose.«

»You can't be expected to think of everything,« said Robert, condescendingly. »I think you did very well, take it all round. Yes—the old boy toddled up to me and told me all about it. He said I wasn't to tell George, because he wasn't quite satisfied with George—about Sheila, you know—and he wanted to think it over and see what was best to be done, in the way of making a new will, you see.«

»Just so. And he went down to the library to do it.«

»That's right; and I went down and had some grub. Well then, afterwards I thought perhaps I hadn't said quite enough on behalf of old George. I mean, the guv'nor needed to have it pointed out to him that George's queerness was caused a great deal by bein' dependent on Sheila and all that, and if he had some tin of his own he'd be much better-tempered—you get me? So I hopped through to the library to find the guv'—and there he was—dead!«

»What time was that?«

»Somewhere round about eightish, I should think. Well, I was staggered. Of course, my first idea was to call for help, but it wasn't any go. He was quite dead. And then it jolly well came over me all at once how perfectly damnably we had missed the train. Just to think of that awful Dorland woman walking into all those thousands—I tell you, it made me so bally wild I could have exploded and blown the place up!\dots And then, you know, I began to get a sort of creepy feeling, alone there with the body and nobody in the library at all. We seemed cut off from the world, as the writing fellows say. And then it just seemed to take hold of my mind, why should he have died like that?—I did have a passing hope that the old girl might have pegged out first, and I was just going along to the telephone to find out, when—thinking of the telephone cabinet, you see—the whole thing popped into my head ready-made, as you might say. In three minutes I'd lugged him along and stuck him up on the seat, and then I hopped back to write a label for the door. I say, I thought I was jolly smart to remember not to blot that label on the library blotting-paper.«

»Believe me,« said Wimsey, »I appreciated that point.«

»Good. I'm glad you did. Well, it was pretty plain sailing after that. I got the guv'nor's togs from the cloak-room and took 'em up to my room, and then I thought about old Woodward sittin' up waitin' for him. So I trundled out and went down to Charing Cross—how do you think?«

»By bus?«

»Not quite as bad as that. By Underground. I did realize it wouldn't work to call a taxi.«

»You show quite a disposition for fraud, Fentiman.«

»Yes, don't I?—Well, all that was easy. I must say, I didn't pass a frightfully good night.«

»You'll take it more calmly another time.«

»Yes—it was my maiden effort in crime, of course. The next morning\longdash«

»Young man,« said Mr~Murbles, in an awful voice, »we will draw a veil over the next morning. I have listened to your shameless statement with a disgust which words cannot express. But I cannot, and I will not sit here and listen while you congratulate yourself, with a cynicism at which you should blush, on having employed those sacred moments when every thought should have been consecrated\longdash«

»Oh, punk!« interrupted Robert, rudely. »My old pals are none the worse because I did a little bit of self-help. I know fraud isn't altogether the clean potato, but, dash it all! surely we have a better right to the old boy's money than that girl. I bet \textit{she} never did anything in the Great War, Daddy. Well, it's all gone bust—but it was a darn good stunt while it lasted.«

»I perceive,« replied Mr~Murbles, icily, »that any appeal to your better feelings would be waste of time. I imagine, however, you realize that fraud is a penal offence.«

»Yes—that's a nuisance, isn't it? What are we going to do about it? Do I have to go and eat humble pie to old Pritchard? Or does Wimsey pretend to have discovered something frightfully abstruse from looking at the body?—Oh, good lord, by the way—what's happened about that confounded exhumation stunt? I never thought a word more about it. I say, Wimsey, was that the idea? Did you know then that I'd been trying to work this stunt and was it your notion you could get me out of it?«

»Partly.«

»Damned decent of you. You know, I did tumble to it that you'd got a line on me when you sent me down with that detective fellow to Charing Cross. And, I say, you nearly had me there! I'd made up my mind to pretend to go after Oliver—you know—and then I spotted that second bloodhound of yours on the train with me. That gave me goose-flesh all over. The only thing I could think of—short of chucking up the whole show—was to accuse some harmless old bird of being Oliver—as a proof of good faith, don't you see.«

»That was it, was it? I thought you must have some reason.«

»Yes—and then, when I got that summons to Paris, I thought I must, somehow, have diddled the lot of you. But I suppose that was all arranged for. I say, Wimsey, why? Did you just want to get your own back, or what? Why did you want me out of England?«

»Yes, indeed, Lord~Peter,« said Mr~Murbles, gravely. »I think you owe \textit{me} at least some explanation on that point.«

»Don't you see,« said Wimsey, »Fentiman was his grandfather's executor. If I got him out of the way, you couldn't stop the exhumation.«

»Ghoul!« said Robert. »I believe you batten on corpses.«

Wimsey laughed, rather excitedly.

»Fentiman,« he said, »what would you give at this moment for your chance of that half-million?«

»Chance?« cried Fentiman. »There's no chance at all. What do you mean?«

Wimsey slowly drew a paper from his pocket.

»This came last night,« he said. »And, by jove, my lad, it's lucky for you that you had a good bit to lose by the old man's death. This is from Lubbock—«

\begin{quotation}
\noindent Dear Lord~Peter,

\indent I am sending you a line in advance to let you know the result of the autopsy on General Fentiman. As regards the ostensible reason for the investigation, I may say that there was no food in the stomach and that the last meal had been taken several hours previously. The important point, however, is that, following your own rather obscurely-expressed suggestion, I tested the viscera for poison and discovered traces of a powerful dose of digitalin, swallowed not very long previous to decease. As you know, with a subject whose heart was already in a weak state, the result of such a dose could not but be fatal. The symptoms would be a slowing-down of the heart's action and collapse—practically indistinguishable from a violent heart-attack.

I do not, of course, know what your attitude in this business is, though I congratulate you on the perspicacity which prompted you to suggest an analysis. In the meanwhile, of course, you will realize that I am obliged to communicate the result of the autopsy to the public prosecutor.
\end{quotation}

Mr~Murbles sat petrified.

»My God!« cried Fentiman. And then again, »My God!—Wimsey—if I'd known—if I'd had the faintest idea—I wouldn't have touched the body for twenty millions. Poison! Poor old blighter! What a damned shame! I remember now his saying that night he felt a bit sickish, but I never thought—I say, Wimsey—you do believe, don't you, that I hadn't the foggiest? I say—that awful female—I knew she was a wrong 'un. But poison! that is too thick. Good lord!«

Parker, who had hitherto preserved the detached expression of a friendly spectator, now beamed. »Damn good, old man!« he cried, and smote Peter on the back. Professional enthusiasm overcame him. »It's a real case,« he said, »and you've handled it finely, Peter. I didn't know you had it in you to hang on so patiently. Forcing the exhumation on 'em through putting pressure on Major Fentiman was simply masterly! Pretty work! Pretty work!«

»Thank you, Charles,« said Wimsey, dryly. »I'm glad somebody appreciates me. Anyhow,« he added, viciously, »I bet that's wiped old Pritchard's eye.«

And at this remark, even Mr~Murbles showed signs of returning animation.