%!TeX root=../bellonatop.tex
\chapter{Lord Peter Plays Dummy}
\lettrine[lines=4,ante=‘]{D}{o} you want to come with me to the Armstrong woman?'

\zz
\enquote{May as well,} said Wimsey, \enquote{you never know.}

\zz
Nurse Armstrong belonged to an expensive nursing home in Great Wimpole Street. She had not been interviewed before, having only returned the previous evening from escorting an invalid lady to Italy. She was a large, good-looking, imperturbable woman, rather like the Venus of Milo, and she answered Parker's questions in a cheerful, matter-of-fact tone, as though they had been about bandages or temperatures.

\enquote{Oh, yes, Constable; I remember the poor old gentleman being brought in, perfectly.}

Parker had a natural dislike to being called constable. However, a detective must not let little things like that irritate him.

\enquote{Was Miss Dorland present at the interview between your patient and her brother?}

\enquote{Only for a few moments. She said good afternoon to the old gentleman and led him up to the bed, and then, when she saw them comfortable together, she went out.}

\enquote{How do you mean, comfortable together?}

\enquote{Well, the patient called the old gentleman by his name, and he answered, and then he took her hand and said, \enquote{I'm sorry, Felicity; forgive me,} or something of that sort, and she said, \enquote{There's nothing to forgive; don't distress yourself, Arthur,}---crying, he was, the poor old man. So he sat down on the chair by the bed, and Miss Dorland went out.}

\enquote{Nothing was said about the will?}

\enquote{Not while Miss Dorland was in the room, if that's what you mean.}

\enquote{Suppose anybody had listened at the door afterwards\allowbreak---\allowbreak could they have heard what was said?}

\enquote{Oh, no! The patient was very weak and spoke very low. I couldn't hear myself half she said.}

\enquote{Where were you?}

\enquote{Well, I went away, because I thought they'd like to be alone. But I was in my own room with the door open between, and I was looking in most of the time. She was so ill, you see, and the old gentleman looked so frail, I didn't like to go out of earshot. In our work, you see, we often have to see and hear a lot that we don't say anything about.}

\enquote{Of course, Nurse\allowbreak---\allowbreak I am sure you did quite right. Now when Miss Dorland brought the brandy up\allowbreak---\allowbreak the General was feeling very ill?}

\enquote{Yes\allowbreak---\allowbreak he had a nasty turn. I put him in the big chair and bent him over till the spasm went off. He asked for his own medicine, and I gave it to him\allowbreak---\allowbreak no, it wasn't drops\allowbreak---\allowbreak it was amyl nitrate; you inhale it. Then I rang the bell and sent the girl for the brandy.}

\enquote{Amyl nitrate\allowbreak---\allowbreak you're sure that's all he had?}

\enquote{Positive; there wasn't anything else. Lady Dormer had been having strychnine injections to keep her heart going, of course, and we'd tried oxygen; but we shouldn't give him those, you know.}

She smiled, competently, condescendingly.

\enquote{Now, you say Lady Dormer had been having this, that and the other. Were there any medicines lying about that General Fentiman might have accidentally taken up and swallowed?}

\enquote{Oh, dear no.}

\enquote{No drops or tabloids or anything of that kind?}

\enquote{Certainly not; the medicines were kept in my room.}

\enquote{Nothing on the bedside table or the mantelpiece?}

\enquote{There was a cup of diluted Listerine by the bed, for washing out the patient's mouth from time to time, that was all.}

\enquote{And there's no digitalin in Listerine\allowbreak---\allowbreak no, of course not. Well now, who brought up the brandy-and-water?}

\enquote{The housemaid went to Mrs Mitcham for it. I should have had some upstairs, as a matter of fact, but the patient couldn't keep it down. Some of them can't, you know.}

\enquote{Did the girl bring it straight up to you?}

\enquote{No\allowbreak---\allowbreak she stopped to call Miss Dorland on the way. Of course, she ought to have brought the brandy at once and gone to Miss Dorland afterwards\allowbreak---\allowbreak but it's anything to save trouble with these girls, as I daresay you know.}

\enquote{Did Miss Dorland bring it straight up---?} began Parker. Nurse Armstrong broke in upon him.

\enquote{If you're thinking, did she put the digitalin into the brandy, you can dismiss that from your mind, constable. If he'd had as big a dose as that in solution at half-past four, he'd have been taken ill ever so much earlier than he was.}

\enquote{You seem to be well up in the case, Nurse.}

\enquote{Oh, I am. Naturally I was interested, Lady Dormer being my patient and all.}

\enquote{Of course. But all the same, \textit{did} Miss Dorland bring the brandy straight along to you?}

\enquote{I think so. I heard Nellie go along the passage on the half landing, and looked out to call to her, but by the time I'd got the door open, I saw Miss Dorland coming out of the studio with the brandy in her hand.}

\enquote{And where was Nellie then?}

\enquote{Just got back to the end of the passage and starting downstairs to the telephone.}

\enquote{At that rate, Miss Dorland couldn't have been more than ten seconds alone with the brandy,} said Peter, thoughtfully. \enquote{And who gave it to General Fentiman?}

\enquote{I did. I took it out of Miss Dorland's hand at the door and gave it to him at once. He seemed better then, and only took a little of it.}

\enquote{Did you leave him again?}

\enquote{I did not. Miss Dorland went out on to the landing presently to see if the taxi was coming.}

\enquote{She was never alone with him?}

\enquote{Not for a moment.}

\enquote{Did you like Miss Dorland, Nurse? Is she a nice girl, I mean?} Wimsey had not spoken for so long that Parker quite started.

\enquote{She was always very pleasant to me,} said Nurse Armstrong. \enquote{I shouldn't call her an attractive girl, not to my mind.}

\enquote{Did she ever mention Lady Dormer's testamentary arrangements in your hearing?} asked Parker, picking up what he conceived to be Wimsey's train of thought.

\enquote{Well\allowbreak---\allowbreak not exactly. But I remember her once talking about her painting, and saying she did it for a hobby, as her aunt would see she always had enough to live on.}

\enquote{That's true enough,} said Parker. \enquote{At the worst, she would get fifteen thousand pounds, which carefully invested, might mean six or seven hundred a year. She didn't say she expected to be very rich?}

\enquote{No.}

\enquote{Nor anything about the General?}

\enquote{Not a word.}

\enquote{Was she happy?} asked Wimsey.

\enquote{She was upset, naturally, with her aunt being so ill.}

\enquote{I don't mean that. You are the sort of person who observes a lot\allowbreak---\allowbreak nurses are awfully quick about that kind of thing, I've noticed. Did she strike you as a person who\allowbreak---\allowbreak who felt right with life, as you might say?}

\enquote{She was one of the quiet ones. But\allowbreak---\allowbreak yes---I should say she was satisfied with things all right.}

\enquote{Did she sleep well?}

\enquote{Oh, she was a very sound sleeper. It was a job to wake her if anything was wanted in the night.}

\enquote{Did she cry much?}

\enquote{She cried over the old lady's death; she had very nice feelings.}

\enquote{Some natural tears she shed, and all that. She didn't lie about and have awful howling fits or anything like that?}

\enquote{Good gracious, no!}

\enquote{How did she walk?}

\enquote{Walk?}

\enquote{Yes, walk. Was she what you'd call droopy?}

\enquote{Oh, no\allowbreak---\allowbreak quick and brisk.}

\enquote{What was her voice like?}

\enquote{Well, now, that was one of the nice things about her. Rather deep for a woman, but with what I might call a tune in it. Melodious,} said Nurse Armstrong, with a faint giggle, \enquote{that's what they call it in novels.}

Parker opened his mouth and shut it again.

\enquote{How long did you stay on at the house after Lady Dormer died?} pursued Wimsey.

\enquote{I waited on till after the funeral, just in case Miss Dorland should need anybody.}

\enquote{Before you left, did you hear anything of this trouble about the lawyers and the wills?}

\enquote{They were talking about it downstairs. Miss Dorland said nothing to me herself.}

\enquote{Did she seem worried?}

\enquote{Not to notice.}

\enquote{Had she any friends with her at the time?}

\enquote{Not staying in the house. She went out to see some friends one evening, I think\allowbreak---\allowbreak the evening before I left. She didn't say who they were.}

\enquote{I see. Thank you, Nurse.}

Parker had no more questions to put, and they took their leave.

\enquote{Well,} said Parker, \enquote{how anybody could admire that girl's voice\longdash}

\enquote{You noticed that! My theory is coming out right, Charles. I wish it wasn't. I'd \textit{rather} be wrong. I should like to have you look pitifully at me and say, \enquote{I told you so.} I can't speak more strongly than that.}

\enquote{Hang your theories!} said Parker. \enquote{It looks to me as if we shall have to wash out the idea that General Fentiman got his dose in Portman Square. By the way, didn't you say you'd met the Dorland girl at the Rushworth's?}

\enquote{No. I said I went hoping to meet her, but she wasn't there.}

\enquote{Oh, I see. Well, that'll do for the moment. How about a spot of lunch?}

At which point they turned the corner and ran slap into Salcombe Hardy, emerging from Harley Street. Wimsey clutched Parker's arm suddenly. \enquote{I've remembered,} he said.

\enquote{What?}

\enquote{Who that portrait reminds me of. Tell you later.}

Sally, it appeared, was also thinking of grub. He was, in fact, due to meet Waffles Newton at the Falstaff. It ended in their all going to the Falstaff.

\enquote{And how's it all going?} demanded Sally, ordering boiled beef and carrots.

He looked limpidly at Parker who shook his head.

\enquote{Discreet man, your friend,} said Sally to Peter. \enquote{I suppose the police are engaged in following up a clew\allowbreak---\allowbreak or have we reached the point when they are completely baffled? Or do we say that an arrest is imminent, eh?}

\enquote{Tell us your own version, Sally. Your opinion's as good as anybody's.}

\enquote{Oh, mine!---Same as yours\allowbreak---\allowbreak same as everybody's. The girl was in league with the doctor, of course. Pretty obvious, isn't it?}

\enquote{Maybe,} said Parker, cautiously. \enquote{But that's a hard thing to prove. We know, of course, that they both sometimes went to Mrs Rushworth's house, but there's no evidence that they knew each other well.}

\enquote{But, you ass, she\longdash} Wimsey blurted out. He shut his mouth again with a snap. \enquote{No, I won't. Fish it out for yourselves.}

Illumination was flooding in on him in great waves. Each point of light touched off a myriad others. Now a date was lit up, and now a sentence. The relief in his mind would have been overwhelming, had it not been for that nagging central uncertainty. It was the portrait that worried him most. Painted as a record, painted to recall beloved features\allowbreak---\allowbreak thrust face to the wall and covered with dust.

Sally and Parker were talking.

\enquote{... moral certainty is not the same thing as proof.}

\enquote{Unless we can show that she knew the terms of the will....}

\enquote{... why wait till the last minute? It could have been done safely any time....}

\enquote{They probably thought it wasn't necessary. The old lady looked like seeing him into his grave easily. If it hadn't been for the pneumonia.}

\enquote{Even so, they had five days.}

\enquote{Yes\allowbreak---\allowbreak well, say she didn't know till the very day of Lady Dormer's death....}

\enquote{She might have told her then. Explained ... seeing the thing had become a probability....}

\enquote{And the Dorland girl arranged for the visit to Harley Street....}

\enquote{... plain as the nose on your face.}

Hardy chuckled.

\enquote{They must have got a thundering shock when the body turned up the next morning at the Bellona. I suppose you gave Penberthy a good grueling about that rigor.}

\enquote{Pretty fair. He fell back on professional caution, naturally.}

\enquote{It's coming to him in the witness-box. Does he admit knowing the girl?}

\enquote{He says he just knows her to speak to. But one's got to find somebody who has seen them together. You remember the Thompson case. It was the interview in the tea-shop that clinched it.}

\enquote{What I want to know,} said Wimsey, \enquote{is why\longdash}

\enquote{Why what?}

\enquote{Why didn't they compromise?} It was not what he had been going to say, but he felt defeated, and those words would end the sentence as well as any others.

\enquote{What's that?} asked Hardy, quickly.

Peter explained.

\enquote{When the question of survivorship came up, the Fentimans were ready to compromise and split the money. Why didn't Miss Dorland agree? If your idea is the right one, it was much the safest way. But it was she who insisted on an inquiry.}

\enquote{I didn't know that,} said Hardy. He was annoyed. All kinds of \enquote{stories} were coming his way to-day, and to-morrow there would probably be an arrest, and he wouldn't be able to use them.

\enquote{They \textit{did} agree to compromise in the end,} said Parker. \enquote{When was that?}

\enquote{After I told Penberthy there was going to be an exhumation,} said Wimsey, as though in spite of himself.

\enquote{There you are! They saw it was getting too dangerous.}

\enquote{Do you remember how nervous Penberthy was at the exhumation?} said Parker. \enquote{That man\allowbreak---\allowbreak what's his name's\allowbreak---\allowbreak joke about Palmer, and knocking over the jar?}

\enquote{What was that?} demanded Hardy again. Parker told him, and he listened, grinding his teeth. Another good story gone west. But it would all come out at the trial, and would be worth a headline.

\enquote{Robert Fentiman ought to be given a medal,} said Hardy. \enquote{If he hadn't gone butting in\longdash}

\enquote{Robert Fentiman?} inquired Parker, distantly.

Hardy grinned.

\enquote{If he didn't fix up the old boy's body, who did? Give us credit for a little intelligence.}

\enquote{One admits nothing,} said Parker, \enquote{but\longdash}

\enquote{But everybody says he did it. Leave it at that. Somebody did it. If Somebody hadn't butted in, it would have been jam for the Dorland.}

\enquote{Well, yes. Old Fentiman would just have gone home and pegged out quietly\allowbreak---\allowbreak and Penberthy would have given the certificate.}

\enquote{I'd like to know how many inconvenient people are polished off that way. Damn it\allowbreak---\allowbreak it's so easy.}

\enquote{I wonder how Penberthy's share of the boodle was to be transferred to him.}

\enquote{I don't,} said Hardy. \enquote{Look here\allowbreak---\allowbreak here's this girl. Calls herself an artist. Paints bad pictures. Right. Then she meets this doctor fellow. He's mad on glands. Shrewd man\allowbreak---\allowbreak knows there's money in glands. \textit{She} starts taking up glands. Why?}

\enquote{That was a year ago.}

\enquote{Precisely. Penberthy isn't a rich man. Retired Army surgeon, with a brass plate and a consulting-room in Harley Street\allowbreak---\allowbreak shares the house with two other hard-up brass-platers. Lives on a few old dodderers down at the Bellona. Has an idea, if only he could start one of these clinics for rejuvenating people, he could be a millionaire. All these giddy old goats who want their gay time over again\allowbreak---\allowbreak why, they're a perfect fortune to the man with a bit of capital and a hell of a lot of cheek. Then this girl comes along\allowbreak---\allowbreak rich old woman's heiress\allowbreak---\allowbreak and he goes after her. It's all fixed up. He's to accommodate her by removing the obstacle to the fortune, and she obligingly responds by putting the money into his clinic. In order not to make it too obvious, she had to pretend to get a dickens of an interest in glands. So she drops painting and takes to medicine. What could be clearer?}

\enquote{But that means,} put in Wimsey, \enquote{that she must have known all about the will at least a year ago.}

\enquote{Why not?}

\enquote{Well that brings us back to the old question: Why the delay?}

\enquote{And it gives us the answer,} said Parker. \enquote{They waited till the interest in the glands and things was so firmly established and recognized by everybody that nobody would connect it with the General's death.}

\enquote{Of course,} said Wimsey. He felt that matters were rushing past him at a bewildering rate. But George was safe, anyhow.

\enquote{How soon do you think you'll be able to take action?} asked Hardy. \enquote{I suppose you'll want a bit more solid proof before you actually arrest them.}

\enquote{I'd have to be certain that they don't wriggle out of it,} said Parker, slowly. \enquote{It's not enough to prove that they were acquainted. There may be letters, of course, when we go over the girl's things. Or Penberthy's\allowbreak---\allowbreak though he's hardly the man to leave compromising documents lying about.}

\enquote{You haven't detained Miss Dorland?}

\enquote{No, we've let her loose\allowbreak---\allowbreak on a string. I don't mind telling you one thing. There's been no communication of any kind with Penberthy.}

\enquote{Of course there hasn't,} said Wimsey. \enquote{They've quarrelled.}

The others stared at him.

\enquote{How do you know that?} demanded Parker, annoyed.

\enquote{Oh, well\allowbreak---\allowbreak it doesn't matter\allowbreak---\allowbreak I \textit{think} so, that's all. And any way, they would take jolly good care not to communicate, once the alarm was given.}

\enquote{Hullo!} broke in Hardy, \enquote{here's Waffles. Late again. Waffles!---what \textit{have} you been doing, old boy?}

\enquote{Interviewing the Rushworths,} said Waffles, edging his way into a chair by Hardy. He was a thin, sandy person, with a tired manner. Hardy introduced him to Wimsey and Parker.

\enquote{Got your story in?}

\enquote{Oh, yes. Awful lot of cats these women are. Ma Rushworth\allowbreak---\allowbreak she's the sloppy sort of woman with her head in the clouds all the time, who never sees anything till it's stuck right under her nose\allowbreak---\allowbreak she pretends, of course, that she always thought Ann Dorland was an unwholesome kind of girl. I nearly asked why, in that case, she had her about the house; but I didn't. Anyway, Mrs Rushworth said, they didn't know her very intimately. They wouldn't, of course. Wonderful how these soulful people sheer off at the least suggestion of unpleasantness.}

\enquote{Did you get anything about Penberthy?}

\enquote{Oh, yes\allowbreak---\allowbreak I got something.}

\enquote{Good?}

\enquote{Oh, yes.}

Hardy, with Fleet Street's delicate reticence towards the man with an exclusive story, did not press the question. The talk turned back and went over the old ground. Waffles Newton agreed with Salcombe Hardy's theory.

\enquote{The Rushworths must surely know something. Not the mother, perhaps\allowbreak---\allowbreak but the girl. If she's engaged to Penberthy, she'll have noticed any other woman who seemed to have an understanding with him. Women see these things.}

\enquote{You don't suppose that they're going to confess that dear Dr Penberthy ever had an understanding with anybody but dear Naomi,} retorted Newton. \enquote{Besides, they aren't such fools as not to know that Penberthy's connection with the Dorland girl must be smothered up at all costs. They know she did it, all right, but they aren't going to compromise him.}

\enquote{Of course not,} said Parker, rather shortly. \enquote{The mother probably knows nothing, anyway. It's a different matter if we get the girl in the witness-box\longdash}

\enquote{You won't,} said Waffles Newton. \enquote{At least, you'll have to be jolly quick.}

\enquote{Why?}

Newton waved an apologetic hand.

\enquote{They're being married to-morrow,} he said, \enquote{special license. I say, that's not to go further, Sally.}

\enquote{That's all right, old man.}

\enquote{Married?} said Parker. \enquote{Good lord! that forces our hand a bit. Perhaps I'd better pop off. So long\allowbreak---\allowbreak and thanks very much for the tip, old man.}

Wimsey followed him into the street.

\enquote{We'll have to put the stopper on this marriage business, quick,} said Parker, madly waving to a taxi, which swooped past and ignored him. \enquote{I didn't want to move just at present, because I wasn't ready, but it'll be the devil and all if the Rushworth girl gets hitched up to Penberthy and we can't take her evidence. Devil of it is, if she's determined to go on with it, we can't stop it without arresting Penberthy. Very dangerous, when there's no real proof. I think we'd better have him down to the Yard for interrogation and detain him.}

\enquote{Yes,} said Wimsey. \enquote{But\allowbreak---\allowbreak look here, Charles.}

A taxi drew up.

\enquote{What?} said Parker, sharply, with his foot on the step. \enquote{I can't wait, old man. What is it?}

\enquote{I\allowbreak---\allowbreak look here, Charles\allowbreak---\allowbreak this is all wrong,} pleaded Wimsey. \enquote{You may have got the right solution, but the working of the sum's all wrong. Same as mine used to be at school, when I'd looked up the answer in the crib and had to fudge in the middle part. I've been a fool. I ought to have known about Penberthy. But I don't believe this story about bribing and corrupting him, and getting him to do the murder. It doesn't fit.}

\enquote{Doesn't fit what?}

\enquote{Doesn't fit the portrait. Or the books. Or the way Nurse Armstrong described Ann Dorland. Or your description of her. It's a mechanically perfect explanation, but I swear it's all wrong.}

\enquote{If it's mechanically perfect,} said Parker, \enquote{that's good enough. It's far more than most explanations are. You've got that portrait on the brain. It's because you're artistic, I suppose.}

For some reason, the word \enquote{artistic} produces the most alarming reactions in people who know anything about art.

\enquote{Artistic be damned!} said Wimsey, spluttering with fury, \enquote{it's because I'm an ordinary person, and have met women, and talked to them like ordinary human beings\longdash}

\enquote{You and your women,} said Parker, rudely.

\enquote{Well\allowbreak---\allowbreak I and my women, what about it? One learns something. You're on the wrong tack about this girl.}

\enquote{I've met her and you haven't,} objected Parker. \enquote{Unless you're suppressing something. You keep on hinting things. Anyhow, I've met the girl, and she impressed me as being guilty.}

\enquote{And I haven't met her, and I'll swear she isn't guilty.}

\enquote{You must know, of course.}

\enquote{I do happen to know about this.}

\enquote{I'm afraid your unsupported opinion will hardly be sufficient to refute the weight of evidence.}

\enquote{You haven't any real evidence, if it comes to that. You don't know that they were ever alone together; you don't know that Ann Dorland knew about the will; you can't prove that Penberthy administered the poison\longdash}

\enquote{I don't despair of getting all the evidence necessary,} said Parker, coldly, \enquote{provided you don't keep me here \textit{all} day.} He slammed the taxi-door.

\enquote{What a beast of a case this is,} thought Wimsey. \enquote{That makes two silly, sordid rows to-day. Well, what next?} He considered a moment.

\enquote{My spirit needs soothing,} he decided. \enquote{Feminine society is indicated. Virtuous feminine society. No emotions. I'll go and have tea with Marjorie Phelps.}