%!TeX root=../bellonatop.tex
\chapter{The Cards On The Table}

\lettrine[lines=4]{T}{here} was nobody in the library at the Bellona Club; there never is. Wimsey led Penberthy into the farthest bay and sent a waiter for two double whiskies.

\enquote{Here's luck!} he said.

\enquote{Good luck,} replied Penberthy. \enquote{What is it?}

\enquote{Look here,} said Wimsey. \enquote{You've been a soldier. I think you're a decent fellow. You've seen George Fentiman. It's a pity, isn't it?}

\enquote{What about it?}

\enquote{If George Fentiman hadn't turned up with that delusion of his,} said Wimsey, \enquote{you would have been arrested for the murder this evening. Now the point is this. When you are arrested, nothing, as things are, can prevent Miss Dorland's being arrested on the same charge. She's quite a decent girl, and you haven't treated her any too well, have you? Don't you think you might make things right for her by telling the truth straight away?}

Penberthy sat with a white face and said nothing.

\enquote{You see,} went on Wimsey, \enquote{if once they get her into the dock, she'll always be a suspected person. Even if the jury believe her story\allowbreak---\allowbreak and they may not, because juries are often rather stupid\allowbreak---\allowbreak people will always think there was 'something in it.' They'll say she was a very lucky woman to get off. That's damning for a girl, isn't it? They might even bring her in guilty. You and I know she isn't\allowbreak---\allowbreak but---you don't want the girl hanged, Penberthy, do you?}

Penberthy drummed on the table.

\enquote{What do you want me to do?} he said at last.

\enquote{Write a clear account of what actually happened,} said Wimsey. \enquote{Make a clean job of it for these other people. Make it clear that Miss Dorland had nothing to do with it.}

\enquote{And then?}

\enquote{Then do as you like. In your place I know what I should do.}

Penberthy propped his chin on his hands and sat for some minutes staring at the works of Dickens in the leather-and-gold binding.

\enquote{Very well,} he said at last. "You're quite right. I ought to have done it before. But\allowbreak---\allowbreak damn it!---if ever a man had rotten luck....

"If only Robert Fentiman hadn't been a rogue. It's funny, isn't it? That's your wonderful poetic justice, isn't it? If Robert Fentiman had been an honest man, I should have got my half-million, and Ann Dorland would have got a perfectly good husband, and the world would have gained a fine clinic, incidentally. But as Robert was a rogue\allowbreak---\allowbreak here we are....

"I didn't intend to be such a sweep to the Dorland girl. I'd have been decent to her if I'd married her. Mind you, she did sicken me a bit. Always wanting to be sentimental. It's true, what I said\allowbreak---\allowbreak she's a bit cracked about sex. Lots of 'em are. Naomi Rushworth, for instance. That's why I asked her to marry me. I had to be engaged to somebody, and I knew she'd take any one who asked her....

"It was so hideously easy, you see ... that was the devil of it. The old man came along and put himself into my hands. Told me with one breath that I hadn't a dog's chance of the money, and in the next, asked me for a dose. I just had to put the stuff into a couple of capsules and tell him to take them at 7 o'clock. He put them in his spectacle-case, to make sure he wouldn't forget them. Not even a bit of paper to give me away. And the next day I'd only to get a fresh supply of the stuff and fill up the bottle. I'll give you the address of the chemist who sold it. Easy?---it was laughable ... people put such power in our hands....

\enquote{I never meant to get led into all this rotten way of doing things\allowbreak---\allowbreak it was just self-defense. I still don't care a damn about having killed the old man. I could have made better use of the money than Robert Fentiman. He hasn't got two ideas in his head, and he's perfectly happy where he is. Though I suppose he'll be leaving the Army now.... As for Ann, she ought to be grateful to me in a way. I've secured her the money anyhow.}

\enquote{Not unless you make it clear that she had no part in the crime,} Wimsey reminded him.

\enquote{That's true. All right. I'll put it all on paper for you. Give me half an hour, will you?}

\enquote{Right you are,} said Wimsey.

He left the library and wandered into the smoking-room. Colonel Marchbanks was there, and greeted him with a friendly smile.

\enquote{Glad you're here, Colonel. Mind if I come and chat to you for a moment?}

\enquote{By all means, my dear boy. I'm in no hurry to get home. My wife's away. What can I do for you?}

Wimsey told him, in a lowered voice. The Colonel was distressed.

\enquote{Ah, well,} he said, \enquote{you've done the best thing, to my mind. I look at these matters from a soldier's point of view, of course. Much better to make a clean job of it all. Dear, dear! Sometimes, Lord Peter, I think that the War has had a bad effect on some of our young men. But then, of course, all are not soldiers by training, and that makes a great difference. I certainly notice a less fine sense of honor in these days than we had when I was a boy. There were not so many excuses made then for people; there were things that were done and things that were not done. Nowadays men\allowbreak---\allowbreak and, I am sorry to say, women too\allowbreak---\allowbreak let themselves go in a way that is to me quite incomprehensible. I can understand a man's committing murder in hot blood\allowbreak---\allowbreak but poisoning\allowbreak---\allowbreak and then putting a good, ladylike girl into such an equivocal position\allowbreak---\allowbreak no! I fail to understand it. Still, as you say, the right course is being taken at last.}

\enquote{Yes,} said Wimsey.

\enquote{Excuse me for a moment,} said the Colonel, and went out.

When he returned, he went with Wimsey into the library. Penberthy had finished writing and was reading his statement through.

\enquote{Will that do?} he asked.

Wimsey read it, Colonel Marchbanks looking over the pages with him.

\enquote{That is quite all right,} he said. \enquote{Colonel Marchbanks will witness it with me.}

This was done. Wimsey gathered the sheets together and put them in his breast-pocket. Then he turned silently to the Colonel, as though passing the word to him.

\enquote{Dr Penberthy,} said the old man, \enquote{now that that paper is in Lord Peter Wimsey's hands, you understand that he can only take the course of communicating with the police. But as that would cause a great deal of unpleasantness to yourself and to other people, you may wish to take another way out of the situation. As a doctor, you will perhaps prefer to make your own arrangements. If not\longdash}

He drew out from his jacket-pocket the thing which he had fetched.

\enquote{If not, I happen to have brought this with me from my private locker. I am placing it here, in the table-drawer, preparatory to taking it down into the country to-morrow. It is loaded.}

\enquote{Thank you,} said Penberthy.

The Colonel closed the drawer slowly, stepped back a couple of paces and bowed gravely. Wimsey put his hand on Penberthy's shoulder for a moment, then took the Colonel's arm. Their shadows moved, lengthened, shortened, doubled and crossed as they passed the seven lights in the seven bays of the library. The door shut after them.

\enquote{How about a drink, Colonel?} said Wimsey.

They went into the bar, which was just preparing to close for the night. Several other men were there, talking over their plans for Christmas.

\enquote{I'm getting away south,} said Tin-Tummy Challoner. \enquote{I'm fed up with this climate and this country.}

\enquote{I wish you'd look us up, Wimsey,} said another man. \enquote{We could give you some very decent shooting. We're having a sort of house-party; my wife, you know\allowbreak---\allowbreak must have all these young people round\allowbreak---\allowbreak awful crowd of women. But I'm getting one or two men who can play bridge and handle a gun, and it would be a positive charity to see me through. Deadly season, Christmas. Can't think why they invented it.}

\enquote{It's all right if you've got kids,} interrupted a large, red-faced man with a bald head. \enquote{The little beggars enjoy it. You ought to start a family, Anstruther.}

\enquote{All very well,} said Anstruther, \enquote{you're cut out by nature to dress up as Father Christmas. I tell you, what with one thing and another, entertaining and going about, and the servants we have to keep in a place like ours, it's a job to keep things going. If you know of a good thing, I wish you'd put me on to it. It's not as though\longdash}

\enquote{Hullo!} said Challoner, \enquote{what was that?}

\enquote{Motor-bike, probably,} said Anstruther. \enquote{As I was saying, it's not as though\longdash}

\enquote{Something's happened,} broke in the red-faced man, setting down his glass.

There were voices, and the running to and fro of feet. The door was flung open. Startled faces turned towards it. Wetheridge burst in, pale and angry.

\enquote{I say, you fellows,} he cried, \enquote{here's another unpleasantness. Penberthy's shot himself in the library. People ought to have more consideration for the members. Where's Culyer?}

Wimsey pushed his way out into the entrance-hall. There, as he had expected, he found the plainclothes detective who had been told off to shadow Penberthy.

\enquote{Send for Inspector Parker,} he said. \enquote{I have a paper to give him. Your job's over; it's the end of the case.}