%!TeX root=../bellonatop.tex
\chapter{Post-Mortem}

\lettrine[lines=4,ante=‘]{A}{nd} George is all right again now?'

\zz
\enquote{Thank heaven, yes\allowbreak---\allowbreak getting on splendidly. The doctor says he worked himself into it, just out of worry lest he should be suspected. It never occurred to me\allowbreak---\allowbreak but then George is very quick at putting two and two together.}

\enquote{Of course he knew he was one of the last people to see his grandfather.}

\enquote{Yes, and seeing the name on the bottle\allowbreak---\allowbreak and the police coming\longdash}

\enquote{That did it. And you're sure he's all right?}

\enquote{Oh, rather. The minute he knew that it was all cleared up, he seemed to come out from under a blanket. He sent you all sorts of messages, by the way.}

\enquote{Well, as soon as he's fit you must come and dine with me....}

\enquote{... A simple case, of course, as soon as you had disentangled the Robert part of it.}

\enquote{A damned unsatisfactory case, Charles. Not the kind I like. No real proof.}

\enquote{Nothing in it for us, of course. Just as well it never came to trial, though. With juries you never know.}

\enquote{No; they might have let Penberthy off; or convicted them both.}

\enquote{Exactly. If you ask me, I think Ann Dorland is a very lucky young woman.}

\enquote{Oh, God!---you \textit{would} say that....}

\enquote{... Yes, of course, I'm sorry for Naomi Rushworth. But she needn't be so spiteful. She goes about hinting that of course dear Walter was got over by that Dorland girl and sacrificed himself to save her.}

\enquote{Well, that's natural, I suppose. You thought Miss Dorland had done it yourself at one time, you know, Marjorie.}

\enquote{I didn't know then about her being engaged to Penberthy. And I think he deserved all he got.... Well, I know he's dead, but it was a rotten way to treat a girl, and Ann's far too good for that kind of thing. People have a perfect right to want love-affairs. You men always think....}

\enquote{Not me, Marjorie. I don't think.}

\enquote{Oh, you! You're almost human. I'd almost take you on myself if you asked me. You don't feel inclined that way, I suppose?}

\enquote{My dear\allowbreak---\allowbreak if a great liking and friendship were enough, I would\allowbreak---\allowbreak like a shot. But that wouldn't satisfy you, would it?}

\enquote{It wouldn't satisfy \textit{you}, Peter. I'm sorry. Forget it.}

\enquote{I won't forget it. It's the biggest compliment I've ever had paid me. Great Scott! I only wish....}

\enquote{There! that's all right, you needn't make a speech. And you won't go away tactfully forever, will you?}

\enquote{Not if you don't want me to.}

\enquote{And you won't be embarrassed?}

\enquote{No, I won't be embarrassed. Portrait of a young man poking the fire to bits to indicate complete freedom from embarrassment. Let's go and feed somewhere, shall we?...}

\enquote{... Well, and how did you get on with the heiress and the lawyers and all that lot?}

\enquote{Oh! there was a long argument. Miss Dorland insisted on dividing the money, and I said no, I couldn't think of it. She said it was only hers as the result of a crime, and Pritchard and Murbles said she wasn't responsible for other people's crimes. And I said it would look like my profiting by my own attempt at fraud, and she said, not at all, and we went on and on, don't you know. That's a damned decent girl, Wimsey.}

\enquote{Yes, I know. The moment I found she preferred burgundy to champagne I had the highest opinion of her.}

\enquote{No, really\allowbreak---\allowbreak there's something very fine and straightforward about her.}

\enquote{Oh, yes\allowbreak---\allowbreak not a bad girl at all; though I shouldn't have said she was quite your sort.}

\enquote{Why not?}

\enquote{Well\allowbreak---\allowbreak arty and all that. And her looks aren't her strong point.}

\enquote{You needn't be offensive, Wimsey. Surely I may be allowed to appreciate a woman of intelligence and character. I may not be highbrow, but I have \textit{some} ideas beyond the front row of the chorus. And what that girl went through with that blighter Penberthy makes my blood boil.}

\enquote{Oh, you've heard all about that?}

\enquote{I have. She told me, and I respected her for it. I thought it most courageous of her. It's about time somebody brought a little brightness into that poor girl's life. You don't realize how desperately lonely she has been. She had to take up that art business to give her an interest, poor child, but she's really cut out for an ordinary, sensible, feminine life. You may not understand that, with your ideas, but she has really a very sweet nature.}

\enquote{Sorry, Fentiman.}

\enquote{She made me ashamed, the way she took the whole thing. When I think of the trouble I got her into, owing to my damned dishonest tinkering about with\allowbreak---\allowbreak you know\longdash}

\enquote{My dear man, you were perfectly providential. If you hadn't tinkered about, as you say, she'd be married to Penberthy by now.}

\enquote{That's true\allowbreak---\allowbreak and that makes it so amazing of her to forgive me. She \textit{loved} that blighter, Wimsey. You don't know. It's absolutely pathetic.}

\enquote{Well, you'll have to do your best to make her forget it.}

\enquote{I look on that as a duty, Wimsey.}

\enquote{Just so. Doing anything to-night? Care to come and look at a show?}

\enquote{Sorry\allowbreak---\allowbreak I'm booked. Taking Miss Dorland to the new thing at the Palladium, in fact. Thought it'd do her good\allowbreak---\allowbreak buck her up and so on.}

\enquote{Oh?---good work!---Here's luck to it....}

\enquote{... and the cooking is getting perfectly disgraceful. I spoke to Culyer about it only yesterday. But he won't do anything. I don't know what's the good of the committee. This club isn't half what it used to be. In fact, Wimsey, I'm thinking of resigning.}

\enquote{Oh, don't do that, Wetheridge. It wouldn't be the same place without you.}

\enquote{Look at all the disturbance there has been lately. Police and reporters\allowbreak---\allowbreak and then Penberthy blowing his brains out in the library. And the coal's all slate. Only yesterday something exploded like a shell\allowbreak---\allowbreak I assure you, exactly like a shell\allowbreak---\allowbreak in the card-room; and as nearly as possible got me in the eye. I said to Culyer, \enquote{This must \textit{not} occur again.} You may laugh, but I knew a man who was blinded by a thing popping out suddenly like that. These things never happened before the War, and\allowbreak---\allowbreak great heavens! William! Look at this wine! Smell it! \textit{Taste} it! Corked? Yes, I should think it \textit{was} corked! My God! I don't know what's come to this Club.}
\vfill
\begin{center}
{\mytitlefont\moderatelyhuge The End}
\end{center}