\chapter[Chapter \thechapter]{}
\lettrine[ante=`]{T}{hey}  won't be long, I shouldn't think,' said Waffles Newton, <it's pretty damned obvious. Look here, old man, I'm going to push my stuff in. Will you let me know what happens?>

\zz
<Sure,> said Salcombe Hardy, <if you don't mind dropping mine in at our place as you go. You couldn't send me a drink by 'phone, could you? My mouth's like the bottom of a parrot's cage.> He looked at his watch. <We shall miss the 6.30 edition, I'm afraid, unless they hurry up. The old man is careful but he's damned slow.>

<They can't in decency not make a pretence of consulting about it,> said Newton. <I give them twenty minutes. They'll want a smoke. So do I\@. I'll be back at ten to, in case.>

He wriggled his way out. Cuthbert Logan, who reported for a morning paper, and was a man of more leisure, settled down to write up a word-picture of the trial. He was a phlegmatic and sober person and could write as comfortably in court as anywhere else. He liked to be on the spot when things happened, and to note down glances, tones of voice, colour effects and so forth. His copy was always entertaining, and sometimes even distinguished.

Freddy Arbuthnot, who had not, after all, gone home after lunch, thought it was time to do so now. He fidgeted, and Wimsey frowned at him. The Dowager Duchess made her way along the benches and squeezed in next to Lord~Peter. Sir~Impey Biggs, having watched over his client's interests to the last, disappeared, chatting cheerfully to the Attorney-General, and followed by the smaller legal fry. The dock was deserted. On the bench the red roses stood solitary, their petals dropping.

Chief-Inspector Parker, disengaging himself from a group of friends, came slowly up through the crowd and greeted the Dowager. <And what do you think of it, Peter?> he added, turning to Wimsey, <rather neatly got up, eh?>

<Charles,> said Wimsey, <you ought not to be allowed out without me. You've made a mistake, old man.>

<Made a mistake?>

<She didn't do it.>

<Oh, come!>

<She did not do it. It's very convincing and water-tight, but it's all wrong.>

<You don't really think that.>

<I do.>

Parker looked distressed. He had confidence in Wimsey's judgment, and, in spite of his own interior certainty, he felt shaken.

<My dear man, where's the flaw in it?>

<There isn't one. It's damnably knife-proof. There's nothing wrong about it at all, except that the girl's innocent.>

<You're turning into a common or garden psychologist,> said Parker, with an uneasy laugh, <isn't he, Duchess?>

<I wish I had known that girl,> replied the Dowager, in her usual indirect manner, <so interesting and a really remarkable face, though perhaps not strictly good-looking, and all the more interesting for that, because good-looking people are so often cows. I have been reading one of her books, really quite good and so well-written, and I didn't guess the murderer till page 200, rather clever, because I usually do it about page 15. So very curious to write books about crimes and then be accused of a crime one's self, some people might say it was a judgment. I wonder whether, if she didn't do it, she has spotted the murderer herself? I don't suppose detective writers detect much in real life, do they, except Edgar Wallace of course, who always seems to be everywhere and dear Conan Doyle and the black man what was his name and of course the Slater person, such a scandal, though now I come to think of it that was in Scotland where they have such very odd laws about everything particularly getting married. Well, I suppose we shall soon know now, not the truth, necessarily, but what the jury have made of it.>

<Yes; they are being rather longer than I expected. But, I say, Wimsey, I wish you'd tell me\longdash>

<Too late, too late, you cannot enter now. I have locked my heart in a silver box and pinned it wi' a golden pin. Nobody's opinion matters now, except the jury's. I expect Miss~Climpson is telling 'em all about it. When once she starts she doesn't stop for an hour or two.>

<Well, they've been half-an-hour now,> said Parker.

<Still waiting?> said Salcombe Hardy, returning to the press-table.

<Yes—so this is what you call twenty minutes! Three-quarters of an hour, I make it.>

<They've been out an hour-and-a-half,> said a girl to her fiancé, just behind Wimsey. <What can they be discussing?>

<Perhaps they don't think she did it after all.>

<What nonsense! Of course she did it. You could see it by her face. Hard, that's what I call it, and she never once cried or anything.>

<Oh, I dunno,> said the young man.

<You don't mean to say you admired her, Frank?>

<Oh, well, I dunno. But she didn't look to me like a murderess.>

<And how do you know what a murderess looks like? Have you ever met one?>

<Well, I've seen them at Madame Tussaud's.>

<Oh, wax-works. Everybody looks like a murderer in a wax-works.>

<Well, p'raps they do. Have a choc.>

<Two hours and a quarter,> said Waffles Newton, impatiently. <They must have gone to sleep. Have to be a special edition. What happens if they are all night about it?>

<We sit here all night, that's all.>

<Well, it's my turn for a drink. Let me know, will you?>

<Right-ho!>

<I've been talking to one of the ushers,> said the Man Who Knows the Ropes, importantly, to a friend. <The judge has just sent round to the jury to ask if he can help them in any way.>

<Has he? And what did they say?>

<I don't know.>

<They've been out three hours and a half now,> whispered the girl behind Wimsey. <I'm getting fearfully hungry.>

<Are you, darling? Shall we go?>

<No—I want to hear the verdict. We've waited so long now, we may as well stop on.>

<Well, I'll go out and get some sandwiches.>

<Oh, that would be nice. But don't be long, because I'm sure I shall get hysterics when I hear the sentence.>

<I'll be as quick as ever I can. Be glad you're not the jury—they're not allowed anything at all.>

<What, nothing to eat or drink?>

<Not a thing. I don't think they're supposed to have light or fire either.>

<Poor things! But it's central-heated, isn't it?>

<It's hot enough here, anyway. I'll be glad of a breath of fresh air.>

Five hours.

<There's a terrific crowd in the street,> said the Man Who Knows the Ropes, returning from a reconnaissance. <Some people started booing the prisoner and a bunch of men attacked them, and one fellow has been carried off in an ambulance.>

<Really, how amusing! Look! There's Mr~Urquhart; he's come back. I'm so sorry for him, aren't you? It must be horrid having somebody die in your house.>

<He's talking to the Attorney-General. They've all had a proper dinner, of course.>

<The Attorney-General isn't as handsome as Sir~Impey Biggs. Is it true he keeps canaries?>

<The Attorney-General?>

<No, Sir~Impey.>

<Yes, quite true. He takes prizes with them.>

<What a funny idea!>

<Bear up, Freddy,> said Lord~Peter Wimsey. <I perceive movements. They are coming, my own, my sweet, were it never so airy a tread.>

The court rose to its feet. The judge took his seat. The prisoner, very white in the electricity, reappeared in the dock. The door leading to the jury-room opened.

<Look at their faces,> said the fiancée, <they say if it's going to be Guilty they never look at the prisoner. Oh, Archie, hold my hand!>

The Clerk of Assizes addressed the jury in tones in which formality struggled with reproach.

<Members of the jury, have you all agreed upon your verdict?>

The foreman rose with an injured and irritable countenance.

<I am sorry to say that we find it impossible to come to an agreement.>

A prolonged gasp and murmur went round the court. The judge leaned forward, very courteous and not in the least fatigued.

<Do you think that with a little more time you may be able to reach an agreement?>

<I'm afraid not, my lord.> The foreman glanced savagely at one corner of the jury-box, where the elderly spinster sat with her head bowed and her hands tightly clasped. <I see no prospect at all of our ever agreeing.>

<Can I assist you in any way?>

<No, thank you, my lord. We quite understand the evidence, but we cannot agree about it.>

<That is unfortunate. I think perhaps you had better try again, and then, if you are still unable to come to a decision, you must come back and tell me. In the meantime, if my knowledge of the law can be of any assistance to you, it is, of course, quite at your disposal.>

The jury stumbled sullenly away. The judge trailed his scarlet robes out at the back of the bench. The murmur of conversation rose and swelled into a loud rumble.

<By jove,> said Freddy Arbuthnot, <I believe it's your Miss~Climpson that's holdin' the jolly old show up, Wimsey. Did you see how the foreman glared at her?>

<Good egg,> said Wimsey, <oh, excellent, excellent egg! She has a fearfully tough conscience—she may stick it out yet.>

<I believe you've been corrupting the jury, Wimsey. Did you signal to her or something?>

<I didn't,> said Wimsey. <Believe me or believe me not, I refrained from so much as a lifted eyebrow.>

<And he himself has said it,> muttered Freddy, <and it's greatly to his credit. But it's damned hard on people who want their dinners.>

Six hours. Six hours and a half.

<At last!>

As the jury filed back for the second time, they showed signs of wear and tear. The harassed woman had been crying and was still choking into her handkerchief. The man with the bad cold looked nearly dead. The artist's hair was rumpled into an untidy bush. The company director and the foreman looked as though they would have liked to strangle somebody, and the elderly spinster had her eyes shut and her lips moving as though she were praying.

<Members of the jury, are you agreed upon your verdict?>

<No; we are quite sure that it is impossible for us ever to agree.>

<You are quite sure?> said the judge. <I do not wish to hurry you in any way. I am quite prepared to wait here as long as ever you like.>

The snarl of the company director was audible even in the gallery. The foreman controlled himself, and replied in a voice ragged with temper and exhaustion.

<We shall never agree, my lord—not if we were to stay here till Doomsday.>

<That is very unfortunate,> said the judge, <but in that case, of course, there is nothing for it but to discharge you and order a fresh trial. I feel sure that you have all done your best and that you have brought all the resources of your intelligence and conscience to bear on this matter to which you have listened with so much patient and zealous attention. You are discharged, and you are entitled to be excused from all further jury service for the next twelve years.>

Almost before the further formalities were completed, and while the judge's robes still flared in the dark little doorway, Wimsey had scrambled down into the well of the court. He caught the defending counsel by the gown.

<Biggy—well done! You've got another chance. Let me in on this and we'll pull it off.>

<You think so, Wimsey? I don't mind confessing that we've done better than I ever expected.>

<We'll do better still next time. I say, Biggy, swear me in as a clerk or something. I want to interview her.>

<Who, my client?>

<Yes, I've got a hunch about this case. We've got to get her off, and I know it can be done.>

<Well, come and see me tomorrow. I must go and speak to her now. I'll be in my chambers at ten. Good-night.>

Wimsey darted off and rushed round to the side-door, from which the jury were emerging. Last of them all, her hat askew and her mackintosh dragged awkwardly round her shoulders, came the elderly spinster. Wimsey dashed up to her and seized her hand.

<Miss~Climpson!>

<Oh, Lord~Peter. Oh, dear! What a dreadful day it has been. Do you know, it was me that caused the trouble, mostly, though two of them most bravely backed me up, and oh, Lord~Peter, I hope I haven't done wrong, but I couldn't, no I \emph{couldn't} in conscience say she had done it when I was sure she hadn't, could I? Oh, dear, oh, dear!>

<You're absolutely right. She didn't do it, and thank God you stood up to them and gave her another chance. I'm going to prove she didn't do it. And I'm going to take you out to dinner, and—I say, Miss~Climpson!>

<Yes?>

<I hope you won't mind, because I haven't shaved since this morning, but I'm going to take you round the next quiet corner and kiss you.>