\chapter[Chapter \thechapter]{}
\lettrine{T}{he} following day was a Sunday, but Sir~Impey Biggs cancelled an engagement to play golf (with the less regret as it was pouring cats and dogs), and held an extraordinary council of war.

\zz
<Well, now, Wimsey,> said the advocate, <what is your idea about this? May I introduce Mr~Crofts of Crofts \& Cooper, solicitors for the defence.>

<My idea is that Miss~Vane didn't do it,> said Wimsey. <I dare say that's an idea which has already occurred to you, but with the weight of my great mind behind it, no doubt it strikes the imagination more forcibly.>

Mr~Crofts, not being quite clear whether this was funny or fatuous, smiled deferentially.

<Quite so,> said Sir~Impey, <but I should be interested to know how many of the jury saw it in that light.>

<Well, I can tell you that, at least, because I know one of them. One woman and half a woman and about three-quarters of a man.>

<Meaning precisely?>

<Well, the woman I know stuck out for it that Miss~Vane wasn't that sort of person. They bullied her a good deal, of course, because she couldn't lay a finger on any real weakness in the chain of evidence, but she said the prisoner's demeanour was part of the evidence and that she was entitled to take that into consideration. Fortunately, she is a tough, thin, elderly woman with a sound digestion and a militant High-Church conscience of remarkable staying-power, and her wind is excellent. She let 'em all gallop themselves dead, and then said she still didn't believe it and wasn't going to say she did.>

<Very useful,> said Sir~Impey. <A person who can believe all the articles of the Christian faith is not going to boggle over a trifle of adverse evidence. But we can never hope for a whole jury-box full of ecclesiastical diehards. How about the other woman and the man?>

<Well, the woman was rather unexpected. She was the stout, prosperous party who keeps a sweet-shop. She said she didn't think the case was proved, and that it was perfectly possible that Boyes had taken the stuff himself, or that his cousin had given it to him. She was influenced, rather oddly, by the fact that she had attended one or two arsenic trials, and had not been satisfied by the verdict in some other cases—notably the Seddon trial. She has no opinion of men in general (she has buried her third) and she disbelieves all expert evidence on principle. She said that, personally, she thought Miss~Vane might have done it, but she wouldn't really hang a dog on medical evidence. At first she was ready to vote with the majority, but she took a dislike to the foreman, who tried to bear her down by his male authority, and eventually she said she was going to back up my friend Miss~Climpson.>

Sir~Impey laughed.

<Very interesting. I wish we always got this inside information about juries. We sweat like hell to prepare evidence, and then one person makes up her mind on what isn't really evidence at all, and another supports her on the ground that evidence can't be relied on. How about the man?>

<The man was the artist, and the only person who really understood the kind of life these people were leading. He believed your client's version of the quarrel, and said that, if the girl really felt like that about the man, the last thing she would want to do would be to kill him. She'd rather stand back and watch him ache, like the man with the hollow tooth in the comic song. He was also able to believe the whole story about purchasing the poisons, which to the others, of course, seemed extremely feeble. He also said that Boyes, from what he had heard, was a conceited prig, and that anybody who disposed of him was doing a public service. He had had the misfortune to read some of his books, and considered the man an excrescence and a public nuisance. Actually he thought it more than likely that he had committed suicide, and if anybody was prepared to take that point of view he was ready to second it. He also alarmed the jury by saying that he was accustomed to late hours and a stale atmosphere, and had not the slightest objection to sitting up all night. Miss~Climpson also said that, in a righteous cause, a little personal discomfort was a trifle, and added that her religion had trained her to fasting. At that point, the third woman had hysterics and another man, who had an important deal to put through next day, lost his temper, so, to prevent bodily violence, the foreman said he thought they had better agree to disagree. So that's how it was.>

<Well, they've given us another chance,> said Mr~Crofts, <so it's all to the good. It can't come on now till the next sessions, which gives us about a month, and we'll probably get Bancroft next time, who's not such a severe judge as Crossley. The thing is, can we do anything to improve the look of our case?>

<I'm going to have a strenuous go at it,> said Wimsey. <There must \textit{be} evidence somewhere, you know. I know you've all worked like beavers, but I'm going to work like a king beaver. And I've got one big advantage over the rest of you.>

<More brains?> suggested Sir~Impey, grinning.

<No—I should hate to suggest that, Biggy. But I do believe in Miss~Vane's innocence.>

<Damn it, Wimsey, didn't my eloquent speeches convince you that I was a whole-hearted believer?>

<Of course they did. I nearly shed tears. Here's old Biggy, I said to myself, going to retire from the Bar and cut his throat if this verdict goes against him, because he won't believe in British justice any more. No—it's your triumph at having secured a disagreement that gives you away, old horse. More than you expected. You said so. By the way, if it's not a rude question, who's paying you, Biggy?>

<Crofts and Cooper,> said Sir~Impey, slyly.

<They're in the thing for their health, I take it?>

<No, Lord~Peter. As a matter of fact, the costs in this case are being borne by Miss~Vane's publishers and by a—well, a certain newspaper, which is running her new book as a serial. They expect a scoop as the result of all this. But frankly, I don't quite know what they'll say to the expense of a fresh trial. I'm expecting to hear from them this morning.>

<The vultures,> said Wimsey. <Well, they'd better carry on, but tell 'em I'll see they're guaranteed. Don't bring my name in, though.>

<This is very generous\longdash>

<Not at all. I wouldn't lose the fun of all this for the world. Sort of case I fairly wallow in. But in return you must do something for me. I want to see Miss~Vane. You must get me passed in as part of your outfit, so that I can hear her version of the story in reasonable privacy. Get me?>

<I expect that can be done,> said Sir~Impey. <In the meantime you have nothing to suggest?>

<Haven't had time yet. But I'll fish out something, don't you worry. I've already started to undermine the confidence of the police. Chief-Inspector Parker has gone home to twine willow-wreaths for his own tomb-stone.>

<You'll be careful,> said Sir~Impey. <Anything we can discover will come in much more effectively if the prosecution don't know of it beforehand.>

<I'll walk as on egg-shells. But if I find the real murderer (if any), you won't object to my having him or her arrested, I take it?>

<No; I won't object to that. The police may. Well, gentlemen, if there's nothing further at the moment, we'd better adjourn the meeting. You'll get Lord~Peter the facilities he wants, Mr~Crofts?>

\divider

Mr~Crofts exerted himself with energy, and on the following morning, Lord~Peter presented himself at the gates of Holloway Gaol, with his credentials.

<Oh, yes, my lord. You are to be treated on the same footing as the prisoner's solicitor. Yes, we have had a separate communication from the police and that will be quite all right, my lord. The warder will take you down, and explain the regulations to you.>

Wimsey was conducted through a number of bare corridors to a small room with a glass door. There was a long deal table in it and a couple of repellent chairs, one at either end of the table.

<Here you are, my lord. You sit at one end and the prisoner at the other, and you must be careful not to move from your seats, nor to pass any object over the table. I shall be outside and see you through the glass, my lord, but I shan't be able to overhear nothing. If you will take a seat, they'll bring the prisoner in, my lord.>

Wimsey sat down and waited, a prey to curious sensations. Presently there was a noise of footsteps, and the prisoner was brought in, attended by a female wardress. She took the chair opposite to Wimsey, the wardress withdrew and the door was shut. Wimsey, who had risen, cleared his throat.

<Good afternoon, Miss~Vane,> he said, unimpressively.

The prisoner looked at him.

<Please sit down,> she said, in the curious, deep voice which had attracted him in Court. <You are Lord~Peter Wimsey, I believe, and have come from Mr~Crofts.>

<Yes,> said Wimsey. Her steady gaze was unnerving him. <Yes, I—er—I heard the case and all that, and—er—I thought there might be something I could do, don't you know.>

<That was very good of you,> said the prisoner.

<Not at all, not at all, dash it! I mean to say, I rather enjoy investigating things, if you know what I mean.>

<I know. Being a writer of detective stories, I have naturally studied your career with interest.>

She smiled suddenly at him and his heart turned to water.

<Well, that's rather a good thing in a way, because you'll understand that I'm not really such an ass as I'm looking at present.>

That made her laugh.

<You're not looking an ass—at least, not more so than any gentleman should under the circumstances. The background doesn't altogether suit your style, but you are a very refreshing sight. And I'm really very grateful to you, though I'm afraid I'm rather a hopeless case.>

<Don't say that. It can't be hopeless, unless you actually did it, and I know you didn't.>

<Well, I didn't, as a matter of fact. But I feel it's like one book I wrote, in which I invented such a perfectly water-tight crime that I couldn't devise any way for my detective to prove it, and had to fall back on the murderer's confession.>

<If necessary, we'll do the same. You don't happen to know who the murderer is, I suppose?>

<I don't think there is one. I really believe Philip took the stuff himself. He was rather a defeatist sort of person, you know.>

<I suppose he took your separation pretty hard?>

<Well, I daresay it was partly that. But I think it was more that he didn't feel he was sufficiently appreciated. He was apt to think that people were in league to spoil his chances.>

<And were they?>

<No, I don't think so. But I do think he offended a great many people. He was rather apt to demand things as a right—and that annoys people, you know.>

<Yes, I see. Did he get on all right with his cousin?>

<Oh, yes; though of course he always said it was no more than Mr~Urquhart's duty to look after him. Mr~Urquhart is fairly well off, as he has quite a big professional connection, but Philip really had no claim on him, as it wasn't family money or anything. His idea was that great artists deserved to be boarded and lodged at the expense of the ordinary man.>

Wimsey was fairly well acquainted with this variety of the artistic temperament. He was struck, however, by the tone of the reply, which was tinged, he thought, with bitterness and even some contempt. He put his next question with some hesitation.

<Forgive my asking, but—you were very fond of Philip Boyes?>

<I must have been, mustn't I—under the circumstances?>

<Not necessarily,> said Wimsey, boldly, <you might have been sorry for him—or bewitched by him—or even badgered to death by him.>

<All those things.>

Wimsey considered for a moment.

<Were you friends?>

<No.> The word broke out with a kind of repressed savagery that startled him. <Philip wasn't the sort of man to make a friend of a woman. He wanted devotion. I gave him that. I did, you know. But I couldn't stand being made a fool of. I couldn't stand being put on probation, like an office-boy, to see if I was good enough to be condescended to. I quite thought he was honest when he said he didn't believe in marriage—and then it turned out that it was a test, to see whether my devotion was abject enough. Well, it wasn't. I didn't like having matrimony offered as a bad-conduct prize.>

<I don't blame you,> said Wimsey.

<Don't you?>

<No. It sounds to me as if the fellow was a prig—not to say a bit of a cad. Like that horrid man who pretended to be a landscape-painter and then embarrassed the unfortunate young woman with the burden of an honour unto which she was not born. I've no doubt he made himself perfectly intolerable about it, with his ancient oaks and family plate, and the curtseying tenantry and all the rest of it.>

Harriet Vane laughed once more.

<Yes—it's ridiculous—but humiliating too. Well, there it is. I thought Philip had made both himself and me ridiculous, and the minute I saw that—well, the whole thing simply shut down—flop!>

She sketched a gesture of finality.

<I quite see that,> said Wimsey. <Such a Victorian attitude, too, for a man with advanced ideas. He for God only, she for God in him, and so on. Well, I'm glad you feel like that about it.>

<Are you? It's not going to be exactly helpful in the present crisis.>

<No; I was looking beyond that. What I mean to say is, when all this is over, I want to marry you, if you can put up with me and all that.>

Harriet Vane, who had been smiling at him, frowned, and an indefinable expression of distaste came into her eyes.

<Oh, are you another of them? That makes forty-seven.>

<Forty-seven what?> asked Wimsey, much taken aback.

<Proposals. They come in by every post. I suppose there are a lot of imbeciles who want to marry anybody who's at all notorious.>

<Oh,> said Wimsey. <Dear me, that makes it very awkward. As a matter of fact, you know, I don't need any notoriety. I can get into the papers off my own bat. It's no treat to me. Perhaps I'd better not mention it again.>

His voice sounded hurt, and the girl eyed him rather remorsefully.

<I'm sorry—but one gets rather a bruised sort of feeling in my position. There have been so many beastlinesses.>

<I know,> said Lord~Peter. <It was stupid of me\longdash>

<No, I think it was stupid of me. But why—?>

<Why? Oh, well—I thought you'd be rather an attractive person to marry. That's all. I mean, I sort of took a fancy to you. I can't tell you why. There's no rule about it, you know.>

<I see. Well, it's very nice of you.>

<I wish you wouldn't sound as if you thought it was rather funny. I know I've got a silly face, but I can't help that. As a matter of fact, I'd like somebody I could talk sensibly to, who would make life interesting. And I could give you a lot of plots for your books, if that's any inducement.>

<But you wouldn't want a wife who wrote books, would you?>

<But I should; it would be great fun. So much more interesting than the ordinary kind that is only keen on clothes and people. Though of course, clothes and people are all right too, in moderation. I don't mean to say I object to clothes.>

<And how about the old oaks and the family plate?>

<Oh, you wouldn't be bothered with them. My brother does all that. I collect first editions and incunabula, which is a little tedious of me, but you wouldn't need to bother with them either unless you liked.>

<I don't mean that. What would your family think about it?>

<Oh, my mother's the only one that counts, and she likes you very much from what she's seen of you.>

<So you had me inspected?>

<No—dash it all, I seem to be saying all the wrong things today. I was absolutely stunned that first day in court, and I rushed off to my mater, who's an absolute dear, and the kind of person who really understands things, and I said, <Look here! here's the absolutely one and only woman, and she's being put through a simply ghastly awful business and for God's sake come and hold my hand!> You simply don't know how foul it was.>

<That does sound rather rotten. I'm sorry I was brutal. But, by the way, you're bearing in mind, aren't you, that I've had a lover?>

<Oh, yes. So have I, if it comes to that. In fact, several. It's the sort of thing that might happen to anybody. I can produce quite good testimonials. I'm told I make love rather nicely—only I'm at a disadvantage at the moment. One can't be very convincing at the other end of a table with a bloke looking in at the door.>

<I will take your word for it. But, however entrancing it is to wander unchecked through a garden of bright images, are we not enticing your mind from another subject of almost equal importance? It seems probable\longdash>

<And if you can quote \textit{Kai Lung}, we should certainly get on together.>

<It seems very probable that I shall not survive to make the experiment.>

<Don't be so damned discouraging,> said Wimsey. <I have already carefully explained to you that this time \textit{I} am investigating this business. Anybody would think you had no confidence in me.>

<People have been wrongly condemned before now.>

<Exactly; simply because I wasn't there.>

<I never thought of that.>

<Think of it now. You will find it very beautiful and inspiring. It might even help to distinguish me from the other forty-six, if you should happen to mislay my features, or anything. Oh, by the way—I don't positively repel you or anything like that, do I? Because, if I do, I'll take my name off the waiting-list at once.>

<No,> said Harriet Vane, kindly and a little sadly. <No, you don't repel me.>

<I don't remind you of white slugs or make you go goose-flesh all over?>

<Certainly not.>

<I'm glad of that. Any minor alterations, like parting the old mane, or growing a tooth-brush, or cashiering the eye-glass, you know, I should be happy to undertake, if it suited your ideas.>

<Don't,> said Miss~Vane, <please don't alter yourself in any particular.>

<You really mean that?> Wimsey flushed a little. <I hope it doesn't mean that nothing I could do would make me even passable. I'll come in a different set of garments each time, so as to give you a good all-round idea of the subject. Bunter—my man, you know—will see to that. He has excellent taste in ties, and socks, and things like that. Well, I suppose I ought to be going. You—er—you'll think it over, won't you, if you have a minute to spare. There's no hurry. Only don't hesitate to say if you think you couldn't stick it at any price. I'm not trying to blackmail you into matrimony, you know. I mean, I should investigate this for the fun of the thing, whatever happened, don't you see.>

<It's very good of you\longdash>

<No, no, not at all. It's my hobby. Not proposing to people, I don't mean, but investigating things. Well, cheer-frightfully-ho and all that. And I'll call again, if I may.>

<I will give the footman orders to admit you,> said the prisoner, gravely; <you will always find me at home.>

\divider

Wimsey walked down the dingy street with a feeling of being almost light-headed.

<I do believe I'll pull it off—she's sore, of course—no wonder, after that rotten brute—but she doesn't feel repelled—one couldn't cope with being repulsive—her skin is like honey—she ought to wear deep red—and old garnets—and lots of rings, rather old-fashioned ones—I could take a house, of course—poor kid, I would damn well work to make it up to her—she's got a sense of humour too—brains—one wouldn't be dull—one would wake up, and there'd be a whole day for jolly things to happen in—and then one would come home and go to bed—that would be jolly, too—and while she was writing, I could go out and mess round, so we shouldn't either of us be dull—I wonder if Bunter was right about this suit—it's a little dark, I always think, but the line is good\longdash>

He paused before a shop window to get a surreptitious view of his own reflection. A large coloured window-bill caught his eye:—

\begin{quote}\scshape
Great Special Offer\\ One Month Only
\end{quote}

<Oh, God!> he said softly, sobered at once. <One month—four weeks—thirty-one days. There isn't much time. And I don't know where to begin.>