\chapter[Chapter \thechapter]{}
\lettrine[ante=`]{W}{ell}  now,' said Wimsey, <why do people kill people?>

\zz
He was sitting in Miss~Katharine Climpson's private office. The establishment was ostensibly a typing bureau, and indeed there were three efficient female typists who did very excellent work for authors and men of science from time to time. Apparently the business was a large and flourishing one, for work frequently had to be refused on the ground that the staff was working at full pressure. But on other floors of the building there were other activities. All the employees were women—mostly elderly, but a few still young and attractive—and if the private register in the steel safe had been consulted, it would have been seen that all these women were of the class unkindly known as <superfluous.> There were spinsters with small fixed incomes, or no incomes at all; widows without family; women deserted by peripatetic husbands and living on a restricted alimony, who, previous to their engagement by Miss~Climpson, had had no resources but bridge and boarding-house gossip. There were retired and disappointed school-teachers; out-of-work actresses; courageous people who had failed with hat-shops and tea-parlours; and even a few Bright Young Things, for whom the cocktail-party and the night-club had grown boring. These women seemed to spend most of their time in answering advertisements. Unmarried gentlemen who desired to meet ladies possessed of competences, with a view to matrimony; sprightly sexagenarians, who wanted housekeepers for remote country districts; ingenious gentlemen with financial schemes on the look-out for capital; literary gentlemen, anxious for female collaborators; plausible gentlemen about to engage talent for productions in the provinces; benevolent gentlemen, who could tell people how to make money in their spare time—gentlemen such as these were very liable to receive applications from members of Miss~Climpson's staff. It may have been coincidence that these gentlemen so very often had the misfortune to appear shortly afterwards before the magistrate on charges of fraud, blackmail or attempted procuration, but it is a fact that Miss~Climpson's office boasted a private telephone-line to Scotland Yard, and that few of her ladies were quite so unprotected as they appeared. It is also a fact that the money which paid for the rent and upkeep of the premises might, by zealous enquirers, have been traced to Lord~Peter Wimsey's banking account. His lordship was somewhat reticent about this venture of his, but occasionally, when closeted with Chief-Inspector Parker or other intimate friends, referred to it as <My Cattery.>

Miss~Climpson poured out a cup of tea before replying. She wore a quantity of little bangles on her spare, lace-covered wrists, and they chinked aggressively with every movement.

<I really don't know,> she said, apparently taking the problem as a psychological one, <it is so \emph{dangerous}, as well as so terribly \emph{wicked}, one wonders that anybody has the \emph{effrontery} to undertake it. And very often they gain so \emph{little} by it.>

<That's what I mean,> said Wimsey, <what do they set out to gain? Of course, some people seem to do it for the fun of the thing, like that German female, what's her name, who enjoyed seeing people die.>

<Such a \emph{strange} taste,< said Miss~Climpson. >No sugar, I think?—You know, dear Lord~Peter, it has been my melancholy duty to attend \emph{many} death-beds, and, though a number of them—such as my dear father's—were \emph{most} Christian and beautiful, I could not call them \emph{fun}. People have very different ideas of fun, of course, and personally I have never greatly cared for George Robey, though Charlie Chaplin always makes me laugh—still, you know, there are \emph{disagreeable details} attending \emph{any} death-bed which one would think could hardly be to anybody's taste, however depraved.>

<I quite agree with you,> said Wimsey. <But it must be fun, in one sense, to feel that you can control the issues of life and death, don't you know.>

<That is an \emph{infringement} upon the prerogative of the Creator,> said Miss~Climpson.

<But rather jolly to know yourself divine, so to speak. Up above the world so high, like a tea-tray in the sky. I admit the fascination. But for practical purposes that theory is the devil—I beg your pardon, Miss~Climpson, respect for sacred personages—I mean, it's unsatisfactory, because it would suit one person just as well as another. If I've got to find a homicidal maniac, I may as well cut my throat at once.>

<Don't say \emph{that},> pleaded Miss~Climpson, <even in jest. Your work here—so good, so valuable—would be worth living for in spite of the \emph{saddest} personal disappointments. And I have known jokes of that kind turn out very badly, in the most surprising ways. There was a young man we used to know, who was given to talking in a sadly \emph{random} way—a long time ago, dear Lord~Peter, while you were still in the nursery, but young men were wild, even then, whatever they say now about the 'eighties—and he said one day to my poor, dear Mother, <Mrs~Climpson, if I don't make a good bag today, I shall shoot myself> (for he was very fond of sport), and he went out with his gun and as he was getting over a stile, he caught the trigger in the hedge and the gun went off and blew his head to pieces. I was quite a girl, and it upset me \emph{dreadfully}, because he was a very handsome young man, with whiskers which we all admired very much, though today they would be smiled at, and they were burnt \emph{right off} him with the explosion, and a shocking hole in the side of his head, so they said, for of course I was not allowed to see him.>

<Poor chap,> said his lordship. <Well, let's dismiss homicidal mania from our minds for the moment. What else do people kill people for?>

<There is—passion,> said Miss~Climpson, with a slight initial hesitation at the word, <for I should not like to call it \emph{love}, when it is so unregulated.>

<That is the explanation put forward by the prosecution,> said Wimsey. <I don't accept it.>

<Certainly not. But—it might be possible, might it not, that there was some other unfortunate young woman who was attached to this Mr~Boyes, and felt vindictively towards him?>

<Yes, or a man who was jealous. But the time is the difficulty. You've got to have some plausible pretext for giving a bloke arsenic. You can't just catch him standing on a doorstep, and say, <Here, have a drink of this,> can you?>

<But there were ten minutes unaccounted for,> said Miss~Climpson, shrewdly. <Might he not have entered some public-house for refreshment, and there met an enemy?>

<By jove, that's a possibility.> Wimsey made a note, and shook his head dubiously. <But it's rather a coincidence. Unless there was a previous appointment to meet there. Still, it's worth looking into. At any rate, it's obvious that Mr~Urquhart's house and Miss~Vane's flat were not the only conceivable places where Boyes might have eaten or drunk between seven and 10.10 that evening. Very well: under the head <Passion> we find ⑴ Miss~Vane (ruled out ex hypothesi), ⑵ jealous lover, ⑶ ditto rival. Place, Public-house (query). Now we go on to the next motive, and that's Money. A very good motive for murdering anybody who has any, but a poor one in Boyes' case. Still, let us say, Money. I can think of three sub-headings for that: ⑴ Robbery from the person (very improbable); ⑵ insurance; ⑶ inheritance.>

<What a clear mind you have,> said Miss~Climpson.

<When I die you will find <Efficiency> written on my heart. I don't know what money Boyes had on him, but I shouldn't think it was much. Urquhart and Vaughan might know; still, it's not very important, because arsenic isn't a sensible drug to use on anyone you want to rob. It takes a long time, comparatively, to begin business, and it doesn't make the victim helpless enough. Unless we suppose the taxi-driver drugged and robbed him, there was no one who could possibly profit by such a silly crime.>

Miss~Climpson agreed, and buttered a second tea-cake.

<Then, insurance. Now we come to the region of the possible. Was Boyes insured? It doesn't seem to have occurred to anybody to find out. Probably he wasn't. Literary blokes have very little forethought, and are careless about trifles like premiums. But one ought to know. Who might have an insurable interest? His father, his cousin (possibly), other relations (if any), his children (if any) and—I suppose—Miss~Vane, if he took out the policy while he was living with her. Also, anybody who may have lent him money on the strength of such insurance. Plenty of possibilities there. I'm feeling better already, Miss~Climpson, fitter and brighter in every way. Either I'm getting a line on the thing, or else it's your tea. That's a good, stout-looking pot. Has it got any more in it?>

<Yes, indeed,> said Miss~Climpson, eagerly. <My dear father used to say I was a great hand at getting the \emph{utmost} out of a tea-pot. The secret is to \emph{fill} up as you \emph{go} and never empty the pot completely.>

<Inheritance,> pursued Lord~Peter. <Had he anything to leave? Not much, I shouldn't think. I'd better hop round and see his publisher. Or had he lately come into anything? His father or cousin would know. The father is a parson—<slashing trade, that,> as the naughty bully says to the new boy in one of Dean Farrar's books. He has a thread-bare look. I shouldn't think there was much money in the family. Still, you never know. Somebody might have left Boyes a fortune for his \binderyfrench{beaux yeux} or out of admiration for his books. If so, to whom did Boyes leave it? Query: did he make a will? But surely the defence must have thought of these things. I am getting depressed again.>

<Have a sandwich,> said Miss~Climpson.

<Thank you,> said Wimsey, <or some hay. There is nothing like it when you are feeling faint, as the White King truly remarked. Well, that more or less disposes of the money motive. There remains Blackmail.>

Miss~Climpson, whose professional connection with the Cattery had taught her something about blackmail, assented with a sigh.

<Who was this fellow Boyes?> enquired Wimsey rhetorically. <I know nothing about him. He may have been a blackguard of the deepest dye. He may have known unmentionable things about all his friends. Why not? Or he may have been writing a book to show somebody up, so that he had to be suppressed at all costs. Dash it all, his cousin's a solicitor. Suppose he has been embezzling Trust deeds or something, and Boyes was threatening to split on him? He'd been living in Urquhart's house, and had every opportunity for finding out. Urquhart drops some arsenic into his soup, and—Ah! there's the snag. He puts arsenic into the soup and eats it himself. That's awkward. I'm afraid Hannah Westlock's evidence rather knocks that on the head. We shall have to fall back on the mysterious stranger in the pub.>

He considered a little, and then said:

<And there's suicide, of course, which is what I'm really rather inclined to believe in. Arsenic is tomfool stuff to commit suicide with, but it has been done. There was the duc de Praslin, for instance—if his \emph{was} suicide. Only, where's the bottle?>

<The bottle?>

<Well, he must have carried it in something. It might be in a paper, if he took the powdered form, though that would be awkward. Did anybody look for a bottle or paper?>

<Where would they look for it?> asked Miss~Climpson.

<That's the rub. If it wasn't on him, it would be anywhere round about Doughty Street, and it's going to be a job looking for a bottle or paper that was chucked away six months ago. I do loathe suicides—they're so difficult to prove. Oh, well, faint heart never won so much as a scrap of paper. Now look here, Miss~Climpson. We've got about a month to work this out in. The Michaelmas Term ends on the 21st; this is the 15th. They can't very well bring it up before then, and the Hilary term starts on January 12th. They'll probably take it early, unless we can show reason for delay. Four weeks to get fresh evidence. Will you reserve the best efforts of yourself and the staff? I don't know yet what I shall want, but I shall probably want something done.>

<Of course I will, Lord~Peter. You know that it is only \emph{too} great a pleasure to do \emph{anything} for you—even if the whole office were not your own property, which it \emph{is}. Only let me know, at \emph{any} minute of the night or day, and I will do my \emph{very} best to help you.>

Wimsey thanked her, made a few enquiries about the work of the bureau and departed. He hailed a taxi and was immediately driven to Scotland Yard.

\divider

Chief Detective-Inspector Parker was, as usual, delighted to see Lord~Peter, but there was a worried expression on his plain though pleasant face as he greeted his visitor.

<What is it, Peter? The Vane case again?>

<Yes. You've come a mucker over this, old man, you really have.>

<Well, I don't know. It looked pretty straightforward to us.>

<Charles, acushla, distrust the straightforward case, the man who looks you straight in the eyes, and the tip straight from the horse's mouth. Only the most guileful deceiver can afford to be so aggressively straight. Even the path of the light is curved—or so they tell us. For God's sake, old man, do what you can to put the thing right before next assizes. If you don't, I'll never forgive you. Damn it, you don't \emph{want} to hang the wrong person, do you?—especially a woman and all that.>

<Have a fag,> said Parker. <You're looking quite wild about the eyes. What have you been doing with yourself? I'm sorry if we've got the wrong pig by the ear, but it's the defence's business to point out where we're wrong, and I can't say they put up a very convincing show.>

<No, confound them. Biggy did his best, but that fool and beast Crofts gave him no materials at all. Blast his ugly eyes! I know the brute thinks she did it. I hope he will fry in hell and be served up with cayenne pepper on a red-hot dish!>

<What eloquence!> said Parker, unimpressed. <Anybody would think you'd gone goopy over the girl.>

<That's a damned friendly way to talk,> said Wimsey, bitterly. <When you went off the deep end about my sister, I may have been unsympathetic—I daresay I was—but I swear I didn't dance on your tenderest feelings and call your manly devotion <going goopy over a girl.> I don't know where you pick up such expressions, as the clergyman's wife said to the parrot. <Goopy,> indeed! I never heard anything so vulgar!>

<Good lord,> exclaimed Parker, <you don't seriously say\longdash>

<Oh, no!> retorted Wimsey, bitterly. <I'm not expected to be serious. A buffoon, that's what I am. I now know exactly what Jack Point feels like. I used to think the <Yeomen> sentimental tosh, but it is all too true. Would you like to see me dance in motley?>

<I'm sorry,> said Parker, taking his cue rather from the tone than the words. <If it's like that, I'm damned sorry, old man. But what can I do?>

<Now you're talking. Look here—the most likely thing is that this unsavoury blighter Boyes committed suicide. The unspeakable defence haven't been able to trace any arsenic to his possession—but then they probably couldn't trace a herd of black cattle over a snow-bound field in broad noon-day with a microscope. I want your people to take it up.>

<Boyes—query arsenic,> said Parker, making a note on a pad. <Anything else?>

<Yes. Find out if Boyes visited any pub. in the neighbourhood of Doughty Street between, say, 9.50 and 10.10 on the night of June 20th—if he met anybody, and what he took to drink.>

<It shall be done. Boyes—query pub.> Parker made another note. <Yes?>

<Thirdly, if any bottle or paper that might have contained arsenic was picked up in that district.>

<Oh, indeed? And would you like me to trace the 'bus ticket dropped by Mrs~Brown outside Selfridge's in the last Christmas rush? No use making it too easy.>

<A bottle is more likely than a paper,> went on Wimsey, ignoring him, <because I think the arsenic must have been taken in liquid form to work so quickly.>

Parker made no further protest, but noted down <Boyes—Doughty Street—query bottle,> and paused expectantly.

<Yes?>

<That's all for the moment. By the way, I should try the garden in Mecklenburgh Square. A thing might lie quite a long time under those bushes.>

<Very well. I'll do my best. And if you find out anything which really proves that we've been on the wrong tack, you'll let us know, won't you? We don't want to make large and ignominious public mistakes.>

<Well—I've just earnestly promised the defence that I'll do no such thing. But if I spot the criminal, I'll let you arrest him.>

<Thanks for small mercies. Well, good luck! Funny for you and me to be on opposite sides, isn't it?>

<Very,> said Wimsey. <I'm sorry about it, but it's your own fault.>

<You shouldn't have been out of England. By the way\longdash>

<Yes?>

<You realise that probably all our young friend did during those missing ten minutes was to stand about in Theobalds Road or somewhere, looking for a stray taxi.>

<Oh, shut up!> said Wimsey, crossly, and went out.