\chapter[Chapter \thechapter]{}
\lettrine{L}{ord} Peter Wimsey almost bounced into Holloway Prison next morning. Harriet Vane greeted him with a kind of rueful smile.

\zz
<So you've reappeared?>

\zz
<Good lord, yes! Surely you expected me to. I fancied I'd left that impression. I say—I've thought of a good plot for a detective story.>

<Really?>

<Top-hole. You know, the sort people bring out and say, <I've often thought of doing it myself, if I could only find time to sit down and write it.> I gather that sitting down is all that is necessary for producing masterpieces. Just a moment, though. I must get through my business first. Let me see\longdash> He made believe to consult a note-book. <Ah, yes. Do you happen to know whether Philip Boyes made a will?>

<I believe he did, when we were living together.>

<In whose favour?>

<Oh, in mine. Not that he had much to leave, poor man. It was chiefly that he wanted a literary executor.>

<Are you, in point of fact, his executrix now?>

<Good heavens! I never thought of that. I took it for granted he would have altered it when we parted. I think he must have, or I should have heard about it when he died, shouldn't I?>

She looked candidly at him, and Wimsey felt a little uncomfortable.

<You didn't \emph{know} he had altered it, then? Before he died, I mean?>

<I never thought a word more about it, as a matter of fact. If I had thought—of course I should have assumed it. Why?>

<Nothing,> said Wimsey. <Only I'm rather glad the will wasn't brought up at the thingummy bob.>

<Meaning the trial? You needn't be so delicate about mentioning it. You mean, if I had thought I was still his heir, I might have murdered him for his money. But it didn't amount to a hill of beans, you know. I was making four times as much as he was.>

<Oh, yes. It was only this silly plot I'd got in my mind. But it \emph{is} rather silly, now I come to think of it.>

<Tell me.>

<Well, you see\longdash> Wimsey choked a little, and then rattled his idea out with an exaggerated lightness.

<Well—it's about a girl (or a man would do, but we'll call it a girl) who writes novels—crime stories, in fact. And she has a—a friend who also writes. Neither of them best-sellers, you see, but just ordinary novelists.>

<Yes? That's a kind of thing that might happen.>

<And the friend makes a will, leaving his money—receipts from books and so on—to the girl.>

<I see.>

<And the girl—who has got rather fed up with him, you know, thinks of a grand scoop, that will make both of them best-sellers.>

<Oh, yes?>

<Yes. She polishes him off by the same method she has used in her latest crime-thriller.>

<A daring stroke,> said Miss~Vane, with grave approval.

<Yes. And of course, his books immediately become best-sellers. And she grabs the pool.>

<That's really ingenious. An entirely new motive for murder—the thing I've been looking for for years. But don't you think it would be a little dangerous? She might even be suspected of the murder.>

<Then \emph{her} books would become best-sellers, too.>

<How true that is! But possibly she wouldn't live to enjoy the profits.>

<That, of course,> said Wimsey, <is the snag.>

<Because, unless she were suspected and arrested and tried, the scoop would only half come off.>

<There you are,> said Wimsey. <But, as an experienced mystery-monger, couldn't you think of a way round that?>

<I daresay. She might prove an ingenious alibi, for instance. Or, if she were very wicked, manage to push the blame on somebody else. Or lead people to suppose that her friend had made away with himself.>

<Too vague,> said Wimsey. <How would she do that?>

<I can't say, off-hand. I'll give it careful thought and let you know. Or—here's an idea!>

<Yes?>

<She is a person with a monomania—no, no—not a homicidal one. That's dull, and not really fair to the reader. But there is somebody she wishes to benefit—somebody, say a father, mother, sister, lover or cause, that badly needs money. She makes a will in his, her or its favour, and lets herself be hanged for the crime, knowing that the beloved object will then come in for the money. How's that?>

<Great!> cried Wimsey, carried away. <Only—wait a minute. They wouldn't give her the friend's money, would they? You're not allowed to profit by a crime.>

<Oh, hang! That's true. It would only be her own money, then. She could make that over by a deed of gift. Yes—look! If she did that immediately after the murder—a deed of gift of everything she possessed—that would include everything she came into under the friend's will. It would then all go direct to the beloved object, and I don't believe the law could stop it!>

She faced him with dancing eyes.

<See here,> said Wimsey. <You're not safe. You're too clever by half. But, I say, it's a good plot, isn't it?>

<It's a winner! Shall we write it?>

<By jove, let's!>

<Only, you know, I'm afraid we shan't get the chance.>

<You're not to say that. Of course we're going to write it. Damn it, what am I here for? Even if I could be reconciled to losing you, I couldn't lose the chance of writing my best-seller!>

<But what you've done so far is to provide me with a very convincing motive for murder. I don't know that that's going to help us a great lot.>

<What I've done,> said Wimsey, <is to prove that that was not the motive, anyway.>

<Why?>

<You wouldn't have told me if it had been. You would have gently led me away from the subject. And besides\longdash>

<Well?>

<Well, I've seen Mr~Cole of Grimsby \& Cole, and I know who is going to get the major part of Philip Boyes' profits. And I don't somehow fancy that he is the beloved object.>

<No?> said Miss~Vane, <and why not? Don't you know that I passionately dote on every chin on his face?>

<If it's chins you admire,> said Wimsey, <I will try to grow some, though it will be rather hard work. Anyway, keep smiling—it suits you.>

\divider

<It's all very well, though,> he thought to himself, when the gates had closed behind him. <Bright back-chat cheers the patient, but gets us no forrarder. How about this fellow Urquhart? He looked all right in court, but you never can tell. I think I'd better pop round and see him.>

He presented himself accordingly in Woburn Square, but was disappointed. Mr~Urquhart had been called away to a sick relative. It was not Hannah Westlock who answered the door, but a stout elderly woman, whom Wimsey supposed to be the cook. He would have liked to question her, but felt that Mr~Urquhart would hardly receive him well if he discovered that his servants had been pumped behind his back. He therefore contented himself with enquiring how long Mr~Urquhart was likely to be away.

<I couldn't rightly say, sir. I understand it depends how the sick lady gets on. If she gets over it, he'll be back at once, for I know he is very busy just now. If she should pass away, he would be engaged some time, with settling up the estate.>

<I see,> said Wimsey. <It's a bit awkward, because I wanted to speak to him rather urgently. You couldn't give me his address, by any chance?>

<Well, sir, I don't rightly know if Mr~Urquhart would wish it. If it's a matter of business, sir, they could give you information at his office in Bedford Row.>

<Thanks very much,> said Wimsey, noting down the number. <I'll call there. Possibly they'd be able to do what I want without bothering him.>

<Yes, sir. Who should I say called?>

Wimsey handed over his card, writing at the top, <In re R. v. Vane,> and added:

<But there is a chance he may be back quite soon?>

<Oh, yes, sir. Last time he wasn't away more than a couple of days, and a merciful providence I am sure that was, with poor Mr~Boyes dying in that dreadful manner.>

<Yes, indeed,> said Wimsey, delighted to find the subject introducing itself of its own accord. <That must have been a shocking upset for you all.>

<Well, there,> said the cook, <I don't hardly like to think of it, even now. A gentleman dying in the house like that, and poisoned too, when one's had the cooking of his dinner—it do seem to bring it home to one, like.>

<It wasn't the dinner that was at fault, anyway,> said Wimsey, genially.

<Oh, dear, no, sir—we proved that most careful. Not that any accident could happen in my kitchen—I should like to see it! But people do say such things if they get half a chance. Still, there wasn't a thing ate but master and Hannah and I had some of it, and very thankful I was for that, I needn't tell you.>

<You must be; I am sure.> Wimsey was framing a further enquiry, when the violent ringing of the area bell interrupted them.

<There's that butcher,> said the cook, <you'll excuse me, sir. The parlour-maid's in bed with the influenza, and I'm single-handed this morning. I'll tell Mr~Urquhart you called.>

She shut the door, and Wimsey departed for Bedford Row, where he was received by an elderly clerk, who made no difficulty about supplying Mr~Urquhart's address.

<Here it is, my lord. Care of Mrs~Wrayburn, Appleford, Windle, Westmorland. But I shouldn't think he would be very long away. In the meantime, could we do anything for you?>

<No, thanks. I rather wanted to see him personally, don't you know. As a matter of fact, it's about that very sad death of his cousin, Mr~Philip Boyes.>

<Indeed, my lord? Shocking affair, that. Mr~Urquhart was greatly upset, with it happening in his own house. A very fine young man, was Mr~Boyes. He and Mr~Urquhart were great friends, and he took it greatly to heart. Were you present at the trial, my lord?>

<Yes. What did you think of the verdict?>

The clerk pursed up his lips.

<I don't mind saying I was surprised. It seemed to me a very clear case. But juries are very unreliable, especially now-a-days, with women on them. We see a good deal of the fair sex in this profession,> said the clerk, with a sly smile, <and very few of them are remarkable for possessing the legal mind.>

<How true that is,> said Wimsey. <If it wasn't for them, though, there'd be much less litigation, so it's all good for business.>

<Ha, ha! Very good, my lord. Well, we have to take things as they come, but in my opinion—I'm an old-fashioned man—the ladies were most adorable when they adorned and inspired and did not take an active part in affairs. Here's our young lady clerk—I don't say she wasn't a good worker—but a whim comes over her and away she goes to get married, leaving me in the lurch, just when Mr~Urquhart is away. Now, with a young man, marriage steadies him, and makes him stick closer to his job, but with a young woman, it's the other way about. It's right she should get married, but it's inconvenient, and in a solicitor's office one can't get temporary assistance very well. Some of the work is confidential, of course, and in any case, an atmosphere of permanence is desirable.>

Wimsey sympathised with the head-clerk's grievance, and bade him an affable good-morning. There is a telephone box in Bedford Row, and he darted into it and immediately rang up Miss~Climpson.

<Lord~Peter Wimsey speaking—oh, hullo, Miss~Climpson! How is everything? All bright and beautiful? Good!—Yes, now listen. There's a vacancy for a confidential female clerk at Mr~Norman Urquhart's, the solicitor's, in Bedford Row—Have you got anybody?—Oh, good!—Yes, send them all along—I particularly want to get someone in there—Oh, no! no special enquiry—just to pick up any gossip about the Vane business—Yes, pick out the steadiest-looking, not too much face-powder, and see that their skirts are the regulation four inches below the knee—the head-clerk's in charge, and the last girl left to be married, so he's feeling anti-sex-appeal. Right-ho! Get her in and I'll give her her instructions. Bless you, may your shadow never grow bulkier!>