\chapter[Chapter \thechapter]{}
\lettrine{B}{y} what ingratiating means Mr~Bunter had contrived to turn the delivery of a note into the acceptance of an invitation to tea was best known to himself. At half-past four on the day which ended so cheerfully for Lord~Peter, he was seated in the kitchen of Mr~Urquhart's house, toasting crumpets. He had been trained to a great pitch of dexterity in the preparation of crumpets, and if he was somewhat lavish in the matter of butter, that hurt nobody except Mr~Urquhart. It was natural that the conversation should turn to the subject of murder. Nothing goes so well with a hot fire and buttered crumpets as a wet day without and a good dose of comfortable horrors within. The heavier the lashing of the rain and the ghastlier the details, the better the flavour seems to be. On the present occasion, all the ingredients of an enjoyable party were present in full force.

<'Orrible white, he looked, when he came in,> said Mrs~Pettican the cook. <I see him when they sent for me to bring up the 'ot bottles. Three of them, they 'ad, one to his feet and one to his back and the big rubber one to 'is stummick. White and shiverin', he was, and that dreadful sick, you never would believe. And he groaned pitiful.>

<Green, he looked to me, Cook,> said Hannah Westlock, <or you might perhaps call it a greenish-yellow. I thought it was jaundice a-coming on—more like them attacks he had in the Spring.>

<He was a bad colour then,> agreed Mrs~Pettican, <but nothink like to what he was that last time. And the pains and cramps in his legs was agonising. That struck Nurse Williams very forcible—a nice young woman she was, and not stuck-up like some as I could name. <Mrs~Pettican,> she said to me, which I call it better manners than callin' you Cook as they mostly do, as though they paid your wages for the right of callin' you out of your name—<Mrs~Pettican,> said she, <never did I see anythink to equal them cramps except in one other case that was the dead spit of this one,> she said, <and you mark my words, Mrs~Pettican, them cramps ain't there for nothin'.> Ah! little did I understand her meanin' at the time.>

<That's a regular feature of these arsenical cases, or so his lordship tells me,> replied Bunter. <A very distressing symptom. Had he ever had anything of the sort before?>

<Not what you could call cramps,> said Hannah, <though I remember when he was ill in the Spring he complained of getting the fidgets in the hands and feet. Something like pins-and-needles, by what I understood him to say. It was a worrit to him, because he was finishing one of his articles in a hurry, and what with that and his eyes being so bad, the writing was a trial to him, poor thing.>

<From what the gentleman for the prosecution said, talking it out with Sir~James Lubbock,> said Mr~Bunter, <I gathered that those pins-and-needles, and bad eyes and so on, were a sign he'd been given arsenic regularly, if I may so phrase it.>

<A dreadful wicked woman she must <a> been,> said Mrs~Pettican, <—'ev another crumpet, do, Mr~Bunter—a-torturin' of the poor soul that long-winded way. Bashin' on the <ed or the 'asty use of a carvin> knife when roused I can understand, but the <orrors of slow poisonin> is the work of a fiend in 'uman form, in my opinion.>

<Fiend is the only word, Mrs~Pettican,> agreed the visitor.

<And the wickedness of it,> said Hannah, <quite apart from the causing of a painful death to a fellow-being. Why, it's only the mercy of Providence we weren't all brought under suspicion.>

<Yes, indeed,> said Mrs~Pettican. <Why, when master told us about them diggin' poor Mr~Boyes up and findin' him full of that there nasty arsenic, it give me sech a turn, I felt as if the room was a-goin' round like the gallopin' 'orses at the roundabouts. <Oh, sir!> I ses, <what, in our 'ouse!> That's what I ses, and he ses, <Mrs~Pettican,> he ses, <I sincerely hope not.>>

Mrs~Pettican, having imparted this Macbeth-like flavour to the story, was pleased with it, and added:

<Yes, that's what I said to 'im. <In our 'ouse.> I said, and I'm sure I never slep' a wink for three nights afterwards, what with the police and the fright and one thing and another.>

<But of course you had no difficulty in proving that it hadn't happened in this house?> suggested Bunter. <Miss~Westlock gave her evidence so beautifully at the trial, I'm sure she made it clear as clear could be to judge and jury. The judge congratulated you, Miss~Westlock, and I'm sure he didn't say nearly enough—so plainly and well as you spoke up before the whole court.>

<Well, I never was one to be shy,> confessed Hannah, <and then, what with going through it all so careful with the master and then with the police, I knew what the questions would be and was prepared, as you might say.>

<I wonder you could speak so exactly to every little detail, all that time ago,> said Bunter, with admiration.

<Well, you see, Mr~Bunter, the very morning after Mr~Boyes was took ill, master comes down to us and he says, sitting in that chair ever so friendly, just as you might be yourself, <I'm afraid Mr~Boyes is very ill,> he says. <He thinks he must have ate something as disagreed with him,> he says, <and perhaps as it might be the chicken. So I want you and Cook,> he says, <to run through with me everything we had for dinner last night to see if we can think what it could have been.> <Well, sir,> I said, <I don't see that Mr~Boyes could have ate anything unwholesome here, for Cook and me had just the same, put aside yourself, sir, and it was all as sweet and good as it could be,> I said.>

<And I said the same,> said the Cook. <Sech a plain, simple dinner as it was, too—no oysters nor mussels nor anything of that sort, as it's well known shell-fish is poison to some people's stummicks, but a good stren'thenin' drop o' soup, and a bit of nice fish and a casseroled chicken with turnips and carrots done in the gravy, and a omelette, wot could be lighter and better? Not but there's people as can't relish eggs in any form, my own mother was just the same, give her so much as a cake what had bin made with a egg in it and she'd be that sick and come out all over spots like nettle-rash, you'd be surprised. But Mr~Boyes was a great gentleman for eggs, and omelettes was his particular favourite.>

<Yes, he made the omelette himself that very night, didn't he?>

<He did,> said Hannah, <and well I remember it, for Mr~Urquhart asked particular after the eggs, was they new-laid, and I reminded him they was some he had brought in himself that afternoon from that shop on the corner of Lamb's Conduit Street where they always have them fresh from the farm, and I reminded him that one of them was a little cracked and he'd said, <We'll use that in the omelette tonight, Hannah,> and I brought out a clean bowl from the kitchen and put them straight in—the cracked one and three more besides, and never touched them again till I brought them to table. <And what's more, sir,> I said, <there's the other eight still here out of the dozen, and you can see for yourself they're as good and fresh as they can be.> Didn't I, Cook?>

<Yes, Hannah. And as for the chicken, that was a little beauty. It was that young and tender, I says to Hannah at the time as it seemed a shame to casserole it, for it would 'ave roasted beautiful. But Mr~Urquhart is very partial to a casseroled chicken; he says as there's more flavour to 'em that way, and I dunno but what he's right.>

<If done with a good beef stock,> pronounced Mr~Bunter, judicially, <the vegetables well packed in layers, on a foundation of bacon, not too fat, and the whole well seasoned with salt, pepper and paprika, there are few dishes to beat a casseroled chicken. For my own part I would recommend a soupçon of garlic, but I am aware that such is not agreeable to all tastes.>

<I can't a-bear the smell or sight of the stuff,> said Mrs~Pettican, frankly, <but as for the rest I'm with you, always allowing that the giblets is added to the stock, and I would personally favour mushrooms when in season, but not them tinned or bottled sorts as looks pretty but has no more taste to 'em than boot-buttons if so much. But the secret is in the cooking, as you know well, Mr~Bunter, the lid being kep' well sealed down to 'old the flavour and the cookin' bein' slow to make the juices perambulate through \emph{and} through each other as you might say. I'm not denyin' as sech is very 'ighly enjoyable, and so Hannah and me found it, though fond of a good roast fowl also, when well-basted with a good rich stuffing to rejuice the dryness. But as to roasting it, Mr~Urquhart wouldn't hear of it, and bein' as it's him that pays the bills, he has the right to give his orders.>

<Well,> said Bunter, <it's certain if there had been anything unwholesome about the casserole, you and Miss~Westlock could scarcely have escaped it.>

<No, indeed,> said Hannah, <for I won't conceal that, being blessed with hearty appetites, we finished it every bit, except a little piece I gave to the cat. Mr~Urquhart asked to see the remains of it next day, and seemed quite put out to find it was all gone and the dish washed up—as though any washing-up was ever left over-night in \emph{this} kitchen.>

<I couldn't a-bear myself if I had to begin the day with dirty dishes,> said Mrs~Pettican. <There was a drop of the soup left—not much, jest a wee drain, and Mr~Urquhart took that up to show to the doctor, and he tasted it and said it was very good, so Nurse Williams told us, though she didn't have none of it herself.>

<And as for the burgundy,> said Hannah Westlock, <which was the only thing Mr~Boyes had to himself, like, Mr~Urquhart told me to cork it up tight and keep it. And just as well we did, because, of course, the police asked to see it when the time came.>

<It was very far-seeing of Mr~Urquhart to take such precautions,> said Bunter, <when there wasn't any thought at the time but that the poor man died naturally.>

<That's what Nurse Williams said,> replied Hannah, <but we put it down to him being a solicitor and knowing what ought to be done in a case of sudden death. Very particular he was, too—got me to put a bit of sticking-plaster over the mouth of the bottle and write my initials on it, so that it shouldn't be opened accidental. Nurse Williams always said he expected an inquest, but Dr~Weare being there to speak to Mr~Boyes having had these kind of bilious attacks all his life, of course there was no question raised about giving the certificate.>

<Of course not,> said Bunter, <but it's very fortunate as it turns out that Mr~Urquhart should have understood his duty so well. Many's the case his lordship has seen in which an innocent man has been brought near to the gallows for lack of a simple little precaution like that.>

<And when I think how near Mr~Urquhart was to being away from 'ome at the time,> said Mrs~Pettican, <the thought fair gives me palpitations. Called away, he was, to that tiresome old woman what's always a-dying and never dies. Why, he's there now—Mrs~Wrayburn, up in Windle. Rich as Sneezes, she is, by all accounts, and no good to nobody, for she's gone quite childish, so they say. A wicked old woman she was, too, in 'er day, and 'er other relations wouldn't 'ave nothink to do with 'er, only Mr~Urquhart, and I don't suppose 'e wouldn't, neither, only 'e's her solicitor and it's his duty so to do.>

<Duty does not always lie in pleasant places,> commented Mr~Bunter, <as you and I well know, Mrs~Pettican.>

<Them that are rich,> said Hannah Westlock, <find no difficulty about getting their duties performed for them. Which I will make bold to say, Mrs~Wrayburn would not have done if she had been poor, great-aunt or no great-aunt, knowing Mr~Urquhart.>

<Ah!> said Bunter.

<I pass no comments,> said Miss~Westlock, <but you and me, Mr~Bunter, know how the world goes.>

<I suppose Mr~Urquhart stands to gain something when the old woman does peg out,> suggested Bunter.

<That's as may be; he's not a talker,> said Hannah, <but it stands to reason he wouldn't be always giving up his time and tearing off to Westmorland for nothing. Though I wouldn't care myself to put my hand to money that's wickedly come by. It would not bring a blessing with it, Mr~Bunter.>

<It's easy talking, my girl, when you ain't likely to be put in the way of temptation,> said Mrs~Pettican. <There's many great families in the Kingdom what never would a bin 'eard of if somebody 'adn't bin a little easier in their ways than what we've bin brought up to. There's skelintons in a many cupboards if the truth was known.>

<Ah!> said Bunter, <I believe you. I've seen diamond necklaces and fur coats that should have been labelled Wages of Sin if deeds done in the dark were to be proclaimed upon the house-tops, Mrs~Pettican. And there are families that hold their heads high that wouldn't ever have existed but for some king or other taking his amusements on the wrong side of the blanket as the old saying goes.>

<They say as some that was high up wasn't too high to take notice of old Mrs~Wrayburn in her young days,> said Hannah, darkly. <Queen Victoria wouldn't never allow her to act before the Royal Family—she knew too much about her goings-on.>

<An actress, was she?>

<And a very beautiful one, they say, though I can't rightly recollect what her stage name was,> mused Mrs~Pettican. <It was a queer one, I know—'Yde Park, or somethink of that. This Wrayburn as she married, 'e was nobody—jest to kiver up the scandal that's what she married 'im for. Two children she 'ad—but 'ose I would not take it upon me to say—and they both died in the cholera, which no doubt it was a judgment.>

<That's not what Mr~Boyes called it,> said Hannah, with a self-righteous sniff. <The devil took care of his own, that was his way of putting it.>

<Ah! he talked careless,> said Mrs~Pettican, <and no wonder, seeing the folks he lived with. But he'd a sobered down in time if he'd bin spared. A very pleasant way he 'ad with 'im when 'e liked. Come in here, he would, and chat upon one thing and another, very amusing-like.>

<You're too soft with the gentlemen, Mrs~Pettican,> said Hannah. <Anyone as has taking ways and poor health is ewe-lambs to you.>

<So Mr~Boyes knew all about Mrs~Wrayburn?>

<Oh, yes—it was all in the family, you see, and no doubt Mr~Urquhart would a told him more than he'd say to us. Which train did Mr~Urquhart say he was a-comin' by, Hannah?>

<He said dinner for half-past seven. That'll be the six-thirty, I should think.>

Mrs~Pettican glanced at the clock and Bunter, taking this as a hint, rose and made his farewells.

<And I 'opes as you'll come again, Mr~Bunter,> said the Cook, graciously. <The master makes no objections to respectable gentlemen visitors at tea-time. Wednesday is my 'arf-day.>

<Mine is Friday,> added Hannah, <and every other Sunday. If you should be Evangelical, Mr~Bunter, the Rev. Crawford in Judd Street is a beautiful preacher. But maybe you'll be going out of town for Christmas.>

Mr~Bunter replied that that season would undoubtedly be spent at Duke's Denver, and departed in a shining halo of vicarious splendour.