\chapter[Chapter \thechapter]{}
\lettrine[ante=`]{H}{ere}  you are, Peter,' said Chief-Inspector Parker, <and here is the lady you are anxious to meet. Mrs~Bulfinch, allow me to introduce Lord~Peter Wimsey.>

\zz
<Pleased, I am sure,> said Mrs~Bulfinch. She giggled, and dabbed her large, blonde face with powder.

<Mrs~Bulfinch, before her union with Mr~Bulfinch, was the life and soul of the saloon bar at the Nine Rings in Grays Inn Road,> said Mr~Parker, <and well-known to all for her charm and wit.>

<Go on,> said Mrs~Bulfinch, <you're a one, aren't you? Don't you pay no attention to him, your lordship. You know what these police fellows are.>

<Sad dogs,> said Wimsey, shaking his head. <But I don't need his testimonials, I can trust my own eyes and ears, Mrs~Bulfinch, and I can only say that, if I had had the happiness to make your acquaintance before it was too late, it would have been my life-time's ambition to wipe Mr~Bulfinch's eye.>

<You're every bit as bad as he is,> said Mrs~Bulfinch, highly gratified, <and what Bulfinch would say to you I \textit{don't} know. Quite upset, he was, when the officer came round to ask me to pop along to the Yard. <I don't like it, Gracie,> he says, <we've always bin respectable in this house and no trouble with disorderlies nor drinks after hours, and once you get among them fellows you don't know the things you may be asked.> <Don't be so soft,> I tells him, <the boys all know me and they haven't got nothing against me, and if it's just to tell them about the gentleman that left the packet behind him at the Rings, I haven't no objection to tell them, having nothing to reproach myself with. What'd they think,> I said, <if I refused to go? Ten to one they'd think there was something funny about it.> <Well,> he says, <I'm coming with you.> <Oh, are you?> I says, <and how about the new barman you was going to engage this morning? For,> I said, <serve in the jug and bottle I will not, never having been accustomed to it, so you can do as you like.> So I came away and left him to it. Mind you, I like him for it. I ain't saying nothing against Bulfinch, but police or no police, I reckon I know how to take care of myself.>

<Quite so,> said Parker, patiently. <Mr~Bulfinch need feel no alarm. All we want you to do is to tell us, to the best of your recollection, about that young man you spoke of and help us to find the white-paper packet. You may be able to save an innocent person from being convicted, and I am sure your husband could not object to that.>

<Poor thing!> said Mrs~Bulfinch, <I'm sure when I read the account of the trial I said to Bulfinch\longdash>

<Just a moment. If you wouldn't mind beginning at the beginning, Mrs~Bulfinch, Lord~Peter would understand better what you have to tell us.>

<Why, of course. Well, my lord, before I was married I was barmaid at the Nine Rings, as the Chief-Inspector says. Miss~Montague I was then—it's a better name than Bulfinch, and I was almost sorry to say good-bye to it, but there! a girl has to make a lot of sacrifices when she marries and one more or less is nothing to signify. I never worked there but in the saloon bar, for I wouldn't undertake the four-ale business, it not being a refined neighbourhood, though there's a lot of very nice legal gentlemen drops in of an evening on the saloon side. Well, as I was saying, I was working there up to my marriage, which was last August Bank Holiday, and I remember one evening a gentleman coming in\longdash>

<Could you remember the date, do you think?>

<Not within a day or so I couldn't, for I wouldn't wish to swear to a fib, but it wasn't far off the longest day, for I remember making that same remark to the gentleman for something to say, you know.>

<That's near enough,> said Parker. <Round about June 20th, or 21st, or something like that?>

<That's right, as near as I can speak to it. And as to the time of night, that I \textit{can} tell you—knowing how keen you <tecs always are on the hands of the clock.< Mrs~Bulfinch giggled again and looked archly round for applause. >There was a gentleman sitting there—I didn't know him, he was a stranger to the district—and he asked what was our closing hour and I told him 11 o'clock, and he said, 'Thank God! I thought I was going to be turned out at 10.30,> and I looked at the clock and said, <Oh, you're all right, anyhow, sir; we always keep that clock a quarter of an hour fast.> The clock said twenty past, so I know it must have been five past ten really. So we got talking a bit about these prohibitionists and the way they had been trying it on again to get our licensing-hour altered to half-past ten, only we had a good friend on the Bench in Mr~Judkins, and while we was discussing it, I remember so well, the door was pushed open hurried-like and a young gentleman comes in, almost falls in, I might say, and he calls, <Give me a double brandy, quick.> Well, I didn't like to serve him all at once, he looked so white and queer, I thought he'd had one or two over the eight already, and the boss was most particular about that sort of thing. Still, he spoke all right—quite clear and not repeating himself nor nothing, and his eyes, though they did look a bit funny, weren't fixed-like, if you understand me. We get to size folks up pretty well in our business, you know. He sort of held on to the bar, all scrunched up together and bent double, and he says, <Make it a stiff one, there's a good girl, I'm feeling awful bad.> The gentleman I'd been talking to, he says to him, <Hold up,> he says, <what's the matter?> and the gentleman says, <I'm going to be ill.> And he puts his hands across his waistcoat like so!>

Mrs~Bulfinch clasped her waist and rolled her big blue eyes dramatically.

<Well, then I see he wasn't drunk, so I mixed him a double Martell with just a splash of soda and he gulps it down, and says, <That's better.> And the other gentleman puts his arm round him and helps him to a seat. There was a good many other people in the bar, but they didn't notice much, being full of the racing news. Presently the gentleman asks me for a glass of water, and I fetched it to him, and he says: <Sorry if I frightened you, but I've just had a bad shock, and it must have gone to my inside. I'm subject to gastric trouble,> he says, <and any worry or shock always affects my stomach. However,> he says, <perhaps this will stop it.> And he takes out a white paper packet with some powder in it, and drops it into the glass of water and stirs it up with a fountain-pen and drinks it off.>

<Did it fizz or anything?> asked Wimsey.

<No; it was just a plain powder, and it took a bit of a time to mix. He drank it off and said, <That settles it,> or <That'll settle it,> or something of that sort. And then he says, <Thanks very much. I'm better now and I'd better get home in case it takes me again.> And he raised his hat—he was quite the gentleman—and off he goes.>

<How much powder do you think he put in?>

<Oh, a good dollop. He didn't measure it or anything, just shot it in out of the packet. Near a dessert spoonful it might have been.>

<And what happened to the packet?> prompted Parker.

<Ah, there you are.> Mrs~Bulfinch took a glance at Wimsey's face and seemed pleased with the effect she was producing.

<We'd just got the last customer out—about five past eleven, that would be, and George was locking the door, when I see something white on the seat. Somebody's handkerchief I thought it was, but when I picked it up, I see it was the paper packet. So I said to George, <Hullo! the gentleman's left his medicine behind him.> So George asked what gentleman, and I told him, and he said, <What is it?> and I looked, but the label had been torn off. It was just one of them chemist's packets, you know, with the ends turned up and a label stuck across, but there wasn't a bit of the label left.>

<You couldn't even see whether it had been printed in black or in red?>

<Well, now.> Mrs~Bulfinch considered. <Well, no, I couldn't say that. Now you mention it, I do seem to recollect that there was something red about the packet, somewhere, but I can't clearly call it to mind. I wouldn't swear. I know there wasn't any name or printing of any kind, because I looked to see what it was.>

<You didn't try tasting it, I suppose?>

<Not me. It might have been poison or something. I tell you, he was a funny-looking customer.> (Parker and Wimsey exchanged glances.)

<Was that what you thought at the time?> enquired Wimsey, <or did it only occur to you later on—after you'd read about the case, you know?>

<I thought it at the time, of course,> retorted Mrs~Bulfinch, snappishly. <Aren't I telling you that's why I didn't taste it? I said so to George at the time, what's more. Besides, if it wasn't poison, it might be <snow> or something. <Best not touch it,> that's what I said to George, and he said <Chuck it in the fire.> But I wouldn't have that. The gentleman might have come back for it. So I stuck it up on the shelf behind the bar, where they keep the spirits, and never thought of it again from that day to yesterday, when your policeman came round about it.>

<It's been looked for there,> said Parker, <but they can't seem to find it anywhere.>

<Well, I don't know about that. I put it there and I left the Rings in August, so what's gone with it I can't say. Daresay they threw it away when they were cleaning. Wait a bit, though—I'm wrong when I say I never thought about it again. I did just wonder about it when I read the report of the trial in the \textit{News of the World}, and I said to George, <I wouldn't be surprised if that was the gentleman who came into the Rings one night and seemed so poorly—just fancy!> I said—just like that. And George said, <Now don't you get fancies, Gracie my girl; you don't want to get mixed up in a police case.> George has always held his head high, you see.>

<It's a pity you didn't come forward with this story,> said Parker, severely.

<Well, how was I to know it was important? The taxi-driver had seen him a few minutes afterwards and he was ill then, so the powder couldn't have had anything to do with it, if it was him, which I couldn't swear to. And anyhow, I didn't see about it till the trial was all over and finished with.>

<There will be a new trial, though,> said Parker, <and you may have to give evidence at that.>

<You know where to find me,> said Mrs~Bulfinch, with spirit. <I shan't run away.>

<We're very much obliged to you for coming now,> added Wimsey, pleasantly.

<Don't mention it,> said the lady. <Is that all you want, Mr~Chief-Inspector?>

<That's all at present. If we find the packet, we may ask you to identify it. And, by the way, it's advisable not to discuss these matters with your friends, Mrs~Bulfinch. Sometimes ladies get talking, and one thing leads to another, and in the end they remember incidents that never took place at all. You understand.>

<I never was one for talking,> said Mrs~Bulfinch, offended. <And it's my opinion, when it comes to putting two-and-two together to make five of 'em, the ladies aren't in it with the gentlemen.>

<I may pass this on to the solicitors for the defence, I suppose?> said Wimsey, when the witness had departed.

<Of course,> said Parker, <that's why I asked you to come and hear it—for what it's worth. Meanwhile, we shall of course have a good hunt for the packet.>

<Yes,> said Wimsey, thoughtfully, <yes—you will have to do that—naturally.>

\divider

Mr~Crofts did not look best pleased when this story was handed on to him.

<I warned you, Lord~Peter,> he said, <what might come of showing our hand to the police. Now they've got hold of this incident, they will have every opportunity to turn it to their own advantage. Why didn't you leave it to us to make the investigation?>

<Damn it,> said Wimsey angrily, <it was left to you for about three months and you did absolutely nothing. The police dug it up in three days. Time's important in this case, you know.>

<Very likely, but don't you see that the police won't rest now till they've found this precious packet?>

<Well?>

<Well, and suppose it isn't arsenic at all? If you'd left it in our hands, we could have sprung the thing on them at the last moment, when it was too late to make enquiries, and then we should have knocked the bottom out of the prosecution. Give the jury Mrs~Bulfinch's story as it stands and they'd have to admit there was some evidence that the deceased poisoned himself. But now, of course, the police will find or fake something and show that the powder was perfectly harmless.>

<And supposing they find it and it \textit{is} arsenic?>

<In \textit{that} case, of course,< said Mr~Crofts, >we shall get an acquittal. But do you believe in that possibility, my lord?>

<It's perfectly evident that \textit{you} don't,< said Wimsey, hotly. >In fact, you think your client's guilty. Well, I don't.>

Mr~Crofts shrugged his shoulders.

<In our client's interests,> he said, <we are bound to look at the unfavourable side of all evidence, so as to anticipate the points that are likely to be made by the prosecution. I repeat, my lord, that you have acted indiscreetly.>

<Look here,> said Wimsey, <I'm not out for a verdict of <Not Proven.> As far as Miss~Vane's honour and happiness are concerned, she might as well be found guilty as acquitted on a mere element of doubt. I want to see her absolutely cleared and the blame fixed in the right quarter. I don't want any shadow of doubt about it.>

<Highly desirable, my lord,> agreed the solicitor, <but you will allow me to remind you that it is not merely a question of honour or happiness, but of saving Miss~Vane's neck from the gallows.>

<And I say,> said Wimsey, <that it would be better for her to be hanged outright than to live and have everybody think her a murderess who got off by a fluke.>

<Indeed?> said Mr~Crofts, <I fear that is not an attitude that the defence can very well adopt. May I ask if it is adopted by Miss~Vane herself?>

<I shouldn't be surprised if it was,> said Wimsey. <But she's innocent, and I'll make you damn well believe it before I've done.>

<Excellent, excellent,> said Mr~Crofts, suavely, <nobody will be more delighted than myself. But I repeat that, in my humble opinion, your lordship will be wiser not to betray too many confidences to Chief-Inspector Parker.>

\divider

Wimsey was still simmering inwardly from this encounter when he entered Mr~Urquhart's office in Bedford Row. The head-clerk remembered him and greeted him with the deference due to an exalted and expected visitor. He begged his lordship to take a seat for a moment, and vanished into an inner office.

A woman typist, with a strong, ugly, rather masculine face, looked up from her machine as the door closed, and nodded abruptly to Lord~Peter. Wimsey recognized her as one of the <Cattery,> and put a commendatory mental note against Miss~Climpson's name for quick and efficient organisation. No words passed, however, and in a few moments the head-clerk returned and begged Lord~Peter to step inside.

Norman Urquhart rose from his desk and held out a friendly hand of greeting. Wimsey had seen him at the trial, and noted his neat dress, thick, smooth dark hair and general appearance of brisk and business-like respectability. Seeing him now more closely, he noticed that he was rather older than he had appeared at a distance. He put him down as being somewhere about the middle forties. His skin was pale and curiously clear, except for a number of little freckles, like sun-spots, rather unexpected at that time of the year, and in a man whose appearance conveyed no other suggestion of an out-door life. The eyes, dark and shrewd, looked a little tired, and were bistred about the orbits, as though anxiety were not unknown to them.

The solicitor welcomed his guest in a high, pleasant voice and asked what he could do for him.

Wimsey explained that he was interested in the Vane poisoning trial, and that he had the authority of Messrs. Crofts \& Cooper to come and bother Mr~Urquhart with questions, adding, as usual, that he was afraid he was being a nuisance.

<Not at all, Lord~Peter, not at all. I'm only too delighted to help you in any way, though really I'm afraid you have heard all I know. Naturally, I was very much taken aback by the result of the autopsy, and rather relieved, I must admit, to find that no suspicion was likely to be thrown on me, under the rather peculiar circumstances.>

<Frightfully tryin' for you,> agreed Wimsey. <But you seem to have taken the most admirable precautions at the time.>

<Well, you know, I suppose we lawyers get into a habit of taking precautions. Not that I had any idea of poison at the time—or, needless to say, I should have insisted on an enquiry then and there. What was in my mind was more in the nature of some kind of food-poisoning; not botulism, the symptoms were all wrong for that, but some contamination from cooking utensils or from some bacillus in the food itself. I am glad it turned out not to be that, though the reality was infinitely worse in one way. I suppose, really, in all cases of sudden and unaccountable illness, an analysis of the secretions ought to be made as a routine part of the business, but Dr~Weare appeared perfectly satisfied, and I trusted entirely to his judgment.>

<Obviously,> said Wimsey. <One doesn't naturally jump to the idea that people are bein' murdered—though I dare say it happens more often than one is apt to suppose.>

<It probably does, and if I'd ever had the handling of a criminal case, the suspicion might have occurred to me, but my work is almost entirely conveyancing and that sort of business—and probate and divorce and so on.>

<Talkin' of probate,> said Wimsey, carelessly, <had Mr~Boyes any sort of financial expectations?>

<None at all that I know of. His father is by no means well off—the usual country parson with a small stipend and a huge Vicarage and tumble-down Church. In fact, the whole family belongs to the unfortunate professional middle-class—over-taxed and with very little financial stamina. I shouldn't think there were more than a few hundred pounds to come to Philip Boyes, even if he had outlived the lot of them.>

<I had an idea there was a rich aunt somewhere.>

<Oh, no—unless you're thinking of old Cremorna Garden. She's a great-aunt, on the mother's side. But she hasn't had anything to do with them for very many years.>

At this moment Lord~Peter had one of those bursts of illumination which come suddenly when two unrelated facts make contact in the mind. In the excitement of hearing Parker's news about the white paper packet, he had paid insufficient attention to Bunter's account of the tea-party with Hannah Westlock and Mrs~Pettican, but now he remembered something about an actress, with a name like <'Yde Park or something of that.> The readjustment made itself so smoothly and mechanically in his mind that his next question followed almost without a pause.

<Isn't that Mrs~Wrayburn of Windle in Westmorland?>

<Yes,> said Mr~Urquhart. <I've just been up to see her, as a matter of fact. Of course, yes, you wrote to me there. She's been quite childish, poor old lady, for the last five years or so. A wretched life—dragging on like that, a misery to herself and everybody else. It always seems to me a cruel thing that one may not put these poor old people out of the way, as one would a favourite animal—but the law will not let us be so merciful.>

<Yes, we'd be hauled over the coals by the N.S.P.C.A. if we let a cat linger on in misery,> said Wimsey. <Silly, isn't it? But it's all of a piece with the people who write to the papers about keepin' dogs in draughty kennels and don't give a hoot—or a penny—to stop landlords allowin' a family of thirteen to sleep in an undrained cellar with no glass in the windows and no windows to put it in. It really makes me quite cross, sometimes, though I'm a peaceful sort of idiot as a rule. Poor old Cremorna Garden—she must be gettin' on now, though. Surely she can't last much longer.>

<As a matter of fact, we all thought she'd gone the other day. Her heart is giving out—she's over ninety, poor soul, and she gets these attacks from time to time. But there's amazing vitality in some of these ancient ladies.>

<I suppose you're about her only living relation now.>

<I suppose I am, except for an uncle of mine in Australia.> Mr~Urquhart accepted the fact of the relationship without enquiring how Wimsey came to know about it. <Not that my being there can do her any good. But I'm her man of business, too, so it's just as well I should be on the spot when anything happens.>

<Oh, quite, quite. And being her man of business, of course you know how she has left her money.>

<Well, yes, of course. Though I don't quite see, if you'll forgive my saying so, what that has to do with the present problem.>

<Why, don't you see,> said Wimsey, <it just occurred to me that Philip Boyes might have got himself into some kind of financial mess-up—it happens to the best of men—and have, well, taken the short way out of it. But, if he had any expectations from Mrs~Wrayburn, and the old girl, I mean, the poor old lady, was so near shuffling off this mortal thingummy, why, then, don't you know, he would have waited, or raised the wind on the strength of a post-obit or something or the other. You get my meaning, what?>

<Oh, I see—you are trying to make out a case for suicide. Well, I agree with you that it's the most hopeful defense for Miss~Vane's friends to put up, and as far as that goes, I can support you. Inasmuch, that is, as Mrs~Wrayburn did not leave Philip anything. Nor, so far as I know, had he the smallest reason to suppose she would do so.>

<You're positive of that?>

<Quite. As a matter of fact,> Mr~Urquhart hesitated, <well, I may as well tell you that he asked me about it one day, and I was obliged to tell him that he hadn't the least chance of getting anything from her.>

<Oh—he did actually ask?>

<Well, yes, he did.>

<That's rather a point, isn't it? How long ago would that be?>

<Oh—about eighteen months ago, I fancy. I couldn't be sure.>

<And as Mrs~Wrayburn is now childish, I suppose he couldn't entertain any hope that she would ever alter the will?>

<Not the slightest.>

<No, I see. Well, I think we might make something of that. Great disappointment, of course—one would make out that he had counted a good deal upon it. Is it much, by the way?>

<Pretty fair—about seventy or eighty thousand.>

<Very sickening, to think of all that good stuff going west and not getting a look-in one's self. By the way, how about you? Don't you get anything? I beg your pardon, fearfully inquisitive and all that, but I mean to say, considering you've been looking after her for years and are her only available relation so to speak, it would be a trifle thick, what?>

The solicitor frowned, and Wimsey apologised.

<I know, I know—I've been fearfully impudent. It's a failing of mine. And anyhow, it'll all be in the papers when the old lady does pop off, so I don't know why I should be so anxious to pump you. Wash it out—I'm sorry.>

<There's no real reason why you shouldn't know,> said Mr~Urquhart, slowly, <though one's professional instinct is to avoid disclosing one's clients' affairs. As a matter of fact, I am the legatee myself.>

<Oh?> said Wimsey, in a disappointed voice. <But in that case—that rather weakens the story, doesn't it? I mean to say, your cousin might very well have felt, in that case, that he could look to you for—that is—of course I don't know what your ideas might have been\longdash>

Mr~Urquhart shook his head.

<I see what you are driving at, and it is a very natural thought. But actually, such a disposal of the money would have been directly contrary to the expressed wish of the testatrix. Even if I could legally have made it over, I should have been morally bound not to do so, and I had to make that clear to Philip. I might, of course, have assisted him with casual gifts of money from time to time, but, to tell the truth, I should hardly have cared to do so. In my opinion, the only hope of salvation for Philip would have been to make his way by his own work. He was a little inclined—though I don't like speaking ill of the dead—to—to rely too much on other people.>

<Ah, quite. No doubt that was Mrs~Wrayburn's idea also?>

<Not exactly. No. It went rather deeper than that. She considered that she had been badly treated by her family. In short, well, as we have gone so far, I don't mind giving you her \textit{ipsissima verba}.>

He rang a bell on his desk.

<I haven't got the will itself here, but I have the draft. Oh, Miss~Murchison, would you kindly bring me in the deed-box labelled <Wrayburn>? Mr~Pond will show it to you. It isn't heavy.>

The lady from the <Cattery> departed silently in quest of the box.

<This is all rather irregular, Lord~Peter,> went on Mr~Urquhart, <but there are times when too much discretion is as bad as too little, and I should like you to see exactly why I was forced to take up this rather uncompromising attitude towards my cousin. Ah, thank you, Miss~Murchison.>

He opened the deed-box with a key attached to a bunch which he took from his trousers' pocket, and turned over a quantity of papers. Wimsey watched him with the expression of a rather foolish terrier who expects a tit-bit.

<Dear, dear,> ejaculated the solicitor, <it doesn't seem to be—oh! of course, how forgetful of me. I'm so sorry, it's in my safe at home. I got it out for reference last June, when the previous alarm occurred about Mrs~Wrayburn's illness, and in the confusion which followed on my cousin's death I quite forgot to bring it back. However, the gist of it was\longdash>

<Never mind,> said Wimsey, <there's no hurry. If I called at your house tomorrow, perhaps I could see it then.>

<By all means, if you think it important. I do apologise for my carelessness. In the meantime, is there anything else I can tell you about the matter?>

Wimsey asked a few questions, covering the ground already traversed by Bunter in his investigations, and took his departure. Miss~Murchison was again at work in the outer office. She did not look up as he passed.

<Curious,> mused Wimsey, as he pattered along Bedford Row, <everybody is so remarkably helpful about this case. They cheerfully answer questions which one has no right to ask and burst into explanations in the most unnecessary manner. None of them seem to have anything to conceal. It's quite astonishing. Perhaps the fellow really did commit suicide. I hope he did. I wish I could question \textit{him}. I'd put him through it, blast him. I've got about fifteen different analyses of his character already—all different\dots It's very ungentlemanly to commit suicide without leaving a note to say you've done it—gets people into trouble. When I blow my brains out\longdash>

He stopped.

<I hope I shan't want to,> he said. <I hope I shan't need to want to. Mother wouldn't like it, and it's messy. But I'm beginning to dislike this job of getting people hanged. It's damnable for their friends\dots I won't think about hanging. It's unnerving.>