\chapter[Chapter \thechapter]{}
\lettrine{W}{imsey} was accustomed to say, when he was an old man and more talkative even than usual, that the recollection of that Christmas at Duke's Denver had haunted him in nightmares, every night regularly, for the following twenty years. But it is possible that he remembered it with advantages. There is no doubt that it tried his temper severely. It began inauspiciously at the tea-table, when Mrs <Freak> Dimsworthy fluted out in her high, overriding voice: <And is it true, Lord~Peter dear, that you are defending that frightful poisoning woman?> The question acted like the drawing of a champagne cork. The whole party's bottled-up curiosity about the Vane case creamed over in one windy gust of stinging froth.

<I've no doubt she did it, and I don't blame her,> said Captain Tommy Bates, <perfectly foul blighter. Has his photograph on the dust-cover of his books, you know, that's the sort of squit he was. Wonderful, the rotters these high-brow females will fall for. The whole lot of 'em ought to be poisoned like rats. Look at the harm they do to the country.>

<But he was a very fine writer,> protested Mrs~Featherstone, a lady in her thirties, whose violently compressed figure suggested that she was engaged in a perpetual struggle to compute her weight in terms of the first syllables of her name rather than the last. <His books are positively Gallic in their audacity and restraint. Audacity is not rare—but that perfect concision of style is a gift which\longdash>

<Oh, if you like dirt,> interrupted the Captain, rather rudely.

<I wouldn't call it that,> said Mrs~Featherstone. <He is frank, of course, and that is what people in this country will not forgive. It is part of our national hypocrisy. But the beauty of the writing puts it all on a higher plane.>

<Well, I wouldn't have the muck in the house,> said the Captain, firmly. <I caught Hilda with it, and I said, <Now you send that book straight back to the library.> I don't often interfere, but one must draw the line somewhere.>

<How did you know what it was like?> asked Wimsey, innocently.

<Why, James Douglas' article in the \textit{Express} was good enough for me,< said Captain Bates. >The paragraphs he quoted were filthy, positively filthy.>

<Well, it's a good thing we've all read them,> said Wimsey. <Forewarned is forearmed.>

<We owe a great debt of gratitude to the press,> said the Dowager Duchess, <so kind of them to pick out all the plums for us and save the trouble of reading the books, don't you think, and such a joy for the poor dear people who can't afford seven-and-sixpence, or even a library subscription, I suppose, though I'm sure that works out cheaply enough if one is a quick reader. Not that the cheap ones will take those books for I asked my maid, such a superior girl and so keen on improving her mind, which is more than I can say for most of my friends, but no doubt it is all due to free education for the people and I suspect her in my heart of voting Labour though I never ask because I don't think it's fair, and besides, if I did, I couldn't very well take any notice of it, could I?>

<Still, I don't suppose the young woman murdered him on that account,> said her daughter-in-law. <From all accounts she was just as bad as he was.>

<Oh, come,> said Wimsey, <you can't think that, Helen. Damn it, she writes detective stories and in detective stories virtue is always triumphant. They're the purest literature we have.>

<The devil is always ready to quote scripture when it pays him to do so,> said the younger Duchess, <and they say the wretched woman's sales are going up by leaps and bounds.>

<It's my belief,> said Mr~Harringay, <that the whole thing is a publicity stunt gone wrong.> He was a large, jovial man, extremely rich and connected with the City. <You never know what these advertising fellows are up to.>

<Well, it looks like a case of hanging the goose that lays the golden eggs this time,> said Captain Bates, with a loud laugh. <Unless Wimsey means to pull off one of his conjuring tricks.>

<I hope he does,> said Miss~Titterton. <I adore detective stories. I'd commute the sentence to penal servitude on condition that she turned out a new story every six months. It would be much more useful than picking oakum or sewing mail-bags for the post-office to mislay.>

<Aren't you being a bit previous?> suggested Wimsey, mildly. <She's not convicted yet.>

<But she will be next time. You can't fight facts, Peter.>

<Of course not,> said Captain Bates. <The police know what they're about. They don't put people into the dock if there isn't something pretty shady about 'em.>

Now this was a fearful brick, for it was not so many years since the Duke of Denver had himself stood his trial on a mistaken charge of murder. There was a ghastly silence, broken by the Duchess, who said icily: <Really, Captain Bates!>

<What? eh? Oh, of course, I mean to say, I know mistakes do happen sometimes, but that's a very different thing. I mean to say, this woman, with no morals at all, that is, I mean\longdash>

<Have a drink, Tommy,> said Lord~Peter, kindly. <You aren't quite up to your usual standard of tact today.>

<No, but do tell us, Lord~Peter,> cried Mrs~Dimsworthy, <what the creature is \textit{like}. Have you talked to her? I thought she had rather a nice voice, though she's as plain as a pancake.>

<Nice voice, Freakie? Oh, no,> said Mrs~Featherstone. <I should have called it rather sinister. It absolutely thrilled me, I got shudders all the way down my spine. A genuine \textit{frisson}. And I think she would be quite attractive, with those queer, smudgy eyes, if she were properly dressed. A sort of \textit{femme fatale}, you know. Does she try to hypnotise you, Peter?>

<I saw in the papers,> said Miss~Titterton, <that she had had hundreds of offers of marriage.>

<Out of one noose into the other,> said Harringay, with his noisy laugh.

<I don't think I should care to marry a murderess,> said Miss~Titterton, <especially one that's been trained on detective stories. One would be always wondering whether there was anything funny about the taste of the coffee.>

<Oh, these people are all mad,> said Mrs~Dimsworthy. <They have a morbid longing for notoriety. It's like the lunatics who make spurious confessions and give themselves up for crimes they haven't committed.>

<A murderess might make quite a good wife,> said Harringay. <There was Madeleine Smith, you know—she used arsenic too, by the way—she married somebody and lived happily to a respectable old age.>

<But did her husband live to a respectable old age?> demanded Miss~Titterton. <That's more to the point, isn't it?>

<Once a poisoner, always a poisoner, \textit{I} believe,> said Mrs~Featherstone. <It's a passion that grows upon you—like drink or drugs.>

<It's the intoxicating sensation of power,> said Mrs~Dimsworthy. <But, Lord~Peter, \textit{do} tell us\longdash>

<Peter!> said his mother, <I do wish you'd go and see what's happened to Gerald. Tell him his tea is getting cold. I think he's in the stables talking to Freddy about thrush or cracked heels or something, so tiresome the way horses are always getting something the matter with them. You haven't trained Gerald properly, Helen, he used to be quite punctual as a boy. Peter was always the tiresome one, but he's becoming almost human in his old age. It's that wonderful man of his who keeps him in order, really a remarkable character and so intelligent, quite one of the old sort, you know, a perfect autocrat, and such manners too. He would be worth thousands to an American millionaire, most impressive. I wonder Peter isn't afraid he'll give warning one of these days, but I really believe he is positively attached to him, Bunter attached to Peter, I mean, though the other way on would be true too, I'm sure Peter pays more attention to his opinion than he does to mine.>

Wimsey had escaped, and was by now on his way to the stables. He met Gerald, Duke of Denver, returning, with Freddy Arbuthnot in tow. The former received the Dowager's message with a grin.

<Got to turn up, I suppose,> he said. <I wish nobody had ever invented tea. Ruins your nerves and spoils your appetite for dinner.>

<Beastly sloppy stuff,> agreed the Hon. Freddy. <I say, Peter, I've been wanting to get hold of you.>

<Same here,> said Wimsey, promptly. <I'm feelin' rather exhausted with conversation. Let's wander through the billiard-room and build our constitutions up before we face the barrage.>

<Today's great thought,> said Freddy, enthusiastically. He pattered happily after Wimsey into the billiard-room, and flung himself down in a large chair. <Great bore, Christmas, isn't it? All the people one hates most gathered together in the name of goodwill and all that.>

<Bring a couple of whiskies,> said Wimsey to the footman. <And, James, if anybody asks for Mr~Arbuthnot or me, you rather think we have gone out. Well, Freddy, here's luck! Has anything transpired, as the journalists say?>

<I've been sleuthing like stink on the tracks of your man,> said Mr~Arbuthnot. <Really, don't you know, I shall soon be qualified to set up in your line of business. Our financial column, edited by Uncle Buthie—that sort of thing. Friend Urquhart has been very careful, though. Bound to be—respectable family lawyer and all that. But I saw a man yesterday who knows a fellow who had it from a chappie that said Urquhart had been dipping himself a bit recklessly off the deep end.>

<Are you sure, Freddy?>

<Well, not to say sure. But this man, you see, owes me one, so to speak, for having warned him off the Megatherium before the band began to play, and he thinks, if he can get hold of the chappie that knows, not the fellow that told him, you understand, but the other one, that he might be able to get something out of him, don't you see, especially if I was able to put this other chappie in the way of something or the other, what?>

<And no doubt you have secrets to sell.>

<Oh, well, I daresay I could make it worth this other chappie's while, because I've got an idea, through this other fellow that my bloke knows, that the chappie is rather up against it, as you might say, through being caught short on some Airways stock, and if I was to put him in touch with Goldberg, don't you see, it might get him out of a hole and so on. And Goldberg will be all right, because, don't you see, he's a cousin of old Levy's, who was murdered, you know, and all these Jews stick together like leeches and as a matter of fact, I think it's very fine of them.>

<But what has old Levy got to do with it?> asked Wimsey, his mind running over the incidents in that half-forgotten murder-episode.

<Well, as a matter of fact,> said the Hon. Freddy, a little nervously, <I've—er—done the trick as you might say. Rachel Levy is—er, in fact—going to become Mrs~Freddy and all that sort of thing.>

<The devil she is,> said Wimsey, ringing the bell. <Tremendous congratters and all that. It's been a long time working up, hasn't it?>

<Why, yes,> said Freddy. <Yes, it has. You see, the trouble was that I was a Christian—at least, I was christened and all that, though I pointed out I wasn't at all a good one, except, of course, that one keeps up the family pew and turns out on Christmas Day and so on. Only it seems they didn't mind that so much as my bein' a Gentile. Well that, of course, is past prayin' for. And then there was the difficulty about the kids—if any. But I explained that I didn't mind what they counted them as—and I don't, you know, because, as I was saying, it would be all to the little beggars' advantage to be in with the Levy and Goldberg crowd, especially if the boys were to turn out anything in the financial way. And then I rather got round Lady Levy by sayin' I had served nearly seven years for Rachel—that was rather smart, don't you think?>

<Two more whiskies, James,> said Lord~Peter. <It was brilliant, Freddy. How did you come to think of it?>

<In church,> said Freddy, <at Diana Rigby's wedding. The bride was fifty minutes late and I had to do something, and somebody had left a Bible in the pew. I saw that—I say, old Laban was a bit of a tough, wasn't he?—and I said to myself, <I'll work that off next time I call,> and so I did, and the old lady was uncommonly touched by it.>

<And the long and the short of it is, you're fixed up,> said Wimsey. <Well, cheerio, here's to it. Am I best man, Freddy, or do you bring it off at the Synagogue?>

<Well, yes—it is to be at the Synagogue—I had to agree to that,> said Freddy, <but I believe some sort of bridegroom's friend comes into it. You'll stand by me, old bean, won't you? You keep your hat on, don't forget.>

<I'll bear it in mind,> said Wimsey, <and Bunter will explain the procedure to me. He's bound to know. He knows everything. But look here, Freddy, you won't forget about this little enquiry, will you?>

<I won't, old chap—upon my word I won't. I'll let you know the very second I hear anything. But I really think you may count on there being something in it.>

Wimsey found some consolation in this. At any rate, he so far pulled himself together as to be the life and soul of the rather restrained revels at Duke's Denver. The Duchess Helen, indeed, observed rather acidly to the Duke that Peter was surely getting too old to play the buffoon, and that it would be better if he took things seriously and settled down.

<Oh, I dunno,> said the Duke, <Peter's a weird fish—you never know what he's thinkin' about. He pulled me out of the soup once and I'm not going to interfere with him. You leave him alone, Helen.>

Lady Mary Wimsey, who had arrived late on Christmas Eve, took another view of the matter. She marched into her younger brother's bedroom at 2 o'clock on the morning of Boxing Day. There had been dinner and dancing and charades of the most exhausting kind. Wimsey was sitting thoughtfully over the fire in his dressing-gown.

<I say, old Peter,> said Lady Mary, <you're being a bit fevered, aren't you? Anything up?>

<Too much plum-pudding,> said Wimsey, <and too much county. I'm a martyr, that's what I am—burning in brandy to make a family holiday.>

<Yes, it's ghastly, isn't it? But how's life? I haven't seen you for an age. You've been away such a long time.>

<Yes—and you seem very much taken up with this house-decorating job you're running.>

<One must do something. I get rather sick of being aimless, you know.>

<Yes. I say, Mary, do you ever see anything of old Parker these days?>

Lady Mary stared into the fire.

<I've had dinner with him once or twice, when I was in town.>

<Have you? He's a very decent sort. Reliable, homespun—that sort of thing. Not amusing, exactly.>

<A little solid.>

<As you say—a little solid.> Wimsey lit a cigarette. <I should hate anything upsettin' to happen to Parker. He'd take it hard. I mean to say, it wouldn't be fair to muck about with his feelin's and so on.>

Mary laughed.

<Worried, Peter?>

<N-no. But I'd rather like him to have fair play.>

<Well, Peter—I can't very well say yes or no till he asks me, can I?>

<Can't you?>

<Well, not to him. It would upset his ideas of decorum, don't you think?>

<I suppose it would. But it would probably upset them just as much if he did ask you. He would feel that the mere idea of hearing a butler announce <Chief-Detective-Inspector and Lady Mary Parker> would have something shocking about it.>

<It's stalemate, then, isn't it?>

<You could stop dining with him.>

<I could do that, of course.>

<And the mere fact that you don't—I see. Would it be any good if I demanded to know his intentions in the true Victorian manner?>

<Why this sudden thirst for getting your family off your hands, old man? Peter—nobody's being horrible to you, are they?>

<No, no. I'm just feeling rather like a benevolent uncle, that's all. Old age creeping on. That passion for being useful which attacks the best of us when we're getting past our prime.>

<Like me with the house-decorating. I designed these pajamas, by the way. Don't you think they're rather entertaining? But I expect Chief-Inspector Parker prefers the old-fashioned night-gown, like Dr~Spooner or whoever it was.>

<That would be a wrench,> said Wimsey.

<Never mind. I'll be brave and devoted. Here and now I cast off my pajamas for ever!>

<No, no,> said Wimsey, <not here and now. Respect a brother's feelings. Very well. I am to tell my friend Charles Parker, that if he will abandon his natural modesty and propose, you will abandon your pajamas and say yes.>

<It will be a great shock for Helen, Peter.>

<Blast Helen. I daresay it won't be the worst shock she'll get.>

<Peter, you're plotting something devilish. All right. If you want me to administer the first shock and let her down by degrees—I'll do it.>

<Right-ho!> said Wimsey, casually.

Lady Mary twisted one arm about his neck and bestowed on him one of her rare sisterly caresses.

<You're a decent old idiot,> she said, <and you look played-out. Go to bed.>

<Go to blazes,> said Lord~Peter, amiably.