\chapter[Chapter \thechapter]{}
\lettrine{M}{iss} Murchison felt a touch of excitement in her well-regulated heart, as she rang the bell of Lord~Peter's flat. It was not caused by the consideration of his title or his wealth or his bachelorhood, for Miss~Murchison had been a business woman all her life, and was accustomed to visiting bachelors of all descriptions without giving a second thought to the matter. But his note had been rather exciting.

Miss~Murchison was thirty-eight, and plain. She had worked in the same financier's office for twelve years. They had been good years on the whole, and it was not until the last two that she had even begun to realise that the brilliant financier who juggled with so many spectacular undertakings was juggling for his life under circumstances of increasing difficulty. As the pace grew faster, he added egg after egg to those which were already spinning in the air. There is a limit to the number of eggs which can be spun by human hands. One day an egg slipped and smashed—then another—then a whole omelette of eggs. The juggler fled from the stage and escaped abroad, his chief assistant blew out his brains, the audience booed, the curtain came down, and Miss~Murchison, at 37, was out of a job.

She had put an advertisement in the papers and had answered many others. Most people appeared to want their secretaries young and cheap. It was discouraging.

Then her own advertisement had brought an answer, from a Miss~Climpson, who kept a typing bureau.

It was not what she wanted, but she went. And she found that it was not quite a typing bureau after all, but something more interesting.

Lord~Peter Wimsey, mysteriously at the back of it all, had been abroad when Miss~Murchison entered the <Cattery,> and she had never seen him till a few weeks ago. This would be the first time she had actually spoken to him. An odd-looking person, she thought, but people said he had brains. Anyhow—

The door was opened by Bunter, who seemed to expect her and showed her at once into a sitting-room lined with bookshelves. There were some fine prints on the walls, an Aubusson carpet, a grand piano, a vast Chesterfield and a number of deep and cosy chairs, upholstered in brown leather. The curtains were drawn, a wood-fire blazed on the hearth, and before it stood a table, with a silver tea-service whose lovely lines were delightful to the eye.

As she entered, her employer uncoiled himself from the depths of an armchair, put down a black-letter folio which he had been studying and greeted her in the cool, husky and rather languid tones which she had already heard in Mr~Urquhart's office.

<Frightfully good of you to come round, Miss~Murchison. Beastly day, isn't it? I'm sure you want your tea. Can you eat crumpets? Or would you prefer something more up-to-date?>

<Thanks,> said Miss~Murchison, as Bunter hovered obsequiously at her elbow, <I like crumpets very much.>

<Oh, good! Well, Bunter, we'll struggle with the tea-pot ourselves. Give Miss~Murchison another cushion and then you can toddle off. Back at work, I suppose? How's our Mr~Urquhart?>

<He's all right.> Miss~Murchison had never been a chatty girl. <There's one thing I wanted to tell you\longdash>

<Plenty of time,> said Wimsey. <Don't spoil your tea.> He waited on her with a kind of anxious courtesy which pleased her. She expressed admiration of the big bronze chrysanthemums heaped here and there about the room.

<Oh! I'm glad you like them. My friends say they give a feminine touch to the place, but Bunter sees to it, as a matter of fact. They make a splash of colour and all that, don't you think?>

<The books look masculine enough.>

<Oh, yes—they're my hobby, you know. Books—and crime, of course. But crime's not very decorative, is it? I don't care about collecting hangmen's ropes and murderers' over-coats. What are you to do with 'em? Is the tea all right? I ought to have asked you to pour out, but it always seems to me rather unfair to invite a person and then make her do all the work. What do you do when you're not working, by the way? Do you keep a secret passion for anything?>

<I go to concerts,> said Miss~Murchison. <And when there isn't a concert I put something on the gramophone.>

<Musician?>

<No—never could afford to learn properly. I ought to have been, I daresay. But there was more money in being a secretary.>

<I suppose so.>

<Unless one is absolutely first-class, and I should never have been that. And third-class musicians are a nuisance.>

<They have a rotten time, too,> said Wimsey. <I hate to see them in cinemas, poor beasts, playing the most ghastly tripe, sandwiched in with snacks of Mendelssohn and torn-off gobbets of the <Unfinished.> Have a sandwich. Do you like Bach? or only the Moderns?>

He wriggled on to the piano stool.

<I'll leave it to you,> said Miss~Murchison, rather surprised.

<I feel rather like the Italian Concerto this evening. It's better on the harpsichord, but I haven't got one here. I find Bach good for the brain. Steadying influence and all that.>

He played the Concerto through, and then, after a few seconds' pause went on to one of the <Forty-eight.> He played well, and gave a curious impression of controlled power, which, in a man so slight and so fantastical in manner, was unexpected and even a little disquieting. When he had finished, he said, still sitting at the piano:

<Did you make the enquiry about the typewriter?>

<Yes; it was bought new three years ago.>

<Good. I gather, by the way, that you are probably right about Urquhart's connection with the Megatherium Trust. That was a very helpful observation of yours. Consider yourself highly commended.>

<Thank you.>

<Anything fresh?>

<No—except that the evening after you called at Mr~Urquhart's office, he stayed on a long time after we had gone, typing something.>

Wimsey sketched an arpeggio with his right hand and demanded:

<How do you know how long he stayed and what he was doing if you had all gone?>

<You said you wanted to know of anything, however small, that was in the least unusual. I thought it might be unusual for him to stay on by himself, so I walked up and down Princeton Street and round Red Lion Square till half-past seven. Then I saw him put the light out and go home. Next morning I noticed that some papers I had left just inside my typewriter cover had been disturbed. So I concluded that he had been typing.>

<Perhaps the charwoman disturbed them?>

<Not she. She never disturbs the dust, let alone the cover.>

Wimsey nodded.

<You have the makings of a first-class sleuth, Miss~Murchison. Very well. In that case, our little job will have to be undertaken. Now, look here—you quite understand that I'm going to ask you to do something illegal?>

<Yes, I understand.>

<And you don't mind?>

<No. I imagine that if I'm taken up you will pay any necessary costs.>

<Certainly.>

<And if I go to prison?>

<I don't think it will come to that. There's a slight risk, I admit—that is, if I'm wrong about what I think is happening—that you might be brought up for attempted theft or for being in possession of safebreaking tools, but that is the most that could happen.>

<Oh! well, it's all in the game, I suppose.>

<You mean that?>

<Yes.>

<Splendid. Well—you know that deed-box you brought in to Mr~Urquhart's room the day I was there?>

<Yes, the one marked Wrayburn.>

<Where is it kept? In the outer office, where you could get hold of it?>

<Oh, yes—on a shelf with a lot of others.>

<Good. Would it be possible for you to get left alone in the office any day for, say, half an hour?>

<Well—at lunch-time I'm supposed to go out at half-past twelve and come back at half-past one. Mr~Pond goes out then, but Mr~Urquhart sometimes comes back. I couldn't be certain that he wouldn't pop out on me. And it would look funny if I wanted to stay on after four-thirty, I expect. Unless I pretended I had made a mistake and wanted to stay and put it right. I could do that. I might come extra early in the morning when the charwoman is there—or would it matter her seeing me?>

<It wouldn't matter very much,> said Wimsey, thoughtfully. <She'd probably think you had legitimate business with the box. I'll leave it to you to choose the time.>

<But what am I to do? Steal the box?>

<Not quite. Do you know how to pick a lock?>

<Not in the least, I'm afraid.>

<I often wonder what we go to school for,> said Wimsey. <We never seem to learn anything really useful. I can pick quite a pretty lock myself, but, as we haven't much time and as you'll need some rather intensive training, I think I'd better take you to an expert. Should you mind putting your coat on and coming round with me to see a friend?>

<Not at all. I should be delighted.>

<He lives in the Whitechapel Road, but he's a very pleasant fellow, if you can overlook his religious opinions. Personally, I find them rather refreshing. Bunter! Get us a taxi, will you?>

On the way to the East End, Wimsey insisted upon talking music—rather to Miss~Murchison's disquietude; she began to think there was something a little sinister in this pointed refusal to discuss the object of their journey.

<By the way,> she ventured, interrupting something Wimsey was saying about fugal form, <this person we are going to see—has he a name?>

<Now you mention it, I believe he has, but he's never called by it. It's Rumm.>

<Not very, perhaps, if he—er—gives lessons in lock-picking.>

<I mean, his name's Rumm.>

<Oh; what is it then?>

<Dash it! I mean, Rumm is his name.>

<Oh! I beg your pardon.>

<But he doesn't care to use it, now that he is a total abstainer.>

<Then what does one call him?>

<\emph{I} call him Bill,< said Wimsey, as the taxi drew up at the entrance to a narrow court, >but when he was at the head of his profession, they called him <Blindfold Bill.> He was a very great man in his time.>

Paying off the taxi-man (who had obviously taken them for welfare-workers till he saw the size of his tip, and now did not know what to make of them), Wimsey steered his companion down the dirty alleyway. At the far end was a small house, from whose lighted windows poured forth the loud strains of a chorus of voices, supported by a harmonium and other instruments.

<Oh, dear!> said Wimsey, <we've struck a meeting. It can't be helped. Here goes.>

Pausing until the strains of <Glory, glory, glory> had been succeeded by a sound as of fervent prayer, he hammered lustily at the door. Presently a small girl put her head out and, seeing Lord~Peter, uttered a shrill cry of delight.

<Hullo, Esmeralda Hyacinth,> said Wimsey. <Is Dad in?>

<Yes, sir, please, sir, they'll be so pleased, will you step in and oh, please?>

<Well?>

<Please, sir, will you sing <Nazareth>?>

<No, I will not sing <Nazareth> on any account, Esmeralda; I'm surprised at you.>

<Daddy says <Nazareth> isn't worldly, and you do sing it so beautiful,> said Esmeralda, her mouth drooping.

Wimsey hid his face in his hands.

<This comes of having done a foolish thing once,> he said. <One never lives it down. I won't promise, Esmeralda, but we'll see. But I want to talk business with Dad when the meeting's over.>

The child nodded; at the same moment, the praying voice within the room ceased, amid ejaculations of <Alleluia!> and Esmeralda, profiting by this momentary pause, pushed open the door and said loudly:

<Here's Mr~Peter and a lady.>

The room was small, very hot and very full of people. In one corner was the harmonium, with the musicians grouped about it. In the middle, standing by a round table covered with a red cloth, was a stout, square man, with a face like a bull-dog. He had a book in his hand, and appeared to be about to announce a hymn, but, seeing Wimsey and Miss~Murchison, he came forward, stretching out a large and hearty hand.

<Welcome one and welcome all!> he said. <Brethren, 'ere is a dear brother and sister in the Lord as is come out of the 'aunts of the rich and the riotous living of the Westend to join with us in singing the Songs of Zion. Let us sing and give praise. Alleluia! We know that many shall come from the East \emph{and} from the West and sit down at the Lord's feast, while many that thinks theirselves chosen shall be cast into outer darkness. Therefore let us not say, because this man wears a shiny eye-glass, that he is not a chosen vessel, or because this woman wears a di'mond necklace and rides in 'er Rolls-Royce, she will not therefore wear a white robe and a gold crown in the New Jerusalem, nor because these people travels in the Blue Train to the Rivereera, therefore they shall not be seen a-castin' down their golden crowns by the River of the Water of Life. We 'ears that there talk sometimes in 'Yde Park o' Sundays, but it's bad and foolish and leads to strife and envyings and not to charity. All we like sheep 'ave gone astray and well I may say so, 'avin' been a black and wicked sinner myself till this 'ere gentleman, for such 'e truly is, laid 'is 'and upon me as I was a-bustin' of 'is safe and was the instrument under God of turnin' me from the broad way that leadeth to destruction. Oh, brethren, what a 'appy day that was for me, alleluia! What a shower of blessings come to me by the grace of the Lord! Let us unite now in thanksgiving for 'Eaven's mercies in Number One 'Undred and Two. (Esmeralda, give our dear friends a 'ymn-book).>

<I'm sorry,> said Wimsey to Miss~Murchison. <Can you bear it? I fancy this is the final outbreak.>

The harmonium, harp, sackbut, psaltery, dulcimer and all kinds of music burst out with a blare which nearly burst the ear-drum, the assembly lifted its combined voices, and Miss~Murchison, to her amazement, found herself joining—at first self-consciously and then with a fine fervour in that stirring chant—

\begin{verse}\itshape
	<Sweeping through the gates,\\
	Sweeping through the gates of the New Jerusalem,\\
	Washed in the Blood of the Lamb.>
\end{verse}

Wimsey, who appeared to find it all very good fun, carolled away happily, without the slightest embarrassment; whether because he was accustomed to the exercise, or merely because he was one of those imperturbably self-satisfied people who cannot conceive of themselves as being out of place in any surroundings, Miss~Murchison was unable to determine.

To her relief, the religious exercise came to an end with the hymn, and the company took their leave, with many hand-shakings all round. The musicians emptied the condensed moisture from their wind-instruments politely into the fireplace and the lady who played the harmonium drew the cover over the keys and came forward to welcome the guests. She was introduced simply as Bella and Miss~Murchison concluded, rightly, that she was the wife of Mr~Bill Rumm and the mother of Esmeralda.

<Well, now,> said Bill, <it's dry work preachin' and singin'—you'll take a cup of tea or coffee, now, won't you?>

Wimsey explained that they had just had tea, but begged that the family might proceed with their own meal.

<It ain't 'ardly supper-time yet,> said Mrs~Rumm. <P'raps if you was to do your business with the lady and gentleman, Bill, they might feel inclined to take a bite with us later. It's trotters,> she added, hopefully.

<It's very kind of you,> said Miss~Murchison, hesitatingly.

<Trotters want a lot of beating,> said Wimsey, <and since our business may take a little time we'll accept with pleasure—if you're sure we're not putting you out.>

<Not at all,> said Mrs~Rumm, heartily. <Eight beautiful trotters they is, and with a bit of cheese they'll go round easy. Come along, 'Meraldy—your Dad's got business.>

<Mr~Peter's going to sing,> said the child, fixing reproachful eyes on Wimsey.

<Now don't you worrit his lordship,> rebuked Mrs~Rumm, <I declare I'm ashamed of you.>

<I'll sing after supper, Esmeralda,> said Wimsey. <Hop along now like a good girl or I'll make faces at you. Bill, I've brought you a new pupil.>

<Always 'appy to serve you, sir, knowing as it's the Lord's work. Glory be.>

<Thank you,> said Wimsey, modestly. <It's a simple matter, Bill, but as the young lady is inexperienced with locks and so on, I've brought her along to be coached. You see, Miss~Murchison, before Bill here saw the light\longdash>

<Praise God!> put in Bill.

<He was the most accomplished burglar and safe-breaker in the three kingdoms. He doesn't mind my telling you this, because he's taken his medicine and finished with it all and is now a very honest and excellent locksmith of the ordinary kind.>

<Thanks be to Him that giveth the victory!>

<But from time to time, when I need a little help in a righteous cause, Bill gives me the benefit of his great experience.>

<And oh! what 'appiness it is, miss, to turn them talents which I so wickedly abused to the service of the Lord. His 'oly Name be blessed that bringeth good out of evil.>

<That's right,> said Wimsey, with a nod. <Now, Bill, I've got my eye on a solicitor's deed-box, which may or may not contain something which will help me to get an innocent person out of trouble. This young lady can get access to the box, Bill, if you can show her the way inside it.>

<If?> grunted Bill, with sovereign contempt. <'Course I can! Deed-box, that's nuffin'. That ain't no field for a man's skill. Robbin' the kids' money-box, that's what it is with they trumpery little locks. There ain't a deed-box in this' 'ere city wot I couldn't open blindfold in boxing-gloves with a stick of boiled macaroni.>

<I know, Bill; but it isn't you that's got to do it. Can you teach the lady how to work it?>

<Sure I can. What kinder lock is it, lidy?>

<I don't know,> said Miss~Murchison. <An ordinary lock, I think. I mean, it has the usual sort of key—not a Bramah, or anything of that kind. Mr—that is, the solicitor has one set of keys and Mr~Pond has another—just plain keys with barrels and wards.>

<Ho!> said Bill, <then 'arf an hour will teach you all you want, miss.> He went to a cupboard and brought out half a dozen lock-plates and a bunch of curious, thin wire hooks, strung on a ring like keys.

<Are those picklocks?> asked Miss~Murchison, curiously.

<That's what they are, miss. Ingines of Satan!> He shook his head as he lovingly fingered the bright steel. <Many's the time sech keys as these 'ave let pore sinners in by the back gate into 'ell.>

<This time,> said Wimsey, <they'll let a poor innocent out of prison into the sunshine—if any, in this beastly climate.>

<Praise Him for His manifold mercies! Well, miss, the fust thing is to understand the construction of a lock. Now jest you look 'ere.>

He picked up one of the locks and showed how, by holding up the spring, the catch could be thrust back.

<There ain't no need of all them fancy wards, you see, miss. The barrel and the spring—that's all there is to it. Jest you try.>

Miss~Murchison accordingly tried, and forced several locks with an ease that astonished her.

<Well now, miss, the difficulty is, you see, that when the lock's in place, you can't use your eyes, but you 'as your 'earin' and you 'as the feelin' in your fingers, giv' you by Providence (praise His Name!) for that purpose. Now what you 'as to do, miss, is to shet your eyes and see with your fingers, like, w'en you've got your spring 'ooked back sufficient ter let the catch go past.>

<I'm afraid I'm very clumsy,> said Miss~Murchison, at the fifth or sixth attempt.

<Now don't you fret, miss. Jest take it easy and you'll find the right way of it come to you all of a sudden, like. Jest feel when it seems to go sweet and use your 'ands independent. Would you like to 'ave a little go at a Combination while you're 'ere, sir? I've got a beauty 'ere. Giv' to me it was by Sam, you know 'oo I mean. Many's the time I've tried to show 'im the error of 'is ways. <No, Bill,> 'e ses, <I ain't got no use for religion,> 'e ses, pore lost sheep, <but I ain't got no quarrel with you, Bill,> ses 'e, <and I'd like for ter give you this 'ere little sooveneer.>>

<Bill, Bill,> said Wimsey, shaking a reproachful finger, <I'm afraid this wasn't honestly come by.>

<Well, sir, if I knowed the owner I'd 'and it over to 'im with the greatest of pleasure. It's quite good, you see. Sam put the soup in at the 'inges and it blowed the ole front clean off, lock and all. It's small, but it's a real beauty—new pattern to me, that is. But I mastered it,> said Bill, with unregenerate pride, <in an hour or two.>

<It'd have to be a good bit of work to beat you, Bill>; Wimsey set the lock up before him, and began to manipulate the knob, his fingers moving with micrometer delicacy and his ear bent to catch the fall of the tumblers.

<Lord!> said Bill—this time with no religious intention—<wot a cracksman you'd a-made, if you'd a-given your mind to it—which the Lord in His mercy forbid you should!>

<Too much work in that life for me, Bill,> said Wimsey. <Dash it! I lost it that time.>

He turned the knob back and started over again.

By the time the trotters arrived, Miss~Murchison had acquired considerable facility with the more usual types of lock and a greatly enhanced respect for burglary as a profession.

<And don't you let yourself be 'urried, miss,> was Bill's final injunction, <else you'll leave scratches on the lock and do yourself no credit. Lovely bit of work, that, ain't it, Lord~Peter, sir?>

<Beyond me, I'm afraid,> said Wimsey, with a laugh.

<Practice,> said Bill, <that's all it is. If you'd a-started early enough you'd a-been a beautiful workman.> He sighed, <There ain't many of <em now-a-days—glory be!—that can do a real artistic job. It fair goes to my 'eart to see a elegant bit o> stuff like that blowed all to bits with gelignite. Wot's gelignite? Any fool can 'andle it as doesn't mind makin' a blinkin' great row. Brutal, I calls it.>

<Now, don't you get 'ankerin' back after them things, Bill,> said Mrs~Rumm, reprovingly. <Come along, do, now and eat yer supper. Ef anybody's goin' ter do sech a wicked thing as breakin' safes, wot do it matter whether it's done artistic or inartistic?>

<Ain't that jest like a woman?—beggin' your pardon, miss.>

<Well, you know it's true,> said Mrs~Rumm.

<I know those trotters look very artistic,> said Wimsey, <and that's quite enough for me.>

The trotters having been eaten, and <Nazareth> duly sung, to the great admiration of the Rumm family, the evening closed pleasantly with the performance of a hymn, and Miss~Murchison found herself walking up the Whitechapel Road, with a bunch of picklocks in her pocket and some surprising items of knowledge in her mind.

<You make some very amusing acquaintances, Lord~Peter.>

<Yes—rather a jape, isn't it? But Blindfold Bill is one of the best. I found him on my premises one night and struck up a sort of an alliance with him. Took lessons from him and all that. He was a bit shy at first, but he got converted by another friend of mine—it's a long story—and the long and short of it was, he got hold of this locksmith business, and is doing very well at it. Do you feel quite competent about locks now?>

<I think so. What am I to look for when I get the box open?>

<Well,> said Wimsey, <the point is this. Mr~Urquhart showed me what purported to be the draft of a will made five years ago by Mrs~Wrayburn. I've written down the gist of it on a bit of paper for you. Here it is. Now the snag about it is that that draft was typed on a machine which, as you tell me, was bought new from the makers only three years ago.>

<Do you mean that's what he was typing that evening he stayed late at the office?>

<It looks like it. Now, why? If he had the original draft, why not show me that? Actually, there was no need for him to show it to me at all, unless it was to mislead me about something. Then, though he said he had the thing at home, and must have known he had it there, he pretended to search for it in Mrs~Wrayburn's box. Again, why? To make me think that it was already in existence when I called. The conclusion I drew is that, if there is a will, it's not along the lines of the one he showed me.>

<It looks rather like that, certainly.>

<What I want you to look for is the real will—either the original or the copy ought to be there. Don't take it away, but try to memorise the chief points in it, especially the names of the chief legatee or legatees and of the residuary legatee. Remember that the residuary legatee gets everything which isn't specifically left to somebody else, or anything which falls in by a legatee's dying before the testatrix. I specially want to know whether anything was left to Philip Boyes or if any mention of the Boyes family is made in the will. Failing a will, there might be some other interesting document, such as a secret trust, instructing the executor to dispose of the money in some special way. In short, I want particulars of any document which may seem to be of interest. Don't waste too much time making notes. Carry the provisions in your head if you can and note them down privately when you get away from the office. And be sure you don't leave those skeleton keys about for people to find.>

Miss~Murchison promised to observe these instructions, and, a taxi coming up at that moment, Wimsey put her into it and sped her to her destination.