\chapter[Chapter \thechapter]{}
\lettrine{M}{r} Norman Urquhart glanced at the clock, which stood at 4.15, and called through the open door:

\zz
<Are those affidavits nearly ready, Miss~Murchison?>

\zz
<I am just on the last page, Mr~Urquhart.>

<Bring them in as soon as you've finished. They ought to go round to Hanson's tonight.>

<Yes, Mr~Urquhart.>

Miss~Murchison galloped noisily over the keys, slamming the shift-lever over with unnecessary violence, and causing Mr~Pond once more to regret the intrusion of female clerks. She completed her page, ornamented the foot of it with a rattling row of fancy lines and dots, threw over the release, spun the roller, twitching the foolscap sheets from under it in vicious haste, flung the carbons into the basket, shuffled the copies into order, slapped them vigorously on all four edges to bring them into symmetry, and bounced with them into the inner office.

<I haven't had time to read them through,> she announced.

<Very well,> said Mr~Urquhart.

Miss~Murchison retired, shutting the door after her. She gathered her belongings together, took out a hand-mirror and unashamedly powdered her rather large nose, stuffed a handful of odds-and-ends into a bulging handbag, pushed some papers under her typewriter cover ready for the next day, jerked her hat from the peg and crammed it on her head, tucking wisps of hair underneath it with vigorous and impatient fingers.

Mr~Urquhart's bell rang—twice.

<Oh, bother!> said Miss~Murchison, with heightened colour.

She snatched the hat off again, and answered the summons.

<Miss~Murchison,> said Mr~Urquhart, with an expression of considerable annoyance, <do you know that you have left out a whole paragraph on the first page of this?>

Miss~Murchison flushed still more deeply.

<Oh, have I? I'm very sorry.>

Mr~Urquhart held up a document resembling in bulk that famous one of which it was said that there was not truth enough in the world to fill so long an affidavit.

<It is very annoying,> he said. <It is the longest and most important of the three, and is urgently required first thing tomorrow morning.>

<I can't think how I could have made such a silly mistake,> muttered Miss~Murchison. <I will stay on this evening and re-type it.>

<I'm afraid you will have to. It is unfortunate, as I shall not be able to look it through myself, but there is nothing else to be done. Please check it carefully this time, and see that Hanson's have it before ten o'clock tomorrow.>

<Yes, Mr~Urquhart. I will be extremely careful. I am very sorry indeed. I will make sure that it is quite correct and take it round myself.>

<Very well, that will do,> said Mr~Urquhart. <Don't let it happen again.>

Miss~Murchison picked up the papers and came out, looking flustered. She dragged the cover off the typewriter with much sound and fury, jerked out the desk-drawers till they slammed against the drawer-stops, shook the top-sheet, carbons and flimsies together as a terrier shakes a rat, and attacked the machine tempestuously.

Mr~Pond, who had just locked his desk, and was winding a silk scarf about his throat, looked at her in mild astonishment.

<Have you some more typing to do tonight, Miss~Murchison?>

<Got to do the whole bally thing again,> said Miss~Murchison. <Left out a paragraph on page one—it would be page one, of course—and he wants the tripe round at Hanson's by 10 o'clock.>

Mr~Pond groaned slightly and shook his head.

<Those machines make you careless,> he reproved her. <In the old days, clerks thought twice about making foolish mistakes, when it meant copying the whole document out again by hand.>

<Glad I didn't live then,> said Miss~Murchison, shortly. <One might as well have been a galley-slave.>

<And we didn't knock off at half-past four, either,> said Mr~Pond. <We \textit{worked} in those days.>

<You may have worked longer,> said Miss~Murchison, <but you didn't get through as much in the time.>

<We worked accurately and neatly,> said Mr~Pond, with emphasis, as Miss~Murchison irritably disentangled two keys which had jammed together under her hasty touch.

Mr~Urquhart's door opened and the retort on the typist's lips was silenced. He said good-night and went out. Mr~Pond followed him.

<I suppose you will have finished before the cleaner goes, Miss~Murchison,> he said. <If not, please remember to extinguish the light and to hand the key to Mrs~Hodges in the basement.>

<Yes, Mr~Pond. Good-night.>

<Good-night.>

His steps pattered through the entrance, sounded again loudly as he passed the window, and died away in the direction of Brownlow Street. Miss~Murchison continued typing till she calculated that he was safely on the tube at Chancery Lane. Then she rose, with a quick glance round her, and approached a high tier of shelves, stacked with black deed-boxes, each of which bore the name of a client in bold white letters.

\textsc{Wrayburn} was there, all right, but had mysteriously shifted its place. This in itself was unaccountable. She clearly remembered having replaced it, just before Christmas, on top of the pile \textsc{Mortimer—Scroggins—Lord Coote—Dolby Bros\@. and Wingfield;} and here it was, on the day after Boxing Day, at the bottom of a pile, heaped over and kept down by \textsc{Bodgers—Sir~J. Penkridge—Flatsby \& Coaten—Trubody Ltd.} and \textsc{Universal Bone Trust}. Somebody had been spring-cleaning, apparently, over the holidays, and Miss~Murchison thought it improbable that it was Mrs~Hodges.

It was tiresome, because all the shelves were full, and it would be necessary to lift down all the boxes and stand them somewhere before she could get out \textsc{Wrayburn}. And Mrs~Hodges would be in soon, and though Mrs~Hodges didn't really matter, it might look odd\dots

Miss~Murchison pulled the chair from her desk (for the shelf was rather high) and, standing on it, lifted down \textsc{Universal Bone Trust}. It was heavyish, and the chair (which was of the revolving kind, and not the modern type with one spindly leg and a stiffly sprung back, which butts you in the lower spine and keeps you up to your job) wobbled unsteadily, as she carefully lowered the box and balanced it on the narrow top of the cupboard. She reached up again and took down \textsc{Trubody Ltd.}, and placed it on \textsc{Bone Trust}. She reached up for the third time and seized \textsc{Flatsby \& Coaten}. As she stooped with it a step sounded in the doorway and an astonished voice said behind her:

<Are you looking for something, Miss~Murchison?>

Miss~Murchison started so violently that the treacherous chair swung through a quarter-turn, nearly shooting her into Mr~Pond's arms. She came down awkwardly, still clasping the black deed-box.

<How you startled me, Mr~Pond! I thought you had gone.>

<So I had,> said Mr~Pond, <but when I got to the Underground I found I had left a little parcel behind me. So tiresome—I had to come back for it. Have you seen it any where? A little round jar, done up in brown paper.>

Miss~Murchison set \textsc{Flatsby \& Coaten} on the seat of the chair and gazed about her.

<It doesn't seem to be in my desk,> said Mr~Pond. <Dear, dear, I shall be so late. And I can't go without it, because it's wanted for dinner—in fact, it's a little jar of caviare. We have guests tonight. Now, where can I have put it?>

<Perhaps you put it down when you washed your hands,> suggested Miss~Murchison, helpfully.

<Well now, perhaps I did.> Mr~Pond fussed out and she heard the door of the little lavabo in the passage open with a loud creak. It suddenly occurred to her that she had left her handbag open on her desk. Suppose the skeleton keys were visible. She darted towards the bag, just as Mr~Pond returned in triumph.

<Much obliged to you for your suggestion, Miss~Murchison. It was there all the time. Mrs~Pond would have been so much upset. Well, good-night again.> He turned towards the door. <Oh, by the way, were you looking for something?>

<I was looking for a mouse,> replied Miss~Murchison with a nervous giggle. <I was just sitting working when I saw it run along the top of the cupboard and—er—up the wall behind those boxes.>

<Dirty little beasts,> said Mr~Pond, <the place is over-run with them. I have often said we ought to have a cat here. No hope of catching it now, though. You're not afraid of mice apparently?>

<No,> said Miss~Murchison, holding her eyes, by a strenuous physical effort, on Mr~Pond's face. If the skeleton keys were—as it seemed to her they must be—indecently exposing their spidery anatomy on her desk, it would be madness to look in that direction. <No—in your days I suppose all women were afraid of mice.>

<Yes, they were,> admitted Mr~Pond, <but then, of course, their garments were longer.>

<Rotten for them,> said Miss~Murchison.

<They were very graceful in appearance,> said Mr~Pond. <Allow me to assist you in replacing those boxes.>

<You will miss your train,> said Miss~Murchison.

<I have missed it already,> replied Mr~Pond, glancing at his watch. <I shall have to take the 5.30.> He politely picked up \textsc{Flatsby \& Coaten} and climbed perilously with it in his hands to the unsteady seat of the rotatory chair.

<It's extremely kind of you,> said Miss~Murchison, watching him as he restored it to its place.

<Not at all. If you would kindly hand me up the others\longdash>

Miss~Murchison handed him \textsc{Trubody Ltd.}, and \textsc{Universal Bone Trust}.

<There!> said Mr~Pond, completing the pile and dusting his hands. <Now let us hope the mouse has gone for good. I will speak to Mrs~Hodges about procuring a suitable kitten.>

<That would be a very good idea,> said Miss~Murchison. <Good-night, Mr~Pond.>

<Good-night, Miss~Murchison.>

His footsteps pattered down the passage, sounded again, more loudly beneath the window and for the second time died away in the direction of Brownlow Street.

<Whew!> said Miss~Murchison. She darted to her desk. Her fears had deceived her. The bag was shut and the keys invisible.

She pulled her chair back to its place and sat down as a clash of brooms and pails outside announced the arrival of Mrs~Hodges.

<Ho!> said Mrs~Hodges, arrested on the threshold at sight of the lady clerk industriously typing away, <beg your pardon, miss, but I didn't know as how anybody was here.>

<Sorry, Mrs~Hodges, I've got a little bit of work to finish. But you carry on. Don't mind me.>

<That's all right, miss,> said Mrs~Hodges, <I can do Mr~Partridge's office fust.>

<Well, if it's all the same to you,> said Miss~Murchison. <I've just got to type a few pages and—er—make a précis—notes you know, of some documents for Mr~Urquhart.>

Mrs~Hodges nodded and vanished again. Presently a loud bumping noise overhead proclaimed her presence in Mr~Partridge's office.

Miss~Murchison waited no longer. She dragged her chair to the shelves again, took down swiftly, one after the other, \textsc{Bone Trust, Trubody Ltd., Flatsby \& Coaten, Sir~J. Penkridge} and \textsc{Bodgers}. Her heart beat heavily as at last she seized \textsc{Wrayburn} and carried it across to her desk.

She opened her bag and shook out its contents. The bunch of picklocks clattered upon the desk, mixed up with a handkerchief, a powder compact and a pocket-comb. The thin and shining steel barrels seemed to burn her fingers.

As she picked the bunch over, looking for the most suitable implement, there came a loud rap at the window.

She wheeled round, terrified. There was nothing there. Thrusting the picklocks into the pocket of her sports-coat, she tip-toed across and looked out. In the lamplight she observed three small boys engaged in climbing the iron railings which guard the sacred areas of Bedford Row. The foremost child saw her and gesticulated, pointing downwards. Miss~Murchison waved her hand and cried, <Be off with you!>

The child shouted something unintelligible and pointed again. Putting two and two together, Miss~Murchison deduced from the rap at the window, the gesture and the cry, that a valuable ball had fallen into the area. She shook her head with severity and returned to her task.

But the incident had reminded her that the window had no blinds and that, under the glare of the electric light, her movements were as visible to anybody in the street as though she stood on a lighted stage. There was no reason to suppose that Mr~Urquhart or Mr~Pond was about, but her uneasy conscience vexed her. Moreover, if a policeman should pass by, would he not be able to recognise picklocks a hundred yards away? She peered out again. Was it her agitated fancy, or was that a sturdy form in dark blue emerging from Hand Court?

Miss~Murchison fled in alarm and, snatching up the deed-box, carried it bodily into Mr~Urquhart's private office.

Here, at least, she could not be overlooked. If anybody came in—even Mrs~Hodges—her presence might cause surprise but she would hear them coming and be warned in advance.

Her hands were cold and shaking, and she was not in the best condition to profit by Blindfold Bill's instructions. She drew a few deep breaths. She had been told not to hurry herself. Very well, then, she would not.

She chose a key with care and slipped it into the lock. For years, as it seemed to her, she scratched about aimlessly, till at length she felt the spring press against the hooked end. Pushing and lifting steadily with one hand, she introduced her second key. She felt the lever move—in another moment there was a sharp click and the lock was open.

There were not a great many papers in the box. The first document was a long list of securities, endorsed <Securities deposited with Lloyd's Bank.> Then came the copies of some title-deeds, of which the originals were similarly deposited. Then came a folder filled with correspondence. Some of this consisted of letters from Mrs~Wrayburn herself, the latest letter being dated five years previously. In addition there were letters from tenants, bankers and stockbrokers, with copies of the replies written from the office and signed by Norman Urquhart.

Miss~Murchison hastened impatiently through all this. There was no sign of a will or copy of a will—not even of the dubious draft that the solicitor had shown to Wimsey. Two papers only now remained at the bottom of the box. Miss~Murchison picked up the first. It was a Power of Attorney, dated January 1925, giving Norman Urquhart full powers to act for Mrs~Wrayburn. The second was thicker and tied neatly with red tape. Miss~Murchison slipped this off and unfolded the document.

It was a Deed of Trust, making over the whole of Mrs~Wrayburn's property to Norman Urquhart, in trust for herself, and providing that he should pay into her current account, from the estate, a certain fixed annual sum for personal expenses. The deed was dated July 1920 and attached to it was a letter, which Miss~Murchison hastily read through:

\begin{mail}{Appleford, Windle.\\15th May, 1920.}{My dear Norman,}

Thank you very much, my dear boy, for your birthday letter and the pretty scarf. It is good of you to remember your old aunt so faithfully.

It has occurred to me that, now that I am over eighty years old, it is time that I put my business into your hands entirely. You and your father have managed very well for me all these years, and you have, of course, always very properly consulted me before taking any step with regard to investments. But I am getting such a \textit{very old woman now} that I am quite out of touch with the modern world, and I cannot pretend that my opinions are of any real value. I am a \textit{tired} old woman, too, and though you always explain everything \textit{most clearly}, I find the \textit{writing of letters a gêne} and a burden to me at my advanced age.

So I have determined to put my property in Trust with you for my lifetime, so that you may have full power to handle everything according to your own discretion, without having to consult me every time. And also, though I am strong and healthy yet, I am glad to say, and have my wits quite about me, still, that happy state of things might alter at any time. I might become paralysed or feeble in my head, or want to make some foolish use of my money, as silly old women have done before now.

So will you draw up a deed of this kind and bring it to me and I will sign it. And at the same time I will give you instructions about my will.

Thanking you again for your good wishes,

\closeletter[Your affec. Great-Aunt,]{Rosanna Wrayburn.}
\end{mail}

<Hurray!> said Miss~Murchison. <There \textit{was} a will, then! And this Trust—that's probably important, too.>

She read the letter again, skimmed through the clauses of the Trust, taking particular notice that Norman Urquhart was named as sole Trustee, and finally made a mental note of some of the larger and more important items in the list of securities. Then she replaced the documents in their original order, re-locked the box—which yielded to treatment like an angel—carried it out, replaced it, piled the other boxes above it, and was back at her machine, just as Mrs~Hodges re-entered the office.

<Just finished, Mrs~Hodges,> she called out cheerfully.

<I wondered if yer would be,> said Mrs~Hodges, <I didn't hear the typewriter a-going.>

<I was making notes by hand,> said Miss~Murchison. She crumpled together the spoiled front page of the affidavit and threw it into the waste-paper basket together with the re-type which she had begun. From her desk-drawer she produced a correctly typed first page, provided beforehand for the purpose, added it to the bundle of script, put the top copy and the required sets of flimsies into an envelope, sealed it, addressed it to Messrs. Hanson \& Hanson, put on her hat and coat and went out, bidding a pleasant farewell to Mrs~Hodges at the door.

A short walk brought her to Messrs. Hanson's office, where she delivered the affidavit through the letter-box. Then, with a brisk step and humming to herself, she made for the 'bus-stop at the junction of Theobalds Road and Gray's Inn Road.

<I think I deserve a little supper in Soho,> said Miss~Murchison.

She was humming again as she walked from Cambridge Circus into Frith Street. <What \textit{is} this beastly tune?< she asked herself abruptly. A little consideration reminded her that it was >Sweeping through the gates, Sweeping through the gates\longdots>

<Bless me!> said Miss~Murchison. <Going dotty, that's what I am.>