\chapter[Chapter \thechapter]{}
\lettrine{L}{ord} Peter congratulated Miss~Murchison and gave her a rather special lunch at Rules, where there is a particularly fine old Cognac for those that appreciate such things. Indeed, Miss~Murchison was a little late in returning to Mr~Urquhart's office, and in her haste omitted to hand back the skeleton keys. But when the wine is good and the company agreeable one cannot always think of everything.

Wimsey himself, by a great act of self-control, had returned to his own flat to think, instead of bolting away to Holloway Gaol. Although it was a work of charity and necessity to keep up the spirits of the prisoner (it was in this way that he excused his almost daily visits) he could not disguise from himself that it would be even more useful and charitable to get her innocence proved. So far, he had not made much real progress.

The suicide theory had been looking very hopeful when Norman Urquhart had produced the draft of the will; but his belief in that draft had now been thoroughly undermined. There was still a faint hope of retrieving the packet of white powder from the <Nine Rings,> but as the days passed remorselessly on, that hope diminished almost to vanishing-point. It irked him to be taking no action in the matter—he wanted to rush to the Gray's Inn Road, to cross-question, bully, bribe, ransack every person and place in and about the <Rings> but he knew that the police could do this better than he could.

Why had Norman Urquhart tried to mislead him about the will? He could so easily have refused all information. There must be some mystery about it. But if Urquhart were not, in fact, the legatee, he was playing rather a dangerous game. If the old lady died, and the will was proved, the facts would probably be published—and she might die any day.

How easy it would be, he thought, regretfully, to hasten Mrs~Wrayburn's death a trifle. She was ninety-three and very frail. An over-dose of something—a shake—a slight shock, even—it did not do to think after that fashion. He wondered idly who lived with the old woman and looked after her\dots

It was the 30th. of December, and he still had no plan. The stately volumes on his shelves, rank after rank of Saint, historian, poet, philosopher, mocked his impotence. All that wisdom and all that beauty, and they could not show him how to save the woman he imperiously wanted from a sordid death by hanging. And he had thought himself rather clever at that kind of thing. The enormous and complicated imbecility of things was all round him like a trap. He ground his teeth and raged helplessly, striding about the suave, wealthy, futile room. The great Venetian mirror over the fireplace showed him his own head and shoulders. He saw a fair, foolish face, with straw-coloured hair sleeked back; a monocle clinging incongruously under a ludicrously twitching brow; a chin shaved to perfection, hairless, epicene; a rather high collar, faultlessly starched, a tie elegantly knotted and matching in colour the handkerchief which peeped coyly from the breast-pocket of an expensive Savile-Row-tailored suit. He snatched up a heavy bronze from the mantelpiece—a beautiful thing, even as he snatched it, his fingers caressed the patina—and the impulse seized him to smash the mirror and smash the face—to break out into great animal howls and gestures.

Silly! One could not do that. The inherited inhibitions of twenty civilised centuries tied one hand and foot in bonds of ridicule. What if he did smash the mirror? Nothing would happen. Bunter would come in, unmoved and unsurprised, would sweep up the débris in a dust-pan, would prescribe a hot bath and massage. And next day a new mirror would be ordered, because people would come in and ask questions, and civilly regret the accidental damage to the old one. And Harriet Vane would still be hanged, just the same.

Wimsey pulled himself together, called for his hat and coat, and went away in a taxi to call on Miss~Climpson.

<I have a job,> he said to her, more abruptly than was his wont, <which I should like you to undertake yourself. I can't trust anybody else.>

<How \emph{kind} of you to put it like that,> said Miss~Climpson.

<The trouble is, I can't in the least tell you how to set about it. It all depends on what you find when you get there. I want you to go to Windle in Westmorland and get hold of an imbecile and paralysed old lady called Mrs~Wrayburn, who lives at a house called Appleford. I don't know who looks after her, or how you are to get into the house. But you've got to do it, and you've got to find out where her will is kept, and, if possible, see it.>

<Dear me!> said Miss~Climpson.

<And what's worse,> said Wimsey, <you've only got about a week to do it in.>

<That's a very short time,> said Miss~Climpson.

<You see,> said Wimsey, <unless we can give some very good reason for delay, they're bound to take the Vane case almost first thing next sessions. If I could persuade the lawyers for the defence that there is the least chance of securing fresh evidence, they could apply for a postponement. But at present I have nothing that could be called evidence—only the vaguest possible hunch.>

<I see,> said Miss~Climpson. <Well, none of us can do more than our best, and it is very necessary to have Faith. That moves mountains, we are told.>

<Then for Heaven's sake lay in a good stock of it,> said Wimsey, gloomily, <because as far as I can see, this job is like shifting the Himalayas and the Alps, with a spot of frosty Caucasus and a touch of the Rockies thrown in.>

<You may count on me to do my poor best,> replied Miss~Climpson, <and I will ask the dear vicar to say a Mass of special intention for one engaged in a difficult undertaking. When would you like me to start?>

<At once,> said Wimsey. <I think you had better go just as your ordinary self, and put up at the local hotel—no—a boarding-house, there will be more opportunities for gossip. I don't know much about Windle, except that there is a boot-factory there and rather a good view, but it's not a large place, and I should think everybody would know about Mrs~Wrayburn. She is very rich, and was notorious in her time. The person you'll have to cotton on to is the female—there must be one of some sort—who nurses and waits on Mrs~Wrayburn and is, generally speaking, about her path and about her bed and all that. When you find out her special weakness, drive a wedge into it like one o'clock. Oh! by the way—it's quite possible the will isn't there at all, but in the hands of a solicitor-fellow called Norman Urquhart who hangs out in Bedford Row. If so, all you can do is to get the pump to work and find out anything—anything at all—to his disadvantage. He's Mrs~Wrayburn's great-nephew, and he goes to see her sometimes.>

Miss~Climpson made a note of these instructions.

<And now I'll tootle off and leave you to it,> said Wimsey. <Draw on the firm for any money you want. And if you need any special outfit, send me a wire.>

On leaving Miss~Climpson, Lord~Peter Wimsey again found himself a prey to Weltschmerz and self-pity. But it now took the form of a gentle, pervading melancholy. Convinced of his own futility, he determined to do what little good lay in his power before retiring to a monastery or to the frozen wastes of the Antarctic. He taxied purposefully round to Scotland Yard, and asked for Chief-Inspector Parker.

Parker was in his office, reading a report which had just come in. He greeted Wimsey with an expression which seemed more embarrassed than delighted.

<Have you come about that packet of powder?>

<Not this time,> said Wimsey, <I don't suppose you'll ever hear anything more of that. No. It's—rather a more—er—delicate matter. It's about my sister.>

Parker started and pushed the report to one side.

<About Lady Mary?>

<Er—yes. I understand she's been going about with you—er—dining—and all that sort of thing, what?>

<Lady Mary has honoured me—on one or two occasions—with her company,> said Parker. <I did not think—I did not know—that is, I understood\longdash>

<Ah! but \emph{did} you understand, that's the point?> said Wimsey, solemnly. <You see, Mary's a very nice-minded sort of girl, though I say it, and\longdash>

<I assure you,> said Parker, <that there is no need to tell me that. Do you suppose that I should misinterpret her kindness? It is the custom now-a-days for women of the highest character to dine unchaperoned with their friends, and Lady Mary has\longdash>

<I'm not suggesting a chaperon,> said Wimsey, <Mary wouldn't stick it for one thing, and I think it's all bosh, anyhow. Still, bein' her brother, and all that—it's Gerald's job really, of course, but Mary and he don't altogether hit it off, you know, and she wouldn't be likely to burble any secrets into his ear, especially as it would all be handed on to Helen—what was I going to say? Oh, yes—as Mary's brother, you know, I suppose it's my so to speak duty to push round and drop the helpful word here and there.>

Parker jabbed the blotting-paper thoughtfully.

<Don't do that,> said Wimsey, <it's bad for your pen. Take a pencil.>

<I suppose,> said Parker, <I ought not to have presumed\longdash>

<What did you presume, old thing?> said Wimsey, his head cocked, sparrow-fashion.

<Nothing to which anybody could object,> said Parker, hotly. <What are you thinking of, Wimsey? I quite see that it is unsuitable, from your point of view, that Lady Mary Wimsey should dine in public restaurants with a policeman, but if you imagine I have ever said a word to her that could not be said with the greatest propriety\longdash>

<—in the presence of her mother, you wrong the purest and sweetest woman that ever lived, and insult your friend,> interrupted Peter, snatching the words from his mouth and rattling them to a glib conclusion. <What a perfect Victorian you are, Charles. I should like to keep you in a glass case. Of course you haven't said a word. What I want to know is, why?>

Parker stared at him.

<For the last five years or so,> said Wimsey, <you have been looking like a demented sheep at my sister, and starting like a rabbit whenever her name is mentioned. What do you mean by it? It is not ornamental. It is not exhilarating. You unnerve the poor girl. You give me a poor idea of your guts, if you will pardon the expression. A man doesn't like to see a man go all wobbly about his sister—at least, not with such a prolonged wobble. It's unsightly. It's irritating. Why not slap the manly thorax and say, <Peter, my dear old mangel-wurzel, I have decided to dig myself into the old family trench and be a brother to you>? What's stopping you? Is it Gerald? He's an ass, I know, but he's not a bad old stick, really. Is it Helen? She's a bit of a wart, but you needn't see much of her. Is it me? Because, if so, I'm thinking of becoming a hermit—there was a Peter the Hermit, wasn't there?—So I shouldn't be in your way. Cough up the difficulty, old thing, and we will have it removed in a plain van. Now, then!>

<Do you—are you asking me—?>

<I'm asking you your intentions, damn it!> said Wimsey, <and if that's not Victorian enough, I don't know what is. I quite understand your having given Mary time to recover from that unfortunate affair with Cathcart and the Goyles fellow, but, dash it all, my dear man, one can over-do the delicacy business. You can't expect a girl to stand on and off for ever, can you? Are you waiting for Leap Year, or what?>

<Look here, Peter, don't be a damned fool. How can I ask your sister to marry me?>

<\emph{How} you do it is your affair. You might say: <What about a spot of matrimony, old dear?> That's up-to-date, and plain and unmistakable. Or you could go down on one knee and say, <Will you honour me with your hand and heart?> which is pretty and old-fashioned and has the merit of originality in these times. Or you could write, or wire, or telephone. But I leave that to your own individual fancy.>

<You're not serious.>

<Oh, God! Shall I ever live down this disastrous reputation for tom-foolery? You're making Mary damned unhappy, Charles, and I wish you'd marry her and have done with it.>

<Making her unhappy?> said Parker, almost in a shout, <me—her—unhappy?>

Wimsey tapped his forehead significantly.

<Wood—solid wood! But the last blow seems to have penetrated. Yes, you—her—unhappy—do you get it now?>

<Peter—if I really thought that\longdash>

<Now don't go off the deep end,> said Wimsey, <it's wasted on me. Keep it for Mary. I've done my brotherly duty and there's an end of it. Calm yourself. Return to your reports\longdash>

<Oh, lord, yes,> said Parker. <Before we go any farther, I've got a report for you.>

<You have? Why didn't you say so at first.>

<You wouldn't let me.>

<Well, what is it?>

<We've found the packet.>

<What?>

<We've found the packet.>

<Actually found it?>

<Yes. One of the barmen\longdash>

<Never mind the barmen. You're sure it's the right packet?>

<Oh, yes; we've identified it.>

<Get on. Have you analysed it?>

<Yes, we've analysed it.>

<Well, what is it?>

Parker looked at him with the eyes of one who breaks bad news, and said, reluctantly:

<Bicarbonate of soda.>