\chapter[Chapter \thechapter]{}
\lettrine{S}{upper} was over. It had been served in a beautiful old panelled room with an Adam ceiling and fireplace, and the food had been good. Miss~Climpson felt braced and ready.

\zz
<We'll sit in my own room, shall we?> said Miss~Booth. <It's the only really comfortable place. Most of this house is shut up, of course. If you'll excuse me, dear, I will just run up and give Mrs~Wrayburn her supper and make her comfortable, poor thing, and then we can begin. I shan't be more than half an hour or so.>

<She's quite helpless, I suppose?>

<Yes, quite.>

<Can she speak?>

<Not to say speak. She mumbles sometimes, but one can't make anything of it. It's sad, isn't it, and her so rich. It will be a happy day for her when she passes over.>

<Poor soul!> said Miss~Climpson.

Her hostess led her into a small, gaily-furnished sitting-room and left her there among the cretonne covers and the ornaments. Miss~Climpson ran her eyes rapidly over the books, which were mostly novels, with the exception of some standard works on Spiritualism, and then turned her attention to the mantelpiece. It was crowded with photographs, as the mantelpieces of nurses usually are. Conspicuous among hospital groups and portraits inscribed <From your grateful patient,> was a cabinet photograph of a gentleman in the dress and moustache of the 'nineties, standing beside a bicycle, apparently upon a stone balcony in mid-air with a distant view over a rocky gorge. The frame was silver, heavy and ornate.

<Too young for a father,> said Miss~Climpson, as she turned it over and pulled back the catch of the frame, <either sweetheart or favourite brother. H'm! <My dearest Lucy from her ever-loving Harry.> Not a brother, I fancy. Photographer's address, Coventry. Cycle trade, possibly. Now what happened to Harry? Not matrimony, obviously. Death, or infidelity. First-class frame and central position; bunch of hot-house narcissus in a vase—I think Harry has passed over. What next? Family group? Yes. Names conveniently beneath. Dearest Lucy in a fringe, Papa and Mamma, Tom and Gertrude. Tom and Gertrude are older, but they may be still alive. Papa is a parson. Largeish house—country rectory, perhaps. Photographer's address, Maidstone. Wait a minute. Here's Papa in another group, with a dozen small boys. Schoolmaster, or takes private pupils. Two boys have straw hats with zig-zag ribbons—school, probably, then. What's that silver cup? Thos. Booth and three other names—Pembroke College Fours 1883. Not an expensive college. Wonder whether Papa objected to Harry on account of the cycle-manufacturing connection? That book over there looks like a school prize. It is. Maidstone Ladies' College—for distinction in English Literature. Just so. Is she coming back?—No, false alarm. Young man in khaki, 'Your loving nephew, G. Booth'—ah! Tom's son, I take it. Did he survive, I wonder? Yes—she is coming, this time.>

When the door opened, Miss~Climpson was sitting by the fire, deeply engaged in \textit{Raymond}.

<So sorry to keep you waiting,> said Miss~Booth, <but the poor old dear is rather restless this evening. She'll do now for a couple of hours, but I shall have to go up again later. Shall we begin at once? I'm \textit{so} eager to try.>

Miss~Climpson readily agreed.

<We usually use this table,> said Miss~Booth, bringing forward a small, round table of bamboo, with a shelf between its legs. Miss~Climpson thought she had never seen a piece of furniture more excellently adapted for the faking of phenomena, and heartily approved of Mrs~Craig's choice.

<Do we sit in the light?> she enquired.

<Not in full light,> said Miss~Booth. <Mrs~Craig explained to me that the blue rays of daylight or electricity are too hard for the spirits. They shatter the vibrations, you see. So we usually put out the light and sit in the firelight, which is quite bright enough for taking notes. Will you write down, or shall I?>

<Oh, I think you had better do it as you're more accustomed to it,> said Miss~Climpson.

<Very well.> Miss~Booth fetched a pencil and a pad of paper and switched off the light.

<Now we just sit down and place our thumbs and finger-tips lightly on the table, near the edge. It's better to make a circle, of course, but one can't do that with two people. And just at first, I think it's better not to talk—till a rapport is established, you know. Which side will you sit?>

<Oh, this will do for me,> said Miss~Climpson.

<You don't mind the fire on your back?>

Miss~Climpson most certainly did not.

<Well, that's a good arrangement, because it helps to screen the rays from the table.>

<That's what I thought,> said Miss~Climpson, truthfully.

They placed thumbs and finger-tips on the table and waited.

Ten minutes passed.

<Did you feel any movement?> whispered Miss~Booth.

<No.>

<It sometimes takes a little time.>

Silence.

<Ah! I thought I felt something then.>

<I've got a feeling like pins and needles in my fingers.>

<So have I. We shall get something soon.>

A pause.

<Would you like to rest a little?>

<My wrists ache rather.>

<They do till you get used to it. It's the power coming through them.>

Miss~Climpson lifted her fingers and rubbed each wrist gently. The thin black hooks came quietly down to the edge of her black velvet sleeve.

<I feel sure there is power all about us. I can feel a cold thrill on my spine.>

<Let's go on,> said Miss~Climpson. <I'm quite rested now.>

Silence.

<I feel,> whispered Miss~Climpson, <as though something was gripping the back of my neck.>

<Don't move.>

<And my arms have gone dead from the elbow.>

<Hush! so have mine.>

Miss~Climpson might have added that she had a pain in her deltoids, if she had known the name for them. This is not an uncommon result of sitting with the thumbs and fingers on a table without support for the wrist.

<I'm tingling from head to foot,> said Miss~Booth.

At this moment the table gave a violent lurch. Miss~Climpson had over-estimated the force necessary to move bamboo furniture.

<Ah!>

After a slight pause for recuperation, the table began to move again, but more gently, till it was rocking with a regular see-saw motion. Miss~Climpson found that by gently elevating one rather large foot, she could take practically all the weight off her wrist-hooks. This was fortunate, as she was doubtful whether their constitution would stand the strain.

<Shall we speak to it?> asked Miss~Climpson.

<Wait a moment,> said Miss~Booth. <It wants to go sideways.>

Miss~Climpson was surprised by this statement, which seemed to argue a high degree of imagination, but she obligingly imparted a slight gyratory movement to the table.

<Shall we stand up?> suggested Miss~Booth.

This was disconcerting, for it is not easy to work a vibrating table while stooping and standing on one leg. Miss~Climpson decided to fall into a trance. She dropped her head on her chest and uttered a slight moan. At the same time she pulled back her hands, releasing the hooks, and the table continued to revolve jerkily, spinning beneath their fingers.

A coal fell from the fire with a crash, sending up a bright jet of flame. Miss~Climpson started, and the table ceased spinning and came down with a little thud.

<Oh, dear!> exclaimed Miss~Booth. <The light has dispersed the vibrations. Are you all right, dear?>

<Yes, yes,> said Miss~Climpson, vaguely. <Did anything happen?>

<The power was tremendous,> said Miss~Booth. <I've never felt it so strong.>

<I think I must have fallen asleep,> said Miss~Climpson.

<You were entranced,> said Miss~Booth. <The control was taking possession. Are you very tired, or can you go on?>

<I feel quite all right,> said Miss~Climpson, <only a little drowsy.>

<You're a wonderfully strong medium,> said Miss~Booth.

Miss~Climpson, surreptitiously flexing her ankle, was inclined to agree.

<We'll put a screen before the fire this time,> said Miss~Booth. <That's better. Now!>

The hands were replaced on the table, which began to rock again almost immediately.

<We won't lose any more time,> said Miss~Booth. She cleared her throat slightly, and addressed the table.

<Is there a spirit here?>

Crack!

The table ceased moving.

<Will you give me one knock for <Yes> and two for <No>?>

Crack!

The advantage of this method of interrogation is that it obliges the enquirer to put leading questions.

<Are you the spirit of one who has passed over?>

<Yes.>

<Are you Fedora?>

<No.>

<Are you one of the spirits who have visited me before?>

<No.>

<Are you friendly to us?>

<Yes.>

<Are you pleased to see us?>

<Yes. Yes. Yes.>

<Are you happy?>

<Yes.>

<Are you here to ask anything for yourself?>

<No.>

<Are you anxious to help us personally?>

<No.>

<Are you speaking on behalf of another spirit?>

<Yes.>

<Does he want to speak to my friend?>

<No.>

<To me, then?>

<Yes. Yes. Yes. Yes.> (The table rocked violently.)

<Is it the spirit of a woman?>

<No.>

<A man?>

<Yes.>

A little gasp.

<Is it the spirit I have been trying to communicate with?>

<Yes.>

A pause and a tilting of the table.

<Will you speak to us by means of the alphabet? One knock for A, two for B, and so on?>

(<Belated caution,> thought Miss~Climpson.)

<Crack!>

<What is your name?>

Eight taps, and a long indrawn breath.

One tap—

<H—A\longdash>

A long succession of taps.

<Was that an R? You go too fast.>

<Crack!>

<H—A—R—is that right?>

<Yes.>

<Is it Harry?>

<Yes, yes, yes.>

<Oh, Harry! At last! How are you? Are you happy?>

<Yes—no—lonely.>

<It wasn't my fault, Harry.>

<Yes. Weak.>

<Ah, but I had my duty to think of. Remember who came between us.>

<Yes, F-A-T-H-E->

<No, no, Harry! It was mo\longdash>

<—A-D!> concluded the table, triumphantly.

<How can you speak so unkindly?>

<Love comes first.>

<I know that now. But I was only a girl. Won't you forgive me now?>

<All forgiven. Mother forgiven too.>

<I'm so glad. What do you do where you are, Harry?>

<Wait. Help. Atone.>

<Have you any special message for me?>

<Go to Coventry!> (Here the table became agitated.)

This message seemed to overwhelm the seeker.

<Oh, it really is you, Harry! You haven't forgotten the dear old joke. Tell me\longdash>

The table showed great signs of excitement at this point and poured out a volley of unintelligible letters.

<What do you want?>

<G—G—G\longdash>

<It must be somebody else interrupting,> said Miss~Booth. <Who is that, please?>

<G-E-O-R-G-E> (very rapidly).

<George? I don't know any George, except Tom's boy. Has anything happened to him, I wonder.>

<Ha! ha! ha! not George Booth, George Washington.>

<George Washington?>

<Ha! ha!> (The table became convulsively agitated, so much so that the medium seemed hardly able to hold it. Miss~Booth, who had been noting down the conversation, now put her hands back on the table, which stopped capering and began to rock.)

<Who is here now?>

<Pongo.>

<Who is Pongo?>

<Your control.>

<Who was that talking just now?>

<Bad spirit. Gone now.>

<Is Harry still there?>

<Gone.>

<Does anybody else want to speak?>

<Helen.>

<Helen who?>

<Don't you remember? Maidstone.>

<Maidstone? Oh, do you mean Ellen Pate?>

<Yes, Pate.>

<Fancy that! Good-evening, Ellen. How nice to hear from you.>

<Remember row.>

<Do you mean the big row in the dormitory?>

<Kate bad girl.>

<No, I don't remember Kate, except Kate Hurley. You don't mean her, do you?>

<Naughty Kate. Lights out.>

<Oh, I \textit{know} what she's trying to say. The cakes after lights were out.>

<That's right.>

<You still spell badly, Ellen.>

<Miss—Miss\longdash>

<Mississippi? Haven't you learnt it yet?>

<Funny.>

<Are there many of our class where you are?>

<Alice and Mabel. Send love.>

<How sweet of them. Give them my love too.>

<Yes. All love. Flowers. Sunshine.>

<What do you\longdash>

<P,> said the table, impatiently.

<Is that Pongo again?>

<Yes. Tired.>

<Do you want us to stop?>

<Yes. Another time.>

<Very well, good-night.>

<Good-night.>

The medium leaned back in her chair with an air of exhaustion which was perfectly justified. It is very tiring to rap out letters of the alphabet, and she was afraid the soap-box was slipping.

Miss~Booth turned on the light.

<That was wonderful!> said Miss~Booth.

<Did you get the answers you wanted?>

<Yes, indeed. Didn't you hear them?>

<I didn't follow it all,> said Miss~Climpson.

<It is a little difficult, counting, till you're used to it. You must be dreadfully tired. We'll stop now and make some tea. Next time perhaps we could use the Ouija. It doesn't take nearly so long to get the answers with that.>

Miss~Climpson considered this. Certainly it would be less wearisome, but she was not sure of being able to manipulate it.

Miss~Booth put the kettle on the fire and glanced at the clock.

<Dear me! it's nearly eleven. How the time has flown! I must run up and see to my old dear. Would you like to read through the questions and answers? I don't suppose I shall be many minutes.>

Satisfactory, so far, thought Miss~Climpson. Confidence was well established. In a few days' time, she would be able to work her plan. But she had nearly tripped up over George. And it was stupid to have said <Helen.> Nellie would have done for either—there was a Nellie in every school forty-five years ago. But after all, it didn't much matter what you said—the other person was sure to help you out of it. How desperately her legs and arms were aching. Wearily she wondered if she had missed the last bus.

<I'm afraid you have,> said Miss~Booth, when the question was put to her on her return. <But we'll ring up a taxi. At my expense, of course, dear. I insist, as you were so good in coming all this way, entirely to please me. Don't you think the communications are too marvellous? Harry would never come before—poor Harry! I'm afraid I was very unkind to him. He married, but you see he has never forgotten me. He lived at Coventry and we used to have a joke about it—that's what he meant by saying that. I wonder which Alice and Mabel that was. There was an Alice Gibbons and an Alice Roach—both such nice girls; I think Mabel must be Mabel Herridge. She married and went out to India years and years ago. I can't remember her married name and I've never heard from her since, but she must have passed to the other side. Pongo is a new control. We must ask him who he is. Mrs~Craig's control is Fedora—she was a slave-girl at the court of Poppaea.>

<Really!> said Miss~Climpson.

<She told us her story one night. So romantic. She was thrown to the lions because she was a Christian and refused to have anything to do with Nero.>

<How very interesting.>

<Yes, isn't it? But she doesn't speak very good English, and it's sometimes rather hard to understand her. And she sometimes lets the tiresome ones in. Pongo was very quick at getting rid of George Washington. You will come again, won't you? Tomorrow night?>

<Certainly, if you like.>

<Yes, please do. And next time you must ask for a message for yourself.>

<I will indeed,> said Miss~Climpson. <It has all been \textit{such} a revelation—quite \textit{wonderful}. I never \textit{dreamed} that I had such a gift.>

And that was true, also.