\chapter[Chapter \thechapter]{}
\lettrine{I}{t} was, of course, useless for Miss~Climpson to try to conceal from the boarding-house ladies where she had been and what she had been doing. Her return at midnight in a taxi had already aroused the liveliest curiosity, and she told the truth to avoid being accused of worse dissipations.

<My dear Miss~Climpson,> said Mrs~Pegler, <you will not, I trust, think me interfering, but I must caution you against having anything to do with Mrs~Craig or her friends. I have no doubt Miss~Booth is an excellent woman, but I do not like the company she keeps. Nor do I approve of spiritualism. It is a prying into matters which we are not intended to know about, and may lead to very undesirable results. If you were a married woman, I could explain myself more clearly, but you may take it from me that these indulgences may have serious effects upon the character in more ways than one.>

<Oh, Mrs~Pegler,> said Miss~Etheredge, <I don't think you should say that. One of the most beautiful characters I know—a woman whom it is a privilege to call one's friend—is a spiritualist, and she is a real saint in her life and influence.>

<Very likely, Miss~Etheredge,> replied Mrs~Pegler, drawing her stout figure to its most impressive uprightness, <but that is not the point. I do not say that a spiritualist \textit{may} not live a good life, but I \textit{do} say that the majority of them are most unsatisfactory people, and far from truthful.>

<I have happened to meet with a number of so-called mediums in the course of my life,> agreed Miss~Tweall, acidly, <and all of them, without \textit{any} exception, were people I would not have trusted any further than I could see them—if as far.>

<That is very true of a great many of them,> said Miss~Climpson, <and I am sure \textit{nobody} could have better opportunities of judging than \textit{myself}. But I think and hope that some of them are at least \textit{sincere} if \textit{mistaken} in their claims. What do \textit{you} think, Mrs~Liffey?> she added, turning to the proprietress of the establishment.

<We-ll,> said Mrs~Liffey—obliged, in her official capacity, to agree as far as possible with all parties. <I must say, from what I have read, and that is not a great deal, for I have little time for reading—still, I think there is a certain amount of evidence to show that, in certain cases and under strictly safeguarded conditions, there is possibly some foundation of truth beneath the spiritualists' claims. Not that I should care to have anything to do with it personally; as Mrs~Pegler says, I do not as a rule care very much for the sort of people who go in for it, though doubtless there are many exceptions. I think perhaps that the subject should be left to properly qualified investigators.>

<There I agree with you,> said Mrs~Pegler. <No words can express the disgust I feel at the intrusion of women like this Mrs~Craig into realms that should be sacred to us all. Imagine, Miss~Climpson, that that woman—whom I do not know and have no intention of knowing—actually had the impertinence once to write to me and say that she had received a message at one of her séances, as she calls them, purporting to come from my dear husband. I cannot tell you what I felt. To have the General's name actually brought up, in public, in connection with such wicked nonsense! And of course it was the purest invention, for the General was the \textit{last} man to have anything to do with goings-on. <Pernicious poppy-cock,> he used to call it in his bluff military way. And when it came to telling me, his widow, that he had come to Mrs~Craig's house and played the accordion and asked for special prayers to deliver him from a place of punishment, I could only look on it as a calculated insult. The General was a regular Church-goer and entirely opposed to prayers for the dead or anything popish; and as to being in any undesirable place, he was the best of men, even if he was a little abrupt at times. As for accordions, I hope, wherever he is, he has something better to do with his time.>

<A most shameful business,> said Miss~Tweall.

<Who is this Mrs~Craig?> asked Miss~Climpson.

<Nobody knows,> said Mrs~Pegler, ominously.

<She is said to be a doctor's widow,> said Mrs~Liffey.

<It's my opinion,> said Miss~Tweall, <that she is no better than she should be.>

<A woman of her age,> said Mrs~Pegler, <with henna'd hair and earrings a foot long\longdash>

<And going about in those extraordinary clothes,> said Miss~Tweall.

<And having such very odd people to stay with her,> said Mrs~Pegler. <You remember that black man, Mrs~Liffey, who wore a green turban and used to say his prayers in the front garden, till the police interfered.>

<What I should like to know,> said Miss~Tweall, <is, where she gets her money from.>

<If you ask me, my dear, the woman's on the make. Heaven knows what she persuades people to do in these spiritualistic meetings.>

<But what brought her to Windle?> asked Miss~Climpson. <I should have thought London, or some big town, would have been a better place for her if she is the kind of person you describe.>

<I shouldn't be surprised if she was in hiding,> said Miss~Tweall, darkly. <There is such a thing as making a place too hot to hold you.>

<Without altogether subscribing to your wholesale condemnation,> said Miss~Climpson, <I must agree that psychical research can be \textit{very dangerous indeed} in the \textit{wrong hands}, and from what Miss~Booth tells me, I do doubt very \textit{much} whether Mrs~Craig is a suitable guide for the inexperienced. Indeed, I quite felt it my \textit{duty} to put Miss~Booth on her guard, and that is what I am endeavouring to do. But, as you know, one has to do that kind of thing \textit{very} tactfully—otherwise one may merely, so to speak, put the person's back up. The first step is to gain her \textit{confidence}, and then, little by little, one may be able to induce a more wholesome frame of mind.>

<That's \textit{so} true,< said Miss~Etheredge, eagerly, her pale blue eyes lighting with something that was almost animation. >I very nearly fell under the influence of a dreadful, fraudulent person myself, till my dear friend showed me a better way.>

<Maybe,> said Mrs~Pegler, <but in my opinion the whole thing is best left alone.>

Undeterred by this excellent advice, Miss~Climpson kept her appointment. After a spirited exhibition of table-rocking, Pongo consented to communicate by means of the Ouija board, though at first he was rather awkward with it. He attributed this, however, to the fact that he had never learned to write while on earth. Asked who he was, he explained that he was an Italian acrobat of the Renaissance period, and that his full name was Pongocelli. He had lived a sadly irregular life, but had redeemed himself by heroically refusing to abandon a sick child during the time of the Great Plague in Florence. He had caught the plague and died of it, and was now working out the period of probation for his sins by serving as guide and interpreter to other spirits. It was a touching story, and Miss~Climpson was rather proud of it.

George Washington was rather intrusive, and the séance also suffered from a number of mysterious interruptions from what Pongo described as a <jealous influence.> Nevertheless, <Harry> reappeared and delivered some consolatory messages, and there were further communications from Mabel Herridge, who gave a vivid description of her life in India. On the whole, and taking the difficulties into account, a successful evening.

On Sunday there was no séance, owing to the revolt of the medium's conscience. Miss~Climpson felt that she could not, really could not, bring herself to do it. She went to church instead, and listened to the Christmas message with a distracted mind.

On Monday, however, the two enquirers again took their seats about the bamboo table, and the following is the report of the séance, as noted down by Miss~Booth.

\divider


	
\textit{7.30 \textsc{p.m.}}

On this occasion proceedings were begun at once with the Ouija board; after a few minutes, a loud succession of raps announced the presence of a control.

\begin{dialogue}
\speak{Question} Good-evening. Who is that?

\speak{Answer} Pongo here. Good-evening! Heaven bless you.

\speak{Q.} We are very glad to have you with us, Pongo.

\speak{A.} Good—very good. Here we are again!

\speak{Q.} Is that you, Harry?

\speak{A.} Yes, only to give my love. Such a crowd.

\speak{Q.} The more the better. We are glad to meet all our friends. What can we do for you?

\speak{A.} Attend. Obey the spirits.

\speak{Q.} We will do all we can, if you will tell us what to do.

\speak{A.} Boil your heads!

\speak{Q.} Go away, George, we don't want you.

\speak{A.} Get off the line, silly.

\speak{Q.} Pongo, can't you send him away?

\direct{Here the pencil drew the sketch of an ugly face.}

\speak{Q.} Is that your portrait?

\speak{A.} That's me. G. W. Ha, ha!

\direct{The pencil zig-zagged violently and drove the board right over the edge of the table. When it was replaced it started to write in the hand we associate with Pongo.}

\speak{A.} I have sent him away. Very noisy tonight. F. jealous and sends him to disturb us. Never mind. Pongo more powerful.

\speak{Q.} Who do you say is jealous?

\speak{A.} Never mind. Bad person. Maladetta.

\speak{Q.} Is Harry still there?

\speak{A.} No. Other business. There is a spirit here who wishes your help.

\speak{Q.} Who is it?

\speak{A.} Very hard. Wait.

\direct{The pencil made a series of wide loops.}

\speak{Q.} What letter is that?

\speak{A.} Silly! don't be impatient. There is difficulty. I will try again.

\direct{The pencil scribbled for a few minutes and then wrote a large C.}

\speak{Q.} We have got the letter C. Is that right?

\speak{A.} C-C-C

\speak{Q.} We have got C.

\speak{A.} C-R-E

\direct{Here there was another violent interruption.}

\speak{A.} \direct{in Pongo's writing} She is trying, but there is much opposition. Think helpful thoughts.

\speak{Q.} Would you like us to sing a hymn?

\speak{A.} \direct{Pongo again, very angry} Stupid! Be quiet! \direct{Here the writing changed again} M-O-

\speak{Q.} Is that part of the same word?

\speak{A.} R-N-A.

\speak{Q.} Do you mean Cremorna?

\speak{A.} \direct{in the new writing} Cremorna, Cremorna. Through! Glad, glad, glad!
\end{dialogue}

At this point, Miss~Booth turned to Miss~Climpson and said in a puzzled voice:

<This is very strange. Cremorna was Mrs~Wrayburn's stage name. I do hope—surely she can't have passed away suddenly. She was perfectly comfortable when I left her. Had I better go and see?>

<Perhaps it's another Cremorna?> suggested Miss~Climpson.

<But it's such an unusual name.>

<Why not ask who it is?>

\begin{dialogue}
\speak{Q.} Cremorna—what is your second name?

\speak{A.} \direct{The pencil writing very fast} Rosegarden—easier now.

\speak{Q.} I don't understand you.

\speak{A.} Rose—Rose—Rose—Silly!

\speak{Q.} Oh!—(My dear, she's mixing up the two names)—Do you mean Cremorna Garden?

\speak{A.} Yes.

\speak{Q.} Rosanna Wrayburn?

\speak{A.} Yes.

\speak{Q.} Have you passed over?

\speak{A.} Not yet. In exile.

\speak{Q.} Are you still in the body?

\speak{A.} Neither in the body nor out of the body. Waiting. (Pongo interposing) When what you call the mind is departed, the spirit waits in exile for the Great Change. Why can't you understand? Make haste. Great difficulties.

\speak{Q.} We are so sorry. Are you in trouble about something?

\speak{A.} Great trouble.

\speak{Q.} I hope it isn't anything in Dr~Brown's treatment, or mine—

\speak{A.} \direct{Pongo} Do not be so foolish. \direct{Cremorna} My will.

\speak{Q.} Do you want to alter your will?

\speak{A.} No.

\speak{Miss~Climpson.} That is fortunate, because I don't think it would be legal. What do you want us to do about it, dear Mrs~Wrayburn?

\speak{A.} Send it to Norman.

\speak{Q.} To Mr~Norman Urquhart?

\speak{A.} Yes. He knows.

\speak{Q.} He knows what is to be done with it?

\speak{A.} He wants it.

\speak{Q.} Very well. Can you tell us where to find it?

\speak{A.} I have forgotten. Search.

\speak{Q.} Is it in the house?

\speak{A.} I tell you I have forgotten. Deep waters. No safety. Failing, failing\dots

(Here the writing became very faint and irregular.)

\speak{Q.} Try to remember.

\speak{A.} In the B—B—B—\direct{a confusion and the pencil staggering wildly}—No good. \direct{Suddenly, in a different hand and very vigorously} Get off the line, get off the line, get off the line.

\speak{Q.} Who is that?

\speak{A.} \direct{Pongo} She has gone. The bad influence back. Ha, ha! Get off! Finished now. \direct{The pencil ran right out of the medium's control, and on being replaced on the table, refused to answer any further questions.}

\end{dialogue}

<How dreadfully vexatious!> exclaimed Miss~Booth.

<I suppose you have no idea where the will is?>

<Not the least. <In the B\longdash> she said. Now, what could that be?>

<In the Bank, perhaps,> suggested Miss~Climpson.

<It might be. If so, of course, Mr~Urquhart would be the only person who could get it out.>

<Then why hasn't he? She said he wanted it.>

<Of course. Then it must be somewhere in the house. What could B stand for?>

<Box, Bag, Bureau—?>

<Bed? It might be almost anything.>

<What a pity she couldn't finish the message. Shall we try again? Or shall we look in all the likely places?>

<Let's look first, and then, if we can't find it, we can try again.>

<That's a good idea. There are some keys in one of the bureau drawers that belong to her boxes and things.>

<Why not try them?> said Miss~Climpson, boldly.

<We will. You'll come and help, won't you?>

<If you think it advisable. I'm a stranger, you know.>

<The message came to you as much as to me. I'd rather you came with me. You might be able to suggest places.>

Miss~Climpson made no further ado, and then went upstairs. It was a queer business—practically robbing a helpless woman in the interests of someone she had never seen. Queer. But the motive must be a good one, if it was Lord~Peter's.

At the top of the beautiful staircase with its ample curve was a long, wide corridor, the walls hung thickly from floor to ceiling with portraits, sketches, framed autograph letters, programmes, and all the reminiscent bric-à-brac of the green-room.

<All her life is here and in these two rooms,> said the nurse. <If this collection was to be sold, it would fetch a lot of money. I suppose it will be, some day.>

<Whom does the money go to, do you know?>

<Well, I've always thought it would be to Mr~Norman Urquhart—he's a relation of hers, about the only one, I believe. But I've never been told anything about it.>

She pushed open a tall door, graceful with curved panels and classical architrave, and turned on the light.

It was a stately great room, with three tall windows and a ceiling gracefully moulded with garlands of flowers and flambeaux. The purity of its lines was, however, defaced and insulted by a hideous rose-trellised wall-paper, and heavy plush curtains of a hot crimson with thick gold fringes and ropes, like the drop-curtain of a Victorian play-house. Every foot of space was crammed thick with furniture—buhl cabinets incongruously jostling mahogany chiffoniers; what-not tables strewn with ornaments cuddling the bases of heavy German marbles and bronzes; lacquer screens, Sheraton bureaux, Chinese vases, alabaster lamps, chairs, ottomans of every shape, colour and period, clustered thick as plants wrestling for existence in a tropical jungle. It was the room of a woman without taste or moderation, who refused nothing and surrendered nothing, to whom the fact of possession had become the one steadfast reality in a world of loss and change.

<It may be in here or in the bedroom,> said Miss~Booth. <I'll get her keys.>

She opened a door on the right. Miss~Climpson, endlessly inquisitive, tip-toed in after her.

The bedroom was even more of a nightmare than the sitting-room. A small electric reading-lamp burned dimly by the bed, huge and gilded, with hangings of rose brocade cascading in long folds from a tester supported by fat golden cupids. Outside the narrow circle of light loomed monstrous wardrobes, more cabinets, tall chests of drawers. The dressing-table, frilled and flounced, held a wide, three-fold mirror, and a monstrous cheval-glass in the centre of the room darkly reflected the towering and shadowy outlines of the furniture.

Miss~Booth opened the middle door of the largest wardrobe. It swung back with a creak, letting out a great gush of frangipani. Nothing, evidently, had been altered in this room since silence and paralysis had struck the owner down.

Miss~Climpson stepped softly up to the bed. Instinct made her move cautiously as a cat, though it was evident that nothing would ever startle or surprise its occupant.

An old, old face, so tiny in the vast expanse of sheet and pillow that it might have been a doll, stared up at her with unblinking, unseeing eyes. It was covered with fine surface-wrinkles, like a hand sodden with soapy water, but all the great lines carved by experience had been smoothed out with the relaxing of the helpless muscles. It was both puffed and crumpled. It reminded Miss~Climpson of a child's pink balloon, from which nearly all the air has leaked away. The escaping breath puffed through the lax lips in little blowing, snorting sounds and added to the resemblance. From under the frilled night-cap straggled a few lank wisps of whitened hair.

<Funny, isn't it,> said Miss~Booth, <to think that with her lying like that, her spirit can communicate with us.>

Miss~Climpson was overcome by a sense of sacrilege. It was only by a great effort that she prevented herself from confessing the truth. She had pulled the garter with the soap-box above her knee for safety, and the elastic was cutting painfully into the muscles of her leg—a kind of reminder of her iniquities.

But Miss~Booth had already turned away, and was pulling open the drawers of one of the bureaux.

Two hours passed, and they were still searching. The letter B. opened up a particularly wide field of search. Miss~Climpson had chosen it on that account, and her foresight was rewarded. By a little ingenuity, that useful letter could be twisted to fit practically any hiding-place in the house. The things that were neither bureaux, beds, bags, boxes, baskets nor bibelot-tables could usually be described as big, black, brown or buhl or, at a pinch, as being bedroom or boudoir furniture, and since every shelf, drawer and pigeon-hole in every object was crammed full of newspaper-cuttings, letters and assorted souvenirs, the searchers soon found their heads, legs and backs aching with effort.

<I'd no idea,> said Miss~Booth, <that there could be so many possible places.>

Miss~Climpson, sitting on the floor, with her back hair uncoiling itself and her decent black petticoats tucked up nearly to the soap-box, agreed wearily.

<It's dreadfully exhausting, isn't it?> said Miss~Booth. <Wouldn't you like to stop? I can go on searching tomorrow by myself. It's a shame to tire you out in this way.>

Miss~Climpson turned this over in her mind. If the will were found in her absence and sent to Norman Urquhart, would Miss~Murchison be able to get hold of it before it was again hidden away or destroyed? She wondered.

Hidden away, not destroyed. The mere fact that the will had been sent to him by Miss~Booth would prevent the solicitor from making away with it, for there would be a witness to its existence. But he might successfully conceal it for a considerable time—and time was of the essence of the adventure.

<Oh, I'm not a scrap tired,> she said brightly, sitting up on her heels and restoring her coiffure to something more like its usual neatness. She had a black note-book in her hand, taken from a drawer in one of the Japanese cabinets, and was turning its pages mechanically. A line of figures caught her eye: 12, 18, 4, 0, 9, 3, 15, and she wondered vaguely what they referred to.

<We've looked through everything here,> said Miss~Booth. <I don't believe we've missed anything—unless, of course, there is a secret drawer somewhere.>

<Could it be in a book, do you think?>

<A book! Why, of course it might. How silly of us not to think of that! In detective stories, wills are always hidden in books.>

<More often than in real life,> thought Miss~Climpson, but she got up and dusted herself and said cheerfully:

<So they are. Are there many books in the house?>

<Thousands,> said Miss~Booth. <Downstairs in the library.>

<I shouldn't have expected Mrs~Wrayburn to be a great reader, somehow.>

<Oh, I don't think she was. The books were bought with the house, so Mr~Urquhart told me. They're nearly all old ones, you know—big things bound in leather. Dreadfully dull. I've never found a thing to read there. But they're just the sort of books to hide wills in.>

They emerged into the corridor.

<By the way,> said Miss~Climpson, <won't the servants think it funny of us to be wandering about the place so late?>

<They all sleep in the other wing. Besides, they know that I sometimes have visitors. Mrs~Craig has often been here as late as this when we have had interesting sittings. There's a spare bedroom where I can put people up when I want to.>

Miss~Climpson made no more objections, and they went downstairs and along the hall into the library. It was big, and books filled the walls and bays in serried ranks—a heart-breaking sight.

<Of course,> said Miss~Booth, <if the communication hadn't insisted on something beginning with B\longdash>

<Well?>

<Well—I should have expected any papers to be in the safe down here.>

Miss~Climpson groaned in spirit. The obvious place, naturally! If only her misplaced ingenuity—well! one must make the best of it.

<Why not look?> she suggested. <The letter B. may have been referring to something quite different. Or it may have been an interruption from George Washington. It would be quite like him to use words beginning with a B, don't you think?>

<But if it was in the safe, Mr~Urquhart would know about it.>

Miss~Climpson began to feel that she had let her invention play about too freely.

<It wouldn't do any harm to make sure,> she suggested.

<But I don't know the combination,> said Miss~Booth. <Mr~Urquhart does, of course. We could write and ask him.>

An inspiration came to Miss~Climpson.

<I believe I know it,> she exclaimed. <There was a row of seven figures in that black note-book I was looking at just now, and it passed through my mind that they must be a memorandum of something.>

<Black Book!> cried Miss~Booth. <Why, there you are! How could we have been so silly! Of course, Mrs~Wrayburn was trying to tell us where to find the combination!>

Miss~Climpson again blessed the all-round utility of the letter B.

<I'll run up and fetch it,> she cried.

When she came down again, Miss~Booth was standing before a section of the bookshelves, which had swung out from the wall, disclosing the green door of a built-in safe. With trembling hands, Miss~Climpson touched the milled knob and turned it.

The first attempt was unsuccessful, owing to the fact that the note did not make it clear which way the knob should be turned first, but at the second attempt the pointer swung over on the seventh figure with a satisfying click.

Miss~Booth seized the handle, and the heavy door moved and stood open.

A bundle of papers lay inside. On the top, staring them in the face, was a long, sealed envelope. Miss~Climpson pounced upon it.


\begin{quote}\centering\scshape
Will of Rosanna Wrayburn\\
5 June 1920.
\end{quote}

<Well, isn't that marvellous?> cried Miss~Booth. On the whole, Miss~Climpson agreed with her.