\chapter[Chapter \thechapter]{}
\lettrine{M}{iss} Climpson stayed the night in the spare bedroom.

\zz
<The best thing,> she said, <will be for you to write a little letter to Mr~Urquhart, explaining about the séance, and saying that you thought it best and safest to send the will on to him.>

<He will be very much surprised,> said Miss~Booth. <I wonder what he will say. Lawyers don't believe in spirit communications as a rule. And he'll think it rather funny that we should have managed to open the safe.>

<Well, but the spirit led us directly to the combination, didn't it? He could hardly expect you to ignore a message like that, could he? The proof of your good faith is that you are sending the will straight to him. And it would be as well, don't you think, if you asked him to come up and check the other contents of the safe and have the combination altered.>

<Wouldn't it be better if I kept the will and asked him to come for it?>

<But perhaps he requires it urgently?>

<Then why hasn't he been to fetch it?>

Miss~Climpson noted with some irritation that, where spiritualistic messages were not concerned, Miss~Booth showed signs of developing an independent judgment.

<Perhaps he doesn't know yet that he wants it. Perhaps the spirits foresaw an urgent need that will only arise tomorrow.>

<Oh, yes, that's quite likely. If only people would avail themselves more fully of the marvellous guidance given to them, so much might be foreseen and provided for! Well, I think you are right. We will find a big envelope to fit it, and I will write a letter and we will send it by the first post tomorrow.>

<It had better be registered,> said Miss~Climpson. <If you will entrust it to me, I will take it down to the post-office first thing.>

<Will you? That will be a great relief to my mind. Well now, I'm sure you're as tired as I am, so I'll put on a kettle for the hot-water bottles and we'll turn in. Will you make yourself comfy in my sitting-room? I've only got to put the sheets on your bed. What? No, indeed, I can do it in a moment; \textit{please} don't bother. I'm so used to making beds.>

<Then I'll see to the kettles,> said Miss~Climpson. <I simply \textit{must} make myself useful.>

<Very well. It won't take long. The water is quite hot in the kitchen boiler.>

Left alone in the kitchen, with a kettle bumping and singing on its way to boiling-point, Miss~Climpson wasted no time. She tip-toed quickly out again and stood with ear cocked at the foot of the stairs, listening to the nurse's footsteps as they pattered into the distance. Then she slipped into the little sitting-room, took up the will in its sealed envelope, and a long thin paper-knife which she had already marked down as a useful weapon, and hastened back to the kitchen.

It is astonishing how long a kettle which seems to be on the verge of boiling will take before the looked-for jet of steady steam emerges from its spout. Delusive little puffs and deceptive pauses in the song tantalise the watcher interminably. It seemed to Miss~Climpson that there would have been time to make twenty beds before the kettle boiled that evening. But even a watched pot cannot absorb heat for ever. After what appeared to be an hour, but was actually about seven minutes, Miss~Climpson, guilty and furtive, was holding the flap of the envelope before the scalding steam.

<I mustn't hurry,> said Miss~Climpson, <oh, blessed saints, I mustn't hurry, or I shall tear it.>

She slipped the paper-knife under the flap; it lifted; it opened cleanly, just as Miss~Booth's step resounded in the passage.

Miss~Climpson adroitly dropped the paper-knife behind the stove and thrust the envelope, with the flap doubled back to prevent it from re-sticking itself, behind a dish-cover on the wall.

<The water's ready!> she cried blithely. <Where are the bottles?>

It is a tribute to her nerve that she filled them with a steady hand. Miss~Booth thanked her, and departed upstairs, a bottle in each hand.

Miss~Climpson pulled the will from its hiding-place, drew it from its envelope and glanced swiftly through it.

It was not a long document, and in spite of the legal phraseology, its purport was easily gathered. Within three minutes she had replaced it, moistened the gum and stuck the flap down again. She put it in her petticoat-pocket—for her garments were of a useful and old-fashioned kind—and went to hunt in the pantry. When Miss~Booth returned, she was making tea peacefully.

<I thought it would refresh us after our labours,> she remarked.

<A very good idea,> said Miss~Booth; <in fact, I was just going to suggest it.>

Miss~Climpson carried the tea-pot to the sitting-room, leaving Miss~Booth to follow with the cups, milk and sugar on a tray. With the tea-pot on the hob and the will once more lying innocently on the table, she smiled and breathed deeply. Her mission was accomplished.

\divider

Letter from Miss~Climpson to Lord~Peter Wimsey.

\begin{mail}{Tuesday, Jan. 7, 1930.}{My dear Lord~Peter,}

As my \textit{telegram} this morning will have informed you, I have \textsc{succeeded}!! Though what excuse I can find in my \textit{conscience} for the \textit{methods} I have used, I \textit{don't} \textsc{know}! but I believe the Church takes into account the necessity of \textit{deception} in certain \textit{professions}, such as that of a \textit{police-detective} or a \textsc{spy} in time of \textsc{warfare}, and I \textit{trust} that my \textit{subterfuges} may be allowed to come under that \textit{category}. However, you will not want to hear about my \textit{religious scruples}! So I will hasten to let you know \textit{what} I have \textsc{discovered}!!

In my last letter I explained the \textit{plan} I had in mind, so you will know what to do about the \textit{Will itself}, which was duly \textit{despatched} by \textit{Registered Post} this morning under cover to \textit{Mr~Norman Urquhart}. How surprised he will be to get it!!! Miss~Booth wrote an excellent \textit{covering letter}, which I \textit{saw} before it went, which explains the circumstances and \textit{mentions} \textsc{no} \textsc{names}!! I have wired to Miss~Murchison to \textit{expect} the package, and I hope that when it comes she will contrive to be \textit{present} at the opening, so as to constitute \textit{yet another} \textsc{witness} to its existence. In any case, I should not think he would \textit{venture} to \textit{tamper} with it. Perhaps Miss~Murchison may be able to \textsc{investigate} it in detail, which I had not \textit{time} to do (it was all \textit{most} adventurous! and I am looking forward to \textit{telling} you \textsc{all} \textsc{about} \textsc{it} when I come back), but in case she is \textit{not} able to do so, I will give you the \textit{rough outline}.

The property consists of \textit{real estate} (the house and grounds) and a \textit{personalty} (am I not \textit{good} at legal terms??) which I am not able to calculate \textit{exactly}. But the gist of it all is this:—

The \textit{real estate} is left to \textit{Philip Boyes}, absolutely.

\textit{Fifty thousand pounds} is left to \textit{Philip Boyes} also, in \textit{cash}.

The remainder (is not this called the residue?) is left to \textsc{Norman Urquhart}, who is appointed sole executor.

There are a few \textit{small legacies} to Stage Charities, of which I did not manage to memorise any \textit{particulars}.

There is a special paragraph, explaining that the greater part of the property is left to \textit{Philip Boyes} in token that the testatrix \textsc{forgives} the ill-treatment meted out to her by \textit{his family}, for which he was \textit{not responsible}.

The date of the Will is 5 June 1920, and the \textit{witnesses} are \textit{Eva Gubbins}, housekeeper, and \textit{John Briggs}, gardener.

I hope, dear Lord~Peter, that this information will be enough for your purpose. I had hoped that even \textit{after} Miss~Booth had enclosed the Will in a \textit{covering envelope} I might be able to take it out and \textit{peruse} it at leisure, but unfortunately she \textit{sealed} it for greater security with Mrs~Wrayburn's \textit{private seal}, which I had not sufficient \textit{dexterity} to \textit{remove and replace}, though I understand it is possible to \textit{do so} with a \textit{hot knife}.

You will \textit{understand} that I cannot leave Windle \textit{just yet}—it would look so odd to do so immediately after this occurrence. Besides, I am hoping, in a further series of <sittings,> to \textit{warn} Miss~Booth against Mrs~Craig and her <control> Fedora, as I am \textit{quite sure} that this person is \textit{quite} as great a \textit{charlatan} as I \textsc{am}!!!—and without my \textit{altruistic} motives!! So you will not be surprised if I am away from Town for, say, \textit{another week}! I am a little worried about the \textit{extra expense} of this, but if you do not think it \textit{justified} for the sake of safety, \textit{let me know}—and I will alter my arrangements accordingly.

Wishing you \textit{all success}, dear Lord~Peter,

\addPS{I managed to do the <job> \textit{very nearly} within the stipulated week, you see. I am \textit{so sorry} it was not \textit{quite} finished yesterday, but I was so \textit{terrified} of \textit{spoiling} the \textsc{whole} \textsc{thing} by \textit{rushing} it!!}

\closeletter[Most sincerely yours,]{Katharine A. Climpson.}
\end{mail}

\divider

<Bunter,> said Lord~Peter, looking up from this letter, <I \textit{knew} there was something fishy about that will.>

<Yes, my lord.>

<There is something about wills which brings out the worst side of human nature. People who under ordinary circumstances are perfectly upright and amiable, go as curly as corkscrews and foam at the mouth, whenever they hear the words <I devise and bequeath.> That reminds me, a spot of champagne in a silver tankard is no bad thing to celebrate on. Get up a bottle of the Pommery and tell Chief-Inspector Parker I should be glad of a word with him. And bring me those notes of Mr~Arbuthnot's. And oh, Bunter!>

<My lord?>

<Get Mr~Crofts on the 'phone and give him my compliments, and say I have found the criminal and the motive and hope presently to produce proof of the way the crime was done, if he will see that the case is put off for a week or so.>

<Very good, my lord.>

<All the same, Bunter, I really don't know how it \textit{was} done.>

<That will undoubtedly suggest itself before long, my lord.>

<Oh, yes,> said Wimsey, airily. <Of course. Of course. I'm not worrying about a trifle like that.>