\chapter[Chapter \thechapter]{}
\lettrine[ante=`]{I}{} have come round,' said Mr~Urquhart, <in answer to your letter. I am greatly interested to hear that you have some fresh information about my unfortunate cousin's death. Of course I shall be delighted to give you any assistance I can.>

<Thank you,> said Wimsey. <Do sit down. You have dined, of course? But you will have a cup of coffee. You prefer the Turkish variety, I fancy. My man brews it rather well.>

Mr~Urquhart accepted the offer, and complimented Bunter on having achieved the right method of concocting that curiously syrupy brew, so offensive to the average Occidental.

Bunter thanked him gravely for his good opinion, and proffered a box of that equally nauseating mess called Turkish Delight, which not only gluts the palate and glues the teeth, but also smothers the consumer in a floury cloud of white sugar. Mr~Urquhart immediately plugged his mouth with a large lump of it, murmuring indistinctly that it was the genuine Eastern variety. Wimsey, with an austere smile, took a few sips of strong black coffee without sugar or milk, and poured himself out a glass of old brandy. Bunter retired, and Lord~Peter, laying a note-book open upon his knee, glanced at the clock and began his narrative.

He recapitulated the circumstances of Philip Boyes' life and death at some length. Mr~Urquhart, yawning surreptitiously, ate, drank and listened.

Wimsey, still with his eye on the clock, then embarked upon the story of Mrs~Wrayburn's will.

Mr~Urquhart, considerably astonished, set his coffee-cup aside, wiped his sticky fingers upon his handkerchief, and stared.

Presently he said:

<May I ask how you have obtained this very remarkable information?>

Wimsey waved his hand.

<The police,> he said, <wonderful thing, police organisation. Surprisin' what they find out when they put their minds to it. You're not denying any of it, I presume?>

<I am listening,> said Mr~Urquhart, grimly. <When you have finished this extraordinary statement, I may perhaps discover exactly what it is I have to deny.>

<Oh, yes,> said Wimsey, <I'll try to make that clear. I'm not a lawyer, of course, but I'm tryin' to be as lucid as I can.>

He droned remorselessly on, and the hands of the clock went round.

<So far as I make it out,> he said, when he had reviewed the whole question of motive, <it was very much to your interest to get rid of Mr~Philip Boyes. And indeed the fellow was, in my opinion, a pimple and a wart, and in your place I should have felt much the same about him.>

<And is this the whole of your fantastic accusation?> enquired the solicitor.

<By no means. I am now coming to the point. Slow but sure is the motto of yours faithfully. I notice that I have taken up seventy minutes of your valuable time, but believe me, the hour has not been unprofitably spent.>

<Allowing that all this preposterous story were true, which I most emphatically deny,> observed Mr~Urquhart, <I should be greatly interested to know how you imagine that I administered the arsenic. Have you worked out something ingenious for that? Or am I supposed to have suborned my cook and parlourmaid to be my accomplices? A little rash of me, don't you think, and affording remarkable opportunities for blackmail?>

<So rash,> said Wimsey, <that it is quite out of the question for a man so full of forethought as yourself. The sealing-up of that bottle of burgundy, for example, argues a mind alive to possibilities—unusually so. In fact, the episode attracted my attention from the start.>

<Indeed?>

<You ask me how and when you administered the poison. It was not before dinner, I think. The thoughtfulness shown in emptying the bedroom water-bottle—oh, no! that point was not missed—the care displayed in meeting your cousin before a witness and never being left alone with him—I think that rules out the period before dinner.>

<I should think it might.>

<The sherry,> pursued Wimsey, thoughtfully. <It was a new bottle, freshly decanted. The disappearance of the remains might be commented on. I fancy we can absolve the sherry.>

Mr~Urquhart bowed ironically.

<The soup—it was shared by the cook and parlourmaid and they survived. I am inclined to pass the soup, and the same thing applies to the fish. It would be easy to poison a portion of fish, but it would involve the co-operation of Hannah Westlock, and that conflicts with my theory. A theory is a sacred thing to me, Mr~Urquhart—almost a what d'you call it—a dogma.>

<An unsafe attitude of mind,> remarked the lawyer, <but in the circumstances I will not quarrel with it.>

<Besides,> said Wimsey, <if the poison had been given in the soup or the fish, it might have started to work before Philip—I may call him so, I hope?—had left the house. We come to the casserole. Mrs~Pettican and Hannah Westlock can give the casserole a clean bill of health, I fancy. And by the way, from the description it must have been most delicious. I speak as a man with some considerable experience in gastronomic matters, Mr~Urquhart.>

<I am well aware of it,> said Mr~Urquhart, politely.

<And now there remains only the omelette. A most admirable thing when well made and eaten—that is so important—eaten immediately. A charming idea to have the eggs and sugar brought to the table and prepared and cooked on the spot. By the way, I take it there was no omelette left over for the kitchen? No, no! One does not let a good thing like that go out half-eaten. Much better that the good cook should make a fine, fresh omelette for herself and her colleague. Nobody but yourself and Philip partook of the omelette, I am sure.>

<Quite so,> said Mr~Urquhart, <I need not trouble to deny it. But you will bear in mind that I did partake of it, without ill-effects. And moreover, that my cousin made it himself.>

<So he did. Four eggs, if I remember rightly, with sugar and jam from what I may call the common stock. No—there would be nothing wrong with the sugar or the jam. Er—I believe I am right in saying that one of the eggs was cracked when it came to the table?>

<Possibly. I do not really remember.>

<No? Well, you are not on oath. But Hannah Westlock remembers that when you brought the eggs in—you purchased them yourself, you know, Mr~Urquhart—you mentioned that one was cracked and particularly desired that it should be used for the omelette. In fact, you yourself laid it in the bowl for that purpose.>

<What about it?> asked Mr~Urquhart, perhaps a trifle less easily than before.

<It is not very difficult to introduce powdered arsenic into a cracked egg,> said Wimsey. <I have made the experiment myself with a small glass tube. Perhaps a small funnel would be even easier. Arsenic is a fairly heavy substance—7 or 8 grains will go into a tea-spoon. It collects at one end of the egg, and any traces on the exterior of the shell can be readily wiped off. Liquid arsenic could be poured in still more easily, of course, but for a particular reason I made my experiment with the ordinary white powder. It is fairly soluble.>

Mr~Urquhart had taken a cigar from his case, and was making rather a business of lighting it.

<Do you suggest,> he enquired, <that in the whisking together of four eggs, one particular poisoned egg was somehow kept miraculously separated from the rest and deposited with its load of arsenic at one end of the omelette only? Or that my cousin deliberately helped himself to the poisoned end and left the rest to me?>

<Not at all, not at all,> said Wimsey. <I suggest merely that the arsenic was in the omelette and came there by way of the egg.>

Mr~Urquhart threw his match into the fireplace.

<There seem to be some flaws in your theory, as well as in the egg.>

<I haven't finished the theory yet. My next bit of it is built up from very trifling indications. Let me enumerate them. Your disinclination to drink at dinner, your complexion, a few nail-parings, a snipping or so from your very well-kept hair—I put these together, add a packet of white arsenic from the secret cupboard in your office, rub the hands a little—so—and produce—hemp, Mr~Urquhart, hemp.>

He sketched the shape of a noose lightly in the air.

<I don't understand you,> said the solicitor, hoarsely.

<Oh \textit{you} know,< said Wimsey. >Hemp—what they make ropes of. Great stuff, hemp. Yes, well, about this arsenic. As you know, it's not good for people in a general way, but there are some people—those tiresome peasants in Styria one hears so much about—who are supposed to eat it for fun. It improves their wind, so they say, and clears their complexions and makes their hair sleek, and they give it to their horses for the same reason; bar the complexion, that is, because a horse hasn't much complexion, but you know what I mean. Then there was that horrid man Maybrick—he used to take it, or so they say. Anyhow, it's well known that some people do take it and manage to put away large dollops after a bit of practice—enough to kill any ordinary person. But you know all this.>

<This is the first time I've heard of such a thing.>

<Where \textit{do} you expect to go to? Never mind. We'll pretend this is all new to you. Well, some fellow—I've forgotten his name\footnote{Valetta.}, but it's all in Dixon Mann—wondered how the dodge was worked, and he got going on some dogs and things and he dosed 'em and killed a lot of 'em I daresay, and in the end he found that whereas liquid arsenic was dealt with by the kidneys and was uncommonly bad for the system, solid arsenic could be given day by day, a little bigger dose each time, so that in time the doings—what an old lady I knew in Norfolk called <the tubes>—got used to it and could push it along without taking any notice of it, so to speak. I read a book somewhere which said it was all done by leucocytes—those jolly little white corpuscles, don't you know—which sort of got round the stuff and bustled it along so that it couldn't do any harm. At all events, the point is that if you go on taking solid arsenic for a good long time—say a year or so—you establish a what-not, an immunity, and can take six or seven grains at a time without so much as a touch of indijaggers.>

<Very interesting,> said Mr~Urquhart.

<Apparently these beastly Styrian peasants do it that way, and they're very careful not to drink for two hours or thereabouts after taking it, for fear it should all get washed into the kidneys and turn poisonous on 'em. I'm not bein' very technical, I'm afraid, but that's the gist of it. Well, it occurred to me, don't you see, old horse, that if you'd had the bright idea to immunise yourself first, you could easily have shared a jolly old arsenical omelette with a friend. It would kill him and it wouldn't hurt you.>

<I see.>

The solicitor licked his lips.

<Well, as I say, you have a nice clear complexion—except that I notice the arsenic has pigmented the skin here and there (it does sometimes), and you've got the sleek hair and so on, and I noticed you were careful not to drink at dinner, and I said to myself, <Peter, my bright lad, what about it?> And when they found a packet of white arsenic in your cupboard—never mind how for the moment!—I said, <Hullo, hullo, how long has this been going on?> Your handy foreign chemist has told the police two years—is that right? About the time of the Megatherium crash that would be, wouldn't it? All right, don't tell me if you don't want to. Then we got hold of some bits of your hair and nails, and lo and behold, they were bung-full of arsenic. And we said <What-ho!> So that's why I asked you to come along and have a chat with me. I thought you might like to offer some sort of suggestion, don't you know.>

<I can only suggest,> said Urquhart, with a ghastly face but a strictly professional manner, <that you should be careful before you communicate this ludicrous theory to anybody. What you and the police—whom, frankly, I believe to be capable of anything—have been planting on my premises I do not know, but to give out that I am addicted to drug-taking habits is slander and criminal. It is quite true that I have for some time been taking a medicine which contains slight traces of arsenic—Dr~Grainger can furnish the prescription—and that may very likely have left a deposit in my skin and hair, but further than that, there is no foundation for this monstrous accusation.>

<None?>

<None.>

<Then how is it,> asked Wimsey, coolly, but with something menacing in his rigidly controlled voice, <how is it that you have this evening consumed, without apparent effect, a dose of arsenic sufficient to kill two or three ordinary people? That disgusting sweetmeat on which you have been gorging yourself in, I may say, a manner wholly unsuited to your age and position, is smothered in white arsenic. You ate it, God forgive you, an hour and a half ago. If arsenic can harm you, you should have been rolling about in agonies for the last hour.>

<You devil!>

<Couldn't you try to get up a few symptoms?> said Wimsey, sarcastically. <Shall I bring you a basin? Or fetch the doctor? Does your throat burn? Is your inside convulsed with agony? It is rather late in the day, but with a little goodwill you could surely produce \textit{some} display of feeling, even now.>

<You are lying. You wouldn't dare to do such a thing! It would be murder.>

<Not in this case, I fancy. But I am willing to wait and see.>

Urquhart stared at him. Wimsey got out of his chair in a single swift movement and stood over him.

<I wouldn't use violence if I were you. Let the poisoner stick to his bottle. Besides, I am armed. Pardon the melodrama. Are you going to be sick or not?>

<You're mad.>

<Don't say that. Come, man—pull yourself together. Have a shot at it. Shall I show you the bathroom?>

<I'm ill.>

<Of course; but your tone is not convincing. Through the door, along the passage, and third on the left.>

The lawyer stumbled out. Wimsey returned to the library and rang the bell.

<I think, Bunter, Mr~Parker may require some assistance in the bathroom.>

<Very good, my lord.>

Bunter departed and Wimsey waited. Presently there were sounds of a scuffle in the distance. A group appeared at the door. Urquhart, very white, his hair and clothes disordered, flanked by Parker and Bunter, who held him firmly by the arms.

<Was he sick?> asked Wimsey, with interest.

<No, he wasn't,> said Parker, grimly, snapping the handcuffs on his prey. <He cursed you fluently for five minutes, then tried to get out of the window, saw it was a three-story drop, charged in through the dressing-room door and ran straight into me. Now don't struggle, my lad, you'll only hurt yourself.>

<And he still doesn't know whether he's poisoned or not?>

<He doesn't seem to think he is. At any rate, he made no effort about it. His one idea was to hop it.>

<That's feeble,> said Wimsey, <if I wanted people to think I'd been poisoned I'd put up a better show than that.>

<Stop talking, for God's sake,> said the prisoner. <You've got me, by a vile, damnable trick. Isn't that enough? You can shut up about it.>

<Oh,> said Parker, <we've got you, have we? Well, I warned you not to talk, and if you \textit{will} do it, it's not my fault. By the way, Peter, I don't suppose you did actually poison him, did you? It doesn't seem to have hurt him, but it'll affect the doctor's report.>

<No, I didn't, as a matter of fact,> said Wimsey. <I only wanted to see how he'd react to the suggestion. Well, cheerio! I can leave it to you now.>

<We'll look after him,> said Parker. <But you might let Bunter ring up a taxi.>

When the prisoner and his escort had departed, Wimsey turned thoughtfully to Bunter, glass in hand.

<\textit{Mithridates he died old}, says the poet. But I doubt it, Bunter. In this case I very much doubt it.>