\chapter[Chapter \thechapter]{}

\lettrine{T}{here} were golden chrysanthemums on the judge's bench; they looked like burning banners.

\zz
The prisoner, too, had a look in her eyes that was a challenge to the crowded court, as the clerk read the indictment. The judge, a plump, elderly man with an eighteenth-century face, looked expectantly at the Attorney-General.

<My lord—I am instructed that the Crown offers no evidence against this prisoner.>

The gasp that went round the room sounded like the rustle of trees in a rising wind.

<Do I understand that the charge against the prisoner is withdrawn?>

<Those are my instructions, my lord.>

<In that case,> said the judge, impassively, turning to the jury, <there is nothing left for you but to return a verdict of <Not Guilty.> Usher, keep those people quiet in the gallery.>

<One moment, my lord.> Sir~Impey Biggs rose up, large and majestic.

<On my client's behalf—on Miss~Vane's behalf, my lord, I beg your lordship's indulgence for a few words. A charge has been brought against her, my lord, the very awful charge of murder, and I should like it to be made clear, my lord, that my client leaves this court without a stain upon her character. As I am informed, my lord, this is not a case of the charge being withdrawn in default of evidence. I understand, my lord, that further information has come to the police which definitely proves the entire innocence of my client. I also understand, my lord, that a further arrest has been made and that an inquiry will follow, my lord, in due course. My lord, this lady must go forth into the world acquitted, not only at this bar, but at the bar of public opinion. Any ambiguity would be intolerable, and I am sure, my lord, that I have the support of the learned Attorney-General for what I say.>

<By all means,> said the Attorney. <I am instructed to say, my lord, that in withdrawing the charge against the prisoner, the Crown proceeds from complete conviction of her absolute innocence.>

<I am very glad to hear it,> said the judge. <Prisoner at the bar, the Crown, by unreservedly withdrawing this dreadful charge against you, has demonstrated your innocence in the clearest possible way. After this, nobody will be able to suppose that the slightest imputation rests upon you, and I most heartily congratulate you on this very satisfactory ending to your long ordeal. Now, please—I sympathise very much with the people who are cheering, but this is not a theatre or a football match, and if they are not quiet, they will have to be put out. Members of the jury, do you find the Prisoner Guilty or Not Guilty?>

<Not Guilty, my lord.>

<Very good. The prisoner is discharged without a stain upon her character. Next case.>

So ended, sensational to the last, one of the most sensational murder trials of the century.

\divider

Harriet Vane, a free woman, found Eiluned Price and Sylvia Marriott waiting for her as she descended the stairs.

<Darling!> said Sylvia.

<Three loud cheers!> said Eiluned.

Harriet greeted them a little vaguely.

<Where is Lord~Peter Wimsey?> she enquired. <I must thank him.>

<You won't,> said Eiluned, bluntly. <I saw him drive off the moment the verdict was given.>

<Oh!> said Miss~Vane.

<He'll come and see you,> said Sylvia.

<No, he won't,> said Eiluned.

<Why not?> said Sylvia.

<Too decent,> said Eiluned.

<I'm afraid you're right,> said Harriet.

<I like that young man,> said Eiluned. <You needn't grin. I do like him. He's not going to do the King Cophetua stunt, and I take off my hat to him. If you want him, you'll have to send for him.>

<I won't do that,> said Harriet.

<Oh, yes, you will,> said Sylvia. <I was right about who did the murder, and I'm going to be right about this.>

\divider

Lord~Peter Wimsey went down to Duke's Denver that same evening. He found the family in a state of perturbation, all except the Dowager, who sat placidly making a rug in the midst of the uproar.

<Look here, Peter,> said the Duke, <you're the only person with any influence over Mary. You've got to do something. She wants to marry your policeman friend.>

<I know,> said Wimsey. <Why shouldn't she?>

<It's ridiculous,> said the Duke.

<Not at all,> said Lord~Peter. <Charles is one of the best.>

<Very likely,> said the Duke, <but Mary can't marry a policeman.>

<Now, look here,> said Wimsey, tucking his sister's arm in his, <you leave Polly alone. Charles made a bit of a mistake at the beginning of this murder case, but he doesn't make many, and one of these days he'll be a big man, with a title, I shouldn't wonder, and everything handsome about him. If you want to have a row with somebody, have it with me.>

<My God!> said the Duke, <you're not going to marry a policewoman?>

<Not quite,> said Wimsey. <I intend to marry the prisoner.>

<What?> said the Duke. <Good lord, what, what?>

<If she'll have me,> said Lord~Peter Wimsey.