%!TeX root=../bodytop.tex
\chapter[Chapter \thechapter]{}
\lettrine[lines=4,ante=‘]{E}{xcellent}, Bunter,' said Lord Peter, sinking with a sigh into a luxurious armchair. \enquote{I couldn’t have done better myself. The thought of the Dante makes my mouth water\allowbreak---\allowbreak and the \textit{Four Sons of Aymon.} And you’ve saved me \textsterling 60\allowbreak---\allowbreak that’s glorious. What shall we spend it on, Bunter? Think of it\allowbreak---\allowbreak all ours, to do as we like with, for as Harold Skimpole so rightly observes, \textsterling 60 saved is \textsterling 60 gained, and I’d reckoned on spending it all. It’s your saving, Bunter, and properly speaking, your \textsterling 60. What do we want? Anything in your department? Would you like anything altered in the flat?}

\enquote{Well, my lord, as your lordship is so good}---the man-servant paused, about to pour an old brandy into a liqueur glass.

\enquote{Well, out with it, my Bunter, you imperturbable old hypocrite. It’s no good talking as if you were announcing dinner\allowbreak---\allowbreak you’re spilling the brandy. The voice is Jacob’s voice, but the hands are the hands of Esau. What does that blessed darkroom of yours want now?}

\enquote{There’s a Double Anastigmat with a set of supplementary lenses, my lord,} said Bunter, with a note almost of religious fervour. \enquote{If it was a case of forgery now\allowbreak---\allowbreak or footprints\allowbreak---\allowbreak I could enlarge them right up on the plate. Or the wide-angled lens would be useful. It’s as though the camera had eyes at the back of its head, my lord. Look\allowbreak---\allowbreak I’ve got it here.}

He pulled a catalogue from his pocket, and submitted it, quivering, to his employer’s gaze.

Lord Peter perused the description slowly, the corners of his long mouth lifted into a faint smile.

\enquote{It’s Greek to me,} he said, \enquote{and \textsterling 50 seems a ridiculous price for a few bits of glass. I suppose, Bunter, you’d say \textsterling 750 was a bit out of the way for a dirty old book in a dead language, wouldn’t you?}

\enquote{It wouldn’t be my place to say so, my lord.}

\enquote{No, Bunter, I pay you \textsterling 200 a year to keep your thoughts to yourself. Tell me, Bunter, in these democratic days, don’t you think that’s unfair?}

\enquote{No, my lord.}

\enquote{You don’t. D’you mind telling me frankly why you don’t think it unfair?}

\enquote{Frankly, my lord, your lordship is paid a nobleman’s income to take Lady Worthington in to dinner and refrain from exercising your lordship’s undoubted powers of repartee.}

Lord Peter considered this.

\enquote{That’s your idea, is it, Bunter? Noblesse oblige\allowbreak---\allowbreak for a consideration. I daresay you’re right. Then you’re better off than I am, because I’d have to behave myself to Lady Worthington if I hadn’t a penny. Bunter, if I sacked you here and now, would you tell me what you think of me?}

\enquote{No, my lord.}

\enquote{You’d have a perfect right to, my Bunter, and if I sacked you on top of drinking the kind of coffee you make, I’d deserve everything you could say of me. You’re a demon for coffee, Bunter\allowbreak---\allowbreak I don’t want to know how you do it, because I believe it to be witchcraft, and I don’t want to burn eternally. You can buy your cross-eyed lens.}

\enquote{Thank you, my lord.}

\enquote{Have you finished in the dining-room?}

\enquote{Not quite, my lord.}

\enquote{Well, come back when you have. I have many things to tell you. Hullo! who’s that?}

The doorbell had rung sharply.

\enquote{Unless it’s anybody interestin’ I’m not at home.}

\enquote{Very good, my lord.}

Lord Peter’s library was one of the most delightful bachelor rooms in London. Its scheme was black and primrose; its walls were lined with rare editions, and its chairs and Chesterfield sofa suggested the embraces of the houris. In one corner stood a black baby grand, a wood fire leaped on a wide old-fashioned hearth, and the Sèvres vases on the chimneypiece were filled with ruddy and gold chrysanthemums. To the eyes of the young man who was ushered in from the raw November fog it seemed not only rare and unattainable, but friendly and familiar, like a colourful and gilded paradise in a mediaeval painting.

\enquote{Mr Parker, my lord.}

Lord Peter jumped up with genuine eagerness.

\enquote{My dear man, I’m delighted to see you. What a beastly foggy night, ain’t it? Bunter, some more of that admirable coffee and another glass and the cigars. Parker, I hope you’re full of crime\allowbreak---\allowbreak nothing less than arson or murder will do for us tonight. ‘On such a night as this---’ Bunter and I were just sitting down to carouse. I’ve got a Dante, and a Caxton folio that is practically unique, at Sir Ralph Brocklebury’s sale. Bunter, who did the bargaining, is going to have a lens which does all kinds of wonderful things with its eyes shut, and

\begin{quote}
We both have got a body in a bath,\\
We both have got a body in a bath---\\
For in spite of all temptations\\
To go in for cheap sensations\\
We insist upon a body in a bath---\\
\end{quote}

Nothing less will do for us, Parker. It’s mine at present, but we’re going shares in it. Property of the firm. Won’t you join us? You really must put \textit{something} in the jack-pot. Perhaps you have a body. Oh, do have a body. Every body welcome.

\begin{quote}
Gin a body meet a body\\
Hauled before the beak,\\
Gin a body jolly well knows who murdered a body\\
and that old Sugg is on the wrong tack,\\
Need a body speak?
\end{quote}

Not a bit of it. He tips a glassy wink to yours truly and yours truly reads the truth.}

\enquote{Ah,} said Parker, \enquote{I knew you’d been round to Queen Caroline Mansions. So’ve I, and met Sugg, and he told me he’d seen you. He was cross, too. Unwarrantable interference, he calls it.}

\enquote{I knew he would,} said Lord Peter. \enquote{I love taking a rise out of dear old Sugg, he’s always so rude. I see by the Star that he has excelled himself by taking the girl, Gladys What’s-her-name, into custody. Sugg of the evening, beautiful Sugg! But what were \textit{you} doing there?}

\enquote{To tell you the truth,} said Parker, \enquote{I went round to see if the Semitic-looking stranger in Mr Thipps’s bath was by any extraordinary chance Sir Reuben Levy. But he isn’t.}

\enquote{Sir Reuben Levy? Wait a minute, I saw something about that. I know! A headline: \enquote{Mysterious disappearance of famous financier.} What’s it all about? I didn’t read it carefully.}

\enquote{Well, it’s a bit odd, though I daresay it’s nothing really\allowbreak---\allowbreak old chap may have cleared for some reason best known to himself. It only happened this morning, and nobody would have thought anything about it, only it happened to be the day on which he had arranged to attend a most important financial meeting and do some deal involving millions\allowbreak---\allowbreak I haven’t got all the details. But I know he’s got enemies who’d just as soon the deal didn’t come off, so when I got wind of this fellow in the bath, I buzzed round to have a look at him. It didn’t seem likely, of course, but unlikelier things do happen in our profession. The funny thing is, old Sugg had got bitten with the idea it is him, and is wildly telegraphing to Lady Levy to come and identify him. But as a matter of fact, the man in the bath is no more Sir Reuben Levy than Adolf Beck, poor devil, was John Smith. Oddly enough, though, he would be really extraordinarily like Sir Reuben if he had a beard, and as Lady Levy is abroad with the family, somebody may say it’s him, and Sugg will build up a lovely theory, like the Tower of Babel, and destined so to perish.}

\enquote{Sugg’s a beautiful, braying ass,} said Lord Peter. \enquote{He’s like a detective in a novel. Well, I don’t know anything about Levy, but I’ve seen the body, and I should say the idea was preposterous upon the face of it. What do you think of the brandy?}

\enquote{Unbelievable, Wimsey\allowbreak---\allowbreak sort of thing makes one believe in heaven. But I want your yarn.}

\enquote{D’you mind if Bunter hears it, too? Invaluable man, Bunter\allowbreak---\allowbreak amazin’ fellow with a camera. And the odd thing is, he’s always on the spot when I want my bath or my boots. I don’t know when he develops things\allowbreak---\allowbreak I believe he does ’em in his sleep. Bunter!}

\enquote{Yes, my lord.}

\enquote{Stop fiddling about in there, and get yourself the proper things to drink and join the merry throng.}

\enquote{Certainly, my lord.}

\enquote{Mr Parker has a new trick: The Vanishing Financier. Absolutely no deception. Hey, presto, pass! and where is he? Will some gentleman from the audience kindly step upon the platform and inspect the cabinet? Thank you, sir. The quickness of the ’and deceives the heye.}

\enquote{I’m afraid mine isn’t much of a story,} said Parker. \enquote{It’s just one of those simple things that offer no handle. Sir Reuben Levy dined last night with three friends at the Ritz. After dinner the friends went to the theatre. He refused to go with them on account of an appointment. I haven’t yet been able to trace the appointment, but anyhow, he returned home to his house\allowbreak---\allowbreak 9a, Park Lane\allowbreak---\allowbreak at twelve o’clock.}

\enquote{Who saw him?}

\enquote{The cook, who had just gone up to bed, saw him on the doorstep, and heard him let himself in. He walked upstairs, leaving his greatcoat on the hall peg and his umbrella in the stand\allowbreak---\allowbreak you remember how it rained last night. He undressed and went to bed. Next morning he wasn’t there. That’s all,} said Parker abruptly, with a wave of the hand.

\enquote{It isn’t all, it isn’t all. Daddy, go on, that’s not \textit{half} a story,} pleaded Lord Peter.

\enquote{But it \textit{is} all. When his man came to call him he wasn’t there. The bed had been slept in. His pyjamas and all his clothes were there, the only odd thing being that they were thrown rather untidily on the ottoman at the foot of the bed, instead of being neatly folded on a chair, as is Sir Reuben’s custom\allowbreak---\allowbreak looking as though he had been rather agitated or unwell. No clean clothes were missing, no suit, no boots\allowbreak---\allowbreak nothing. The boots he had worn were in his dressing-room as usual. He had washed and cleaned his teeth and done all the usual things. The housemaid was down cleaning the hall at half-past six, and can swear that nobody came in or out after that. So one is forced to suppose that a respectable middle-aged Hebrew financier either went mad between twelve and six \textsc{a.m.} and walked quietly out of the house in his birthday suit on a November night, or else was spirited away like the lady in the \textit{Ingoldsby Legends,} body and bones, leaving only a heap of crumpled clothes behind him.}

\enquote{Was the front door bolted?}

\enquote{That’s the sort of question you \textit{would} ask, straight off; it took me an hour to think of it. No; contrary to custom, there was only the Yale lock on the door. On the other hand, some of the maids had been given leave to go to the theatre, and Sir Reuben may quite conceivably have left the door open under the impression they had not come in. Such a thing has happened before.}

\enquote{And that’s really all?}

\enquote{Really all. Except for one very trifling circumstance.}

\enquote{I love trifling circumstances,} said Lord Peter, with childish delight; \enquote{so many men have been hanged by trifling circumstances. What was it?}

\enquote{Sir Reuben and Lady Levy, who are a most devoted couple, always share the same room. Lady Levy, as I said before, is in Mentonne at the moment for her health. In her absence, Sir Reuben sleeps in the double bed as usual, and invariably on his own side\allowbreak---\allowbreak the outside\allowbreak---\allowbreak of the bed. Last night he put the two pillows together and slept in the middle, or, if anything, rather closer to the wall than otherwise. The housemaid, who is a most intelligent girl, noticed this when she went up to make the bed, and, with really admirable detective instinct, refused to touch the bed or let anybody else touch it, though it wasn’t till later that they actually sent for the police.}

\enquote{Was nobody in the house but Sir Reuben and the servants?}

\enquote{No; Lady Levy was away with her daughter and her maid. The valet, cook, parlourmaid, housemaid and kitchenmaid were the only people in the house, and naturally wasted an hour or two squawking and gossiping. I got there about ten.}

\enquote{What have you been doing since?}

\enquote{Trying to get on the track of Sir Reuben’s appointment last night, since, with the exception of the cook, his \enquote{appointer} was the last person who saw him before his disappearance. There may be some quite simple explanation, though I’m dashed if I can think of one for the moment. Hang it all, a man doesn’t come in and go to bed and walk away again \enquote{mid nodings on} in the middle of the night.}

\enquote{He may have been disguised.}

\enquote{I thought of that\allowbreak---\allowbreak in fact, it seems the only possible explanation. But it’s deuced odd, Wimsey. An important city man, on the eve of an important transaction, without a word of warning to anybody, slips off in the middle of the night, disguised down to his skin, leaving behind his watch, purse, cheque-book, and\allowbreak---\allowbreak most mysterious and important of all\allowbreak---\allowbreak his spectacles, without which he can’t see a step, as he is extremely short-sighted. He\longdash}

\enquote{That \textit{is} important,} interrupted Wimsey. \enquote{You are sure he didn’t take a second pair?}

\enquote{His man vouches for it that he had only two pairs, one of which was found on his dressing-table, and the other in the drawer where it is always kept.}

Lord Peter whistled.

\enquote{You’ve got me there, Parker. Even if he’d gone out to commit suicide he’d have taken those.}

\enquote{So you’d think\allowbreak---\allowbreak or the suicide would have happened the first time he started to cross the road. However, I didn’t overlook the possibility. I’ve got particulars of all today’s street accidents, and I can lay my hand on my heart and say that none of them is Sir Reuben. Besides, he took his latchkey with him, which looks as though he’d meant to come back.}

\enquote{Have you seen the men he dined with?}

\enquote{I found two of them at the club. They said that he seemed in the best of health and spirits, spoke of looking forward to joining Lady Levy later on\allowbreak---\allowbreak perhaps at Christmas\allowbreak---\allowbreak and referred with great satisfaction to this morning’s business transaction, in which one of them\allowbreak---\allowbreak a man called Anderson of Wyndham’s\allowbreak---\allowbreak was himself concerned.}

\enquote{Then up till about nine o’clock, anyhow, he had no apparent intention or expectation of disappearing.}

\enquote{None\allowbreak---\allowbreak unless he was a most consummate actor. Whatever happened to change his mind must have happened either at the mysterious appointment which he kept after dinner, or while he was in bed between midnight and 5.30 \textsc{a.m.}}

\enquote{Well, Bunter,} said Lord Peter, \enquote{what do you make of it?}

\enquote{Not in my department, my lord. Except that it is odd that a gentleman who was too flurried or unwell to fold his clothes as usual should remember to clean his teeth and put his boots out. Those are two things that quite frequently get overlooked, my lord.}

\enquote{If you mean anything personal, Bunter,} said Lord Peter, \enquote{I can only say that I think the speech an unworthy one. It’s a sweet little problem, Parker mine. Look here, I don’t want to butt in, but I should dearly love to see that bedroom tomorrow. ’Tis not that I mistrust thee, dear, but I should uncommonly like to see it. Say me not nay\allowbreak---\allowbreak take another drop of brandy and a Villar Villar, but say not, say not nay!}

\enquote{Of course you can come and see it\allowbreak---\allowbreak you’ll probably find lots of things I’ve overlooked,} said the other, equably, accepting the proffered hospitality.

\enquote{Parker, acushla, you’re an honour to Scotland Yard. I look at you, and Sugg appears a myth, a fable, an idiot-boy, spawned in a moonlight hour by some fantastic poet’s brain. Sugg is too perfect to be possible. What does he make of the body, by the way?}

\enquote{Sugg says,} replied Parker, with precision, \enquote{that the body died from a blow on the back of the neck. The doctor told him that. He says it’s been dead a day or two. The doctor told him that, too. He says it’s the body of a well-to-do Hebrew of about fifty. Anybody could have told him that. He says it’s ridiculous to suppose it came in through the window without anybody knowing anything about it. He says it probably walked in through the front door and was murdered by the household. He’s arrested the girl because she’s short and frail-looking and quite unequal to downing a tall and sturdy Semite with a poker. He’d arrest Thipps, only Thipps was away in Manchester all yesterday and the day before and didn’t come back till late last night\allowbreak---\allowbreak in fact, he wanted to arrest him till I reminded him that if the body had been a day or two dead, little Thipps couldn’t have done him in at 10.30 last night. But he’ll arrest him tomorrow as an accessory\allowbreak---\allowbreak and the old lady with the knitting, too, I shouldn’t wonder.}

\enquote{Well, I’m glad the little man has so much of an alibi,} said Lord Peter, \enquote{though if you’re only glueing your faith to cadaveric lividity, rigidity, and all the other quiddities, you must be prepared to have some sceptical beast of a prosecuting counsel walk slap-bang through the medical evidence. Remember Impey Biggs defending in that Chelsea tea-shop affair? Six bloomin’ medicos contradictin’ each other in the box, an’ old Impey elocutin’ abnormal cases from Glaister and Dixon Mann till the eyes of the jury reeled in their heads! \enquote{Are you prepared to swear, Dr Thingumtight, that the onset of rigor mortis indicates the hour of death without the possibility of error?} \enquote{So far as my experience goes, in the majority of cases,} says the doctor, all stiff. \enquote{Ah!} says Biggs, \enquote{but this is a Court of Justice, Doctor, not a Parliamentary election. We can’t get on without a minority report. The law, Dr Thingumtight, respects the rights of the minority, alive or dead.} Some ass laughs, and old Biggs sticks his chest out and gets impressive. \enquote{Gentlemen, this is no laughing matter. My client\allowbreak---\allowbreak an upright and honourable gentleman\allowbreak---\allowbreak is being tried for his life\allowbreak---\allowbreak for his life, gentlemen\allowbreak---\allowbreak and it is the business of the prosecution to show his guilt\allowbreak---\allowbreak if they can\allowbreak---\allowbreak without a shadow of doubt. Now, Dr Thingumtight, I ask you again, can you solemnly swear, without the least shadow of doubt,---probable, possible shadow of doubt\allowbreak---\allowbreak that this unhappy woman met her death neither sooner nor later than Thursday evening? A probable opinion? Gentlemen, we are not Jesuits, we are straightforward Englishmen. You cannot ask a British-born jury to convict any man on the authority of a probable opinion.} Hum of applause.}

\enquote{Biggs’s man was guilty all the same,} said Parker.

\enquote{Of course he was. But he was acquitted all the same, an’ what you’ve just said is libel.} Wimsey walked over to the bookshelf and took down a volume of Medical Jurisprudence. \enquote{\enquote{Rigor mortis\allowbreak---\allowbreak can only be stated in a very general way\allowbreak---\allowbreak many factors determine the result.} Cautious brute. \enquote{On the average, however, stiffening will have begun\allowbreak---\allowbreak neck and jaw\allowbreak---\allowbreak 5 to 6 hours after death}---m’m---\enquote{in all likelihood have passed off in the bulk of cases by the end of 36 hours. Under certain circumstances, however, it may appear unusually early, or be retarded unusually long!} Helpful, ain’t it, Parker? \enquote{Brown-Séquard states ... 3½ minutes after death.... In certain cases not until lapse of 16 hours after death ... present as long as 21 days thereafter.} Lord! \enquote{Modifying factors\allowbreak---\allowbreak age---muscular state\allowbreak---\allowbreak or febrile diseases\allowbreak---\allowbreak or where temperature of environment is high}---and so on and so on\allowbreak---\allowbreak any bloomin’ thing. Never mind. You can run the argument for what it’s worth to Sugg. \textit{He} won’t know any better.} He tossed the book away. \enquote{Come back to facts. What did \textit{you} make of the body?}

\enquote{Well,} said the detective, \enquote{not very much\allowbreak---\allowbreak I was puzzled\allowbreak---\allowbreak frankly. I should say he had been a rich man, but self-made, and that his good fortune had come to him fairly recently.}

\enquote{Ah, you noticed the calluses on the hands\allowbreak---\allowbreak I thought you wouldn’t miss that.}

\enquote{Both his feet were badly blistered\allowbreak---\allowbreak he had been wearing tight shoes.}

\enquote{Walking a long way in them, too,} said Lord Peter, \enquote{to get such blisters as that. Didn’t that strike you as odd, in a person evidently well off?}

\enquote{Well, I don’t know. The blisters were two or three days old. He might have got stuck in the suburbs one night, perhaps\allowbreak---\allowbreak last train gone and no taxi\allowbreak---\allowbreak and had to walk home.}

\enquote{Possibly.}

\enquote{There were some little red marks all over his back and one leg I couldn’t quite account for.}

\enquote{I saw them.}

\enquote{What did you make of them?}

\enquote{I’ll tell you afterwards. Go on.}

\enquote{He was very long-sighted\allowbreak---\allowbreak oddly long-sighted for a man in the prime of life; the glasses were like a very old man’s. By the way, they had a very beautiful and remarkable chain of flat links chased with a pattern. It struck me he might be traced through it.}

\enquote{I’ve just put an advertisement in the \textit{Times} about it,} said Lord Peter. \enquote{Go on.}

\enquote{He had had the glasses some time\allowbreak---\allowbreak they had been mended twice.}

\enquote{Beautiful, Parker, beautiful. Did you realize the importance of that?}

\enquote{Not specially, I’m afraid\allowbreak---\allowbreak why?}

\enquote{Never mind\allowbreak---\allowbreak go on.}

\enquote{He was probably a sullen, ill-tempered man\allowbreak---\allowbreak his nails were filed down to the quick as though he habitually bit them, and his fingers were bitten as well. He smoked quantities of cigarettes without a holder. He was particular about his personal appearance.}

\enquote{Did you examine the room at all? I didn’t get a chance.}

\enquote{I couldn’t find much in the way of footprints. Sugg \& Co. had tramped all over the place, to say nothing of little Thipps and the maid, but I noticed a very indefinite patch just behind the head of the bath, as though something damp might have stood there. You could hardly call it a print.}

\enquote{It rained hard all last night, of course.}

\enquote{Yes; did you notice that the soot on the window-sill was vaguely marked?}

\enquote{I did,} said Wimsey, \enquote{and I examined it hard with this little fellow, but I could make nothing of it except that something or other had rested on the sill.} He drew out his monocle and handed it to Parker.

\enquote{My word, that’s a powerful lens.}

\enquote{It is,} said Wimsey, \enquote{and jolly useful when you want to take a good squint at somethin’ and look like a bally fool all the time. Only it don’t do to wear it permanently\allowbreak---\allowbreak if people see you full-face they say: \enquote{Dear me! how weak the sight of that eye must be!} Still, it’s useful.}

\enquote{Sugg and I explored the ground at the back of the building,} went on Parker, \enquote{but there wasn’t a trace.}

\enquote{That’s interestin’. Did you try the roof?}

\enquote{No.}

\enquote{We’ll go over it tomorrow. The gutter’s only a couple of feet off the top of the window. I measured it with my stick\allowbreak---\allowbreak the gentleman-scout’s vade-mecum, I call it\allowbreak---\allowbreak it’s marked off in inches. Uncommonly handy companion at times. There’s a sword inside and a compass in the head. Got it made specially. Anything more?}

\enquote{Afraid not. Let’s hear your version, Wimsey.}

\enquote{Well, I think you’ve got most of the points. There are just one or two little contradictions. For instance, here’s a man wears expensive gold-rimmed pince-nez and has had them long enough to be mended twice. Yet his teeth are not merely discoloured, but badly decayed and look as if he’d never cleaned them in his life. There are four molars missing on one side and three on the other and one front tooth broken right across. He’s a man careful of his personal appearance, as witness his hair and his hands. What do you say to that?}

\enquote{Oh, these self-made men of low origin don’t think much about teeth, and are terrified of dentists.}

\enquote{True; but one of the molars has a broken edge so rough that it had made a sore place on the tongue. Nothing’s more painful. D’you mean to tell me a man would put up with that if he could afford to get the tooth filed?}

\enquote{Well, people are queer. I’ve known servants endure agonies rather than step over a dentist’s doormat. How did you see that, Wimsey?}

\enquote{Had a look inside; electric torch,} said Lord Peter. \enquote{Handy little gadget. Looks like a matchbox. Well\allowbreak---\allowbreak I daresay it’s all right, but I just draw your attention to it. Second point: Gentleman with hair smellin’ of Parma violet and manicured hands and all the rest of it, never washes the inside of his ears. Full of wax. Nasty.}

\enquote{You’ve got me there, Wimsey; I never noticed it. Still\allowbreak---\allowbreak old bad habits die hard.}

\enquote{Right oh! Put it down at that. Third point: Gentleman with the manicure and the brilliantine and all the rest of it suffers from fleas.}

\enquote{By Jove, you’re right! Flea-bites. It never occurred to me.}

\enquote{No doubt about it, old son. The marks were faint and old, but unmistakable.}

\enquote{Of course, now you mention it. Still, that might happen to anybody. I loosed a whopper in the best hotel in Lincoln the week before last. I hope it bit the next occupier!}

\enquote{Oh, all these things \textit{might} happen to anybody\allowbreak---\allowbreak separately. Fourth point: Gentleman who uses Parma violet for his hair, etc., etc., washes his body in strong carbolic soap\allowbreak---\allowbreak so strong that the smell hangs about twenty-four hours later.}

\enquote{Carbolic to get rid of the fleas.}

\enquote{I will say for you, Parker, you’ve an answer for everything. Fifth point: Carefully got-up gentleman, with manicured, though masticated, finger-nails, has filthy black toe-nails which look as if they hadn’t been cut for years.}

\enquote{All of a piece with habits as indicated.}

\enquote{Yes, I know, but such habits! Now, sixth and last point: This gentleman with the intermittently gentlemanly habits arrives in the middle of a pouring wet night, and apparently through the window, when he has already been twenty-four hours dead, and lies down quietly in Mr Thipps’s bath, unseasonably dressed in a pair of pince-nez. Not a hair on his head is ruffled\allowbreak---\allowbreak the hair has been cut so recently that there are quite a number of little short hairs stuck on his neck and the sides of the bath\allowbreak---\allowbreak and he has shaved so recently that there is a line of dried soap on his cheek\longdash}

\enquote{Wimsey!}

\enquote{Wait a minute\allowbreak---\allowbreak and \textit{dried soap in his mouth}.}

Bunter got up and appeared suddenly at the detective’s elbow, the respectful man-servant all over.

\enquote{A little more brandy, sir?} he murmured.

\enquote{Wimsey,} said Parker, \enquote{you are making me feel cold all over.} He emptied his glass\allowbreak---\allowbreak stared at it as though he were surprised to find it empty, set it down, got up, walked across to the bookcase, turned round, stood with his back against it and said:

\enquote{Look here, Wimsey\allowbreak---\allowbreak you’ve been reading detective stories; you’re talking nonsense.}

\enquote{No, I ain’t,} said Lord Peter, sleepily, \enquote{uncommon good incident for a detective story, though, what? Bunter, we’ll write one, and you shall illustrate it with photographs.}

\enquote{Soap in his\allowbreak---\allowbreak Rubbish!} said Parker. \enquote{It was something else\allowbreak---\allowbreak some discoloration\longdash}

\enquote{No,} said Lord Peter, \enquote{there were hairs as well. Bristly ones. He had a beard.}

He took his watch from his pocket, and drew out a couple of longish, stiff hairs, which he had imprisoned between the inner and the outer case.

Parker turned them over once or twice in his fingers, looked at them close to the light, examined them with a lens, handed them to the impassible Bunter, and said:

\enquote{Do you mean to tell me, Wimsey, that any man alive would}---he laughed harshly---\enquote{shave off his beard with his mouth open, and then go and get killed with his mouth full of hairs? You’re mad.}

\enquote{I don’t tell you so,} said Wimsey. \enquote{You policemen are all alike\allowbreak---\allowbreak only one idea in your skulls. Blest if I can make out why you’re ever appointed. He was shaved after he was dead. Pretty, ain’t it? Uncommonly jolly little job for the barber, what? Here, sit down, man, and don’t be an ass, stumpin’ about the room like that. Worse things happen in war. This is only a blinkin’ old shillin’ shocker. But I’ll tell you what, Parker, we’re up against a criminal---\textit{the} criminal\allowbreak---\allowbreak the real artist and blighter with imagination\allowbreak---\allowbreak real, artistic, finished stuff. I’m enjoyin’ this, Parker.}