%!TeX root=../bodytop.tex
\chapter[Chapter \thechapter]{}
\lettrine[lines=4]{T}{he} vile, raw fog tore your throat and ravaged your eyes. You could not see your feet. You stumbled in your walk over poor men’s graves.

The feel of Parker’s old trench-coat beneath your fingers was comforting. You had felt it in worse places. You clung on now for fear you should get separated. The dim people moving in front of you were like Brocken spectres.

\enquote{Take care, gentlemen,} said a toneless voice out of the yellow darkness, \enquote{there’s an open grave just hereabouts.}

You bore away to the right, and floundered in a mass of freshly turned clay.

\enquote{Hold up, old man,} said Parker.

\enquote{Where is Lady Levy?}

\enquote{In the mortuary; the Duchess of Denver is with her. Your mother is wonderful, Peter.}

\enquote{Isn’t she?} said Lord Peter.

A dim blue light carried by somebody ahead wavered and stood still.

\enquote{Here you are,} said a voice.

Two Dantesque shapes with pitchforks loomed up.

\enquote{Have you finished?} asked somebody.

\enquote{Nearly done, sir.} The demons fell to work again with the pitchforks\allowbreak---\allowbreak no, spades.

Somebody sneezed. Parker located the sneezer and introduced him.

\enquote{Mr Levett represents the Home Secretary. Lord Peter Wimsey. We are sorry to drag you out on such a day, Mr Levett.}

\enquote{It’s all in the day’s work,} said Mr Levett, hoarsely. He was muffled to the eyes.

The sound of the spades for many minutes. An iron noise of tools thrown down. Demons stooping and straining.

A black-bearded spectre at your elbow. Introduced. The Master of the Workhouse.

\enquote{A very painful matter, Lord Peter. You will forgive me for hoping you and Mr Parker may be mistaken.}

\enquote{I should like to be able to hope so too.}

Something heaving, straining, coming up out of the ground.

\enquote{Steady, men. This way. Can you see? Be careful of the graves\allowbreak---\allowbreak they lie pretty thick hereabouts. Are you ready?}

\enquote{Right you are, sir. You go on with the lantern. We can follow you.}

Lumbering footsteps. Catch hold of Parker’s trench-coat again. \enquote{That you, old man? Oh, I beg your pardon, Mr Levett\allowbreak---\allowbreak thought you were Parker.}

\enquote{Hullo, Wimsey\allowbreak---\allowbreak here you are.}

More graves. A headstone shouldered crookedly aslant. A trip and jerk over the edge of the rough grass. The squeal of gravel under your feet.

\enquote{This way, gentlemen, mind the step.}

The mortuary. Raw red brick and sizzling gas-jets. Two women in black, and Dr Grimbold. The coffin laid on the table with a heavy thump.

\enquote{’Ave you got that there screw-driver, Bill? Thank ’ee. Be keerful wi’ the chisel now. Not much substance to these ’ere boards, sir.}

Several long creaks. A sob. The Duchess’s voice, kind but peremptory.

\enquote{Hush, Christine. You mustn’t cry.}

A mutter of voices. The lurching departure of the Dante demons\allowbreak---\allowbreak good, decent demons in corduroy.

Dr Grimbold’s voice\allowbreak---\allowbreak cool and detached as if in the consulting room.

\enquote{Now\allowbreak---\allowbreak have you got that lamp, Mr Wingate? Thank you. Yes, here on the table, please. Be careful not to catch your elbow in the flex, Mr Levett. It would be better, I think, if you came on this side. Yes\allowbreak---\allowbreak yes---thank you. That’s excellent.}

The sudden brilliant circle of an electric lamp over the table. Dr Grimbold’s beard and spectacles. Mr Levett blowing his nose. Parker bending close. The Master of the Workhouse peering over him. The rest of the room in the enhanced dimness of the gas-jets and the fog.

A low murmur of voices. All heads bent over the work.

Dr Grimbold again\allowbreak---\allowbreak beyond the circle of the lamplight.

\enquote{We don’t want to distress you unnecessarily, Lady Levy. If you will just tell us what to look for\allowbreak---\allowbreak the---? Yes, yes, certainly\allowbreak---\allowbreak and---yes\allowbreak---\allowbreak stopped with gold? Yes\allowbreak---\allowbreak the lower jaw, the last but one on the right? Yes\allowbreak---\allowbreak no teeth missing\allowbreak---\allowbreak no---yes? What kind of a mole? Yes\allowbreak---\allowbreak just over the left breast? Oh, I beg your pardon, just under\allowbreak---\allowbreak yes---ap\-pen\-dici\-tis? Yes\allowbreak---\allowbreak a long one\allowbreak---\allowbreak yes---in the middle? Yes, I quite understand\allowbreak---\allowbreak a scar on the arm? Yes, I don’t know if we shall be able to find that\allowbreak---\allowbreak yes---any little constitutional weakness that might---? Oh, yes\allowbreak---\allowbreak arthritis---yes\allowbreak---\allowbreak thank you, Lady Levy\allowbreak---\allowbreak that’s very clear. Don’t come unless I ask you to. Now, Wingate.}

A pause. A murmur. \enquote{Pulled out? After death, you think\allowbreak---\allowbreak well, so do I. Where is Dr Colegrove? You attended this man in the workhouse? Yes. Do you recollect---? No? You’re quite certain about that? Yes\allowbreak---\allowbreak we mustn’t make a mistake, you know. Yes, but there are reasons why Sir Julian can’t be present; I’m asking \textit{you}, Dr Colegrove. Well, you’re certain\allowbreak---\allowbreak that’s all I want to know. Just bring the light closer, Mr Wingate, if you please. These miserable shells let the damp in so quickly. Ah! what do you make of this? Yes\allowbreak---\allowbreak yes---well, that’s rather unmistakable, isn’t it? Who did the head? Oh, Freke\allowbreak---\allowbreak of course. I was going to say they did good work at St Luke’s. Beautiful, isn’t it, Dr Colegrove? A wonderful surgeon\allowbreak---\allowbreak I saw him when he was at Guy’s. Oh, no, gave it up years ago. Nothing like keeping your hand in. Ah\allowbreak---\allowbreak yes, undoubtedly that’s it. Have you a towel handy, sir? Thank you. Over the head, if you please\allowbreak---\allowbreak I think we might have another here. Now, Lady Levy\allowbreak---\allowbreak I am going to ask you to look at a scar, and see if you recognise it. I’m sure you are going to help us by being very firm. Take your time\allowbreak---\allowbreak you won’t see anything more than you absolutely must.}

\enquote{Lucy, don’t leave me.}

\enquote{No, dear.}

A space cleared at the table. The lamplight on the Duchess’s white hair.

\enquote{Oh, yes\allowbreak---\allowbreak oh, yes! No, no\allowbreak---\allowbreak I couldn’t be mistaken. There’s that funny little kink in it. I’ve seen it hundreds of times. Oh, Lucy\allowbreak---\allowbreak Reuben!}

\enquote{Only a moment more, Lady Levy. The mole\longdash}

\enquote{I\allowbreak---\allowbreak I think so\allowbreak---\allowbreak oh, yes, that is the very place.}

\enquote{Yes. And the scar\allowbreak---\allowbreak was it three-cornered, just above the elbow?}

\enquote{Yes, oh, yes.}

\enquote{Is this it?}

\enquote{Yes\allowbreak---\allowbreak yes\longdash}

\enquote{I must ask you definitely, Lady Levy. Do you, from these three marks identify the body as that of your husband?}

\enquote{Oh! I must, mustn’t I? Nobody else could have them just the same in just those places? It is my husband. It is Reuben. Oh\longdash}

\enquote{Thank you, Lady Levy. You have been very brave and very helpful.}

\enquote{But\allowbreak---\allowbreak I don’t understand yet. How did he come here? Who did this dreadful thing?}

\enquote{Hush, dear,} said the Duchess; \enquote{the man is going to be punished.}

\enquote{Oh, but\allowbreak---\allowbreak how cruel! Poor Reuben! Who could have wanted to hurt him? Can I see his face?}

\enquote{No, dear,} said the Duchess. \enquote{That isn’t possible. Come away\allowbreak---\allowbreak you mustn’t distress the doctors and people.}

\enquote{No\allowbreak---\allowbreak no---they’ve all been so kind. Oh, Lucy!}

\enquote{We’ll go home, dear. You don’t want us any more, Dr Grimbold?}

\enquote{No, Duchess, thank you. We are very grateful to you and to Lady Levy for coming.}

There was a pause, while the two women went out, Parker, collected and helpful, escorting them to their waiting car. Then Dr Grimbold again:

\enquote{I think Lord Peter Wimsey ought to see\allowbreak---\allowbreak the correctness of his deductions\allowbreak---\allowbreak Lord Peter\allowbreak---\allowbreak very painful\allowbreak---\allowbreak you may wish to see\allowbreak---\allowbreak yes, I was uneasy at the inquest\allowbreak---\allowbreak yes---Lady Levy\allowbreak---\allowbreak remarkably clear evidence\allowbreak---\allowbreak yes---most shocking case\allowbreak---\allowbreak ah, here’s Mr Parker\allowbreak---\allowbreak you and Lord Peter Wimsey entirely justified\allowbreak---\allowbreak do I really under\-stand---? Really? I can hardly believe it\allowbreak---\allowbreak so distinguished a man\allowbreak---\allowbreak as you say, when a great brain turns to crime\allowbreak---\allowbreak yes---look here! Marvellous work\allowbreak---\allowbreak marvellous---somewhat obscured by this time, of course\allowbreak---\allowbreak but the most beautiful sections\allowbreak---\allowbreak here, you see, the left hemisphere\allowbreak---\allowbreak and here\allowbreak---\allowbreak through the corpus striatum\allowbreak---\allowbreak here again\allowbreak---\allowbreak the very track of the damage done by the blow\allowbreak---\allowbreak wonderful---guessed it\allowbreak---\allowbreak saw the effect of the blow as he struck it, you know\allowbreak---\allowbreak ah, I should like to see \textit{his} brain, Mr Parker\allowbreak---\allowbreak and to think that\allowbreak---\allowbreak heavens, Lord Peter, you don’t know what a blow you have struck at the whole profession\allowbreak---\allowbreak the whole civilized world! Oh, my dear sir! Can you ask me? My lips are sealed of course\allowbreak---\allowbreak all our lips are sealed.}

The way back through the burial ground. Fog again, and the squeal of wet gravel.

\enquote{Are your men ready, Charles?}

\enquote{They have gone. I sent them off when I saw Lady Levy to the car.}

\enquote{Who is with them?}

\enquote{Sugg.}

\enquote{Sugg?}

\enquote{Yes\allowbreak---\allowbreak poor devil. They’ve had him up on the mat at headquarters for bungling the case. All that evidence of Thipps’s about the night club was corroborated, you know. That girl he gave the gin-and-bitters to was caught, and came and identified him, and they decided their case wasn’t good enough, and let Thipps and the Horrocks girl go. Then they told Sugg he had overstepped his duty and ought to have been more careful. So he ought, but he can’t help being a fool. I was sorry for him. It may do him some good to be in at the death. After all, Peter, you and I had special advantages.}

\enquote{Yes. Well, it doesn’t matter. Whoever goes won’t get there in time. Sugg’s as good as another.}

But Sugg\allowbreak---\allowbreak an experience rare in his career\allowbreak---\allowbreak was in time.

Parker and Lord Peter were at 110 Piccadilly. Lord Peter was playing Bach and Parker was reading Origen when Sugg was announced.

\enquote{We’ve got our man, sir,} said he.

\enquote{Good God!} said Peter. \enquote{Alive?}

\enquote{We were just in time, my lord. We rang the bell and marched straight up past his man to the library. He was sitting there doing some writing. When we came in, he made a grab for his hypodermic, but we were too quick for him, my lord. We didn’t mean to let him slip through our hands, having got so far. We searched him thoroughly and marched him off.}

\enquote{He is actually in gaol, then?}

\enquote{Oh, yes\allowbreak---\allowbreak safe enough\allowbreak---\allowbreak with two warders to see he doesn’t make away with himself.}

\enquote{You surprise me, Inspector. Have a drink.}

\enquote{Thank you, my lord. I may say that I’m very grateful to you\allowbreak---\allowbreak this case was turning out a pretty bad egg for me. If I was rude to your lordship\longdash}

\enquote{Oh, it’s all right, Inspector,} said Lord Peter, hastily. \enquote{I don’t see how you could possibly have worked it out. I had the good luck to know something about it from other sources.}

\enquote{That’s what Freke says.} Already the great surgeon was a common criminal in the inspector’s eyes\allowbreak---\allowbreak a mere surname. \enquote{He was writing a full confession when we got hold of him, addressed to your lordship. The police will have to have it, of course, but seeing it’s written for you, I brought it along for you to see first. Here it is.}

He handed Lord Peter a bulky document.

\enquote{Thanks,} said Peter. \enquote{Like to hear it, Charles?}

\enquote{Rather.}

Accordingly Lord Peter read it aloud.